### 2013-09-25 paper.tex
initial commit

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}

\makeatother

\usepackage{babel}
\providecommand{\definitionname}{Definition}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}

\begin{document}

\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
\thanks{The authors are with the Dipartimento di Ingegneria
Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}

\title{Parameter space representation of Pareto set}
%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
%set come un sottoinsieme dello spazio delle configurazioni.

\maketitle
\begin{abstract}
qualcosa blah blah blah
\end{abstract}

\section{Introduction}

The design of an embedded system requires several objectives (energy
consumption, area occupation, ...) to be fulfilled. The fulfilling
of these objectives depends on several parameters and in the real
cases no analytical results are known to show the relation between
configurations (combination of parameters) and objectives. Therefore
the simulation is the only way to have a picture of how parameters
impact on the objectives. The problem is that the number of parameters
and the number of values that each of them may take lead to an enormous
number of possible configurations, such that simulating all of them
is an unfeasible activity. Therefore there is the need for the ``Design
Space Exploration'', i.e. a methodology to select a subset of all
possible configurations and simulate only this subset.

Many different design space exploration algorithms have been proposed.
A design space exploration algorithm is typically not based on precise
/ analytical / mathematical evidences. The motivations of an exploration
algorithm are rather heuristic, have some form of arbitrariness and,
to a large extend, intuition lies behind them.

The result of every design space exploration is a subset of the configurations
called Pareto Set (\cite{key-8}). Roughly speaking, it is a set of
configurations such that there are no other configurations, among
the simulated ones, that have all the objectives, at the same time,
better fulfilled. If all possible configurations were evaluated, the
ideal Pareto set (the ``true'' Pareto set) could be calculated.
But, as stated above, evaluating all the configurations is not feasable.
Therefore the Pareto set returned by an exploration algorithm is an
approximation of the ``true'' Pareto set.

Many exploration algorithms form the resulting Pareto set in an incremental
way. The algorithm adds and removes configurations in Pareto set while
choosing the configurations to evaluate and simulating them. So Pareto
set ``evolves'' towards the final one. The dynamical view of the
Pareto set shaping can be seen as the ``behavior'' of the algorithm.
This behavior tells us how the Pareto set ``converges'' towards
the final Pareto set.

The ``quality'' of an exploration algorithm involves two aspects:
\begin{itemize}
\item how much the Pareto set returned by the exploration algorithm is similar
to the ``true'' Pareto set (notice that this cannot be evaluated
because the true Pareto set is unknown - it is only an ``ideal''
quality factor)
\item how fast the Pareto set converges towards the final one. If algorithm
$1$ returns the final Pareto set after simulating $n_{1}$ configurations
and algorithm $2$ returns its final Pareto set after $n_{2}$ simulations,
algorithm $1$ is said to be faster than algorithm $2$, iff $n_{1}<n_{2}$.
\end{itemize}

\section{\label{sec:Related-work}Related work}

There are a number of design space exploration algorithms proposed
in literature.

The ``Dependency analysis'' proposed in \cite{key-3}, is meant
to take advantage of the dependency among the parameters in a multiobjective
optimization problem. It is required that the designer knows, prior
to the exploration, if a parameter X is dependent from a parameter
Y, i.e. changing the value of Y ``impacts the optimal parameter value''
for X. With this a-priori knowledge, the designer can construct a
``dependency graph'' and recognize clusters, i.e. subsets of strongly
dependency-connected parameters. Each cluster is exhaustively evaluated
and its ``local Pareto set'' is found. Then, all local Pareto sets
are merged. Doing this way, a ``sum'' of local exhaustive evaluations
are performed instead of an exhaustive evaluation of all the possible
configurations. Some problems arise: i) In real scenarios, it may
be very difficult to recognize really independent clusters of parameters,
because there may be interdependencies among a very large number of
parameters. This may lead to the need of an exhaustive search through
almost all the possible configurations. ii) A designer may not have
a precise and complete picture of the dependencies among parameters;
for this reason the need of ``automated approaches for computing
{[}...{]} interdependencies'' is declared in \cite{key-3}. iii)
There may be some ``local dependencies'', i.e. dependencies that
emerge only if parameter values are bounded to certain ranges.

These drawbacks are not present in our solution. The algorithm presented
here is also meant to take advantage of dependency but is not directly
based on dependency itself, but rather it ``catches'' dependencies
in terms of ``interesting or uninteresting regions''; as a consequence
no a-priori knowledge of dependencies is required as they are discovered
during exploration. Moreover, recognizing regions offers the capability
to capture local dependencies.

Abraham, Rau and Schreiber proposed in \cite{key-1} to decompose
the system to be evaluated into components that interact minimally
with each other. ``Alternative designs for each component are evaluated
in isolation to determine the best designs for individual components.
Combinations of these designs are then put together to build the complete
system design''. Pareto sets for each component are found and, provided
that ``monotonicity'' exists, the complete Pareto set is computed
merging the component Pareto sets. Roughly speaking (see section 4
of \cite{key-1} for more details), monotonicity property guarantees
that the best system can be obtained as a composition of the best
components. This approach would perfectly work if all the components
were perfectly isolated, i.e., if there were no dependencies among
different components (in a sense similar (but not necesarily equal)
to the one of Dependency analisys). But real scenarios seldom if ever
expose monotonicity property. This leads to some ``inaccuracies''
(as stated in section 4.6.1 of \cite{key-1}).

Other approaches take into account the concept of ``sensitivity''.
The sensitivity of an objective with the respect to a parameter is
a measure of how much the objective varies when varying that parameter.
A ``sensitivity analysis'' was used in \cite{key-5} in an optimization
problem with only one objective (the power-delay product of an electronic
device). This method was extended in \cite{key-7} to a multiobjective
optimization. In \cite{key-7}, the sensitivity of objectives with
the respect to each parameter is measured, and parameters are ordered
on the base on these sensitivity measures. Then, a first Pareto set
is obtained varying the first parameter, having fixed to arbitrary
values all other parameters. The Pareto set is then refined varying,
in a similar way, the other parameters, one by one. Experimental results
(see section 4.2 of \cite{key-7}) show that this method is not of
good ``quality'' (as broadly defined in the introduction). The reason
can be found in the very limited and rigid exploration of the parameter
space: after computing the first Pareto set, there are no more chances
to consider configurations with values of the first parameter other
than the ones assumed in the first Pareto set calculation. Similar
limitations are imposed after computing the second Pareto set, the
third and so on. It is worth noticing that this approach can not capture
``local sensitivity'' (this drawback will be called ``local sensitivity
limitation''), i.e. the objectives may be more sensitive to some
ranges of a parameter and less sensitive to other ranges of the same
parameter. Moreover it can not capture ``combined sensitivity''
(``combined sensitivity limitation''), i.e. the objectives may be
more sensitive to a range of a parameter $p_{1}$, only when other
parameters are within certain ranges, and less sensitive to the same
range of parameter $p_{1}$ when the other parameters are not within
those ranges. Therefore, in the method we propose, we do not use the
sensitivity directly, but we use the concept of innovation (that can
be considered, at least weakly related to the sensitivity). We do
not measure innovation of a parameter (as done for the sensitivity),
but rather we measure the innovation of a ``region'' of parameter
space, in order to overcome both the ``local sensitivity limitation''
and the ``combined sensitivity limitation'' stated above for the
sensitivity analysis.

Many studies focus on genetic approaches to resolve multiobjective
optimization problems (\cite{key-11,key-7} and others). Genetic approaches
have many advantages: they have proved good quality (as broadly defined
in the introduction), they are customizable, they are very general
and require no a-priori knowledge to the designer. Genetic algorithms
run in subsequent iterations. Configurations are represented as chromosomes.
In each iteration a ``population'' of configurations is evaluated.
Some configurations are discarded. Each selected configuration is
combined with the preceding population and then ``mutated'' (i.e.
the resulting configuration is varied a little). Iterating this operations,
populations are expected to become ``better and better''. The strong
point of genetic approaches can be summarized saying that they consist
in a broad exploration (the mutation permits to make the exploration
not rigidly restricted to limited parts of parameter space), although
this exploration is not random but is guided by the performances of
the already evaluated configurations. Therefore, the exploration is
neither too much constrained nor too much random. We claim that the
approach presented in this paper has all the benefits of the genetic
approaches, although the rational is completely different.

\section{Preliminaries}

\subsection{Representation}
\begin{defn}
\emph{Configuration}

Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
may assume. A configuration is a vector
\[
\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
\]

\end{defn}

\begin{defn}
\emph{Objective function}

Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
we can always say:
\[
o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
\]

$o_{i}$ can be viewed as a function
\[
o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]
 To take into account all of the objectives, the following function
is defined:
\[
\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]

\end{defn}

{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
\begin{defn}
\emph{\label{pers02.def:Pareto-set}Pareto set}

Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
configurations is:
\[
Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
\]

Its Pareto set is defined as:
\[
\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
\]

When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
\end{defn}

\begin{defn}
\emph{Pareto front}

The Pareto front is the representation in the objective space of the
Pareto set, i.e.:
\[
\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
\]

\end{defn}
On the contrary, we call ``parameter space representation'' of the
Pareto set the representation in which each configuration $\mathbf{p}$
is simply represented as a point of $P_{1}\times\dots\times P_{n}$
space. We will investigate the relation between the ``objective space
representation'' and the ``parameter space representation''. We
are particularly interested in the relation between the evolution
of the objective space representation of the Pareto set and the evolution
of its parameter space representation.

!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
DELLA TRATTAZIONE

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}

\caption{Relation between Pareto set (its ``parameter space representation'')
and Pareto front (``objective space representation'')}

\end{figure}

\subsection{Regions}

In the design process, there are often a lot of ``local decisions''
in which the designer can take advantage of well-known results or
heuristics. For example, in a VLIW architecture consider a configuration
with very few registers. It is well-known that, in such a condition,
increasing the number of ALUs doesn't lead to tangible better performances
but leads to an increase in area occupation. An intelligent exploration
algorithm wouldn't waste time evaluating configurations with many
ALUs and few registers. If $p_{1}$ is the parameter ``number of
registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
can say that the region:
\[
R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
\]
 (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
interest. This example shows that some ``dependency relation'' between
parameters may exist and can be exploited to guide the exploration:
the dependencies between parameters can suggest to the designer that,
if a parameter lies in a range, there are ranges of the other there
aren't worth exploring. Intuitively, the Cartesian product of these
ranges is an ``uninteresting region''.

The problem is that, in complex scenarios, not all relations of this
kind are known in advance. Some dependency may exist but may be hidden
to the designer. Or there may be ``local dependencies'', i.e. two
parameters may be related by a dependency but only if their values
lie on some ranges (so we can't treat them as they were related by
a true dependency). Therefore, as stated in section \ref{sec:Related-work},
setting up an exploration trying to take into account as much dependencies
as possible is a very hard task that is destined to be incompletely
accomplished. We need a methodology to ``automatically'' recognize
interesting or uninteresting regions without requiring a priori knowledge
to the designer.

We also consider, in measuring how much iteresting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated ineresting as much
as how different are its added Pareto front points from the ones already
found.
\begin{rem}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{rem}
{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
PARAMETRI SENZA ORDINAMENTO{]}
\begin{defn}
\emph{Parameter interval}

Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
A $p_{i}$- interval is
\[
\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
\]
 (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
\end{defn}

\begin{defn}
\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}

Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
be two $p_{i}$-intervals. They are said to be contiguous iff
\begin{itemize}
\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
and
\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
is a $p_{i}$- interval
\end{itemize}
\end{defn}
\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}

\caption{Examples of contiguous and not contiguous intervals}

\end{figure}

\begin{defn}
\emph{Region}

A region is a set of the following form:
\[
R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
\]
 (see figure \ref{pers02.fig:Examples-of-regions})

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/regions}

\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}

\end{figure}
\end{defn}
\begin{rem}
We will talk later of ``big'' and ``small'' regions. The sense
of these terms is related to the cardinality of regions. A region
$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
\[
\left|R_{1}\right|>\left|R_{2}\right|
\]
 where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
if:
\[
\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
\]

Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
\end{rem}
We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{defn}
\emph{\label{pers02.def:Splitting-a-region}Splitting a region}

If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
it can be split in two contiguous intervals
\[
\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
\]
 such that
\[
\begin{cases}
\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
\end{cases}
\]

If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
cannot be split.

If $\left[a_{i}..b_{i}\right]$ can be split, we define
\[
I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
\]
 else
\[
I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
\]

The whole region can be split in the following subregions
\[
\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
\]

See figure \ref{pers02.fig:Splitting-a-region}.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}

\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}

\end{figure}

\end{defn}

\begin{defn}
\emph{Contiguous regions}

Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
be two regions. They are said to be contiguous iff
\begin{itemize}
\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
for all $i\neq j$ 
\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
\end{itemize}
\end{defn}
See figure \ref{pers02.fig:Contiguous-regions}.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}

\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
regions}
\end{figure}

\begin{defn}
\emph{\label{pers02.def:Merging-regions}Merging regions}

Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
ones. Because of the definition of contiguous intervals, it is possible
that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
intervals and obtain a new interval, as the following
\[
\left[t_{j},z_{j}\right]=\begin{cases}
\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
\end{cases}
\]

The region ``$R_{1}$ merged with $R_{2}$'' is defined as
\[
R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
\]

Such an $R$ will be indicated with the following notation:
\[
R=R_{1}+R_{2}
\]
\end{defn}
\begin{rem}
$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
However, using $R_{1}+R_{2}$ notation, we enforce the argument that
$R_{1}$ and $R_{2}$ must be to contiuguous regions.
\end{rem}

\begin{defn}
\emph{Separation}

Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
be two points of $O_{1}\times\dots\times O_{m}$. The separation between
$\mathbf{o}$ and $\mathbf{q}$ is 
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

Notice that the separation is not a commutative operator.\end{defn}
\begin{rem}
The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
The separation is a ``normalized'' measure that is independent of
the nature and the unit of measurement of the objectives
\end{rem}

\begin{defn}
\emph{Separation (alternative)}

Another definition of separation could be:
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

\end{defn}

\section{The algorithm}

The algorithm we present is iterative. Each iteration is called \emph{era}.

Each era $era_{i}$ is characterized by 
\begin{itemize}
\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
$P_{1}\times\dots\times P_{n}$ is divided
\item its Pareto set $\mathscr{P}_{i}$
\item a set $test_{i}$ of at most $K$ configurations to evaluate
\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.

\paragraph{START CONDITION}
\begin{itemize}
\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
i.e. era $0$ has only one region that is the whole parameter space.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated (see def \ref{pers02.def:Pareto-set} for the definition
of the operator $\mathscr{P}_{i}$ over a set)
\end{itemize}

\paragraph{ITERATION RULES}

For $era_{i}$ with $i>0$ the following operations must be performed.
\begin{enumerate}
\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
$test_{R,i}$ of configurations is randomly chosen in%
\footnote{Therefore the chosen configurations can only be configurations of
$R$ not yet evaluated in past eras.%
} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
in $test_{R,i}$ is set to%
\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
are to be chosen, but if not yet evaluated configurations in $R$
are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
are chosen%
} 
\[
\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
\]
The set 
\[
test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
\]
 is defined. 
\item All configurations on $test_{i}$ are simulated.
\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
\[
\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
\]

\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
of%
\footnote{The innovation score is not given to those points in $test_{i}$ that
are not in the Pareto set%
} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
}defined as:
\[
is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
\]
 (a configuration $\mathbf{p}$ is characterized by as much innovation
as more separated it is from the configurations of the previous era)\@.
\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
as:
\[
is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
\]

\item The total innovation score for the entire era is:
\[
is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
\]

\item The avarage innovation score for the entire era is also calculated
as:
\[
is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
\]
where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
era $i$ .
\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
will be discussed later):

\begin{enumerate}
\item high innovation regions 
\[
\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
\]
 where $\alpha$ is a constant defined by the designer (for example
$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
(as stated in def \ref{pers02.def:Splitting-a-region})
\item low innovation regions 
\[
\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
\]
They are not changed.
\item no innovation regions 
\[
\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
\]

\end{enumerate}
\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
couples is indicated as $\mathcal{C}$. The couples of regions are
merged:
\[
\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
\]
 (see def \ref{pers02.def:Merging-regions})
\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
as:
\[
\mathcal{R}_{i+1}=
\]
\[
=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
\]
\[
\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
\]
\[
\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
\]

\end{enumerate}

\paragraph{TERMINATION CONDITION}
\begin{itemize}
\item The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).\end{itemize}
\begin{rem}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/small_and_big}

\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
are evaluated in a small region and in a bigger region. In can be
seen that smaller region is more crowded.}

\end{figure}

\end{rem}

\begin{rem}
The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
a configuration whose objectives are more ``separated'' by the previous
Pareto front, has to be taken in greater account than others. A configuration
that is very near, in the objective space, to the previous Pareto
front doesn't add a true innovation. Therefore, the innovation score
of a configuration is a measure of how much interest we have in considering
it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/novelty_score}

\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
configuration}

\end{figure}

\end{rem}

\begin{rem}
The innovation score of a region is a measure of how much different
are the points that it adds to Pareto Front compared to the previous
Pareto front. ``High innovation regions'' are the ones in which
more configurations are worth evaluating, because they add many points
on not yet well explored Pareto front areas. Therefore, these regions
are split in the next era (see remark \ref{pers02.rem:smaller_regions})
and more ``crowded'' by simulations. ``No innovation regions''
are the ones that have proved to add few points on Pareto fronts,
probably very near to previous Pareto front points and a Pareto front
point near to previous points is not so much interesting. Therefore
it's not worth evaluating many of their configurations and it is useful
to merge these regions , in order to less densely evaluate them.

ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
\end{rem}

\begin{rem}
\label{rem:termination}The algorithm terminates when in the last
$\beta$ iterations not a great ``amount of innovation'' has been
discovered. Therefore it is very probably that carrying on iterating
will not considerably change the Pareto front already formed. It's
not recommended to chose $\beta=1$, because it is possible that the
Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
are not very different but next Pareto fronts could be. In other words,
it's unsafe to terminate as soon as the Pareto front doesn't change
enough, passing from an era to the next. It's better taking into account
more than one era.
\end{rem}
!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')

\begin{rem}
Merging and splitting the regions are very dynamic processes. A portion
of the parameter space can be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This can be explained saying that, after a number
of eras of intense exploration of a portion of parameter space, this
exploration has turned to be enough thorough and so it was time for
other portions to be minutely scanned.
\end{rem}

\section{Experiments}

\section{Conclusions}
\begin{thebibliography}{References}
\bibitem{key-8}V. Pareto. ``Cours d\textquoteright{}E\textasciiacute{}conomie
Politique, volume 1''. F. Rouge \& Cie., Lausanne, Switzerland, 1896.

\bibitem{key-2} Ewa Gajda-Zagórska - ``Recognizing Sets in Evolutionary
Multiobjective Optimization''

\bibitem{key-3}Tony Givargis, Frank Vahid, and Jörg Henkel - ``System-Level
Exploration for Pareto-Optimal Configurations in Parameterized System-on-a-Chip''
(2002)

\bibitem{key-1} Santosh G. Abraham, B. Ramakrishna Rau, Robert Schreiber
- ``Fast Design Space Exploration Through Validity and Quality Filtering
of Subsystem Designs''

\bibitem{key-5}W. Fornaciari, D. Sciuto, C. Silvano, and V. Zaccaria
- \textquotedblleft{}A design framework to efficiently explore energy-delay
tradeoffs\textquotedblright{}, 9th. International Symposium on Hardware/Software
Co-Design, Copenhagen, Denmark, Apr. 25-27 2001, pp. 260-265.

\bibitem{key-7}G. Ascia, V. Catania, M. Palesi - ``Tuning methodologies
for parameterized systems design'', IEEE International workshop on
system-on-Chip for Real-Time Applications IWSOC, 2002.

\bibitem{key-11}Ascia, G., Catania, V. and Palesi, M. - ``A GA based
design space exploration framework for parameterized system-on-a-chip
platforms''. IEEE Transactions on Evolutionary Computation. v8 i4.
329-346.\end{thebibliography}

\end{document}

### 2013-09-25 paper.tex
moved bib

@@
-%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[english]{IEEEtran}
+\documentclass[final,journal,letterpaper]{IEEEtran}
+
+\usepackage{cite}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{url}
+\usepackage{balance}
+\usepackage{float}
+\usepackage{threeparttable}
+
 \usepackage[T1]{fontenc}
@@
 \usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
 
+\usepackage{mathptmx}
+\usepackage[scaled=.90]{helvet}
+\usepackage{courier}
+
+\usepackage{listings}
+\usepackage{listings}
+
+\lstset{
+   language=C,
+   basicstyle=\small,
+   keywordstyle=\bfseries,
+   identifierstyle=\ttfamily,
+   stringstyle=\ttfamily,
+   numbers=left,
+   numberstyle=\tiny,
+   stepnumber=1,
+   numbersep=-5pt,
+   showstringspaces=false
+%   frame=single %trbl%
+}
+
+\usepackage[normalem]{ulem}
+
+%------------------------------------------------------------------------------
+
+\newcommand{\etal}{\emph{et al.}}
+\newcommand{\eg}{\emph{e.g.}}
+\newcommand{\ie}{\emph{i.e.}}
+\newcommand{\etc}{\emph{etc.}}
+\renewcommand{\baselinestretch}{0.98}\normalsize
+%------------------------------------------------------------------------------
 \makeatletter
@@
 
-\usepackage{babel}
+%\usepackage{babel}
 \providecommand{\definitionname}{Definition}
@@
 \begin{abstract}
-qualcosa blah blah blah
+In this paper ...
 \end{abstract}
 
+%------------------------------------------------------------------------------
+%\IEEEkeywords{...}
+
+\begin{IEEEkeywords}
+Nanotechnology, DNA, Self-assembly, Routing
+\end{IEEEkeywords}
+%------------------------------------------------------------------------------
 \section{Introduction}
@@
 The result of every design space exploration is a subset of the configurations
-called Pareto Set (\cite{key-8}). Roughly speaking, it is a set of
+called Pareto Set (\cite{pareto}). Roughly speaking, it is a set of
 configurations such that there are no other configurations, among
@@
 
-The ``Dependency analysis'' proposed in \cite{key-3}, is meant
+The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
 to take advantage of the dependency among the parameters in a multiobjective
@@
 for this reason the need of ``automated approaches for computing
-{[}...{]} interdependencies'' is declared in \cite{key-3}. iii)
+{[}...{]} interdependencies'' is declared in the same paper. iii)
 There may be some ``local dependencies'', i.e. dependencies that
@@
 
-Abraham, Rau and Schreiber proposed in \cite{key-1} to decompose
+Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
 the system to be evaluated into components that interact minimally
@@
 merging the component Pareto sets. Roughly speaking (see section 4
-of \cite{key-1} for more details), monotonicity property guarantees
+of the same paper for more details), monotonicity property guarantees
 that the best system can be obtained as a composition of the best
@@
 expose monotonicity property. This leads to some ``inaccuracies''
-(as stated in section 4.6.1 of \cite{key-1}).
+(as stated in section 4.6.1 of the same paper).
 
@@
 a measure of how much the objective varies when varying that parameter.
-A ``sensitivity analysis'' was used in \cite{key-5} in an optimization
+A ``sensitivity analysis'' was used in \cite{fornaciari_codes01} in an optimization
 problem with only one objective (the power-delay product of an electronic
-device). This method was extended in \cite{key-7} to a multiobjective
-optimization. In \cite{key-7}, the sensitivity of objectives with
+device). This method was extended in \cite{palesi_iwsoc02} to a multiobjective
+optimization. In that work the sensitivity of objectives with
 the respect to each parameter is measured, and parameters are ordered
@@
 in a similar way, the other parameters, one by one. Experimental results
-(see section 4.2 of \cite{key-7}) show that this method is not of
+(see section 4.2 of the same work) show that this method is not of
 good ``quality'' (as broadly defined in the introduction). The reason
@@
 Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{key-11,key-7} and others). Genetic approaches
+optimization problems (\cite{} and others). Genetic approaches
 have many advantages: they have proved good quality (as broadly defined
@@
 \section{Conclusions}
-\begin{thebibliography}{References}
-\bibitem{key-8}V. Pareto. ``Cours d\textquoteright{}E\textasciiacute{}conomie
-Politique, volume 1''. F. Rouge \& Cie., Lausanne, Switzerland, 1896.
+This is the end
 
-\bibitem{key-2} Ewa Gajda-Zagórska - ``Recognizing Sets in Evolutionary
-Multiobjective Optimization''
+\balance
 
-\bibitem{key-3}Tony Givargis, Frank Vahid, and Jörg Henkel - ``System-Level
-Exploration for Pareto-Optimal Configurations in Parameterized System-on-a-Chip''
-(2002)
+\bibliographystyle{IEEEtran} 
+\bibliography{bibliography}
 
-\bibitem{key-1} Santosh G. Abraham, B. Ramakrishna Rau, Robert Schreiber
-- ``Fast Design Space Exploration Through Validity and Quality Filtering
-of Subsystem Designs''
-
-\bibitem{key-5}W. Fornaciari, D. Sciuto, C. Silvano, and V. Zaccaria
-- \textquotedblleft{}A design framework to efficiently explore energy-delay
-tradeoffs\textquotedblright{}, 9th. International Symposium on Hardware/Software
-Co-Design, Copenhagen, Denmark, Apr. 25-27 2001, pp. 260-265.
-
-\bibitem{key-7}G. Ascia, V. Catania, M. Palesi - ``Tuning methodologies
-for parameterized systems design'', IEEE International workshop on
-system-on-Chip for Real-Time Applications IWSOC, 2002.
-
-\bibitem{key-11}Ascia, G., Catania, V. and Palesi, M. - ``A GA based
-design space exploration framework for parameterized system-on-a-chip
-platforms''. IEEE Transactions on Evolutionary Computation. v8 i4.
-329-346.\end{thebibliography}
+% TODO: G2012 bib not used ?
 

### 2013-09-25 algorithm.tex
splitted sections

--- 2013-09-25 paper.tex
@@
-\documentclass[final,journal,letterpaper]{IEEEtran}
-
-\usepackage{cite}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{balance}
-\usepackage{float}
-\usepackage{threeparttable}
-
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{textcomp}
-\usepackage{mathrsfs}
-\usepackage{amsthm}
-
-\usepackage{mathptmx}
-\usepackage[scaled=.90]{helvet}
-\usepackage{courier}
-
-\usepackage{listings}
-\usepackage{listings}
-
-\lstset{
-   language=C,
-   basicstyle=\small,
-   keywordstyle=\bfseries,
-   identifierstyle=\ttfamily,
-   stringstyle=\ttfamily,
-   numbers=left,
-   numberstyle=\tiny,
-   stepnumber=1,
-   numbersep=-5pt,
-   showstringspaces=false
-%   frame=single %trbl%
-}
-
-\usepackage[normalem]{ulem}
-
-%------------------------------------------------------------------------------
-
-\newcommand{\etal}{\emph{et al.}}
-\newcommand{\eg}{\emph{e.g.}}
-\newcommand{\ie}{\emph{i.e.}}
-\newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.98}\normalsize
-%------------------------------------------------------------------------------
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-
-\makeatother
-
-%\usepackage{babel}
-\providecommand{\definitionname}{Definition}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-
-\begin{document}
-
-\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
-\thanks{The authors are with the Dipartimento di Ingegneria
-Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}
-
-\title{Parameter space representation of Pareto set}
-%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
-%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
-%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
-%set come un sottoinsieme dello spazio delle configurazioni.
-
-\maketitle
-\begin{abstract}
-In this paper ...
-\end{abstract}
-
-%------------------------------------------------------------------------------
-%\IEEEkeywords{...}
-
-\begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing
-\end{IEEEkeywords}
-%------------------------------------------------------------------------------
-\section{Introduction}
-
-The design of an embedded system requires several objectives (energy
-consumption, area occupation, ...) to be fulfilled. The fulfilling
-of these objectives depends on several parameters and in the real
-cases no analytical results are known to show the relation between
-configurations (combination of parameters) and objectives. Therefore
-the simulation is the only way to have a picture of how parameters
-impact on the objectives. The problem is that the number of parameters
-and the number of values that each of them may take lead to an enormous
-number of possible configurations, such that simulating all of them
-is an unfeasible activity. Therefore there is the need for the ``Design
-Space Exploration'', i.e. a methodology to select a subset of all
-possible configurations and simulate only this subset.
-
-Many different design space exploration algorithms have been proposed.
-A design space exploration algorithm is typically not based on precise
-/ analytical / mathematical evidences. The motivations of an exploration
-algorithm are rather heuristic, have some form of arbitrariness and,
-to a large extend, intuition lies behind them.
-
-The result of every design space exploration is a subset of the configurations
-called Pareto Set (\cite{pareto}). Roughly speaking, it is a set of
-configurations such that there are no other configurations, among
-the simulated ones, that have all the objectives, at the same time,
-better fulfilled. If all possible configurations were evaluated, the
-ideal Pareto set (the ``true'' Pareto set) could be calculated.
-But, as stated above, evaluating all the configurations is not feasable.
-Therefore the Pareto set returned by an exploration algorithm is an
-approximation of the ``true'' Pareto set.
-
-Many exploration algorithms form the resulting Pareto set in an incremental
-way. The algorithm adds and removes configurations in Pareto set while
-choosing the configurations to evaluate and simulating them. So Pareto
-set ``evolves'' towards the final one. The dynamical view of the
-Pareto set shaping can be seen as the ``behavior'' of the algorithm.
-This behavior tells us how the Pareto set ``converges'' towards
-the final Pareto set.
-
-The ``quality'' of an exploration algorithm involves two aspects:
-\begin{itemize}
-\item how much the Pareto set returned by the exploration algorithm is similar
-to the ``true'' Pareto set (notice that this cannot be evaluated
-because the true Pareto set is unknown - it is only an ``ideal''
-quality factor)
-\item how fast the Pareto set converges towards the final one. If algorithm
-$1$ returns the final Pareto set after simulating $n_{1}$ configurations
-and algorithm $2$ returns its final Pareto set after $n_{2}$ simulations,
-algorithm $1$ is said to be faster than algorithm $2$, iff $n_{1}<n_{2}$.
-\end{itemize}
-
-\section{\label{sec:Related-work}Related work}
-
-There are a number of design space exploration algorithms proposed
-in literature.
-
-The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
-to take advantage of the dependency among the parameters in a multiobjective
-optimization problem. It is required that the designer knows, prior
-to the exploration, if a parameter X is dependent from a parameter
-Y, i.e. changing the value of Y ``impacts the optimal parameter value''
-for X. With this a-priori knowledge, the designer can construct a
-``dependency graph'' and recognize clusters, i.e. subsets of strongly
-dependency-connected parameters. Each cluster is exhaustively evaluated
-and its ``local Pareto set'' is found. Then, all local Pareto sets
-are merged. Doing this way, a ``sum'' of local exhaustive evaluations
-are performed instead of an exhaustive evaluation of all the possible
-configurations. Some problems arise: i) In real scenarios, it may
-be very difficult to recognize really independent clusters of parameters,
-because there may be interdependencies among a very large number of
-parameters. This may lead to the need of an exhaustive search through
-almost all the possible configurations. ii) A designer may not have
-a precise and complete picture of the dependencies among parameters;
-for this reason the need of ``automated approaches for computing
-{[}...{]} interdependencies'' is declared in the same paper. iii)
-There may be some ``local dependencies'', i.e. dependencies that
-emerge only if parameter values are bounded to certain ranges.
-
-These drawbacks are not present in our solution. The algorithm presented
-here is also meant to take advantage of dependency but is not directly
-based on dependency itself, but rather it ``catches'' dependencies
-in terms of ``interesting or uninteresting regions''; as a consequence
-no a-priori knowledge of dependencies is required as they are discovered
-during exploration. Moreover, recognizing regions offers the capability
-to capture local dependencies.
-
-Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
-the system to be evaluated into components that interact minimally
-with each other. ``Alternative designs for each component are evaluated
-in isolation to determine the best designs for individual components.
-Combinations of these designs are then put together to build the complete
-system design''. Pareto sets for each component are found and, provided
-that ``monotonicity'' exists, the complete Pareto set is computed
-merging the component Pareto sets. Roughly speaking (see section 4
-of the same paper for more details), monotonicity property guarantees
-that the best system can be obtained as a composition of the best
-components. This approach would perfectly work if all the components
-were perfectly isolated, i.e., if there were no dependencies among
-different components (in a sense similar (but not necesarily equal)
-to the one of Dependency analisys). But real scenarios seldom if ever
-expose monotonicity property. This leads to some ``inaccuracies''
-(as stated in section 4.6.1 of the same paper).
-
-Other approaches take into account the concept of ``sensitivity''.
-The sensitivity of an objective with the respect to a parameter is
-a measure of how much the objective varies when varying that parameter.
-A ``sensitivity analysis'' was used in \cite{fornaciari_codes01} in an optimization
-problem with only one objective (the power-delay product of an electronic
-device). This method was extended in \cite{palesi_iwsoc02} to a multiobjective
-optimization. In that work the sensitivity of objectives with
-the respect to each parameter is measured, and parameters are ordered
-on the base on these sensitivity measures. Then, a first Pareto set
-is obtained varying the first parameter, having fixed to arbitrary
-values all other parameters. The Pareto set is then refined varying,
-in a similar way, the other parameters, one by one. Experimental results
-(see section 4.2 of the same work) show that this method is not of
-good ``quality'' (as broadly defined in the introduction). The reason
-can be found in the very limited and rigid exploration of the parameter
-space: after computing the first Pareto set, there are no more chances
-to consider configurations with values of the first parameter other
-than the ones assumed in the first Pareto set calculation. Similar
-limitations are imposed after computing the second Pareto set, the
-third and so on. It is worth noticing that this approach can not capture
-``local sensitivity'' (this drawback will be called ``local sensitivity
-limitation''), i.e. the objectives may be more sensitive to some
-ranges of a parameter and less sensitive to other ranges of the same
-parameter. Moreover it can not capture ``combined sensitivity''
-(``combined sensitivity limitation''), i.e. the objectives may be
-more sensitive to a range of a parameter $p_{1}$, only when other
-parameters are within certain ranges, and less sensitive to the same
-range of parameter $p_{1}$ when the other parameters are not within
-those ranges. Therefore, in the method we propose, we do not use the
-sensitivity directly, but we use the concept of innovation (that can
-be considered, at least weakly related to the sensitivity). We do
-not measure innovation of a parameter (as done for the sensitivity),
-but rather we measure the innovation of a ``region'' of parameter
-space, in order to overcome both the ``local sensitivity limitation''
-and the ``combined sensitivity limitation'' stated above for the
-sensitivity analysis.
-
-Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{} and others). Genetic approaches
-have many advantages: they have proved good quality (as broadly defined
-in the introduction), they are customizable, they are very general
-and require no a-priori knowledge to the designer. Genetic algorithms
-run in subsequent iterations. Configurations are represented as chromosomes.
-In each iteration a ``population'' of configurations is evaluated.
-Some configurations are discarded. Each selected configuration is
-combined with the preceding population and then ``mutated'' (i.e.
-the resulting configuration is varied a little). Iterating this operations,
-populations are expected to become ``better and better''. The strong
-point of genetic approaches can be summarized saying that they consist
-in a broad exploration (the mutation permits to make the exploration
-not rigidly restricted to limited parts of parameter space), although
-this exploration is not random but is guided by the performances of
-the already evaluated configurations. Therefore, the exploration is
-neither too much constrained nor too much random. We claim that the
-approach presented in this paper has all the benefits of the genetic
-approaches, although the rational is completely different.
-
-\section{Preliminaries}
-
-\subsection{Representation}
-\begin{defn}
-\emph{Configuration}
-
-Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
-of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
-may assume. A configuration is a vector
-\[
-\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-\begin{defn}
-\emph{Objective function}
-
-Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
-values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
-operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
-we can always say:
-\[
-o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
-\]
-
-$o_{i}$ can be viewed as a function
-\[
-o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
- To take into account all of the objectives, the following function
-is defined:
-\[
-\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
-\begin{defn}
-\emph{\label{pers02.def:Pareto-set}Pareto set}
-
-Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
-configurations is:
-\[
-Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
-\]
-
-Its Pareto set is defined as:
-\[
-\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
-\]
-
-When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
-\end{defn}
-
-\begin{defn}
-\emph{Pareto front}
-
-The Pareto front is the representation in the objective space of the
-Pareto set, i.e.:
-\[
-\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
-\]
-
-\end{defn}
-On the contrary, we call ``parameter space representation'' of the
-Pareto set the representation in which each configuration $\mathbf{p}$
-is simply represented as a point of $P_{1}\times\dots\times P_{n}$
-space. We will investigate the relation between the ``objective space
-representation'' and the ``parameter space representation''. We
-are particularly interested in the relation between the evolution
-of the objective space representation of the Pareto set and the evolution
-of its parameter space representation.
-
-!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
-PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
-DELLA TRATTAZIONE
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}
-
-\caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'')}
-
-\end{figure}
-
-\subsection{Regions}
-
-In the design process, there are often a lot of ``local decisions''
-in which the designer can take advantage of well-known results or
-heuristics. For example, in a VLIW architecture consider a configuration
-with very few registers. It is well-known that, in such a condition,
-increasing the number of ALUs doesn't lead to tangible better performances
-but leads to an increase in area occupation. An intelligent exploration
-algorithm wouldn't waste time evaluating configurations with many
-ALUs and few registers. If $p_{1}$ is the parameter ``number of
-registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
-can say that the region:
-\[
-R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
-\]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
-interest. This example shows that some ``dependency relation'' between
-parameters may exist and can be exploited to guide the exploration:
-the dependencies between parameters can suggest to the designer that,
-if a parameter lies in a range, there are ranges of the other there
-aren't worth exploring. Intuitively, the Cartesian product of these
-ranges is an ``uninteresting region''.
-
-The problem is that, in complex scenarios, not all relations of this
-kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or there may be ``local dependencies'', i.e. two
-parameters may be related by a dependency but only if their values
-lie on some ranges (so we can't treat them as they were related by
-a true dependency). Therefore, as stated in section \ref{sec:Related-work},
-setting up an exploration trying to take into account as much dependencies
-as possible is a very hard task that is destined to be incompletely
-accomplished. We need a methodology to ``automatically'' recognize
-interesting or uninteresting regions without requiring a priori knowledge
-to the designer.
-
-We also consider, in measuring how much iteresting a region is, the
-``innovation'' that it adds. If, during a design space exploration,
-a Pareto front is temporarily calculated, adding a new Pareto front
-point near to the previous ones is not a considerable ``innovation'',
-because the way it fulfils the objectives is very similar to other
-already evaluated configurations. On the contrary, adding a new Pareto
-front point that is very distant from previous ones is remarkable,
-because it let the experimenter realize that the objectives can be
-fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated ineresting as much
-as how different are its added Pareto front points from the ones already
-found.
-\begin{rem}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{rem}
-{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-PARAMETRI SENZA ORDINAMENTO{]}
-\begin{defn}
-\emph{Parameter interval}
-
-Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
-A $p_{i}$- interval is
-\[
-\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
-\]
- (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
-is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
-\end{defn}
-
-\begin{defn}
-\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}
-
-Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous iff
-\begin{itemize}
-\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
-and
-\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
-interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
-is a $p_{i}$- interval
-\end{itemize}
-\end{defn}
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}
-
-\caption{Examples of contiguous and not contiguous intervals}
-
-\end{figure}
-
-\begin{defn}
-\emph{Region}
-
-A region is a set of the following form:
-\[
-R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
-\]
- (see figure \ref{pers02.fig:Examples-of-regions})
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/regions}
-
-\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}
-
-\end{figure}
-\end{defn}
-\begin{rem}
-We will talk later of ``big'' and ``small'' regions. The sense
-of these terms is related to the cardinality of regions. A region
-$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
-\[
-\left|R_{1}\right|>\left|R_{2}\right|
-\]
- where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
-of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-if:
-\[
-\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
-\]
-
-Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{rem}
-We now provide some rules to split and merge regions. They will be
-useful when explaining our proposed exploration algorithm.
-\begin{defn}
-\emph{\label{pers02.def:Splitting-a-region}Splitting a region}
-
-If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
-it can be split in two contiguous intervals
-\[
-\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
-\]
- such that
-\[
-\begin{cases}
-\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
-\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
-\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
-\end{cases}
-\]
-
-If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
-cannot be split.
-
-If $\left[a_{i}..b_{i}\right]$ can be split, we define
-\[
-I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
-\]
- else
-\[
-I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
-\]
-
-The whole region can be split in the following subregions
-\[
-\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
-\]
-
-See figure \ref{pers02.fig:Splitting-a-region}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}
-
-\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}
-
-\end{figure}
-
-\end{defn}
-
-\begin{defn}
-\emph{Contiguous regions}
-
-Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff
-\begin{itemize}
-\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
-for all $i\neq j$ 
-\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
-contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
-\end{itemize}
-\end{defn}
-See figure \ref{pers02.fig:Contiguous-regions}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}
-
-\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
-regions}
-\end{figure}
-
-\begin{defn}
-\emph{\label{pers02.def:Merging-regions}Merging regions}
-
-Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
-ones. Because of the definition of contiguous intervals, it is possible
-that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
-intervals and obtain a new interval, as the following
-\[
-\left[t_{j},z_{j}\right]=\begin{cases}
-\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
-\end{cases}
-\]
-
-The region ``$R_{1}$ merged with $R_{2}$'' is defined as
-\[
-R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
-\]
-
-Such an $R$ will be indicated with the following notation:
-\[
-R=R_{1}+R_{2}
-\]
-\end{defn}
-\begin{rem}
-$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
-However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiuguous regions.
-\end{rem}
-
-\begin{defn}
-\emph{Separation}
-
-Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
-be two points of $O_{1}\times\dots\times O_{m}$. The separation between
-$\mathbf{o}$ and $\mathbf{q}$ is 
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-Notice that the separation is not a commutative operator.\end{defn}
-\begin{rem}
-The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
-The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives
-\end{rem}
-
-\begin{defn}
-\emph{Separation (alternative)}
-
-Another definition of separation could be:
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-\end{defn}
-
 \section{The algorithm}
@@
 \end{rem}
-
-\section{Experiments}
-
-\section{Conclusions}
-This is the end
-
-\balance
-
-\bibliographystyle{IEEEtran} 
-\bibliography{bibliography}
-
-% TODO: G2012 bib not used ?
-
-\end{document}

### 2013-09-25 concepts.tex
splitted sections

--- 2013-09-25 paper.tex
@@
-\documentclass[final,journal,letterpaper]{IEEEtran}
-
-\usepackage{cite}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{balance}
-\usepackage{float}
-\usepackage{threeparttable}
-
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{textcomp}
-\usepackage{mathrsfs}
-\usepackage{amsthm}
-
-\usepackage{mathptmx}
-\usepackage[scaled=.90]{helvet}
-\usepackage{courier}
-
-\usepackage{listings}
-\usepackage{listings}
-
-\lstset{
-   language=C,
-   basicstyle=\small,
-   keywordstyle=\bfseries,
-   identifierstyle=\ttfamily,
-   stringstyle=\ttfamily,
-   numbers=left,
-   numberstyle=\tiny,
-   stepnumber=1,
-   numbersep=-5pt,
-   showstringspaces=false
-%   frame=single %trbl%
-}
-
-\usepackage[normalem]{ulem}
-
-%------------------------------------------------------------------------------
-
-\newcommand{\etal}{\emph{et al.}}
-\newcommand{\eg}{\emph{e.g.}}
-\newcommand{\ie}{\emph{i.e.}}
-\newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.98}\normalsize
-%------------------------------------------------------------------------------
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-
-\makeatother
-
-%\usepackage{babel}
-\providecommand{\definitionname}{Definition}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-
-\begin{document}
-
-\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
-\thanks{The authors are with the Dipartimento di Ingegneria
-Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}
-
-\title{Parameter space representation of Pareto set}
-%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
-%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
-%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
-%set come un sottoinsieme dello spazio delle configurazioni.
-
-\maketitle
-\begin{abstract}
-In this paper ...
-\end{abstract}
-
-%------------------------------------------------------------------------------
-%\IEEEkeywords{...}
-
-\begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing
-\end{IEEEkeywords}
-%------------------------------------------------------------------------------
-\section{Introduction}
-
-The design of an embedded system requires several objectives (energy
-consumption, area occupation, ...) to be fulfilled. The fulfilling
-of these objectives depends on several parameters and in the real
-cases no analytical results are known to show the relation between
-configurations (combination of parameters) and objectives. Therefore
-the simulation is the only way to have a picture of how parameters
-impact on the objectives. The problem is that the number of parameters
-and the number of values that each of them may take lead to an enormous
-number of possible configurations, such that simulating all of them
-is an unfeasible activity. Therefore there is the need for the ``Design
-Space Exploration'', i.e. a methodology to select a subset of all
-possible configurations and simulate only this subset.
-
-Many different design space exploration algorithms have been proposed.
-A design space exploration algorithm is typically not based on precise
-/ analytical / mathematical evidences. The motivations of an exploration
-algorithm are rather heuristic, have some form of arbitrariness and,
-to a large extend, intuition lies behind them.
-
-The result of every design space exploration is a subset of the configurations
-called Pareto Set (\cite{pareto}). Roughly speaking, it is a set of
-configurations such that there are no other configurations, among
-the simulated ones, that have all the objectives, at the same time,
-better fulfilled. If all possible configurations were evaluated, the
-ideal Pareto set (the ``true'' Pareto set) could be calculated.
-But, as stated above, evaluating all the configurations is not feasable.
-Therefore the Pareto set returned by an exploration algorithm is an
-approximation of the ``true'' Pareto set.
-
-Many exploration algorithms form the resulting Pareto set in an incremental
-way. The algorithm adds and removes configurations in Pareto set while
-choosing the configurations to evaluate and simulating them. So Pareto
-set ``evolves'' towards the final one. The dynamical view of the
-Pareto set shaping can be seen as the ``behavior'' of the algorithm.
-This behavior tells us how the Pareto set ``converges'' towards
-the final Pareto set.
-
-The ``quality'' of an exploration algorithm involves two aspects:
-\begin{itemize}
-\item how much the Pareto set returned by the exploration algorithm is similar
-to the ``true'' Pareto set (notice that this cannot be evaluated
-because the true Pareto set is unknown - it is only an ``ideal''
-quality factor)
-\item how fast the Pareto set converges towards the final one. If algorithm
-$1$ returns the final Pareto set after simulating $n_{1}$ configurations
-and algorithm $2$ returns its final Pareto set after $n_{2}$ simulations,
-algorithm $1$ is said to be faster than algorithm $2$, iff $n_{1}<n_{2}$.
-\end{itemize}
-
-\section{\label{sec:Related-work}Related work}
-
-There are a number of design space exploration algorithms proposed
-in literature.
-
-The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
-to take advantage of the dependency among the parameters in a multiobjective
-optimization problem. It is required that the designer knows, prior
-to the exploration, if a parameter X is dependent from a parameter
-Y, i.e. changing the value of Y ``impacts the optimal parameter value''
-for X. With this a-priori knowledge, the designer can construct a
-``dependency graph'' and recognize clusters, i.e. subsets of strongly
-dependency-connected parameters. Each cluster is exhaustively evaluated
-and its ``local Pareto set'' is found. Then, all local Pareto sets
-are merged. Doing this way, a ``sum'' of local exhaustive evaluations
-are performed instead of an exhaustive evaluation of all the possible
-configurations. Some problems arise: i) In real scenarios, it may
-be very difficult to recognize really independent clusters of parameters,
-because there may be interdependencies among a very large number of
-parameters. This may lead to the need of an exhaustive search through
-almost all the possible configurations. ii) A designer may not have
-a precise and complete picture of the dependencies among parameters;
-for this reason the need of ``automated approaches for computing
-{[}...{]} interdependencies'' is declared in the same paper. iii)
-There may be some ``local dependencies'', i.e. dependencies that
-emerge only if parameter values are bounded to certain ranges.
-
-These drawbacks are not present in our solution. The algorithm presented
-here is also meant to take advantage of dependency but is not directly
-based on dependency itself, but rather it ``catches'' dependencies
-in terms of ``interesting or uninteresting regions''; as a consequence
-no a-priori knowledge of dependencies is required as they are discovered
-during exploration. Moreover, recognizing regions offers the capability
-to capture local dependencies.
-
-Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
-the system to be evaluated into components that interact minimally
-with each other. ``Alternative designs for each component are evaluated
-in isolation to determine the best designs for individual components.
-Combinations of these designs are then put together to build the complete
-system design''. Pareto sets for each component are found and, provided
-that ``monotonicity'' exists, the complete Pareto set is computed
-merging the component Pareto sets. Roughly speaking (see section 4
-of the same paper for more details), monotonicity property guarantees
-that the best system can be obtained as a composition of the best
-components. This approach would perfectly work if all the components
-were perfectly isolated, i.e., if there were no dependencies among
-different components (in a sense similar (but not necesarily equal)
-to the one of Dependency analisys). But real scenarios seldom if ever
-expose monotonicity property. This leads to some ``inaccuracies''
-(as stated in section 4.6.1 of the same paper).
-
-Other approaches take into account the concept of ``sensitivity''.
-The sensitivity of an objective with the respect to a parameter is
-a measure of how much the objective varies when varying that parameter.
-A ``sensitivity analysis'' was used in \cite{fornaciari_codes01} in an optimization
-problem with only one objective (the power-delay product of an electronic
-device). This method was extended in \cite{palesi_iwsoc02} to a multiobjective
-optimization. In that work the sensitivity of objectives with
-the respect to each parameter is measured, and parameters are ordered
-on the base on these sensitivity measures. Then, a first Pareto set
-is obtained varying the first parameter, having fixed to arbitrary
-values all other parameters. The Pareto set is then refined varying,
-in a similar way, the other parameters, one by one. Experimental results
-(see section 4.2 of the same work) show that this method is not of
-good ``quality'' (as broadly defined in the introduction). The reason
-can be found in the very limited and rigid exploration of the parameter
-space: after computing the first Pareto set, there are no more chances
-to consider configurations with values of the first parameter other
-than the ones assumed in the first Pareto set calculation. Similar
-limitations are imposed after computing the second Pareto set, the
-third and so on. It is worth noticing that this approach can not capture
-``local sensitivity'' (this drawback will be called ``local sensitivity
-limitation''), i.e. the objectives may be more sensitive to some
-ranges of a parameter and less sensitive to other ranges of the same
-parameter. Moreover it can not capture ``combined sensitivity''
-(``combined sensitivity limitation''), i.e. the objectives may be
-more sensitive to a range of a parameter $p_{1}$, only when other
-parameters are within certain ranges, and less sensitive to the same
-range of parameter $p_{1}$ when the other parameters are not within
-those ranges. Therefore, in the method we propose, we do not use the
-sensitivity directly, but we use the concept of innovation (that can
-be considered, at least weakly related to the sensitivity). We do
-not measure innovation of a parameter (as done for the sensitivity),
-but rather we measure the innovation of a ``region'' of parameter
-space, in order to overcome both the ``local sensitivity limitation''
-and the ``combined sensitivity limitation'' stated above for the
-sensitivity analysis.
-
-Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{} and others). Genetic approaches
-have many advantages: they have proved good quality (as broadly defined
-in the introduction), they are customizable, they are very general
-and require no a-priori knowledge to the designer. Genetic algorithms
-run in subsequent iterations. Configurations are represented as chromosomes.
-In each iteration a ``population'' of configurations is evaluated.
-Some configurations are discarded. Each selected configuration is
-combined with the preceding population and then ``mutated'' (i.e.
-the resulting configuration is varied a little). Iterating this operations,
-populations are expected to become ``better and better''. The strong
-point of genetic approaches can be summarized saying that they consist
-in a broad exploration (the mutation permits to make the exploration
-not rigidly restricted to limited parts of parameter space), although
-this exploration is not random but is guided by the performances of
-the already evaluated configurations. Therefore, the exploration is
-neither too much constrained nor too much random. We claim that the
-approach presented in this paper has all the benefits of the genetic
-approaches, although the rational is completely different.
-
 \section{Preliminaries}
@@
 \end{defn}
-
-\section{The algorithm}
-
-The algorithm we present is iterative. Each iteration is called \emph{era}.
-
-Each era $era_{i}$ is characterized by 
-\begin{itemize}
-\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
-$P_{1}\times\dots\times P_{n}$ is divided
-\item its Pareto set $\mathscr{P}_{i}$
-\item a set $test_{i}$ of at most $K$ configurations to evaluate
-\end{itemize}
-$K$ is a parameter that must be set before the algorithm runs.
-
-\paragraph{START CONDITION}
-\begin{itemize}
-\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
-i.e. era $0$ has only one region that is the whole parameter space.
-A random set $test_{0}$ of $K$ configurations is evaluated. The
-Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
-calculated (see def \ref{pers02.def:Pareto-set} for the definition
-of the operator $\mathscr{P}_{i}$ over a set)
-\end{itemize}
-
-\paragraph{ITERATION RULES}
-
-For $era_{i}$ with $i>0$ the following operations must be performed.
-\begin{enumerate}
-\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
-$test_{R,i}$ of configurations is randomly chosen in%
-\footnote{Therefore the chosen configurations can only be configurations of
-$R$ not yet evaluated in past eras.%
-} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
-in $test_{R,i}$ is set to%
-\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
-are to be chosen, but if not yet evaluated configurations in $R$
-are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
-are chosen%
-} 
-\[
-\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
-\]
-The set 
-\[
-test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
-\]
- is defined. 
-\item All configurations on $test_{i}$ are simulated.
-\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
-\[
-\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
-\]
-
-\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
-of%
-\footnote{The innovation score is not given to those points in $test_{i}$ that
-are not in the Pareto set%
-} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
-}defined as:
-\[
-is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
-\]
- (a configuration $\mathbf{p}$ is characterized by as much innovation
-as more separated it is from the configurations of the previous era)\@.
-\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
-as:
-\[
-is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
-\]
-
-\item The total innovation score for the entire era is:
-\[
-is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
-\]
-
-\item The avarage innovation score for the entire era is also calculated
-as:
-\[
-is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
-\]
-where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
-era $i$ .
-\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
-will be discussed later):
-
-\begin{enumerate}
-\item high innovation regions 
-\[
-\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
-\]
- where $\alpha$ is a constant defined by the designer (for example
-$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
-(as stated in def \ref{pers02.def:Splitting-a-region})
-\item low innovation regions 
-\[
-\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
-\]
-They are not changed.
-\item no innovation regions 
-\[
-\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
-\]
-
-\end{enumerate}
-\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
-with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
-couples is indicated as $\mathcal{C}$. The couples of regions are
-merged:
-\[
-\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
-\]
- (see def \ref{pers02.def:Merging-regions})
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
-as:
-\[
-\mathcal{R}_{i+1}=
-\]
-\[
-=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
-\]
-\[
-\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
-\]
-\[
-\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
-\]
-
-\end{enumerate}
-
-\paragraph{TERMINATION CONDITION}
-\begin{itemize}
-\item The algorithm terminates at step $k$ if
-\[
-is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
-\]
- where $\beta$ and $\gamma$ are selected by the experimenter (see
-remark \ref{rem:termination}).\end{itemize}
-\begin{rem}
-\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
-the iteration rules says that the smaller is a region, the more ``crowded''
-it is. It means that configurations in smaller regions are evaluated
-with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/small_and_big}
-
-\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
-are evaluated in a small region and in a bigger region. In can be
-seen that smaller region is more crowded.}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
-a configuration whose objectives are more ``separated'' by the previous
-Pareto front, has to be taken in greater account than others. A configuration
-that is very near, in the objective space, to the previous Pareto
-front doesn't add a true innovation. Therefore, the innovation score
-of a configuration is a measure of how much interest we have in considering
-it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/novelty_score}
-
-\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
-configuration}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The innovation score of a region is a measure of how much different
-are the points that it adds to Pareto Front compared to the previous
-Pareto front. ``High innovation regions'' are the ones in which
-more configurations are worth evaluating, because they add many points
-on not yet well explored Pareto front areas. Therefore, these regions
-are split in the next era (see remark \ref{pers02.rem:smaller_regions})
-and more ``crowded'' by simulations. ``No innovation regions''
-are the ones that have proved to add few points on Pareto fronts,
-probably very near to previous Pareto front points and a Pareto front
-point near to previous points is not so much interesting. Therefore
-it's not worth evaluating many of their configurations and it is useful
-to merge these regions , in order to less densely evaluate them.
-
-ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
-DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
-\end{rem}
-
-\begin{rem}
-\label{rem:termination}The algorithm terminates when in the last
-$\beta$ iterations not a great ``amount of innovation'' has been
-discovered. Therefore it is very probably that carrying on iterating
-will not considerably change the Pareto front already formed. It's
-not recommended to chose $\beta=1$, because it is possible that the
-Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
-are not very different but next Pareto fronts could be. In other words,
-it's unsafe to terminate as soon as the Pareto front doesn't change
-enough, passing from an era to the next. It's better taking into account
-more than one era.
-\end{rem}
-!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
-FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
-
-\begin{rem}
-Merging and splitting the regions are very dynamic processes. A portion
-of the parameter space can be populated by a large number of small
-regions in some eras, but can be covered by a small number of large
-regions in next eras. This can be explained saying that, after a number
-of eras of intense exploration of a portion of parameter space, this
-exploration has turned to be enough thorough and so it was time for
-other portions to be minutely scanned.
-\end{rem}
-
-\section{Experiments}
-
-\section{Conclusions}
-This is the end
-
-\balance
-
-\bibliographystyle{IEEEtran} 
-\bibliography{bibliography}
-
-% TODO: G2012 bib not used ?
-
-\end{document}

### 2013-09-25 introduction.tex
splitted sections

--- 2013-09-25 paper.tex
@@
-\documentclass[final,journal,letterpaper]{IEEEtran}
-
-\usepackage{cite}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{balance}
-\usepackage{float}
-\usepackage{threeparttable}
-
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{textcomp}
-\usepackage{mathrsfs}
-\usepackage{amsthm}
-
-\usepackage{mathptmx}
-\usepackage[scaled=.90]{helvet}
-\usepackage{courier}
-
-\usepackage{listings}
-\usepackage{listings}
-
-\lstset{
-   language=C,
-   basicstyle=\small,
-   keywordstyle=\bfseries,
-   identifierstyle=\ttfamily,
-   stringstyle=\ttfamily,
-   numbers=left,
-   numberstyle=\tiny,
-   stepnumber=1,
-   numbersep=-5pt,
-   showstringspaces=false
-%   frame=single %trbl%
-}
-
-\usepackage[normalem]{ulem}
-
-%------------------------------------------------------------------------------
-
-\newcommand{\etal}{\emph{et al.}}
-\newcommand{\eg}{\emph{e.g.}}
-\newcommand{\ie}{\emph{i.e.}}
-\newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.98}\normalsize
-%------------------------------------------------------------------------------
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-
-\makeatother
-
-%\usepackage{babel}
-\providecommand{\definitionname}{Definition}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-
-\begin{document}
-
-\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
-\thanks{The authors are with the Dipartimento di Ingegneria
-Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}
-
-\title{Parameter space representation of Pareto set}
-%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
-%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
-%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
-%set come un sottoinsieme dello spazio delle configurazioni.
-
-\maketitle
-\begin{abstract}
-In this paper ...
-\end{abstract}
-
-%------------------------------------------------------------------------------
-%\IEEEkeywords{...}
-
-\begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing
-\end{IEEEkeywords}
-%------------------------------------------------------------------------------
 \section{Introduction}
@@
 approaches, although the rational is completely different.
-
-\section{Preliminaries}
-
-\subsection{Representation}
-\begin{defn}
-\emph{Configuration}
-
-Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
-of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
-may assume. A configuration is a vector
-\[
-\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-\begin{defn}
-\emph{Objective function}
-
-Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
-values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
-operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
-we can always say:
-\[
-o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
-\]
-
-$o_{i}$ can be viewed as a function
-\[
-o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
- To take into account all of the objectives, the following function
-is defined:
-\[
-\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
-\begin{defn}
-\emph{\label{pers02.def:Pareto-set}Pareto set}
-
-Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
-configurations is:
-\[
-Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
-\]
-
-Its Pareto set is defined as:
-\[
-\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
-\]
-
-When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
-\end{defn}
-
-\begin{defn}
-\emph{Pareto front}
-
-The Pareto front is the representation in the objective space of the
-Pareto set, i.e.:
-\[
-\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
-\]
-
-\end{defn}
-On the contrary, we call ``parameter space representation'' of the
-Pareto set the representation in which each configuration $\mathbf{p}$
-is simply represented as a point of $P_{1}\times\dots\times P_{n}$
-space. We will investigate the relation between the ``objective space
-representation'' and the ``parameter space representation''. We
-are particularly interested in the relation between the evolution
-of the objective space representation of the Pareto set and the evolution
-of its parameter space representation.
-
-!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
-PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
-DELLA TRATTAZIONE
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}
-
-\caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'')}
-
-\end{figure}
-
-\subsection{Regions}
-
-In the design process, there are often a lot of ``local decisions''
-in which the designer can take advantage of well-known results or
-heuristics. For example, in a VLIW architecture consider a configuration
-with very few registers. It is well-known that, in such a condition,
-increasing the number of ALUs doesn't lead to tangible better performances
-but leads to an increase in area occupation. An intelligent exploration
-algorithm wouldn't waste time evaluating configurations with many
-ALUs and few registers. If $p_{1}$ is the parameter ``number of
-registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
-can say that the region:
-\[
-R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
-\]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
-interest. This example shows that some ``dependency relation'' between
-parameters may exist and can be exploited to guide the exploration:
-the dependencies between parameters can suggest to the designer that,
-if a parameter lies in a range, there are ranges of the other there
-aren't worth exploring. Intuitively, the Cartesian product of these
-ranges is an ``uninteresting region''.
-
-The problem is that, in complex scenarios, not all relations of this
-kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or there may be ``local dependencies'', i.e. two
-parameters may be related by a dependency but only if their values
-lie on some ranges (so we can't treat them as they were related by
-a true dependency). Therefore, as stated in section \ref{sec:Related-work},
-setting up an exploration trying to take into account as much dependencies
-as possible is a very hard task that is destined to be incompletely
-accomplished. We need a methodology to ``automatically'' recognize
-interesting or uninteresting regions without requiring a priori knowledge
-to the designer.
-
-We also consider, in measuring how much iteresting a region is, the
-``innovation'' that it adds. If, during a design space exploration,
-a Pareto front is temporarily calculated, adding a new Pareto front
-point near to the previous ones is not a considerable ``innovation'',
-because the way it fulfils the objectives is very similar to other
-already evaluated configurations. On the contrary, adding a new Pareto
-front point that is very distant from previous ones is remarkable,
-because it let the experimenter realize that the objectives can be
-fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated ineresting as much
-as how different are its added Pareto front points from the ones already
-found.
-\begin{rem}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{rem}
-{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-PARAMETRI SENZA ORDINAMENTO{]}
-\begin{defn}
-\emph{Parameter interval}
-
-Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
-A $p_{i}$- interval is
-\[
-\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
-\]
- (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
-is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
-\end{defn}
-
-\begin{defn}
-\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}
-
-Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous iff
-\begin{itemize}
-\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
-and
-\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
-interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
-is a $p_{i}$- interval
-\end{itemize}
-\end{defn}
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}
-
-\caption{Examples of contiguous and not contiguous intervals}
-
-\end{figure}
-
-\begin{defn}
-\emph{Region}
-
-A region is a set of the following form:
-\[
-R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
-\]
- (see figure \ref{pers02.fig:Examples-of-regions})
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/regions}
-
-\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}
-
-\end{figure}
-\end{defn}
-\begin{rem}
-We will talk later of ``big'' and ``small'' regions. The sense
-of these terms is related to the cardinality of regions. A region
-$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
-\[
-\left|R_{1}\right|>\left|R_{2}\right|
-\]
- where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
-of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-if:
-\[
-\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
-\]
-
-Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{rem}
-We now provide some rules to split and merge regions. They will be
-useful when explaining our proposed exploration algorithm.
-\begin{defn}
-\emph{\label{pers02.def:Splitting-a-region}Splitting a region}
-
-If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
-it can be split in two contiguous intervals
-\[
-\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
-\]
- such that
-\[
-\begin{cases}
-\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
-\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
-\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
-\end{cases}
-\]
-
-If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
-cannot be split.
-
-If $\left[a_{i}..b_{i}\right]$ can be split, we define
-\[
-I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
-\]
- else
-\[
-I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
-\]
-
-The whole region can be split in the following subregions
-\[
-\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
-\]
-
-See figure \ref{pers02.fig:Splitting-a-region}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}
-
-\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}
-
-\end{figure}
-
-\end{defn}
-
-\begin{defn}
-\emph{Contiguous regions}
-
-Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff
-\begin{itemize}
-\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
-for all $i\neq j$ 
-\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
-contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
-\end{itemize}
-\end{defn}
-See figure \ref{pers02.fig:Contiguous-regions}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}
-
-\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
-regions}
-\end{figure}
-
-\begin{defn}
-\emph{\label{pers02.def:Merging-regions}Merging regions}
-
-Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
-ones. Because of the definition of contiguous intervals, it is possible
-that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
-intervals and obtain a new interval, as the following
-\[
-\left[t_{j},z_{j}\right]=\begin{cases}
-\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
-\end{cases}
-\]
-
-The region ``$R_{1}$ merged with $R_{2}$'' is defined as
-\[
-R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
-\]
-
-Such an $R$ will be indicated with the following notation:
-\[
-R=R_{1}+R_{2}
-\]
-\end{defn}
-\begin{rem}
-$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
-However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiuguous regions.
-\end{rem}
-
-\begin{defn}
-\emph{Separation}
-
-Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
-be two points of $O_{1}\times\dots\times O_{m}$. The separation between
-$\mathbf{o}$ and $\mathbf{q}$ is 
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-Notice that the separation is not a commutative operator.\end{defn}
-\begin{rem}
-The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
-The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives
-\end{rem}
-
-\begin{defn}
-\emph{Separation (alternative)}
-
-Another definition of separation could be:
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-\end{defn}
-
-\section{The algorithm}
-
-The algorithm we present is iterative. Each iteration is called \emph{era}.
-
-Each era $era_{i}$ is characterized by 
-\begin{itemize}
-\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
-$P_{1}\times\dots\times P_{n}$ is divided
-\item its Pareto set $\mathscr{P}_{i}$
-\item a set $test_{i}$ of at most $K$ configurations to evaluate
-\end{itemize}
-$K$ is a parameter that must be set before the algorithm runs.
-
-\paragraph{START CONDITION}
-\begin{itemize}
-\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
-i.e. era $0$ has only one region that is the whole parameter space.
-A random set $test_{0}$ of $K$ configurations is evaluated. The
-Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
-calculated (see def \ref{pers02.def:Pareto-set} for the definition
-of the operator $\mathscr{P}_{i}$ over a set)
-\end{itemize}
-
-\paragraph{ITERATION RULES}
-
-For $era_{i}$ with $i>0$ the following operations must be performed.
-\begin{enumerate}
-\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
-$test_{R,i}$ of configurations is randomly chosen in%
-\footnote{Therefore the chosen configurations can only be configurations of
-$R$ not yet evaluated in past eras.%
-} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
-in $test_{R,i}$ is set to%
-\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
-are to be chosen, but if not yet evaluated configurations in $R$
-are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
-are chosen%
-} 
-\[
-\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
-\]
-The set 
-\[
-test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
-\]
- is defined. 
-\item All configurations on $test_{i}$ are simulated.
-\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
-\[
-\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
-\]
-
-\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
-of%
-\footnote{The innovation score is not given to those points in $test_{i}$ that
-are not in the Pareto set%
-} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
-}defined as:
-\[
-is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
-\]
- (a configuration $\mathbf{p}$ is characterized by as much innovation
-as more separated it is from the configurations of the previous era)\@.
-\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
-as:
-\[
-is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
-\]
-
-\item The total innovation score for the entire era is:
-\[
-is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
-\]
-
-\item The avarage innovation score for the entire era is also calculated
-as:
-\[
-is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
-\]
-where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
-era $i$ .
-\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
-will be discussed later):
-
-\begin{enumerate}
-\item high innovation regions 
-\[
-\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
-\]
- where $\alpha$ is a constant defined by the designer (for example
-$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
-(as stated in def \ref{pers02.def:Splitting-a-region})
-\item low innovation regions 
-\[
-\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
-\]
-They are not changed.
-\item no innovation regions 
-\[
-\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
-\]
-
-\end{enumerate}
-\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
-with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
-couples is indicated as $\mathcal{C}$. The couples of regions are
-merged:
-\[
-\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
-\]
- (see def \ref{pers02.def:Merging-regions})
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
-as:
-\[
-\mathcal{R}_{i+1}=
-\]
-\[
-=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
-\]
-\[
-\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
-\]
-\[
-\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
-\]
-
-\end{enumerate}
-
-\paragraph{TERMINATION CONDITION}
-\begin{itemize}
-\item The algorithm terminates at step $k$ if
-\[
-is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
-\]
- where $\beta$ and $\gamma$ are selected by the experimenter (see
-remark \ref{rem:termination}).\end{itemize}
-\begin{rem}
-\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
-the iteration rules says that the smaller is a region, the more ``crowded''
-it is. It means that configurations in smaller regions are evaluated
-with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/small_and_big}
-
-\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
-are evaluated in a small region and in a bigger region. In can be
-seen that smaller region is more crowded.}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
-a configuration whose objectives are more ``separated'' by the previous
-Pareto front, has to be taken in greater account than others. A configuration
-that is very near, in the objective space, to the previous Pareto
-front doesn't add a true innovation. Therefore, the innovation score
-of a configuration is a measure of how much interest we have in considering
-it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/novelty_score}
-
-\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
-configuration}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The innovation score of a region is a measure of how much different
-are the points that it adds to Pareto Front compared to the previous
-Pareto front. ``High innovation regions'' are the ones in which
-more configurations are worth evaluating, because they add many points
-on not yet well explored Pareto front areas. Therefore, these regions
-are split in the next era (see remark \ref{pers02.rem:smaller_regions})
-and more ``crowded'' by simulations. ``No innovation regions''
-are the ones that have proved to add few points on Pareto fronts,
-probably very near to previous Pareto front points and a Pareto front
-point near to previous points is not so much interesting. Therefore
-it's not worth evaluating many of their configurations and it is useful
-to merge these regions , in order to less densely evaluate them.
-
-ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
-DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
-\end{rem}
-
-\begin{rem}
-\label{rem:termination}The algorithm terminates when in the last
-$\beta$ iterations not a great ``amount of innovation'' has been
-discovered. Therefore it is very probably that carrying on iterating
-will not considerably change the Pareto front already formed. It's
-not recommended to chose $\beta=1$, because it is possible that the
-Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
-are not very different but next Pareto fronts could be. In other words,
-it's unsafe to terminate as soon as the Pareto front doesn't change
-enough, passing from an era to the next. It's better taking into account
-more than one era.
-\end{rem}
-!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
-FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
-
-\begin{rem}
-Merging and splitting the regions are very dynamic processes. A portion
-of the parameter space can be populated by a large number of small
-regions in some eras, but can be covered by a small number of large
-regions in next eras. This can be explained saying that, after a number
-of eras of intense exploration of a portion of parameter space, this
-exploration has turned to be enough thorough and so it was time for
-other portions to be minutely scanned.
-\end{rem}
-
-\section{Experiments}
-
-\section{Conclusions}
-This is the end
-
-\balance
-
-\bibliographystyle{IEEEtran} 
-\bibliography{bibliography}
-
-% TODO: G2012 bib not used ?
-
-\end{document}

### 2013-09-25 paper.tex
splitted sections

@@
 \begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing
+DSE, VLIW, MultiObjective
 \end{IEEEkeywords}
 %------------------------------------------------------------------------------
-\section{Introduction}
-
-The design of an embedded system requires several objectives (energy
-consumption, area occupation, ...) to be fulfilled. The fulfilling
-of these objectives depends on several parameters and in the real
-cases no analytical results are known to show the relation between
-configurations (combination of parameters) and objectives. Therefore
-the simulation is the only way to have a picture of how parameters
-impact on the objectives. The problem is that the number of parameters
-and the number of values that each of them may take lead to an enormous
-number of possible configurations, such that simulating all of them
-is an unfeasible activity. Therefore there is the need for the ``Design
-Space Exploration'', i.e. a methodology to select a subset of all
-possible configurations and simulate only this subset.
-
-Many different design space exploration algorithms have been proposed.
-A design space exploration algorithm is typically not based on precise
-/ analytical / mathematical evidences. The motivations of an exploration
-algorithm are rather heuristic, have some form of arbitrariness and,
-to a large extend, intuition lies behind them.
-
-The result of every design space exploration is a subset of the configurations
-called Pareto Set (\cite{pareto}). Roughly speaking, it is a set of
-configurations such that there are no other configurations, among
-the simulated ones, that have all the objectives, at the same time,
-better fulfilled. If all possible configurations were evaluated, the
-ideal Pareto set (the ``true'' Pareto set) could be calculated.
-But, as stated above, evaluating all the configurations is not feasable.
-Therefore the Pareto set returned by an exploration algorithm is an
-approximation of the ``true'' Pareto set.
-
-Many exploration algorithms form the resulting Pareto set in an incremental
-way. The algorithm adds and removes configurations in Pareto set while
-choosing the configurations to evaluate and simulating them. So Pareto
-set ``evolves'' towards the final one. The dynamical view of the
-Pareto set shaping can be seen as the ``behavior'' of the algorithm.
-This behavior tells us how the Pareto set ``converges'' towards
-the final Pareto set.
-
-The ``quality'' of an exploration algorithm involves two aspects:
-\begin{itemize}
-\item how much the Pareto set returned by the exploration algorithm is similar
-to the ``true'' Pareto set (notice that this cannot be evaluated
-because the true Pareto set is unknown - it is only an ``ideal''
-quality factor)
-\item how fast the Pareto set converges towards the final one. If algorithm
-$1$ returns the final Pareto set after simulating $n_{1}$ configurations
-and algorithm $2$ returns its final Pareto set after $n_{2}$ simulations,
-algorithm $1$ is said to be faster than algorithm $2$, iff $n_{1}<n_{2}$.
-\end{itemize}
-
-\section{\label{sec:Related-work}Related work}
-
-There are a number of design space exploration algorithms proposed
-in literature.
-
-The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
-to take advantage of the dependency among the parameters in a multiobjective
-optimization problem. It is required that the designer knows, prior
-to the exploration, if a parameter X is dependent from a parameter
-Y, i.e. changing the value of Y ``impacts the optimal parameter value''
-for X. With this a-priori knowledge, the designer can construct a
-``dependency graph'' and recognize clusters, i.e. subsets of strongly
-dependency-connected parameters. Each cluster is exhaustively evaluated
-and its ``local Pareto set'' is found. Then, all local Pareto sets
-are merged. Doing this way, a ``sum'' of local exhaustive evaluations
-are performed instead of an exhaustive evaluation of all the possible
-configurations. Some problems arise: i) In real scenarios, it may
-be very difficult to recognize really independent clusters of parameters,
-because there may be interdependencies among a very large number of
-parameters. This may lead to the need of an exhaustive search through
-almost all the possible configurations. ii) A designer may not have
-a precise and complete picture of the dependencies among parameters;
-for this reason the need of ``automated approaches for computing
-{[}...{]} interdependencies'' is declared in the same paper. iii)
-There may be some ``local dependencies'', i.e. dependencies that
-emerge only if parameter values are bounded to certain ranges.
-
-These drawbacks are not present in our solution. The algorithm presented
-here is also meant to take advantage of dependency but is not directly
-based on dependency itself, but rather it ``catches'' dependencies
-in terms of ``interesting or uninteresting regions''; as a consequence
-no a-priori knowledge of dependencies is required as they are discovered
-during exploration. Moreover, recognizing regions offers the capability
-to capture local dependencies.
-
-Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
-the system to be evaluated into components that interact minimally
-with each other. ``Alternative designs for each component are evaluated
-in isolation to determine the best designs for individual components.
-Combinations of these designs are then put together to build the complete
-system design''. Pareto sets for each component are found and, provided
-that ``monotonicity'' exists, the complete Pareto set is computed
-merging the component Pareto sets. Roughly speaking (see section 4
-of the same paper for more details), monotonicity property guarantees
-that the best system can be obtained as a composition of the best
-components. This approach would perfectly work if all the components
-were perfectly isolated, i.e., if there were no dependencies among
-different components (in a sense similar (but not necesarily equal)
-to the one of Dependency analisys). But real scenarios seldom if ever
-expose monotonicity property. This leads to some ``inaccuracies''
-(as stated in section 4.6.1 of the same paper).
-
-Other approaches take into account the concept of ``sensitivity''.
-The sensitivity of an objective with the respect to a parameter is
-a measure of how much the objective varies when varying that parameter.
-A ``sensitivity analysis'' was used in \cite{fornaciari_codes01} in an optimization
-problem with only one objective (the power-delay product of an electronic
-device). This method was extended in \cite{palesi_iwsoc02} to a multiobjective
-optimization. In that work the sensitivity of objectives with
-the respect to each parameter is measured, and parameters are ordered
-on the base on these sensitivity measures. Then, a first Pareto set
-is obtained varying the first parameter, having fixed to arbitrary
-values all other parameters. The Pareto set is then refined varying,
-in a similar way, the other parameters, one by one. Experimental results
-(see section 4.2 of the same work) show that this method is not of
-good ``quality'' (as broadly defined in the introduction). The reason
-can be found in the very limited and rigid exploration of the parameter
-space: after computing the first Pareto set, there are no more chances
-to consider configurations with values of the first parameter other
-than the ones assumed in the first Pareto set calculation. Similar
-limitations are imposed after computing the second Pareto set, the
-third and so on. It is worth noticing that this approach can not capture
-``local sensitivity'' (this drawback will be called ``local sensitivity
-limitation''), i.e. the objectives may be more sensitive to some
-ranges of a parameter and less sensitive to other ranges of the same
-parameter. Moreover it can not capture ``combined sensitivity''
-(``combined sensitivity limitation''), i.e. the objectives may be
-more sensitive to a range of a parameter $p_{1}$, only when other
-parameters are within certain ranges, and less sensitive to the same
-range of parameter $p_{1}$ when the other parameters are not within
-those ranges. Therefore, in the method we propose, we do not use the
-sensitivity directly, but we use the concept of innovation (that can
-be considered, at least weakly related to the sensitivity). We do
-not measure innovation of a parameter (as done for the sensitivity),
-but rather we measure the innovation of a ``region'' of parameter
-space, in order to overcome both the ``local sensitivity limitation''
-and the ``combined sensitivity limitation'' stated above for the
-sensitivity analysis.
-
-Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{} and others). Genetic approaches
-have many advantages: they have proved good quality (as broadly defined
-in the introduction), they are customizable, they are very general
-and require no a-priori knowledge to the designer. Genetic algorithms
-run in subsequent iterations. Configurations are represented as chromosomes.
-In each iteration a ``population'' of configurations is evaluated.
-Some configurations are discarded. Each selected configuration is
-combined with the preceding population and then ``mutated'' (i.e.
-the resulting configuration is varied a little). Iterating this operations,
-populations are expected to become ``better and better''. The strong
-point of genetic approaches can be summarized saying that they consist
-in a broad exploration (the mutation permits to make the exploration
-not rigidly restricted to limited parts of parameter space), although
-this exploration is not random but is guided by the performances of
-the already evaluated configurations. Therefore, the exploration is
-neither too much constrained nor too much random. We claim that the
-approach presented in this paper has all the benefits of the genetic
-approaches, although the rational is completely different.
-
-\section{Preliminaries}
-
-\subsection{Representation}
-\begin{defn}
-\emph{Configuration}
-
-Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
-of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
-may assume. A configuration is a vector
-\[
-\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-\begin{defn}
-\emph{Objective function}
-
-Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
-values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
-operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
-we can always say:
-\[
-o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
-\]
-
-$o_{i}$ can be viewed as a function
-\[
-o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
- To take into account all of the objectives, the following function
-is defined:
-\[
-\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
-
-\end{defn}
-
-{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
-\begin{defn}
-\emph{\label{pers02.def:Pareto-set}Pareto set}
-
-Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
-configurations is:
-\[
-Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
-\]
-
-Its Pareto set is defined as:
-\[
-\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
-\]
-
-When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
-\end{defn}
-
-\begin{defn}
-\emph{Pareto front}
-
-The Pareto front is the representation in the objective space of the
-Pareto set, i.e.:
-\[
-\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
-\]
-
-\end{defn}
-On the contrary, we call ``parameter space representation'' of the
-Pareto set the representation in which each configuration $\mathbf{p}$
-is simply represented as a point of $P_{1}\times\dots\times P_{n}$
-space. We will investigate the relation between the ``objective space
-representation'' and the ``parameter space representation''. We
-are particularly interested in the relation between the evolution
-of the objective space representation of the Pareto set and the evolution
-of its parameter space representation.
-
-!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
-PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
-DELLA TRATTAZIONE
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}
-
-\caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'')}
-
-\end{figure}
-
-\subsection{Regions}
-
-In the design process, there are often a lot of ``local decisions''
-in which the designer can take advantage of well-known results or
-heuristics. For example, in a VLIW architecture consider a configuration
-with very few registers. It is well-known that, in such a condition,
-increasing the number of ALUs doesn't lead to tangible better performances
-but leads to an increase in area occupation. An intelligent exploration
-algorithm wouldn't waste time evaluating configurations with many
-ALUs and few registers. If $p_{1}$ is the parameter ``number of
-registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
-can say that the region:
-\[
-R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
-\]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
-interest. This example shows that some ``dependency relation'' between
-parameters may exist and can be exploited to guide the exploration:
-the dependencies between parameters can suggest to the designer that,
-if a parameter lies in a range, there are ranges of the other there
-aren't worth exploring. Intuitively, the Cartesian product of these
-ranges is an ``uninteresting region''.
-
-The problem is that, in complex scenarios, not all relations of this
-kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or there may be ``local dependencies'', i.e. two
-parameters may be related by a dependency but only if their values
-lie on some ranges (so we can't treat them as they were related by
-a true dependency). Therefore, as stated in section \ref{sec:Related-work},
-setting up an exploration trying to take into account as much dependencies
-as possible is a very hard task that is destined to be incompletely
-accomplished. We need a methodology to ``automatically'' recognize
-interesting or uninteresting regions without requiring a priori knowledge
-to the designer.
-
-We also consider, in measuring how much iteresting a region is, the
-``innovation'' that it adds. If, during a design space exploration,
-a Pareto front is temporarily calculated, adding a new Pareto front
-point near to the previous ones is not a considerable ``innovation'',
-because the way it fulfils the objectives is very similar to other
-already evaluated configurations. On the contrary, adding a new Pareto
-front point that is very distant from previous ones is remarkable,
-because it let the experimenter realize that the objectives can be
-fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated ineresting as much
-as how different are its added Pareto front points from the ones already
-found.
-\begin{rem}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{rem}
-{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-PARAMETRI SENZA ORDINAMENTO{]}
-\begin{defn}
-\emph{Parameter interval}
-
-Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
-A $p_{i}$- interval is
-\[
-\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
-\]
- (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
-is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
-\end{defn}
-
-\begin{defn}
-\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}
-
-Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous iff
-\begin{itemize}
-\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
-and
-\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
-interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
-is a $p_{i}$- interval
-\end{itemize}
-\end{defn}
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}
-
-\caption{Examples of contiguous and not contiguous intervals}
-
-\end{figure}
-
-\begin{defn}
-\emph{Region}
-
-A region is a set of the following form:
-\[
-R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
-\]
- (see figure \ref{pers02.fig:Examples-of-regions})
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/regions}
-
-\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}
-
-\end{figure}
-\end{defn}
-\begin{rem}
-We will talk later of ``big'' and ``small'' regions. The sense
-of these terms is related to the cardinality of regions. A region
-$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
-\[
-\left|R_{1}\right|>\left|R_{2}\right|
-\]
- where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
-of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-if:
-\[
-\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
-\]
-
-Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{rem}
-We now provide some rules to split and merge regions. They will be
-useful when explaining our proposed exploration algorithm.
-\begin{defn}
-\emph{\label{pers02.def:Splitting-a-region}Splitting a region}
-
-If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
-it can be split in two contiguous intervals
-\[
-\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
-\]
- such that
-\[
-\begin{cases}
-\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
-\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
-\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
-\end{cases}
-\]
-
-If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
-cannot be split.
-
-If $\left[a_{i}..b_{i}\right]$ can be split, we define
-\[
-I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
-\]
- else
-\[
-I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
-\]
-
-The whole region can be split in the following subregions
-\[
-\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
-\]
-
-See figure \ref{pers02.fig:Splitting-a-region}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}
-
-\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}
-
-\end{figure}
-
-\end{defn}
-
-\begin{defn}
-\emph{Contiguous regions}
-
-Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff
-\begin{itemize}
-\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
-for all $i\neq j$ 
-\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
-contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
-\end{itemize}
-\end{defn}
-See figure \ref{pers02.fig:Contiguous-regions}.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}
-
-\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
-regions}
-\end{figure}
-
-\begin{defn}
-\emph{\label{pers02.def:Merging-regions}Merging regions}
-
-Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
-ones. Because of the definition of contiguous intervals, it is possible
-that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
-intervals and obtain a new interval, as the following
-\[
-\left[t_{j},z_{j}\right]=\begin{cases}
-\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
-\end{cases}
-\]
-
-The region ``$R_{1}$ merged with $R_{2}$'' is defined as
-\[
-R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
-\]
-
-Such an $R$ will be indicated with the following notation:
-\[
-R=R_{1}+R_{2}
-\]
-\end{defn}
-\begin{rem}
-$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
-However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiuguous regions.
-\end{rem}
-
-\begin{defn}
-\emph{Separation}
-
-Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
-be two points of $O_{1}\times\dots\times O_{m}$. The separation between
-$\mathbf{o}$ and $\mathbf{q}$ is 
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-Notice that the separation is not a commutative operator.\end{defn}
-\begin{rem}
-The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
-The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives
-\end{rem}
-
-\begin{defn}
-\emph{Separation (alternative)}
-
-Another definition of separation could be:
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-\end{defn}
-
-\section{The algorithm}
-
-The algorithm we present is iterative. Each iteration is called \emph{era}.
-
-Each era $era_{i}$ is characterized by 
-\begin{itemize}
-\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
-$P_{1}\times\dots\times P_{n}$ is divided
-\item its Pareto set $\mathscr{P}_{i}$
-\item a set $test_{i}$ of at most $K$ configurations to evaluate
-\end{itemize}
-$K$ is a parameter that must be set before the algorithm runs.
-
-\paragraph{START CONDITION}
-\begin{itemize}
-\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
-i.e. era $0$ has only one region that is the whole parameter space.
-A random set $test_{0}$ of $K$ configurations is evaluated. The
-Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
-calculated (see def \ref{pers02.def:Pareto-set} for the definition
-of the operator $\mathscr{P}_{i}$ over a set)
-\end{itemize}
-
-\paragraph{ITERATION RULES}
-
-For $era_{i}$ with $i>0$ the following operations must be performed.
-\begin{enumerate}
-\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
-$test_{R,i}$ of configurations is randomly chosen in%
-\footnote{Therefore the chosen configurations can only be configurations of
-$R$ not yet evaluated in past eras.%
-} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
-in $test_{R,i}$ is set to%
-\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
-are to be chosen, but if not yet evaluated configurations in $R$
-are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
-are chosen%
-} 
-\[
-\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
-\]
-The set 
-\[
-test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
-\]
- is defined. 
-\item All configurations on $test_{i}$ are simulated.
-\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
-\[
-\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
-\]
-
-\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
-of%
-\footnote{The innovation score is not given to those points in $test_{i}$ that
-are not in the Pareto set%
-} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
-}defined as:
-\[
-is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
-\]
- (a configuration $\mathbf{p}$ is characterized by as much innovation
-as more separated it is from the configurations of the previous era)\@.
-\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
-as:
-\[
-is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
-\]
-
-\item The total innovation score for the entire era is:
-\[
-is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
-\]
-
-\item The avarage innovation score for the entire era is also calculated
-as:
-\[
-is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
-\]
-where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
-era $i$ .
-\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
-will be discussed later):
-
-\begin{enumerate}
-\item high innovation regions 
-\[
-\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
-\]
- where $\alpha$ is a constant defined by the designer (for example
-$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
-(as stated in def \ref{pers02.def:Splitting-a-region})
-\item low innovation regions 
-\[
-\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
-\]
-They are not changed.
-\item no innovation regions 
-\[
-\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
-\]
-
-\end{enumerate}
-\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
-with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
-couples is indicated as $\mathcal{C}$. The couples of regions are
-merged:
-\[
-\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
-\]
- (see def \ref{pers02.def:Merging-regions})
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
-as:
-\[
-\mathcal{R}_{i+1}=
-\]
-\[
-=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
-\]
-\[
-\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
-\]
-\[
-\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
-\]
-
-\end{enumerate}
-
-\paragraph{TERMINATION CONDITION}
-\begin{itemize}
-\item The algorithm terminates at step $k$ if
-\[
-is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
-\]
- where $\beta$ and $\gamma$ are selected by the experimenter (see
-remark \ref{rem:termination}).\end{itemize}
-\begin{rem}
-\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
-the iteration rules says that the smaller is a region, the more ``crowded''
-it is. It means that configurations in smaller regions are evaluated
-with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/small_and_big}
-
-\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
-are evaluated in a small region and in a bigger region. In can be
-seen that smaller region is more crowded.}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
-a configuration whose objectives are more ``separated'' by the previous
-Pareto front, has to be taken in greater account than others. A configuration
-that is very near, in the objective space, to the previous Pareto
-front doesn't add a true innovation. Therefore, the innovation score
-of a configuration is a measure of how much interest we have in considering
-it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/novelty_score}
-
-\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
-configuration}
-
-\end{figure}
-
-\end{rem}
-
-\begin{rem}
-The innovation score of a region is a measure of how much different
-are the points that it adds to Pareto Front compared to the previous
-Pareto front. ``High innovation regions'' are the ones in which
-more configurations are worth evaluating, because they add many points
-on not yet well explored Pareto front areas. Therefore, these regions
-are split in the next era (see remark \ref{pers02.rem:smaller_regions})
-and more ``crowded'' by simulations. ``No innovation regions''
-are the ones that have proved to add few points on Pareto fronts,
-probably very near to previous Pareto front points and a Pareto front
-point near to previous points is not so much interesting. Therefore
-it's not worth evaluating many of their configurations and it is useful
-to merge these regions , in order to less densely evaluate them.
-
-ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
-DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
-\end{rem}
-
-\begin{rem}
-\label{rem:termination}The algorithm terminates when in the last
-$\beta$ iterations not a great ``amount of innovation'' has been
-discovered. Therefore it is very probably that carrying on iterating
-will not considerably change the Pareto front already formed. It's
-not recommended to chose $\beta=1$, because it is possible that the
-Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
-are not very different but next Pareto fronts could be. In other words,
-it's unsafe to terminate as soon as the Pareto front doesn't change
-enough, passing from an era to the next. It's better taking into account
-more than one era.
-\end{rem}
-!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
-FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
-
-\begin{rem}
-Merging and splitting the regions are very dynamic processes. A portion
-of the parameter space can be populated by a large number of small
-regions in some eras, but can be covered by a small number of large
-regions in next eras. This can be explained saying that, after a number
-of eras of intense exploration of a portion of parameter space, this
-exploration has turned to be enough thorough and so it was time for
-other portions to be minutely scanned.
-\end{rem}
-
-\section{Experiments}
+\input{introduction.tex}
+\input{concepts.tex}
+\input{experiments.tex}
+%------------------------------------------------------------------------------
 

### 2013-09-26 concepts.tex
commented comments

@@
 
-{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
+%{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
 \begin{defn}
@@
 of its parameter space representation.
-
-!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
-PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
-DELLA TRATTAZIONE
 
@@
 \end{rem}
-{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-PARAMETRI SENZA ORDINAMENTO{]}
+%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
+%PARAMETRI SENZA ORDINAMENTO{]}
 \begin{defn}

### 2013-09-26 concepts.tex
new formal definition of the problem

@@
-\section{Preliminaries}
+\section{Preliminary Concepts}
 
-\subsection{Representation}
-\begin{defn}
-\emph{Configuration}
+\subsection{Formulation of the Problem}
 
-Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
-of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
-may assume. A configuration is a vector
-\[
-\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
-\]
+\label{sec:statement_of_the_problem}\index{DSE}
 
-\end{defn}
+Let $S$ be a parameterized system with $n$ parameters. The generic
+parameter $p_i, \ i \in \{1,2,\ldots,n\}$ can take any value in
+the set $V_i$. A {\em configuration} $\mathbf{c}$ of the system
+$S$ is a $n$-tuple $\langle v_1,v_2,\ldots,v_n \rangle$ in which
+$v_i \in V_i$ is the value fixed for the parameter $p_i$. The {\em
+configuration space} (or {\em design space}) of $S$ [which we will
+indicate as $\mathcal{C}(S)$] is the complete range of possible
+configurations [$\mathcal{C}(S) = V_1 \times V_2 \times \ldots
+\times V_n$]. Naturally not all the configurations of
+$\mathcal{C}(S)$ can really be mapped on $S$. We will call the set
+of configurations that can be physically mapped on $S$ the {\em
+feasible configuration space} of $S$ [and indicate it as
+$\mathcal{C}^*(S)$].
 
-\begin{defn}
-\emph{Objective function}
+Let $m$ be the number of objectives to be optimized (e.g. power,
+cost, performance, etc.). An {\em evaluation function}
+$E:\mathcal{C}^*(S)\times \mathcal{B} \longrightarrow \Re^m$ is a
+function that associates each feasible configuration of $S$ with
+an $m$-tuple of values corresponding to the objectives to be
+optimized when any application belonging to the set of benchmarks
+$\mathcal{B}$ is executed.
 
-Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
-values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
-operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
-we can always say:
-\[
-o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
-\]
- or
-\[
-o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
-\]
+Given a system $S$, an application $b \in \mathcal{B}$ and two
+configurations $\mathbf{c}', \mathbf{c}'' \in \mathcal{C}^*(S)$,
+$\mathbf{c}'$ is said to {\em dominate} (or {\em eclipse})
+$\mathbf{c}''$, and is indicated as $\mathbf{c}' \succ
+\mathbf{c}''$, if given $\mathbf{o}'=E(\mathbf{c}', b)$ and
+$\mathbf{o}''=E(\mathbf{c}'', b)$ it results that $\mathbf{o}'
+\leq \mathbf{o}''$ and $\mathbf{o}' \neq \mathbf{o}''$. Where
+vector comparisons are interpreted component-wise and are true
+only if all of the individual comparisons are true ($o'_i \leq
+o''_i \ \forall \ i = 1,2,\ldots,m$).
 
-$o_{i}$ can be viewed as a function
-\[
-o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
- To take into account all of the objectives, the following function
-is defined:
-\[
-\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
-\]
+The {\em Pareto-optimal set} of $S$ for the application $b$ is the
+set:
+\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
+that is, the set of configurations $\mathbf{c} \in
+\mathcal{C}^*(S)$ not dominated by any other configuration.
+Pareto-optimal configurations are configurations belonging to the
+Pareto-optimal set and the {\em Pareto-optimal front} is the image
+of the Pareto-optimal configurations, i.e. the set:
+\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
 
-\end{defn}
+The aim of a Design Space Exploration (DSE) strategy is to give a
+good approximation of the Pareto-optimal front for a system $S$ and an
+application $b$, simulating as few configurations as possible.
 
-%{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
-\begin{defn}
-\emph{\label{pers02.def:Pareto-set}Pareto set}
+%----------------------------------------------------------------
 
-Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
-configurations is:
-\[
-Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
-\]
-
-Its Pareto set is defined as:
-\[
-\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
-\]
-
-When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
-\end{defn}
-
-\begin{defn}
-\emph{Pareto front}
-
-The Pareto front is the representation in the objective space of the
-Pareto set, i.e.:
-\[
-\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
-\]
-
-\end{defn}
 On the contrary, we call ``parameter space representation'' of the
@@
 
-\subsection{Regions}
+\subsection{Required Definitions and Concepts}
 

### 2013-09-26 algorithm.tex
Cleaning lists

@@
 
-\paragraph{START CONDITION}
-\begin{itemize}
-\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
+\subsection{Start Condition}
+$\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
 i.e. era $0$ has only one region that is the whole parameter space.
@@
 of the operator $\mathscr{P}_{i}$ over a set)
-\end{itemize}
 
-\paragraph{ITERATION RULES}
+\subsection{Iteration Rules}
 
@@
 \]
+\end{enumerate}
 
-\end{enumerate}
 \item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
@@
 
-\paragraph{TERMINATION CONDITION}
-\begin{itemize}
-\item The algorithm terminates at step $k$ if
+\subsection{Termination Condition}
+The algorithm terminates at step $k$ if
 \[
@@
  where $\beta$ and $\gamma$ are selected by the experimenter (see
-remark \ref{rem:termination}).\end{itemize}
+remark \ref{rem:termination}).
 \begin{rem}

### 2014-03-25 experiments.tex
Added draft of experiments section

\section{A Case Study: VLIW Hardware/Software Design Space}
\label{sec:ee}
In this subsection we evaluating the behavior of the proposed approach
using a parameterized Very Long Instruction
Word (VLIW) architecture~\cite{kathail_tr00} as a testbed. The same philosophy
behind a VLIW system makes it a natural choice for several reasons:
\begin{itemize}
\item{Multi-Objective trade-offs}: these architectures let designers
easily trade between power, energy and performances~\cite{}, leading
to Pareto sets whose extension is an ideal ground for testing the
proposed Parameters space representation.
\item{Compiler awareness}: Instruction Level Parallelism (ILP)
constitutes the key feature to enable the multi-objective trade-offs
of the point above. It is statically obtained by the compiler which
performs code trasformations being aware of the underlying hardware
configuration.  This tight hardware/software dependence, makes the
VLIW scenario more suitable for investigating hardly predictable
hardware/software interactions, especially when compared to
architectures where, in order to preserve binary compatibility,
software generation processes are independent from the hardware that
will execute it.

System parameters can be classified in three main categories:
\emph{processor}, \emph{memory sub-system} and \emph{compiling options}. 
The first is directly related to the VLIW core and includes the size
of the register files and the number of functional
units for each type of opera. In particular, five different types of register files can be identified:
GPR (32-bit registers for integers), FPR (64-bit registers for
floating point values) PR (1-bit registers used to store the Boolean
values of predicated instructions), BTR (64-bit registers containing
information about possible future branches) and CR (32-bit control
registers containing information about the internal state of the
processor). The functional units involved are: \emph{Integer units},
\emph{floating point units}, \emph{memory units} (associated with
load/store operations) and \emph{branch units} (associated with branch
operations). With respect to the memory sub-system, the parameters
include \emph{size}, \emph{associativity} and
\emph{block size} for each of the three caches: First-level data cache
(L1D), first-level instruction cache (L1I) and second-level unified
cache (L2U).

Further, a set of the most impacting compilation parameters has been
selected and included in the configuration space:
\begin{itemize}
\item{tcc\_region}: Specifies the scope of action of the compiler and the type
of code transformation involved (basic block, super block and hyper
block) 
\item {max\_unroll\_allowed}: The number of unroll iterations allowed
\item{regroup\_only}: Avoids inlining 
\item{do\_classic\_opti}: A set of classical optimization, not VLIW related,
such as common expression removal 
\item{do\_prepass\_scalar\_scheduling}: Performs a schedule before
forming regions 
\item{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
do\_modulo\_scheduling & Modular scheduling 
\item{memvr\_profiled}: Performs a memory-dependencies profiling 
\end{itemize}

\subsection{Evaluation Metrics}

The results presented in the next section compare PS against a widely
adpted Multi-objective Genetic Algorithm~\cite{}. At best of our
knowledge, genetic approaches
still represent the best compromise between efficiency (i.e. time
required for exploration) and accuracy of the reported Paret Sets. Of
course mono-objective approaches have been
deliberately excluded from this analysis. Other
approaches~\cite{dep} that make use of some a-priori knowledge about the
role and meaning of each parameter have been also excluded, since our
aim is evaluate the capacity of the strategy to focus on interesting
parameter regions without any external judgement or help based on
euristics.  Finally, it should be pointed
out that in this introductory work we explicitly focus on TODO
remainding to works like~\cite{} for a detailed analysis of other
similar multi-objective strategies.

The class of benchmark being considered is representative of some common
frequently running application kernels in an embedded multimedia
environment. Table~\ref{tab:bench} shows the set of applications
chosen along with a brief description.
\begin{table}
	\centering
	\caption{Benchmarks}
	\label{tab:bench}
	\begin{tabular}{ll}
	\hline
	\multicolumn{1}{c}{Benchmark} & \multicolumn{1}{c}{Application} \\
	\hline
	Alloca\_test & Memory array allocation test \\
	Bmm & Matrices multiplication and elements sum \\
	Fir\_int & Finite impulse response \\
	Fib & Fibonacci series \\
	Mm & Floating point matrices multiplication \\
	Wave & Wavefront computation \\
	\hline
	\end{tabular}
\end{table}
%------------------------------------------------------------------------------

\section{Results}

Each data set is obtained evaluation a 1,000 randomly chosen point of
the configuration space. In particular, two different scenarios have
been considered: the first one, referred as \emph{Variable Compilation
Profile (VCP)}, includes all compilation parameters described
in the Table~\ref{tab:compiler}; a second scenario, \emph{Fixed
Compilation Profile (FCP)}, which excludes any of those parameters
exploring all the remaining hardware aspects of the architecture as
described in Section~\ref{subsec:arch}.

Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
respectively show the visited configurations and the
Pareto fronts found for both FCP and VCP scenarios for different
application benchmarks. How it can be observed, VCP solutions
are on average  more widely and evenly distributed over the objective
space as compared to those found for the FCP case.

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{pictures/100bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fir_int.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/100mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fib.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/100alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/100wave.eps}
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
  \label{fig:pareto_fronts_100}
\end{figure}

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{pictures/bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fir_int.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fib.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/wave.eps}
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
  \label{fig:pareto_fronts}
\end{figure}

Let us now analyse the Pareto fronts from a quantitative viewpoint. We
consider two metrics, namely, the \emph{variation range} and the
\emph{average normalised absolute dispersion error}. For a given
objective, the variation range represents the ratio between the
maximum and the minimum value observed for that objective. A
comparison between the variation range for different benchmarks
between a FCP and a VCP exploration for both power dissipation and
execution time is shown in Fig.~\ref{fig:variation_range}. As it can
be observed, the VCP exploration provides solutions which fall on a
range that is, on average, 23\% and 40\% wider than that provided by a
FCP exploration for power dissipation and execution time,
respectively.
\begin{figure}
  \centering
  \begin{tabular}{c}
    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps}
  \end{tabular}
  \caption{Variation range for different benchmarks between a FCP and
    a VCP exploration for power dissipation and execution time.}
  \label{fig:variation_range}
\end{figure}

The average normalised absolute dispersion error measures
the average absolute difference between the distribution of points in
the objective space and an ideal distribution in which the points are
uniformly distributed over the objective space. Formally, let $O$ be
the image, in the objective space, of the configurations visited by
the design space exploration. The generic element of $O$ (\ie, a
solution) is a pair $(p,t)$ where $p$ and $t$ are the average power
and execution time, respectively. The two-dimensional objective space
is then partitioned by a $M_x \times M_y$ mesh. For each tile $T_i,
\ i=1, 2, \ldots, M_xM_y$ of the mesh, let $N_i$ be the number
of points in $O$ which fall in $T_i$. The average absolute error, $E_i$, for
$T_i$ is the absolute value of the difference between $N_i$ and the
ideal number of solutions, $\overline{N}$, which should fall in $T_i$
in case of uniform distribution. Such $\overline{N}$ can be simply
computed as the ratio between the cardinality of $O$ and the number of
tiles. Thus,
\[ E_i = |N_i - \overline{N}|, \]
where $\overline{N} = |O| / (M_x M_y)$. The average
normalised absolute dispersion error ($ANADE$) is the average of $E_i$
normalised to the maximum absolute error $E_{max}$:
\[ ANADE = \frac{\sum_{i=1}^{M_xM_y} E_i/(M_xM_y)}{E_{max}}, \]
where $E_{max}$ can be computed as the average absolute error in the worst
case in which all the solutions fall in a single tile:
\[ E_{max} = \frac{(M_x M_y - 1) \overline{N} + |\overline{N} -
    |O|| }{M_x M_y}. \]

Fig.~\ref{fig:dispersion} shows the average normalised absolute
dispersion errors for different benchmarks for FCP and VCP
exploration. As it can be observed, VCP exploration reduces the
dispersion error on average by 20\% as compared to a FCP exporation.
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
  \caption{Average normalised absolute dispersion errors for different
    benchmarks for FCP and VCP exploration.}
  \label{fig:dispersion}
\end{figure}

### 2014-03-28 TEST/sha/src/sha256_example.c
sha256

@@ -1,0 +1,197 @@
+#include <stdio.h>
+
+// Signed variables are for wimps 
+#define uchar unsigned char // 8-bit byte
+#define uint unsigned long // 32-bit word
+
+// DBL_INT_ADD treats two unsigned ints a and b as one 64-bit integer and adds c to it
+#define DBL_INT_ADD(a,b,c) if (a > 0xffffffff - (c)) ++b; a += c;
+#define ROTLEFT(a,b) (((a) << (b)) | ((a) >> (32-(b))))
+#define ROTRIGHT(a,b) (((a) >> (b)) | ((a) << (32-(b))))
+
+#define CH(x,y,z) (((x) & (y)) ^ (~(x) & (z)))
+#define MAJ(x,y,z) (((x) & (y)) ^ ((x) & (z)) ^ ((y) & (z)))
+#define EP0(x) (ROTRIGHT(x,2) ^ ROTRIGHT(x,13) ^ ROTRIGHT(x,22))
+#define EP1(x) (ROTRIGHT(x,6) ^ ROTRIGHT(x,11) ^ ROTRIGHT(x,25))
+#define SIG0(x) (ROTRIGHT(x,7) ^ ROTRIGHT(x,18) ^ ((x) >> 3))
+#define SIG1(x) (ROTRIGHT(x,17) ^ ROTRIGHT(x,19) ^ ((x) >> 10))
+
+typedef struct {
+   uchar data[64];
+   uint datalen;
+   uint bitlen[2];
+   uint state[8];
+} SHA256_CTX;
+
+uint k[64] = {
+   0x428a2f98,0x71374491,0xb5c0fbcf,0xe9b5dba5,0x3956c25b,0x59f111f1,0x923f82a4,0xab1c5ed5,
+   0xd807aa98,0x12835b01,0x243185be,0x550c7dc3,0x72be5d74,0x80deb1fe,0x9bdc06a7,0xc19bf174,
+   0xe49b69c1,0xefbe4786,0x0fc19dc6,0x240ca1cc,0x2de92c6f,0x4a7484aa,0x5cb0a9dc,0x76f988da,
+   0x983e5152,0xa831c66d,0xb00327c8,0xbf597fc7,0xc6e00bf3,0xd5a79147,0x06ca6351,0x14292967,
[…]

### 2014-04-29 experiments.tex
update exp

@@
 \label{sec:ee}
-In this subsection we evaluating the behavior of the proposed approach
-using a parameterized Very Long Instruction
-Word (VLIW) architecture~\cite{kathail_tr00} as a testbed. The same philosophy
-behind a VLIW system makes it a natural choice for several reasons:
+In order to evaluate the behavior of the proposed approach
+we will be using a parameterized Very Long Instruction
+Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The same philosophy
+behind a VLIW system makes this a natural choice for several reasons:
 \begin{itemize}
-\item{Multi-Objective trade-offs}: these architectures let designers
+\item{Multi-Objective trade-offs}: VLIW architectures let designers
 easily trade between power, energy and performances~\cite{}, leading
-to Pareto sets whose extension is an ideal ground for testing the
-proposed Parameters space representation.
+to Pareto sets whose extension is an ideal ground for our testing
+purposes focused on parameter-space space representation of Paretos.
 \item{Compiler awareness}: Instruction Level Parallelism (ILP)
-constitutes the key feature to enable the multi-objective trade-offs
+constitutes the key feature to enable the multi-objective trade offs
 of the point above. It is statically obtained by the compiler which
@@
 configuration.  This tight hardware/software dependence, makes the
-VLIW scenario more suitable for investigating hardly predictable
+VLIW scenario well suitable for investigating hardly predictable
 hardware/software interactions, especially when compared to
-architectures where, in order to preserve binary compatibility,
-software generation processes are independent from the hardware that
+architectures that, in order to preserve binary compatibility,
+separate software generation processes from the hardware that
 will execute it.
@@
 System parameters can be classified in three main categories:
-\emph{processor}, \emph{memory sub-system} and \emph{compiling options}. 
+\emph{processor}, \emph{memory sub-system} and \emph{compiler}. 
 The first is directly related to the VLIW core and includes the size
 of the register files and the number of functional
-units for each type of opera. In particular, five different types of register files can be identified:
+units for each type. In particular, five different types of register
+files are supported:
 GPR (32-bit registers for integers), FPR (64-bit registers for
@@
 
-Further, a set of the most impacting compilation parameters has been
+Next, a set of the most impacting code compilation parameters has been
 selected and included in the configuration space:
@@
 required for exploration) and accuracy of the reported Paret Sets. Of
-course mono-objective approaches have been
+course, mono-objective approaches have been
 deliberately excluded from this analysis. Other
@@
 role and meaning of each parameter have been also excluded, since our
-aim is evaluate the capacity of the strategy to focus on interesting
+aim is evaluate the capacity of focusing on interesting
 parameter regions without any external judgement or help based on
 euristics.  Finally, it should be pointed
-out that in this introductory work we explicitly focus on TODO
-remainding to works like~\cite{} for a detailed analysis of other
-similar multi-objective strategies.
+out that in this introductory work we will explicitly use the TODO
+variant of MOGA, remainding to works like~\cite{} for a detailed
+analysis on how it differs and what could be expected from similar multi-objective strategies.
 
@@
 	Fir\_int & Finite impulse response \\
-	Fib & Fibonacci series \\
 	Mm & Floating point matrices multiplication \\
+	Sha256 & Cryptocurrency header Hashing \\
 	Wave & Wavefront computation \\
@@
 
-\section{Results}
+\subsection{Results}
 
-Each data set is obtained evaluation a 1,000 randomly chosen point of
-the configuration space. In particular, two different scenarios have
-been considered: the first one, referred as \emph{Variable Compilation
-Profile (VCP)}, includes all compilation parameters described
-in the Table~\ref{tab:compiler}; a second scenario, \emph{Fixed
-Compilation Profile (FCP)}, which excludes any of those parameters
-exploring all the remaining hardware aspects of the architecture as
-described in Section~\ref{subsec:arch}.
+Set of Figures~\ref{fig:pareto_fronts_100}
+and~\ref{fig:pareto_fronts} show the resultig pareto fronts for two
+different scenarios of 100 and 500 simulations budget.
 
@@
 
-Let us now analyse the Pareto fronts from a quantitative viewpoint. We
-consider two metrics, namely, the \emph{variation range} and the
+In order to evaluate the Paretos from a quantitative point-of-view we
+will consider two metrics, namely, the \emph{variation range} and the
 \emph{average normalised absolute dispersion error}. For a given
@@
   \end{tabular}
-  \caption{Variation range for different benchmarks between a FCP and
-    a VCP exploration for power dissipation and execution time.}
+  \caption{Variation range for different benchmarks between PS and GA
+  exploration for power dissipation and execution time.}
   \label{fig:variation_range}

### 2014-05-16 experiments.tex
added pics

@@
 \item{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
-do\_modulo\_scheduling & Modular scheduling 
+do\_modulo\_scheduling  Modular scheduling 
 \item{memvr\_profiled}: Performs a memory-dependencies profiling 
@@
 still represent the best compromise between efficiency (i.e. time
-required for exploration) and accuracy of the reported Paret Sets. Of
-course, mono-objective approaches have been
-deliberately excluded from this analysis. Other
-approaches~\cite{dep} that make use of some a-priori knowledge about the
-role and meaning of each parameter have been also excluded, since our
+required for exploration) and accuracy of the reported Paret Sets.
+Note that for the reasons described above, mono-objective approaches have been
+explicitly excluded from this analysis. Same decision has been taken
+for other approaches (e.g. dependecy based~\cite{dep}) that make use of some a-priori knowledge about the
+role and meaning of each parameter, since our
 aim is evaluate the capacity of focusing on interesting
@@
 
+\begin{table*}
+  \centering
+  \begin{tabular}{ccc}
+    \includegraphics[width=0.32\textwidth]{pictures/alloca_100.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/bmm_100.eps} & 
+    \includegraphics[width=0.32\textwidth]{pictures/fir_int100.eps} \\
+    \includegraphics[width=0.32\textwidth]{pictures/mm_100.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/sha_100.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/wave_100.eps} 
+  \end{tabular}
+  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
+  \label{fig:pareto_fronts_100}
+\end{table*}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{ccc}
+    \includegraphics[width=0.32\textwidth]{pictures/alloca_500.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/bmm_500.eps} & 
+    \includegraphics[width=0.32\textwidth]{pictures/fir_int500.eps} \\
+    \includegraphics[width=0.32\textwidth]{pictures/mm_500.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/sha_500.eps} &
+    \includegraphics[width=0.32\textwidth]{pictures/wave_500.eps} 
+  \end{tabular}
+  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
+  \label{fig:pareto_fronts_100}
+\end{table*}
 Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
@@
 space as compared to those found for the FCP case.
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.45\textwidth]{pictures/100bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fir_int.eps} \\
-    \includegraphics[width=0.45\textwidth]{pictures/100mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fib.eps} \\
-    \includegraphics[width=0.45\textwidth]{pictures/100alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/100wave.eps}
-  \end{tabular}
-  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
-  \label{fig:pareto_fronts_100}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.45\textwidth]{pictures/bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fir_int.eps} \\
-    \includegraphics[width=0.45\textwidth]{pictures/mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fib.eps} \\
-    \includegraphics[width=0.45\textwidth]{pictures/alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/wave.eps}
-  \end{tabular}
-  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
-  \label{fig:pareto_fronts}
-\end{figure}
 

### 2014-05-16 TEST/analyse.m
completed results

@@ -1,0 +1,8 @@
+function analyse(f, v)
+
+region = [min([f(:,1);v(:,1)]) min([f(:,2);v(:,2)]) max([f(:,1);v(:,1)]) max([f(:,2);v(:,2)])];
+
+df = dispersion(f, region, 10, 10);
+dv = dispersion(v, region, 10, 10);
+
+[ df dv  min(f(:,1)) max(f(:,1)) min(f(:,2)) max(f(:,2))  min(v(:,1)) max(v(:,1)) min(v(:,2)) max(v(:,2))]

### 2014-05-16 TEST/btc/adj_points.m

@@ -1,0 +1,13 @@
+function adj_data=adj_points(data)
+
+freq_scale = 2500/200;
+tech_scale = 130/32;
+
+adj_data = data;
+adj_data(:,1) = adj_data(:,1)*freq_scale/tech_scale;
+
+adj_data(:,2) = 2*adj_data(:,2)/1000/freq_scale;
+
+
+
+

### 2014-05-16 TEST/btc/btcplot.m

@@ -1,0 +1,40 @@
+neb = load('sha_GA_500');
+par = load('sha_GA_pareto');
+
+par = par(:,2:3);
+
+neb = adj_points(neb);
+par = adj_points(par);
+
+figure;
+hold on;
+
+plot(neb(:,2),neb(:,1),'r.');
+plot(par(:,2),par(:,1),'g*-');
+xlabel('time (s)');
+ylabel('power (W)');
+legend('visited configurations','Pareto front');
+
+min_time = par(1,:);
+min_power = par(size(par,1),:);
+
+mid_config = par(size(par,1)/2,:);
+
+plot(min_time(2),min_time(1),'ko');
+plot(min_power(2),min_power(1),'ko');
+plot(mid_config(2),mid_config(1),'ko');
+
+min_time_mh = 1/min_time(2);
+min_power_mh = 1/min_power(2);
+mid_config_mh = 1/mid_config(2);
+
+[min_time_mh min_time(1) min_time_mh/min_time(1)]
+[min_power_mh min_power(1) min_power_mh/min_power(1)]
+[mid_config_mh mid_config(1) mid_config_mh/mid_config(1)]
+
+
+
+
+
+
+

### 2014-05-19 experiments.tex
added dispersion pics

@@
 Set of Figures~\ref{fig:pareto_fronts_100}
-and~\ref{fig:pareto_fronts} show the resultig pareto fronts for two
+and~\ref{fig:pareto_fronts_500} show the resultig pareto fronts for two
 different scenarios of 100 and 500 simulations budget.
@@
   \begin{tabular}{ccc}
-    \includegraphics[width=0.32\textwidth]{pictures/alloca_100.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/bmm_100.eps} & 
-    \includegraphics[width=0.32\textwidth]{pictures/fir_int100.eps} \\
-    \includegraphics[width=0.32\textwidth]{pictures/mm_100.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/sha_100.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/wave_100.eps} 
+    \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps} & 
+    \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps} \\
+    \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
   \end{tabular}
@@
   \begin{tabular}{ccc}
-    \includegraphics[width=0.32\textwidth]{pictures/alloca_500.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/bmm_500.eps} & 
-    \includegraphics[width=0.32\textwidth]{pictures/fir_int500.eps} \\
-    \includegraphics[width=0.32\textwidth]{pictures/mm_500.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/sha_500.eps} &
-    \includegraphics[width=0.32\textwidth]{pictures/wave_500.eps} 
+    \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps} & 
+    \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps} \\
+    \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps} &
+    \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 
   \end{tabular}
   \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
-  \label{fig:pareto_fronts_100}
+  \label{fig:pareto_fronts_500}
 \end{table*}
-Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
-respectively show the visited configurations and the
-Pareto fronts found for both FCP and VCP scenarios for different
-application benchmarks. How it can be observed, VCP solutions
-are on average  more widely and evenly distributed over the objective
-space as compared to those found for the FCP case.
+
+As can be seen TODO...
 
@@
 respectively.
-\begin{figure}
+\begin{table}
   \centering
   \begin{tabular}{c}
-    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
-    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps}
+    \includegraphics[width=0.4\textwidth]{pictures/variation_power.eps} \\
+    (a) \\
+    \includegraphics[width=0.4\textwidth]{pictures/variation_etime.eps}
+    (b) \\
+    \includegraphics[width=0.4\textwidth]{pictures/dispersion.eps} \\
+    (c) 
   \end{tabular}
-  \caption{Variation range for different benchmarks between PS and GA
-  exploration for power dissipation and execution time.}
-  \label{fig:variation_range}
-\end{figure}
+  \caption{(a)(b) Variation range for different benchmarks between PS and GA
+  and average dispersion absolute dispersion (c)}
+  \label{fig:dispersion}
+\end{table}
 
@@
 
-Fig.~\ref{fig:dispersion} shows the average normalised absolute
+Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
 dispersion errors for different benchmarks for FCP and VCP
@@
 dispersion error on average by 20\% as compared to a FCP exporation.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
-  \caption{Average normalised absolute dispersion errors for different
-    benchmarks for FCP and VCP exploration.}
-  \label{fig:dispersion}
-\end{figure}

### 2014-05-19 TEST/exp_dispersion/analyse.m

@@ -1,0 +1,8 @@
+function x = analyse(f, v)
+
+region = [min([f(:,1);v(:,1)]) min([f(:,2);v(:,2)]) max([f(:,1);v(:,1)]) max([f(:,2);v(:,2)])];
+
+df = dispersion(f, region, 10, 10);
+dv = dispersion(v, region, 10, 10);
+
+x = [ df dv  min(f(:,1)) max(f(:,1)) min(f(:,2)) max(f(:,2))  min(v(:,1)) max(v(:,1)) min(v(:,2)) max(v(:,2))]

### 2014-05-19 TEST/exp_dispersion/dispersion.m

@@ -1,0 +1,47 @@
+function d = dispersion(data, region, gridx, gridy)
+
+figure;
+plot(data(:,1), data(:,2), '.k');
+hold on;
+
+points = size(data,1);
+
+% maxx = max(data(:,1));
+% minx = min(data(:,1));
+% maxy = max(data(:,2));
+% miny = min(data(:,2));
+
+minx = region(1);
+miny = region(2);
+maxx = region(3);
+maxy = region(4);
+
+die_w = (maxx - minx)/gridx;
+die_h = (maxy - miny)/gridy;
+
+ndies = gridx * gridy;
+
+abs_error = 0;
+
+for n=0:ndies-1,
+    col = rem(n, gridx);
+    row = fix(n/gridx);
+
+    x1 = minx + (col * die_w);
+    y1 = miny + (row * die_h);
+    x2 = x1 + die_w;
+    y2 = y1 + die_h;
+
+    rectangle('Position',[x1 y1 die_w, die_h]);
+
+    count = 0;
+    for j=1:points,
+    	if (data(j,1) >= x1 & data(j,1) < x2 & data(j,2) >= y1 & data(j,2) < y2)
+	   count = count + 1;
+	end
+    end
+
+    abs_error = abs_error + abs(count - (points/ndies));
+end
+
+d = abs_error / ndies;

### 2014-05-19 TEST/exp_dispersion/run_script.m

@@ -1,0 +1,36 @@
+% load bmm_comp_fisso.mat
+% f = bmm_RAND_default_space_sub;
+% load bmm_comp_variabile.mat
+% v = bmm_RAND_default_space_sub;
+% analyse(f,v);
+
+% load fir_random_fissi.mat
+% f = fir_int_RAND_default_space_sub;
+% load fir_random_var.mat
+% v = fir_int_RAND_default_space_sub;
+% analyse(f,v);
+
+% load mm_comp_fissi.mat
+% f = mm_RAND_default_space_sub;
+% load mm_comp_variabili.mat
+% v = mm_RAND_default_space_sub;
+% analyse(f,v);
+
+% load sqrt_random_fissi.mat
+% f = sqrt_RAND_default_space_sub;
+% load sqrt_random_variabili.mat
+% v = sqrt_RAND_default_space_sub;
+% analyse(f,v);
+
+% load struct_test_comp_fissi.mat
+% f = struct_test_RAND_default_space_sub;
+% load struct_test_comp_variabili.mat
+% v = struct_test_RAND_default_space_sub;
+% analyse(f,v);
+
+load wave_comp_fissi.mat
+f = wave_RAND_default_space_sub;
+load wave_comp_variabili.mat
+v = wave;
+analyse(f,v);
+

### 2014-07-16 algorithm.tex
missing references

@@
 it's not worth evaluating many of their configurations and it is useful
-to merge these regions , in order to less densely evaluate them.
+to merge these regions, in order to less densely evaluate them.
 
-ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
-DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
+%ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
+%DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
+
 \end{rem}
@@
 it's unsafe to terminate as soon as the Pareto front doesn't change
-enough, passing from an era to the next. It's better taking into account
-more than one era.
+enough between two consecutive eras, thus a strategy taking into
+account the history of the Pareto fronts has been adopted in the
+proposed approach.
 \end{rem}
-!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
-FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
+%!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
+%FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
 

### 2014-07-16 experiments.tex
missing references

@@
 \label{sec:ee}
+\subsection{Motivation}
 In order to evaluate the behavior of the proposed approach
@@
 \item{Multi-Objective trade-offs}: VLIW architectures let designers
-easily trade between power, energy and performances~\cite{}, leading
-to Pareto sets whose extension is an ideal ground for our testing
+easily trade between power, energy and performances~\cite{}, resulting
+in Pareto sets whose extension is an ideal ground for our testing
 purposes focused on parameter-space space representation of Paretos.
@@
 will execute it.
+\end{itemize}
 
+\subsection{Parameter Space}
 System parameters can be classified in three main categories:
@@
 
-\subsection{Evaluation Metrics}
-
-The results presented in the next section compare PS against a widely
-adpted Multi-objective Genetic Algorithm~\cite{}. At best of our
-knowledge, genetic approaches
-still represent the best compromise between efficiency (i.e. time
-required for exploration) and accuracy of the reported Paret Sets.
-Note that for the reasons described above, mono-objective approaches have been
-explicitly excluded from this analysis. Same decision has been taken
-for other approaches (e.g. dependecy based~\cite{dep}) that make use of some a-priori knowledge about the
-role and meaning of each parameter, since our
-aim is evaluate the capacity of focusing on interesting
-parameter regions without any external judgement or help based on
-euristics.  Finally, it should be pointed
-out that in this introductory work we will explicitly use the TODO
-variant of MOGA, remainding to works like~\cite{} for a detailed
-analysis on how it differs and what could be expected from similar multi-objective strategies.
-
-The class of benchmark being considered is representative of some common
-frequently running application kernels in an embedded multimedia
-environment. Table~\ref{tab:bench} shows the set of applications
-chosen along with a brief description.
+As regards the class of benchmark being considered, a set applications representative of some common
+frequently running code kernels in an embedded multimedia
+environment has been chosen. Table~\ref{tab:bench} shows the set of applications
+along with a brief description.
 \begin{table}
@@
 \end{table}
+
+\subsection{Evaluation Metrics}
+
+The results presented in the next section compare PS against one
+widely adopted Multi-objective Genetic
+Algorithm~\cite{knowles_techrep06}. At best of our knowledge, genetic
+approaches in general still represent the best compromise between
+efficiency (i.e. time required for exploration) and accuracy of the
+reported Paret Sets.  Note that for the reasons described above,
+mono-objective approaches have been explicitly excluded from this
+analysis. Same decision has been taken for other approaches (e.g.
+dependecy based~\cite{givargis_tvlsi02}) that make use of some
+a-priori knowledge about the role and meaning of each parameter, since
+our aim is evaluate the capacity of focusing on interesting parameter
+regions without any external judgement or help based on euristics.
+Finally, it should be pointed out that in this introductory work we
+will explicitly use the SPEA~\cite{zitzler_eurogen01} variant of MOGA,
+remainding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for
+a detailed analysis on how it differs and what could be expected from
+similar multi-objective strategies.
+
 %------------------------------------------------------------------------------
@@
 between a FCP and a VCP exploration for both power dissipation and
-execution time is shown in Fig.~\ref{fig:variation_range}. As it can
+execution time is shown in Fig.~\ref{fig:dispersion}(a) and (b)
+respectively. As it can
 be observed, the VCP exploration provides solutions which fall on a

### 2014-07-22 experiments.tex
draft of comments on results

@@
 \item{Multi-Objective trade-offs}: VLIW architectures let designers
-easily trade between power, energy and performances~\cite{}, resulting
-in Pareto sets whose extension is an ideal ground for our testing
-purposes focused on parameter-space space representation of Paretos.
+easily trade between power, energy and performances, resulting
+in extended Pareto sets which are an ideal ground for our testing
+purposes focused on parameter-space space representation
 \item{Compiler awareness}: Instruction Level Parallelism (ILP)
-constitutes the key feature to enable the multi-objective trade offs
-of the point above. It is statically obtained by the compiler which
+is statically obtained by the compiler which
 performs code trasformations being aware of the underlying hardware
 configuration.  This tight hardware/software dependence, makes the
-VLIW scenario well suitable for investigating hardly predictable
-hardware/software interactions, especially when compared to
-architectures that, in order to preserve binary compatibility,
-separate software generation processes from the hardware that
-will execute it.
+VLIW scenario perfectly suitable for investigating hardly predictable
+hardware/software interactions.
 \end{itemize}
@@
 \subsection{Parameter Space}
-System parameters can be classified in three main categories:
+In general, system parameters can be classified in three main categories:
 \emph{processor}, \emph{memory sub-system} and \emph{compiler}. 
@@
 As regards the class of benchmark being considered, a set applications representative of some common
-frequently running code kernels in an embedded multimedia
-environment has been chosen. Table~\ref{tab:bench} shows the set of applications
+frequently running code kernels has been selected. Table~\ref{tab:bench} shows the set of applications
 along with a brief description.
@@
 Set of Figures~\ref{fig:pareto_fronts_100}
-and~\ref{fig:pareto_fronts_500} show the resultig pareto fronts for two
-different scenarios of 100 and 500 simulations budget.
+and~\ref{fig:pareto_fronts_500} show the resulting pareto fronts for two
+different scenarios of 100 and 500 simulations budget. When possible,
+similar algorithm parameters have been adopted. In particular a
+population size of 30 has been chosen for GA, corresponding to the
+same value for the $K$ of PS. The number of generations (or era)
+has been chosen so that the only the given amount of simulations is
+actually performed. Thus, when accounting these simulations only unique simulations
+has been considered, removing repeations and unfeasibile
+configurations.
 
@@
 
-As can be seen TODO...
+Low budget Pareto sets are shown in
+Figure~\ref{fig:pareto_fronts_100}. With a so small number of
+configuration being investigated the two sets are often overlapping,
+being also strongly depended upon the application being considered.
+These results are obtained in about 5 eras, and the main aim was
+demonstrating that with a so limited budget PS still can competer with
+genetic approach while even discovering very different Pareto fronts.
+Continuing with a more extendent simulation budget as depicted in
+Figure~\ref{fig:pareto_fronts_500}, we can qualitatively observe that
+even if PS does not stricly outperforms genetic in terms of dominance, it shows in
+some cases largely Pareto in terms of extension. We can intuitively
+relate this to the ``novelty-based'' score system, so that instead of
+focusing on getting better points inside a given range it tries to
+enlarge the range itself, resulting in less dense but more extended
+Paretos. Of course we cannot classify this different behavior as
+``better'' or ``worse'' as compared to the genetic one, it depends on
+various design factors such as desired results granularity, prefixed objective
+range constraints, estimated error of the models used etc~\ldots.
 
@@
 execution time is shown in Fig.~\ref{fig:dispersion}(a) and (b)
-respectively. As it can
-be observed, the VCP exploration provides solutions which fall on a
-range that is, on average, 23\% and 40\% wider than that provided by a
-FCP exploration for power dissipation and execution time,
-respectively.
+respectively. As it can be observed, the PS exploration provides solutions which fall on a
+range that is, on average, wider than that provided by a
+MOGA exploration for power dissipation and execution time, respectively.
 \begin{table}
@@
     (a) \\
-    \includegraphics[width=0.4\textwidth]{pictures/variation_etime.eps}
+    \includegraphics[width=0.4\textwidth]{pictures/variation_etime.eps} \\
     (b) \\
@@
 Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
-dispersion errors for different benchmarks for FCP and VCP
-exploration. As it can be observed, VCP exploration reduces the
-dispersion error on average by 20\% as compared to a FCP exporation.
+dispersion errors for different benchmarks for PS and MOGA
+exploration. As it can be observed, MOGA still shows a tendency in
+discovering more uniformly dispersed points (i.e. higher values). These results,
+together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
+(b) confirm the the availability of density vs extension trade-offs
+when comparing PS and multi-objective genetic approaches.

### 2014-07-22 introduction.tex
Results data
draft of comments on results

@@
 
-The design of an embedded system requires several objectives (energy
-consumption, area occupation, ...) to be fulfilled. The fulfilling
-of these objectives depends on several parameters and in the real
-cases no analytical results are known to show the relation between
-configurations (combination of parameters) and objectives. Therefore
-the simulation is the only way to have a picture of how parameters
-impact on the objectives. The problem is that the number of parameters
-and the number of values that each of them may take lead to an enormous
-number of possible configurations, such that simulating all of them
-is an unfeasible activity. Therefore there is the need for the ``Design
-Space Exploration'', i.e. a methodology to select a subset of all
-possible configurations and simulate only this subset.
+The design of an embedded system requires different conflicting
+objectives (energy consumption, performance, area) to be fulfilled.
+Several factors are involved in this goal and real cases show how
+often no analytical results are known to predict the relation between
+system configurations and objectives. In such cases an high level
+system simulation is the only way to have a picture of how system
+parameters impact on the objectives.  The key problem is that the size
+of the design space to be simulated grows with the product of
+cardinalities of parameters, easily yelding an untractable number
+of simulations. In order to address such task a ``Design Space
+Exploration'' strategy is required, i.e. a methodology to evaluate
+only a small subset of all possible configurations while maintaining a
+good level of efficiency and accuracy.
 
-Many different design space exploration algorithms have been proposed.
-A design space exploration algorithm is typically not based on precise
-/ analytical / mathematical evidences. The motivations of an exploration
-algorithm are rather heuristic, have some form of arbitrariness and,
-to a large extend, intuition lies behind them.
+The final result of every design space exploration is a subset of the
+configurations called Pareto Set (\cite{pareto}). Roughly speaking, it
+is a set of configurations representing the trade-offs between
+objectives: for each of configuration of the Pareto Set there is no
+other configuration performing better for all the objectives
+considered. Of course this is an high level estimation so in a
+subsequent step of the design flow these few promising configurations
+can be more accurately evaluated using detailed low level simulations.
 
-The result of every design space exploration is a subset of the configurations
-called Pareto Set (\cite{pareto}). Roughly speaking, it is a set of
-configurations such that there are no other configurations, among
-the simulated ones, that have all the objectives, at the same time,
-better fulfilled. If all possible configurations were evaluated, the
-ideal Pareto set (the ``true'' Pareto set) could be calculated.
-But, as stated above, evaluating all the configurations is not feasable.
-Therefore the Pareto set returned by an exploration algorithm is an
-approximation of the ``true'' Pareto set.
+In this work we present PS, a multiobjective design exploration
+strategy which introduce the concept of Parameter Space representation
+of Pareto Set. The main idea is to ....
 
@@
 
-The ``quality'' of an exploration algorithm involves two aspects:
-\begin{itemize}
-\item how much the Pareto set returned by the exploration algorithm is similar
-to the ``true'' Pareto set (notice that this cannot be evaluated
-because the true Pareto set is unknown - it is only an ``ideal''
-quality factor)
-\item how fast the Pareto set converges towards the final one. If algorithm
-$1$ returns the final Pareto set after simulating $n_{1}$ configurations
-and algorithm $2$ returns its final Pareto set after $n_{2}$ simulations,
-algorithm $1$ is said to be faster than algorithm $2$, iff $n_{1}<n_{2}$.
-\end{itemize}
+\section{\label{sec:Related-work}Related work}
+% TODO: short, remove descriptions
+% SPEA2 as choice, comparison of it agains other GA is available
 
-\section{\label{sec:Related-work}Related work}
-
-There are a number of design space exploration algorithms proposed
-in literature.
+Many different design space exploration algorithms have been proposed.
+A design space exploration algorithm is typically not based on precise
+/ analytical / mathematical evidences. The motivations of an exploration
+algorithm are rather heuristic, have some form of arbitrariness and,
+to a large extend, intuition lies behind them.
 

### 2014-07-22 introduction.tex
added abstract, modified intro

@@
-\section{Introduction}
+\section{Introduction and Motivation}
 
@@
 system configurations and objectives. In such cases an high level
-system simulation is the only way to have a picture of how system
-parameters impact on the objectives.  The key problem is that the size
+system simulation is often the only way to have a picture of how system
+parameters impact on the objectives.  A key problem is that the size
 of the design space to be simulated grows with the product of
-cardinalities of parameters, easily yelding an untractable number
-of simulations. In order to address such task a ``Design Space
+cardinalities of each parameter, easily resulting in an untractable number
+of simulations. In these cases a ``Design Space
 Exploration'' strategy is required, i.e. a methodology to evaluate
 only a small subset of all possible configurations while maintaining a
-good level of efficiency and accuracy.
+good level of efficiency and accuracy~\cite{surviving_soc}.
 
-The final result of every design space exploration is a subset of the
-configurations called Pareto Set (\cite{pareto}). Roughly speaking, it
-is a set of configurations representing the trade-offs between
-objectives: for each of configuration of the Pareto Set there is no
+The final result of a design space exploration is a subset of the
+configurations called Pareto Set (\cite{pareto}) (See also Definition
+\ref{pers02.def:Pareto-set}. It represents the trade-offs between
+objectives, so that for each of configuration of the Pareto Set there is no
 other configuration performing better for all the objectives
-considered. Of course this is an high level estimation so in a
-subsequent step of the design flow these few promising configurations
-can be more accurately evaluated using detailed low level simulations.
+considered. Once these few promising configurations have been obtained, a
+subsequent step of the design flow can eventually afford a more
+accurate low level simulation.
 
 In this work we present PS, a multiobjective design exploration
-strategy which introduce the concept of Parameter Space representation
-of Pareto Set. The main idea is to ....
+strategy that introduces the concept of Parameter Space Representation
+of Pareto Set. The main idea is focusing on the ``innovation''
+introduced in the Pareto sets and then accordingly distribuiting the
+exploration effort in regions created in the multidimensional space of
+system parameters.
 
-Many exploration algorithms form the resulting Pareto set in an incremental
-way. The algorithm adds and removes configurations in Pareto set while
-choosing the configurations to evaluate and simulating them. So Pareto
-set ``evolves'' towards the final one. The dynamical view of the
-Pareto set shaping can be seen as the ``behavior'' of the algorithm.
-This behavior tells us how the Pareto set ``converges'' towards
-the final Pareto set.
-
-\section{\label{sec:Related-work}Related work}
-% TODO: short, remove descriptions
-% SPEA2 as choice, comparison of it agains other GA is available
-
-Many different design space exploration algorithms have been proposed.
-A design space exploration algorithm is typically not based on precise
-/ analytical / mathematical evidences. The motivations of an exploration
+Many different design space exploration algorithms have been proposed
+in literature.  The motivations of an exploration
 algorithm are rather heuristic, have some form of arbitrariness and,
@@
 
+Some exploration strategies assume some kind of ``knowledge'' about
+the system parameters, their meaning and impact on design objectives.
 The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
 to take advantage of the dependency among the parameters in a multiobjective
-optimization problem. It is required that the designer knows, prior
-to the exploration, if a parameter X is dependent from a parameter
-Y, i.e. changing the value of Y ``impacts the optimal parameter value''
-for X. With this a-priori knowledge, the designer can construct a
+optimization problem.  With this a-priori knowledge, the designer can construct a
 ``dependency graph'' and recognize clusters, i.e. subsets of strongly
@@
 a precise and complete picture of the dependencies among parameters;
-for this reason the need of ``automated approaches for computing
-{[}...{]} interdependencies'' is declared in the same paper. iii)
-There may be some ``local dependencies'', i.e. dependencies that
-emerge only if parameter values are bounded to certain ranges.
-
-These drawbacks are not present in our solution. The algorithm presented
+for this reason the need of ``automated approaches for computing interdependencies'' is declared in the same paper. 
+These drawbacks are not present in our contribution. The algorithm presented
 here is also meant to take advantage of dependency but is not directly
@@
 during exploration. Moreover, recognizing regions offers the capability
-to capture local dependencies.
+to capture local dependencies,  i.e. dependencies that
+emerge only if parameter values are bounded to certain ranges.
 
@@
 the system to be evaluated into components that interact minimally
-with each other. ``Alternative designs for each component are evaluated
-in isolation to determine the best designs for individual components.
-Combinations of these designs are then put together to build the complete
-system design''. Pareto sets for each component are found and, provided
+with each other. Pareto sets for each component are found and, provided
 that ``monotonicity'' exists, the complete Pareto set is computed
@@
 Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{} and others). Genetic approaches
+optimization problems (\cite{coello_easmop} and others). Genetic approaches
 have many advantages: they have proved good quality (as broadly defined
 in the introduction), they are customizable, they are very general
-and require no a-priori knowledge to the designer. Genetic algorithms
-run in subsequent iterations. Configurations are represented as chromosomes.
-In each iteration a ``population'' of configurations is evaluated.
-Some configurations are discarded. Each selected configuration is
-combined with the preceding population and then ``mutated'' (i.e.
-the resulting configuration is varied a little). Iterating this operations,
-populations are expected to become ``better and better''. The strong
+and require no a-priori knowledge to the designer.  The strong
 point of genetic approaches can be summarized saying that they consist
@@
 neither too much constrained nor too much random. We claim that the
-approach presented in this paper has all the benefits of the genetic
+approach presented in this paper has most of the benefits of the genetic
 approaches, although the rational is completely different.
+
+The paper is organized as follows: in
+Section~\ref{sec:statement_of_the_problem} we formally introduce the
+main concepts and the definitions required to apply the proposed strategy. Next in
+Section~\ref{sec:algorithm} we present the PS algorithm in detail.
+Finally in Section~\ref{sec:ee} we show a case study involving the
+exploration of the hardware/software parameters of a VLIW
+architecture, performing a qualitative and quantitative comparison of
+PS agains the state-of-art of multiobjective genetic based approaches.

### 2014-07-22 paper.tex
Fixed theorem/remarks numbering
fix
Results data
added abstract, modified intro

@@
 \newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.98}\normalsize
+%\renewcommand{\baselinestretch}{0.98}\normalsize
 %------------------------------------------------------------------------------
@@
 \theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
+\newtheorem{defn}{\protect\definitionname}
 \theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
+\newtheorem{rem}{\protect\remarkname}
 
-\makeatother
+%\newtheorem{defn}[thm]{\protect\definitionname}
+%\theoremstyle{remark}
+%\newtheorem{rem}[thm]{\protect\remarkname}
+%\makeatother
 
@@
 
-\title{Parameter space representation of Pareto set}
+\title{Parameter Space Representation of Pareto Front to
+Explore Hardware-Software Dependencies}
 %ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
@@
 \begin{abstract}
-In this paper ...
+Embedded Systems Design often requires conflicting objectives to be
+optimised with an approapriate choice of hardware/software parameters
+. Interdependencies among these parameters can make this task even
+more difficult, since an a-priori knowledge of them would  be required
+to develop an analytical model of the system. In this work we present
+PS, a multiobjective exploration strategy that introduces the notion
+of Parameters Space Representation. After a detailed formal
+description of the algorithm and its concepts, we show an
+hardware/software exploration case study. Qualitative and quantitative
+comparisons of PS against a well-know multiobjective genetic approach
+demonstrate that, while not outperforming it in terms of dominance, the
+proposed approach can trade the uniformity and granularity
+qualities of the solutions found for obtaining larger Pareto sets,
+thus representing a further choice for designer when objective constrains allow it.
 \end{abstract}
@@
 \input{concepts.tex}
+\input{algorithm.tex}
 \input{experiments.tex}

### 2014-07-23 concepts.tex
Results data
missing references
AA: intro + related work reviewed

@@
 set:
+\begin{defn}
+\label{pers02.def:Pareto-set}
 \[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
+\end{defn}
 that is, the set of configurations $\mathbf{c} \in
@@
 \includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}
-
 \caption{Relation between Pareto set (its ``parameter space representation'')
 and Pareto front (``objective space representation'')}
-
 \end{figure}
 
-\subsection{Required Definitions and Concepts}
+\subsection{Sketch of the Idea}
 
@@
 found.
-\begin{rem}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{rem}
-%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-%PARAMETRI SENZA ORDINAMENTO{]}
+
+%TODO: sync name of values with formulation
+\subsection{Required Definitions}
 \begin{defn}
@@
 
+\begin{rem}
+We will consider only parameters $p_{i}$ with ordering, i.e. such
+that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
+to say $a<b$ or $a=b$ or $a>b$.
+\end{rem}
+%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
+%PARAMETRI SENZA ORDINAMENTO{]}
 \begin{defn}
@@
 \end{defn}
+
+\comment{ CERCARE DI FAR CAPIRE CONCETTUALMENTE IL SEGUENTE CONFRONTO CON LA SENSITIVITY ANALYSIS:
+It is worth noticing that this approach can not capture
+``local sensitivity'' (this drawback will be called ``local sensitivity
+limitation''), i.e. the objectives may be more sensitive to some
+ranges of a parameter and less sensitive to other ranges of the same
+parameter. Moreover it can not capture ``combined sensitivity''
+(``combined sensitivity limitation''), i.e. the objectives may be
+more sensitive to a range of a parameter $p_{1}$, only when other
+parameters are within certain ranges, and less sensitive to the same
+range of parameter $p_{1}$ when the other parameters are not within
+those ranges. Therefore, in the method we propose, we do not use the
+sensitivity directly, but we use the concept of innovation (that can
+be considered, at least weakly related to the sensitivity). We do
+not measure innovation of a parameter (as done for the sensitivity),
+but rather we measure the innovation of a ``region'' of parameter
+space, in order to overcome both the ``local sensitivity limitation''
+and the ``combined sensitivity limitation'' stated above for the
+sensitivity analysis.}

### 2014-07-23 introduction.tex
AA: intro + related work reviewed

@@
 often no analytical results are known to predict the relation between
-system configurations and objectives. In such cases an high level
+system configurations and objectives. In such cases a high level
 system simulation is often the only way to have a picture of how system
@@
 configurations called Pareto Set (\cite{pareto}) (See also Definition
-\ref{pers02.def:Pareto-set}. It represents the trade-offs between
-objectives, so that for each of configuration of the Pareto Set there is no
+\ref{pers02.def:Pareto-set}). It represents the trade-offs between
+objectives, so that for each configuration of the Pareto Set there is no
 other configuration performing better for all the objectives
@@
 of Pareto Set. The main idea is focusing on the ``innovation''
-introduced in the Pareto sets and then accordingly distribuiting the
+introduced in the Pareto sets and then accordingly distributing the
 exploration effort in regions created in the multidimensional space of
-system parameters.
+system parameters. \comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }
 
+\section{Related work}
+\comment{Preferisci che i related work siano in un'unica sezione con Intro?}
 Many different design space exploration algorithms have been proposed
@@
 
-Some exploration strategies assume some kind of ``knowledge'' about
-the system parameters, their meaning and impact on design objectives.
-The ``Dependency analysis'' proposed in \cite{givargis_tvlsi02}, is meant
-to take advantage of the dependency among the parameters in a multiobjective
-optimization problem.  With this a-priori knowledge, the designer can construct a
+Some exploration strategies assume some kind of knowledge about
+the system parameters, their meaning and their impact on design objectives.
+The \emph{Dependency analysis}, proposed in \cite{givargis_tvlsi02}, is meant
+to take advantage of the parameter dependencies, a-priori known by the designer \comment{E' giusto, cosi'?}. Starting from them, he can construct a
 ``dependency graph'' and recognize clusters, i.e. subsets of strongly
 dependency-connected parameters. Each cluster is exhaustively evaluated
-and its ``local Pareto set'' is found. Then, all local Pareto sets
-are merged. Doing this way, a ``sum'' of local exhaustive evaluations
+and its ``local'' Pareto set is found. Then, all local Pareto sets
+are merged. In this way, a series of local exhaustive evaluations
 are performed instead of an exhaustive evaluation of all the possible
 configurations. Some problems arise: i) In real scenarios, it may
-be very difficult to recognize really independent clusters of parameters,
-because there may be interdependencies among a very large number of
-parameters. This may lead to the need of an exhaustive search through
+be difficult to recognize really independent clusters of parameters,
+because there may be interdependencies among a large number of
+parameters. This may lead to the need of an evaluation of
 almost all the possible configurations. ii) A designer may not have
-a precise and complete picture of the dependencies among parameters;
+a precise and complete a-priori picture of the dependencies among parameters;
 for this reason the need of ``automated approaches for computing interdependencies'' is declared in the same paper. 
-These drawbacks are not present in our contribution. The algorithm presented
-here is also meant to take advantage of dependency but is not directly
-based on dependency itself, but rather it ``catches'' dependencies
-in terms of ``interesting or uninteresting regions''; as a consequence
-no a-priori knowledge of dependencies is required as they are discovered
-during exploration. Moreover, recognizing regions offers the capability
-to capture local dependencies,  i.e. dependencies that
-emerge only if parameter values are bounded to certain ranges.
+These drawbacks are not present in our algorithm, since, although it leverages dependencies as in \cite{givargis_tvlsi02}, it is able to detect them automatically, with no a-priori knowledge required.
+Moreover, our algorithm is able to capture also ``local dependencies", i.e.
+dependencies that
+emerge only among certain ranges of parameters and may not hold when considering the entires ranges. This cannot be modeled in Dependency Analysis.
 
 Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
-the system to be evaluated into components that interact minimally
+the system under evaluation into components that interact minimally
 with each other. Pareto sets for each component are found and, provided
@@
 were perfectly isolated, i.e., if there were no dependencies among
-different components (in a sense similar (but not necesarily equal)
-to the one of Dependency analisys). But real scenarios seldom if ever
-expose monotonicity property. This leads to some ``inaccuracies''
-(as stated in section 4.6.1 of the same paper).
+them. But real scenarios seldom if ever
+expose monotonicity property thus resulting in inaccuracies, as stated in the same paper).
 
-Other approaches take into account the concept of ``sensitivity''.
-The sensitivity of an objective with the respect to a parameter is
-a measure of how much the objective varies when varying that parameter.
-A ``sensitivity analysis'' was used in \cite{fornaciari_codes01} in an optimization
-problem with only one objective (the power-delay product of an electronic
-device). This method was extended in \cite{palesi_iwsoc02} to a multiobjective
-optimization. In that work the sensitivity of objectives with
-the respect to each parameter is measured, and parameters are ordered
-on the base on these sensitivity measures. Then, a first Pareto set
-is obtained varying the first parameter, having fixed to arbitrary
-values all other parameters. The Pareto set is then refined varying,
-in a similar way, the other parameters, one by one. Experimental results
-(see section 4.2 of the same work) show that this method is not of
-good ``quality'' (as broadly defined in the introduction). The reason
-can be found in the very limited and rigid exploration of the parameter
-space: after computing the first Pareto set, there are no more chances
-to consider configurations with values of the first parameter other
-than the ones assumed in the first Pareto set calculation. Similar
-limitations are imposed after computing the second Pareto set, the
-third and so on. It is worth noticing that this approach can not capture
-``local sensitivity'' (this drawback will be called ``local sensitivity
-limitation''), i.e. the objectives may be more sensitive to some
+Other approaches, as \cite{fornaciari_codes01,palesi_iwsoc02}, are based the concept of \emph{sensitivity analysis}, i.e. measuring of how much the objective varies when varying each parameter.
+Parameters are ordered based on their sensitivity.
+The first parameter (the most sensitive one) is varied, while keeping the other parameters fixed to arbitrary values, and its best value is found.
+The limited accuracy shown by these approaches can be explained by the limited and rigid exploration of the parameter
+space: after fixing the best first parameter value, there are no more chances to consider different values. It is worth noticing that this approach can not capture
+``local sensitivity'', i.e. the objectives may be more sensitive to some
 ranges of a parameter and less sensitive to other ranges of the same
-parameter. Moreover it can not capture ``combined sensitivity''
-(``combined sensitivity limitation''), i.e. the objectives may be
+parameter. Moreover it can not capture ``combined sensitivity'', i.e. the objectives may be
 more sensitive to a range of a parameter $p_{1}$, only when other
 parameters are within certain ranges, and less sensitive to the same
-range of parameter $p_{1}$ when the other parameters are not within
-those ranges. Therefore, in the method we propose, we do not use the
-sensitivity directly, but we use the concept of innovation (that can
-be considered, at least weakly related to the sensitivity). We do
-not measure innovation of a parameter (as done for the sensitivity),
-but rather we measure the innovation of a ``region'' of parameter
-space, in order to overcome both the ``local sensitivity limitation''
-and the ``combined sensitivity limitation'' stated above for the
-sensitivity analysis.
+range of $p_{1}$ when the other parameters are in different ranges. Otherwise, our algorithm can both capture local and combined sensitivity.
 
-Many studies focus on genetic approaches to resolve multiobjective
-optimization problems (\cite{coello_easmop} and others). Genetic approaches
-have many advantages: they have proved good quality (as broadly defined
-in the introduction), they are customizable, they are very general
+Many studies, as \cite{coello_easmop} and others, focus on genetic approaches to solve multiobjective
+optimization problems. Genetic approaches
+have many advantages: they provide good accuracy, they are customizable and very general
 and require no a-priori knowledge to the designer.  The strong
 point of genetic approaches can be summarized saying that they consist
-in a broad exploration (the mutation permits to make the exploration
-not rigidly restricted to limited parts of parameter space), although
-this exploration is not random but is guided by the performances of
-the already evaluated configurations. Therefore, the exploration is
-neither too much constrained nor too much random. We claim that the
+in exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
+the already evaluated configurations. We claim that the
 approach presented in this paper has most of the benefits of the genetic
-approaches, although the rational is completely different.
+approaches, although the rationale is completely different.
 

### 2014-07-23 paper.tex
AA: intro + related work reviewed

@@
 \usepackage{courier}
+
+\usepackage{color}
 
@@
 \newcommand{\etc}{\emph{etc.}}
+
+\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
+%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
+
 %\renewcommand{\baselinestretch}{0.98}\normalsize
@@
 Embedded Systems Design often requires conflicting objectives to be
-optimised with an approapriate choice of hardware/software parameters
+optimized with an appropriate choice of hardware/software parameters
 . Interdependencies among these parameters can make this task even
@@
 of Parameters Space Representation. After a detailed formal
-description of the algorithm and its concepts, we show an
+description of the algorithm and its concepts, we show a
 hardware/software exploration case study. Qualitative and quantitative

### 2014-07-23 introduction.tex
Fixes and more contribution description

@@
 
-In this work we present PS, a multiobjective design exploration
-strategy that introduces the concept of Parameter Space Representation
-of Pareto Set. The main idea is focusing on the ``innovation''
+In this work we present a multiobjective design exploration strategy
+that introduces the concept of Parameter Space Representation of
+Pareto Set (PS). The main idea is focusing on the ``innovation''
 introduced in the Pareto sets and then accordingly distributing the
 exploration effort in regions created in the multidimensional space of
-system parameters. \comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }
+system parameters. The aim of the PS approach is to propose a new
+perspective on the configuration space, where parameter
+interdependencies play the fundamental role of making some regions
+more capable of generating hardly predictable solutions: catching this
+sort of ``chaoticity'' in the parameter space is the main idea behind
+the strategy that is being introduced in this work.
+
+\comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }
 

### 2014-07-23 concepts.tex
typos

@@
 
-We also consider, in measuring how much iteresting a region is, the
+We also consider, in measuring how much interesting a region is, the
 ``innovation'' that it adds. If, during a design space exploration,
@@
 fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated ineresting as much
+during exploration. So a region will be evaluated interesting as much
 as how different are its added Pareto front points from the ones already
@@
 However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiuguous regions.
+$R_{1}$ and $R_{2}$ must be to contiguous regions.
 \end{rem}
@@
 The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
+much we must vary $\mathbf{o}$ to transform it in $\mathbf{q}$.
 The separation is a ``normalized'' measure that is independent of

### 2014-07-23 experiments.tex
typos

@@
 is statically obtained by the compiler which
-performs code trasformations being aware of the underlying hardware
+performs code transformations being aware of the underlying hardware
 configuration.  This tight hardware/software dependence, makes the
@@
 analysis. Same decision has been taken for other approaches (e.g.
-dependecy based~\cite{givargis_tvlsi02}) that make use of some
+dependency based~\cite{givargis_tvlsi02}) that make use of some
 a-priori knowledge about the role and meaning of each parameter, since
 our aim is evaluate the capacity of focusing on interesting parameter
-regions without any external judgement or help based on euristics.
+regions without any external judgement or help based on heuristics.
 Finally, it should be pointed out that in this introductory work we
 will explicitly use the SPEA~\cite{zitzler_eurogen01} variant of MOGA,
-remainding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for
+remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for
 a detailed analysis on how it differs and what could be expected from
@@
 actually performed. Thus, when accounting these simulations only unique simulations
-has been considered, removing repeations and unfeasibile
+has been considered, removing repetitions and unfeasible
 configurations.
@@
 These results are obtained in about 5 eras, and the main aim was
-demonstrating that with a so limited budget PS still can competer with
+demonstrating that with a so limited budget PS still can compete with
 genetic approach while even discovering very different Pareto fronts.
-Continuing with a more extendent simulation budget as depicted in
+Continuing with a more extended simulation budget as depicted in
 Figure~\ref{fig:pareto_fronts_500}, we can qualitatively observe that
-even if PS does not stricly outperforms genetic in terms of dominance, it shows in
+even if PS does not strictly outperforms genetic in terms of dominance, it shows in
 some cases largely Pareto in terms of extension. We can intuitively
@@
 enlarge the range itself, resulting in less dense but more extended
-Paretos. Of course we cannot classify this different behavior as
+Paretos. Of course we cannot classify this different behaviour as
 ``better'' or ``worse'' as compared to the genetic one, it depends on

### 2014-07-23 introduction.tex
typos

@@
 of the design space to be simulated grows with the product of
-cardinalities of each parameter, easily resulting in an untractable number
+cardinalities of each parameter, easily resulting in an intractable number
 of simulations. In these cases a ``Design Space
@@
 
-\section{Related work}
+\section{Related work and Contribution}
+\label{sec:Related-work}
 \comment{Preferisci che i related work siano in un'unica sezione con Intro?}
@@
 
-Some exploration strategies assume some kind of knowledge about
-the system parameters, their meaning and their impact on design objectives.
-The \emph{Dependency analysis}, proposed in \cite{givargis_tvlsi02}, is meant
-to take advantage of the parameter dependencies, a-priori known by the designer \comment{E' giusto, cosi'?}. Starting from them, he can construct a
-``dependency graph'' and recognize clusters, i.e. subsets of strongly
-dependency-connected parameters. Each cluster is exhaustively evaluated
-and its ``local'' Pareto set is found. Then, all local Pareto sets
-are merged. In this way, a series of local exhaustive evaluations
-are performed instead of an exhaustive evaluation of all the possible
-configurations. Some problems arise: i) In real scenarios, it may
-be difficult to recognize really independent clusters of parameters,
-because there may be interdependencies among a large number of
-parameters. This may lead to the need of an evaluation of
-almost all the possible configurations. ii) A designer may not have
-a precise and complete a-priori picture of the dependencies among parameters;
-for this reason the need of ``automated approaches for computing interdependencies'' is declared in the same paper. 
-These drawbacks are not present in our algorithm, since, although it leverages dependencies as in \cite{givargis_tvlsi02}, it is able to detect them automatically, with no a-priori knowledge required.
-Moreover, our algorithm is able to capture also ``local dependencies", i.e.
-dependencies that
-emerge only among certain ranges of parameters and may not hold when considering the entires ranges. This cannot be modeled in Dependency Analysis.
+Some exploration strategies assume some kind of knowledge about the
+system parameters, their meaning and their impact on design
+objectives.  The \emph{Dependency analysis}, proposed in
+\cite{givargis_tvlsi02}, is meant to take advantage of the parameter
+dependencies. Starting from them, he can construct a ``dependency graph''
+and recognize clusters, i.e. subsets of strongly dependency-connected
+parameters. Each cluster is exhaustively evaluated and its ``local''
+Pareto set is found. Then, all local Pareto sets are merged. In this
+way, a series of local exhaustive evaluations are performed instead of
+an exhaustive evaluation of all the possible configurations. Some
+problems arise: i) In real scenarios, it may be difficult to recognize
+really independent clusters of parameters, because there may be
+interdependencies among a large number of parameters. This may lead to
+the need of an evaluation of almost all the possible configurations.
+ii) A designer may not have a precise and complete a-priori picture of
+the dependencies among parameters; for this reason the need of
+``automated approaches for computing interdependencies'' is declared
+in the same paper.  These drawbacks are not present in our algorithm,
+since, although it leverages dependencies as in
+\cite{givargis_tvlsi02}, it is able to detect them automatically, with
+no a-priori knowledge required. Moreover, our algorithm is able to
+capture also ``local dependencies", i.e. dependencies that emerge only
+among certain ranges of parameters and may not hold when considering
+the entires ranges. This cannot be modelled in Dependency Analysis.
 

### 2014-07-23 algorithm.tex
added abstract, modified intro
typos
applied ACM style

@@
 \section{The algorithm}
+\label{sec:algorithm}
 
@@
 
-\item The avarage innovation score for the entire era is also calculated
+\item The average innovation score for the entire era is also calculated
 as:
@@
 remark \ref{rem:termination}).
-\begin{rem}
+\begin{remark}
 \label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/small_and_big}
+\includegraphics[width=0.5\columnwidth]{img/small_and_big}
 
@@
 
-\end{rem}
+\end{remark}
 
-\begin{rem}
+\begin{remark}
 The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/novelty_score}
+\includegraphics[width=0.5\columnwidth]{img/novelty_score}
 
@@
 
-\end{rem}
+\end{remark}
 
-\begin{rem}
+\begin{remark}
 The innovation score of a region is a measure of how much different
@@
 
-\end{rem}
+\end{remark}
 
-\begin{rem}
+\begin{remark}
 \label{rem:termination}The algorithm terminates when in the last
@@
 proposed approach.
-\end{rem}
+\end{remark}
 %!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
@@
 
-\begin{rem}
+\begin{remark}
 Merging and splitting the regions are very dynamic processes. A portion
@@
 other portions to be minutely scanned.
-\end{rem}
+\end{remark}

### 2014-07-23 concepts.tex
applied ACM style

--- 2013-09-26 concepts.tex
@@
 
-\label{sec:statement_of_the_problem}\index{DSE}
+\label{sec:statement_of_the_problem}
 
@@
 
+\begin{definition}[Pareto Set]
+\label{pers02.def:Pareto-set}
 The {\em Pareto-optimal set} of $S$ for the application $b$ is the
@@
 \[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
+\end{definition}
 that is, the set of configurations $\mathbf{c} \in
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}
-
+\includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
 \caption{Relation between Pareto set (its ``parameter space representation'')
 and Pareto front (``objective space representation'')}
-
 \end{figure}
 
-\subsection{Required Definitions and Concepts}
+\subsection{Sketch of the Idea}
 
@@
 fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated ineresting as much
+during exploration. So a region will be evaluated interesting as much
 as how different are its added Pareto front points from the ones already
 found.
-\begin{rem}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{rem}
-%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-%PARAMETRI SENZA ORDINAMENTO{]}
-\begin{defn}
-\emph{Parameter interval}
 
-Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
+%TODO: sync name of values with formulation
+\subsection{Required Definitions}
+\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
 A $p_{i}$- interval is
@@
 is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
-\end{defn}
+\end{definition}
 
-\begin{defn}
-\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}
+\begin{remark}
+We will consider only parameters $p_{i}$ with ordering, i.e. such
+that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
+to say $a<b$ or $a=b$ or $a>b$.
+\end{remark}
 
+%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
+%PARAMETRI SENZA ORDINAMENTO{]}
+\begin{definition}[Contiguous intervals]
+\label{pers02.def:Contiguous-intervals}
 Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
@@
 \end{itemize}
-\end{defn}
+\end{definition}
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}
+\includegraphics[width=0.5\columnwidth]{img/contiguous_intervals_or_not}
 
@@
 
-\begin{defn}
-\emph{Region}
-
-A region is a set of the following form:
+\begin{definition}[Region]A region is a set of the following form:
 \[
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/regions}
+\includegraphics[width=0.5\columnwidth]{img/regions}
 
@@
 \end{figure}
-\end{defn}
-\begin{rem}
+\end{definition}
+
+\begin{remark}
 We will talk later of ``big'' and ``small'' regions. The sense
@@
 is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{rem}
+\end{remark}
+
 We now provide some rules to split and merge regions. They will be
 useful when explaining our proposed exploration algorithm.
-\begin{defn}
-\emph{\label{pers02.def:Splitting-a-region}Splitting a region}
-
+\begin{definition}[Splitting a region]
+\label{pers02.def:Splitting-a-region}
 If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}
+\includegraphics[width=0.5\columnwidth]{img/splitting_the_region}
 
@@
 
-\end{defn}
+\end{definition}
 
-\begin{defn}
-\emph{Contiguous regions}
-
-Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
+\begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
 be two regions. They are said to be contiguous iff
@@
 \end{itemize}
-\end{defn}
+\end{definition}
 See figure \ref{pers02.fig:Contiguous-regions}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}
+\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}
 
@@
 
-\begin{defn}
-\emph{\label{pers02.def:Merging-regions}Merging regions}
-
+\begin{definition}[Merging regions]
+\label{pers02.def:Merging-regions}
 Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
@@
 \]
-\end{defn}
-\begin{rem}
+\end{definition}
+
+\begin{remark}
 $R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
 However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiuguous regions.
-\end{rem}
+$R_{1}$ and $R_{2}$ must be to contiguous regions.
+\end{remark}
 
-\begin{defn}
-\emph{Separation}
-
-Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
+\begin{definition}[Separation]Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
 be two points of $O_{1}\times\dots\times O_{m}$. The separation between
@@
 \]
+Notice that the separation is not a commutative operator.
+\end{definition}
 
-Notice that the separation is not a commutative operator.\end{defn}
-\begin{rem}
+\begin{remark}
 The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
+much we must vary $\mathbf{o}$ to transform it in $\mathbf{q}$.
 The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives
-\end{rem}
+the nature and the unit of measurement of the objectives.
+\end{remark}
 
-\begin{defn}
-\emph{Separation (alternative)}
-
-Another definition of separation could be:
+\begin{definition}[Separation (alternative)] Another definition of separation could be:
 \[
@@
 
-\end{defn}
+\end{definition}

### 2014-07-23 paper_ieee.tex
applied ACM style

--- 2014-07-23 paper.tex
@@
 
-\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
-%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
+%\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
+\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
 
@@
 Embedded Systems Design often requires conflicting objectives to be
-optimized with an appropriate choice of hardware/software parameters
-. Interdependencies among these parameters can make this task even
-more difficult, since an a-priori knowledge of them would  be required
-to develop an analytical model of the system. In this work we present
-PS, a multiobjective exploration strategy that introduces the notion
-of Parameters Space Representation. After a detailed formal
-description of the algorithm and its concepts, we show a
-hardware/software exploration case study. Qualitative and quantitative
-comparisons of PS against a well-know multiobjective genetic approach
-demonstrate that, while not outperforming it in terms of dominance, the
-proposed approach can trade the uniformity and granularity
-qualities of the solutions found for obtaining larger Pareto sets,
-thus representing a further choice for designer when objective constrains allow it.
+optimized with an appropriate choice of hardware/software parameters .
+Interdependencies among these parameters can make this task even more
+difficult, since an a-priori knowledge of them would  be required to
+develop an analytical model of the system. In this work we present PS,
+a multiobjective exploration strategy that introduces the notion of
+Parameters Space Representation. After a detailed formal description
+of the algorithm and its concepts, we show a hardware/software
+exploration case study. Qualitative and quantitative comparisons of PS
+against a well-know multiobjective genetic approach demonstrate that,
+while not outperforming it in terms of dominance, the proposed
+approach can trade the uniformity and granularity qualities of the
+solutions found for obtaining larger Pareto sets, thus representing a
+further choice for designer when objective constrains allow it.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-DSE, VLIW, MultiObjective
+DSE, MultiObjective Optimization, Genetic Algorithms
 \end{IEEEkeywords}
@@
 \section{Conclusions}
-This is the end
+In this work we presented a multiobjective strategy which 
+introduces the concept of Parameter Space representation of Pareto
+Set. A case study of a VLIW architecture involving strong
+hardware/software dependencies has been carried out to evaluate
+effectiveness with different amount of simulations budget.
+A qualitative/quantitative comparison against a widespread multiobjective genetic
+approach showed how the proposed strategy can result in a different
+distribution of Pareto points which trades solutions granularity with
+improved pareto extension.
 

### 2014-07-23 concepts.tex
AA: non ho fatto niente di che. Riprendo stasera

@@
 configurations [$\mathcal{C}(S) = V_1 \times V_2 \times \ldots
-\times V_n$]. Naturally not all the configurations of
-$\mathcal{C}(S)$ can really be mapped on $S$. We will call the set
-of configurations that can be physically mapped on $S$ the {\em
-feasible configuration space} of $S$ [and indicate it as
+\times V_n$]. Naturally, not all the configurations of
+$\mathcal{C}(S)$ can really be mapped on $S$, but only a subset 
+is feasible. We call this subset {\em
+feasible configuration space} $S$ and indicate it as
 $\mathcal{C}^*(S)$].
@@
 $\mathbf{c}'$ is said to {\em dominate} (or {\em eclipse})
-$\mathbf{c}''$, and is indicated as $\mathbf{c}' \succ
-\mathbf{c}''$, if given $\mathbf{o}'=E(\mathbf{c}', b)$ and
-$\mathbf{o}''=E(\mathbf{c}'', b)$ it results that $\mathbf{o}'
-\leq \mathbf{o}''$ and $\mathbf{o}' \neq \mathbf{o}''$. Where
+$\mathbf{c}''$, if, given $\mathbf{o}'=E(\mathbf{c}', b)$ and
+$\mathbf{o}''=E(\mathbf{c}'', b)$, it results that $\mathbf{o}'
+\leq \mathbf{o}''$ and $\mathbf{o}' \neq \mathbf{o}''$, where
 vector comparisons are interpreted component-wise and are true
 only if all of the individual comparisons are true ($o'_i \leq
-o''_i \ \forall \ i = 1,2,\ldots,m$).
+o''_i \ \forall \ i = 1,2,\ldots,m$). To indicate that 
+$\mathbf{c}'$ dominates $\mathbf{c}''$, we use the notation
+$\mathbf{c}' \succ \mathbf{c}''$.
 
@@
 set:
-\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
+\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ | \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
 \end{definition}
 that is, the set of configurations $\mathbf{c} \in
-\mathcal{C}^*(S)$ not dominated by any other configuration.
-Pareto-optimal configurations are configurations belonging to the
-Pareto-optimal set and the {\em Pareto-optimal front} is the image
-of the Pareto-optimal configurations, i.e. the set:
-\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
+\mathcal{C}^*(S)$ not dominated by any other \comment{feasible}
+ configuration.
+The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} is their image, i.e. the set:
+\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} | \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
 
@@
 
+\comment{Mi sembra solo un cambio di notazione. }
 On the contrary, we call ``parameter space representation'' of the
@@
 in which the designer can take advantage of well-known results or
-heuristics. For example, in a VLIW architecture consider a configuration
-with very few registers. It is well-known that, in such a condition,
-increasing the number of ALUs doesn't lead to tangible better performances
-but leads to an increase in area occupation. An intelligent exploration
-algorithm wouldn't waste time evaluating configurations with many
+heuristics. For example, if we consider a VLIW architecture in a configuration with very few registers, it is well-known that increasing the number of ALUs does not bring tangible better performances
+but only cause an increase in area occupation. An intelligent exploration
+algorithm would not waste time evaluating configurations with many
 ALUs and few registers. If $p_{1}$ is the parameter ``number of
@@
 \]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
+ (where $s_{1}$ and $s_{2}$ are some threshold values) is of modest
 interest. This example shows that some ``dependency relation'' between

### 2014-07-23 introduction.tex
AA: non ho fatto niente di che. Riprendo stasera

@@
 
-\comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }
-
 \section{Related work and Contribution}
 \label{sec:Related-work}
-\comment{Preferisci che i related work siano in un'unica sezione con Intro?}
 Many different design space exploration algorithms have been proposed
@@
 Finally in Section~\ref{sec:ee} we show a case study involving the
-exploration of the hardware/software parameters of a VLIW
-architecture, performing a qualitative and quantitative comparison of
+exploration of the hardware/software parameters of a Very Long
+ Instruction Word (VLIW) architecture, performing a qualitative
+ and quantitative comparison of
 PS agains the state-of-art of multiobjective genetic based approaches.

### 2014-07-23 paper.tex
AA: non ho fatto niente di che. Riprendo stasera

@@
-\documentclass[final,journal,letterpaper]{IEEEtran}
+%\documentclass[final,journal,letterpaper]{IEEEtran}
+\documentclass[prodmode,acmtecs]{acmsmall}
 
@@
 \usepackage{mathrsfs}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 
@@
 
-\usepackage{listings}
 \usepackage{listings}
@@
 %------------------------------------------------------------------------------
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{definition}
-\newtheorem{defn}{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{rem}{\protect\remarkname}
-
-%\newtheorem{defn}[thm]{\protect\definitionname}
+%\makeatletter
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+%\theoremstyle{plain}
+%\newtheorem{thm}{\protect\theoremname}
+%\theoremstyle{definition}
+%\newtheorem{defn}{\protect\definitionname}
 %\theoremstyle{remark}
-%\newtheorem{rem}[thm]{\protect\remarkname}
-%\makeatother
+%\newtheorem{rem}{\protect\remarkname}
 
@@
 \begin{document}
-
-\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
-\thanks{The authors are with the Dipartimento di Ingegneria
-Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}
+% Page heads
+\markboth{V. Catania et al.}{Parameter Space Representation of Pareto Front to
+Explore Hardware-Software Dependencies}
 
@@
 Explore Hardware-Software Dependencies}
-%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
-%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
-%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
-%set come un sottoinsieme dello spazio delle configurazioni.
+\author{VINCENZO CATANIA
+\affil{University of Catania}
+ANDREA ARALDO
+\affil{University of Catania}
+DAVIDE PATTI
+\affil{University of Catania}
+}
+
+%\maketitle
+\begin{abstract}
+Embedded Systems Design often requires conflicting objectives to be
+optimized with an appropriate choice of hardware/software parameters .
+Interdependencies among these parameters can make this task even more
+difficult, since an a-priori knowledge of them would  be required to
+develop an analytical model of the system. In this work we present PS,
+a multiobjective exploration strategy that introduces the notion of
+Parameters Space Representation. After a detailed formal description
+of the algorithm and its concepts, we show a hardware/software
+exploration case study. Qualitative and quantitative comparisons of PS
+against a well-know multiobjective genetic approach demonstrate that,
+while not outperforming it in terms of dominance, the proposed
+approach can trade the uniformity and granularity qualities of the
+solutions found for obtaining larger Pareto sets, thus representing a
+further choice for designer when objective constrains allow it.
+\end{abstract}
+
+\category{D.2.2}{Design Tools and Techniques}{}
+
+\terms{Design, Algorithms, Performance}
+
+\keywords{DSE, MultiObjective Optimization, Genetic Algorithms}
+
+\acmformat{Vincenzo Catania, Andrea Araldo and Davide Patti, 2014. Parameter Space Representation of Pareto Front to
+Explore Hardware-Software Dependencies.}
+
+\begin{bottomstuff}
+Author's addresses: V. Catania, DIEEI University of Catania;
+A. Araldo, DIEEI University of Catania;
+D. Patti, DIEEI University of Catania.
+\end{bottomstuff}
 
 \maketitle
-\begin{abstract}
-Embedded Systems Design often requires conflicting objectives to be
-optimized with an appropriate choice of hardware/software parameters
-. Interdependencies among these parameters can make this task even
-more difficult, since an a-priori knowledge of them would  be required
-to develop an analytical model of the system. In this work we present
-PS, a multiobjective exploration strategy that introduces the notion
-of Parameters Space Representation. After a detailed formal
-description of the algorithm and its concepts, we show a
-hardware/software exploration case study. Qualitative and quantitative
-comparisons of PS against a well-know multiobjective genetic approach
-demonstrate that, while not outperforming it in terms of dominance, the
-proposed approach can trade the uniformity and granularity
-qualities of the solutions found for obtaining larger Pareto sets,
-thus representing a further choice for designer when objective constrains allow it.
-\end{abstract}
-
-%------------------------------------------------------------------------------
-%\IEEEkeywords{...}
-
-\begin{IEEEkeywords}
-DSE, VLIW, MultiObjective
-\end{IEEEkeywords}
 %------------------------------------------------------------------------------
@@
 
-\bibliographystyle{IEEEtran} 
+\bibliographystyle{ACM-Reference-Format-Journals} 
 \bibliography{bibliography}

### 2014-07-24 appendix.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni

--- 2014-07-23 concepts.tex
@@
-\section{Preliminary Concepts}
-
-\subsection{Formulation of the Problem}
-
-\label{sec:statement_of_the_problem}
-
-Let $S$ be a parameterized system with $n$ parameters. The generic
-parameter $p_i, \ i \in \{1,2,\ldots,n\}$ can take any value in
-the set $V_i$. A {\em configuration} $\mathbf{c}$ of the system
-$S$ is a $n$-tuple $\langle v_1,v_2,\ldots,v_n \rangle$ in which
-$v_i \in V_i$ is the value fixed for the parameter $p_i$. The {\em
-configuration space} (or {\em design space}) of $S$ [which we will
-indicate as $\mathcal{C}(S)$] is the complete range of possible
-configurations [$\mathcal{C}(S) = V_1 \times V_2 \times \ldots
-\times V_n$]. Naturally not all the configurations of
-$\mathcal{C}(S)$ can really be mapped on $S$. We will call the set
-of configurations that can be physically mapped on $S$ the {\em
-feasible configuration space} of $S$ [and indicate it as
-$\mathcal{C}^*(S)$].
-
-Let $m$ be the number of objectives to be optimized (e.g. power,
-cost, performance, etc.). An {\em evaluation function}
-$E:\mathcal{C}^*(S)\times \mathcal{B} \longrightarrow \Re^m$ is a
-function that associates each feasible configuration of $S$ with
-an $m$-tuple of values corresponding to the objectives to be
-optimized when any application belonging to the set of benchmarks
-$\mathcal{B}$ is executed.
-
-Given a system $S$, an application $b \in \mathcal{B}$ and two
-configurations $\mathbf{c}', \mathbf{c}'' \in \mathcal{C}^*(S)$,
-$\mathbf{c}'$ is said to {\em dominate} (or {\em eclipse})
-$\mathbf{c}''$, and is indicated as $\mathbf{c}' \succ
-\mathbf{c}''$, if given $\mathbf{o}'=E(\mathbf{c}', b)$ and
-$\mathbf{o}''=E(\mathbf{c}'', b)$ it results that $\mathbf{o}'
-\leq \mathbf{o}''$ and $\mathbf{o}' \neq \mathbf{o}''$. Where
-vector comparisons are interpreted component-wise and are true
-only if all of the individual comparisons are true ($o'_i \leq
-o''_i \ \forall \ i = 1,2,\ldots,m$).
-
-\begin{definition}[Pareto Set]
-\label{pers02.def:Pareto-set}
-The {\em Pareto-optimal set} of $S$ for the application $b$ is the
-set:
-\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
-\end{definition}
-that is, the set of configurations $\mathbf{c} \in
-\mathcal{C}^*(S)$ not dominated by any other configuration.
-Pareto-optimal configurations are configurations belonging to the
-Pareto-optimal set and the {\em Pareto-optimal front} is the image
-of the Pareto-optimal configurations, i.e. the set:
-\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
-
-The aim of a Design Space Exploration (DSE) strategy is to give a
-good approximation of the Pareto-optimal front for a system $S$ and an
-application $b$, simulating as few configurations as possible.
-
-%----------------------------------------------------------------
-
-On the contrary, we call ``parameter space representation'' of the
-Pareto set the representation in which each configuration $\mathbf{p}$
-is simply represented as a point of $P_{1}\times\dots\times P_{n}$
-space. We will investigate the relation between the ``objective space
-representation'' and the ``parameter space representation''. We
-are particularly interested in the relation between the evolution
-of the objective space representation of the Pareto set and the evolution
-of its parameter space representation.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
-\caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'')}
-\end{figure}
-
-\subsection{Sketch of the Idea}
-
-In the design process, there are often a lot of ``local decisions''
-in which the designer can take advantage of well-known results or
-heuristics. For example, in a VLIW architecture consider a configuration
-with very few registers. It is well-known that, in such a condition,
-increasing the number of ALUs doesn't lead to tangible better performances
-but leads to an increase in area occupation. An intelligent exploration
-algorithm wouldn't waste time evaluating configurations with many
-ALUs and few registers. If $p_{1}$ is the parameter ``number of
-registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
-can say that the region:
-\[
-R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
-\]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
-interest. This example shows that some ``dependency relation'' between
-parameters may exist and can be exploited to guide the exploration:
-the dependencies between parameters can suggest to the designer that,
-if a parameter lies in a range, there are ranges of the other there
-aren't worth exploring. Intuitively, the Cartesian product of these
-ranges is an ``uninteresting region''.
-
-The problem is that, in complex scenarios, not all relations of this
-kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or there may be ``local dependencies'', i.e. two
-parameters may be related by a dependency but only if their values
-lie on some ranges (so we can't treat them as they were related by
-a true dependency). Therefore, as stated in section \ref{sec:Related-work},
-setting up an exploration trying to take into account as much dependencies
-as possible is a very hard task that is destined to be incompletely
-accomplished. We need a methodology to ``automatically'' recognize
-interesting or uninteresting regions without requiring a priori knowledge
-to the designer.
-
-We also consider, in measuring how much interesting a region is, the
-``innovation'' that it adds. If, during a design space exploration,
-a Pareto front is temporarily calculated, adding a new Pareto front
-point near to the previous ones is not a considerable ``innovation'',
-because the way it fulfils the objectives is very similar to other
-already evaluated configurations. On the contrary, adding a new Pareto
-front point that is very distant from previous ones is remarkable,
-because it let the experimenter realize that the objectives can be
-fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated interesting as much
-as how different are its added Pareto front points from the ones already
-found.
-
-%TODO: sync name of values with formulation
-\subsection{Required Definitions}
-\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
-A $p_{i}$- interval is
-\[
-\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
-\]
- (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
-is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
-\end{definition}
-
-\begin{remark}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-\end{remark}
-
-%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-%PARAMETRI SENZA ORDINAMENTO{]}
-\begin{definition}[Contiguous intervals]
-\label{pers02.def:Contiguous-intervals}
-Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous iff
-\begin{itemize}
-\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
-and
-\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
-interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
-is a $p_{i}$- interval
-\end{itemize}
-\end{definition}
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/contiguous_intervals_or_not}
-
-\caption{Examples of contiguous and not contiguous intervals}
-
-\end{figure}
-
-\begin{definition}[Region]A region is a set of the following form:
-\[
-R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
-\]
- (see figure \ref{pers02.fig:Examples-of-regions})
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/regions}
-
-\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}
-
-\end{figure}
-\end{definition}
-
-\begin{remark}
-We will talk later of ``big'' and ``small'' regions. The sense
-of these terms is related to the cardinality of regions. A region
-$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
-\[
-\left|R_{1}\right|>\left|R_{2}\right|
-\]
- where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
-of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-if:
-\[
-\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
-\]
-
-Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{remark}
-
-We now provide some rules to split and merge regions. They will be
-useful when explaining our proposed exploration algorithm.
-\begin{definition}[Splitting a region]
-\label{pers02.def:Splitting-a-region}
-If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
-it can be split in two contiguous intervals
-\[
-\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
-\]
- such that
-\[
-\begin{cases}
-\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
-\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
-\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
-\end{cases}
-\]
-
-If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
-cannot be split.
-
-If $\left[a_{i}..b_{i}\right]$ can be split, we define
-\[
-I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
-\]
- else
-\[
-I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
-\]
-
-The whole region can be split in the following subregions
-\[
-\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
-\]
-
-See figure \ref{pers02.fig:Splitting-a-region}.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/splitting_the_region}
-
-\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}
-
-\end{figure}
-
-\end{definition}
-
-\begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff
-\begin{itemize}
-\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
-for all $i\neq j$ 
-\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
-contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
-\end{itemize}
-\end{definition}
-See figure \ref{pers02.fig:Contiguous-regions}.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}
-
-\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
-regions}
-\end{figure}
-
-\begin{definition}[Merging regions]
-\label{pers02.def:Merging-regions}
-Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
-ones. Because of the definition of contiguous intervals, it is possible
-that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
-intervals and obtain a new interval, as the following
-\[
-\left[t_{j},z_{j}\right]=\begin{cases}
-\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
-\end{cases}
-\]
-
-The region ``$R_{1}$ merged with $R_{2}$'' is defined as
-\[
-R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
-\]
-
-Such an $R$ will be indicated with the following notation:
-\[
-R=R_{1}+R_{2}
-\]
-\end{definition}
-
-\begin{remark}
-$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
-However, using $R_{1}+R_{2}$ notation, we enforce the argument that
-$R_{1}$ and $R_{2}$ must be to contiguous regions.
-\end{remark}
-
-\begin{definition}[Separation]Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
-be two points of $O_{1}\times\dots\times O_{m}$. The separation between
-$\mathbf{o}$ and $\mathbf{q}$ is 
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-Notice that the separation is not a commutative operator.
-\end{definition}
-
-\begin{remark}
-The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transform it in $\mathbf{q}$.
-The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives.
-\end{remark}
+Metto qua tutte le cose che non si possono lasciare nel testo ma che e' un peccato buttare nel dimenticatoio
 

### 2014-07-24 concepts.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni

@@
-\section{Preliminary Concepts}
+\section{Underlying concepts and theoretical formulation}
+\comment{Attenzione: siamo capaci di avere a che fare con unfeasible configurations?}
 
-\subsection{Formulation of the Problem}
+\comment{Theoretical suona troppo pomposo? Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio e aggiutare i nomi degli assi}
+In this section we provide the concepts and the formal definitions that we will use later to express our algorithm.
+\comment{Ha un nome l'algoritmo?} First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on.
+Then, we sketch the fundamental idea behind our algorithm.
+Finally, we provide a formal definition of the regions, of their properties and of the operations that will be performed on them by the algorithm.
 
-\label{sec:statement_of_the_problem}
+\subsection{Pareto-set and Pareto-front}
+\label{sec:pareto}
 
@@
 \caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'')}
+and Pareto front (``objective space representation'').
+\comment{Questa figura sembra molto ``didattica''.
+La relazione tra Pareto front e Pareto set magari deve essere illustarta a studenti ma in un paper va bene?
+Io la apprezzerei se la trovassi, ma di solito si fa cosi'?}}
 \end{figure}
@@
 \subsection{Sketch of the Idea}
+\secL{sketch}
 
@@
 \]
- (where $s_{1}$ and $s_{2}$ are some threshold values) is of modest
-interest. This example shows that some ``dependency relation'' between
-parameters may exist and can be exploited to guide the exploration:
-the dependencies between parameters can suggest to the designer that,
-if a parameter lies in a range, there are ranges of the other there
-aren't worth exploring. Intuitively, the Cartesian product of these
-ranges is an ``uninteresting region''.
+ (where $s_{1}$ and $s_{2}$ are some threshold values) is \emph{uninteresting}. This clearly shows that there are cases when, if a parameter lies in
+a certain range, there are ranges of the other that are not worth exploring. Intuitively, the Cartesian product of these ranges is an ``uninteresting
+ region''.
 
@@
 kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or there may be ``local dependencies'', i.e. two
+to the designer. Or they may be ``local'', i.e. two
 parameters may be related by a dependency but only if their values
-lie on some ranges (so we can't treat them as they were related by
-a true dependency). Therefore, as stated in section \ref{sec:Related-work},
+lie on some ranges (so we cannot treat them as they were related by
+a ``complete'' dependency). 
+Therefore, as stated in section \ref{sec:Related-work},
 setting up an exploration trying to take into account as much dependencies
-as possible is a very hard task that is destined to be incompletely
+as possible is a hard task that is destined to be incompletely
 accomplished. We need a methodology to ``automatically'' recognize
 interesting or uninteresting regions without requiring a priori knowledge
-to the designer.
+to the designer, that is what our algorithm does.
 
 We also consider, in measuring how much interesting a region is, the
-``innovation'' that it adds. If, during a design space exploration,
+\emph{innovation} that it adds. If, during a design space exploration,
 a Pareto front is temporarily calculated, adding a new Pareto front
-point near to the previous ones is not a considerable ``innovation'',
-because the way it fulfils the objectives is very similar to other
+point near to the previous ones is not a considerable innovation,
+because the way it fulfills the objectives is similar to the other
 already evaluated configurations. On the contrary, adding a new Pareto
-front point that is very distant from previous ones is remarkable,
-because it let the experimenter realize that the objectives can be
-fulfilled in a completely different way from what he already found
-during exploration. So a region will be evaluated interesting as much
-as how different are its added Pareto front points from the ones already
-found.
+front point that is distant from previous ones is remarkable,
+since it let the experimenter discover potential performance that have not yet considered before.
 
 %TODO: sync name of values with formulation
-\subsection{Required Definitions}
-\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
+\subsection{Formal definitions}
+We start by defining the parameter interval and the concept of interval contiguity.
+Using these definition we construct the region and define the region contiguity.
+Then we define the operations of splitting and merging regions.
+Finally, we provide the definition of separation.
+
+\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in V_{i},a_{i}<b_{i}$.
 A $p_{i}$- interval is
@@
 \]
- (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
-is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
+i.e. taking the interval $\left[a_{i}..b_{i}\right]$
+is the set of values of $V_{i}$ lying in $\left[a_{i},b_{i}\right]$)
 \end{definition}
 
-\begin{remark}
-We will consider only parameters $p_{i}$ with ordering, i.e. such
-that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
+We consider only parameters $p_{i}$ with ordering, i.e. such
+that $\forall a,b\in V_{i}$ it is possible
 to say $a<b$ or $a=b$ or $a>b$.
-\end{remark}
 
@@
 %PARAMETRI SENZA ORDINAMENTO{]}
+
+	\begin{figure}[t]
+		\begin{center}
+			\subfigure[Examples of contiguous and non contiguous intervals.]{
+				\includegraphics[width=0.45\textwidth]{img/contiguous_intervals_or_not} }
+			\subfigure[Examples of regions.]{
+				\includegraphics[width=0.45\textwidth]{img/regions} }
+		    \figLC{interval_and_region}{Intervals and regions.}
+		\end{center}
+	\end{figure}
+
 \begin{definition}[Contiguous intervals]
 \label{pers02.def:Contiguous-intervals}
-Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous iff
-\begin{itemize}
-\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
-and
-\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
-interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
-is a $p_{i}$- interval
-\end{itemize}
+Two intervals are contiguous iff they do not overlap and merging them results in a new interval.More formally, let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
+be two $p_{i}$-intervals. They are said to be contiguous (see \figR{interval_and_region}(a) ) iff
+\begin{align}\begin{array}{l}
+	\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset \mbox{      and} \\
+	\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
+interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]
+\end{array}\end{align}
 \end{definition}
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/contiguous_intervals_or_not}
 
-\caption{Examples of contiguous and not contiguous intervals}
-
-\end{figure}
-
-\begin{definition}[Region]A region is a set of the following form:
+\begin{definition}[Region] 
+A region is a cartesian product of parameter intervals, as illustrated in \figR{interval_and_region} (b).
+More formally, if $p_1,\dots,p_n$ are the parameters of the system, and $\left[ a_{i}..b_{i} \right]$ is a $p_i$-interval, a region is a set of the following form:
 \[
@@
 \]
- (see figure \ref{pers02.fig:Examples-of-regions})
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/regions}
-
-\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}
-
-\end{figure}
 \end{definition}
 
-\begin{remark}
-We will talk later of ``big'' and ``small'' regions. The sense
-of these terms is related to the cardinality of regions. A region
-$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
-\[
-\left|R_{1}\right|>\left|R_{2}\right|
-\]
- where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
-of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
+We will refer later to ``big'' and ``small'' regions. The sense
+of these terms is related to the cardinality of regions.
+\begin{definition}[Interval and region comparison]
+A $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
 is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-if:
-\[
-\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
-\]
-
-Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
-is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
-\end{remark}
+iff 
+$\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|$.
+Similarly, a region $R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
+$\left|R_{1}\right|>\left|R_{2}\right|$
+\end{definition}
+Note that with $|\cdot|$ we indicate the cardinality of a set.
+Therefore, $\left|\left[a_{i}..b_{i}\right]\right|$ is the number of values of $V_i$ lying between $a_{i}$ and $b_{i}$ and has not to be confused with $b_i - a_i$.
+Similarly $\left|R_{i}\right|$ is the number of configurations inside the region $R_i$.
 
@@
 useful when explaining our proposed exploration algorithm.
-\begin{definition}[Splitting a region]
+\begin{definition}[Splitting an interval]
 \label{pers02.def:Splitting-a-region}
-If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
-it can be split in two contiguous intervals
-\[
-\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
-\]
+Given a $p_i$ interval $\left[a_{i}..b_{i}\right]$ with more than one element, i.e.
+$\left|\left[a_{i}..b_{i}\right]\right|>1$, the splitting operation produces as result two contiguous intervals $\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]$
  such that
-\[
+	\begin{align}
 		\begin{cases}
@@
 		\end{cases}
-\]
+	\end{align}
 
-If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
-cannot be split.
+We define the split operator $\psi$ as the one that, applied to the intervals, gives the result of the split operation, i.e., in the case above, $\psi \left[a_{i}..b_{i}\right]=\lbrace \left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right] \rbrace$.
+If $\left|\left[a_{i}..b_{i}\right]\right|=1$, the interval
+cannot be split and $\psi \left[a_{i}..b_{i}\right]=\left[a_{i}..b_{i}\right]$.
+\end{definition}
 
-If $\left[a_{i}..b_{i}\right]$ can be split, we define
-\[
-I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
-\]
- else
-\[
-I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
-\]
+The interval split is illustrated in \figR{split}~(a).
+Note that, when splitting an interval, the resulting intervals must satisfy two conditions: (i) they must be contiguous and, merging them, the initial interval must be obtained; (ii) the point in which we cut the interval is not arbitrary, but it is close to the middle.
 
-The whole region can be split in the following subregions
-\[
-\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
-\]
-
-See figure \ref{pers02.fig:Splitting-a-region}.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/splitting_the_region}
-
-\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}
-
-\end{figure}
+\begin{definition}[Splitting a region]
+\label{pers02.def:Splitting-a-region}
+Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it in a set of subregions obtained splitting each $p_i$-interval and combining the resulting subintervals with the cartesian product, as in \figR{split}~(b).
+Formally:
+	\begin{align}
+		\psi(R) = \left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in \psi\left[a_{i}..b_{i}\right]  \right\} 
+	\end{align}
 
@@
 
+	\begin{figure}[t]
+		\begin{center}
+			\subfigure[Splitting an interval.]{
+				\includegraphics[width=0.30\textwidth]{img/splitting_intervals} }
+			\subfigure[Splitting a region.]{
+				\includegraphics[width=0.60\textwidth]{img/splitting_regions} }
+		    \figLC{split}{Split operations.}
+		\end{center}
+	\end{figure}
+
 \begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff
-\begin{itemize}
-\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
-for all $i\neq j$ 
-\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
-contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
-\end{itemize}
+be two regions. They are said to be contiguous iff they do not overlap and, merging them, a new region can be obtained. Formally, $R_1$ and $R_2$ are contiguous iff there exists a $j$ such that:
+	\begin{align}\begin{array}{l}
+		\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
+	\mbox{ for } $i\neq j \mbox{      and} \\
+		\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right] \mbox{ are contiguous intervals}
+	\end{array}\end{align}
+\noindent We call $p_j$ the \emph{contiguity parameter} for the two regions.
 \end{definition}
-See figure \ref{pers02.fig:Contiguous-regions}.
+
+Examples of contiguous and non contiguous regions are given in \figR{contiguous_regions}. 
+\comment{Spiegare le figure e inserire a dx una figura con le contiguous regions mergiate.
+Le definizioni buttate cosi' rendono difficile la lettura a chi non sa ancora dove vogliamo andare a parare.
+Giustifica ogni definizione prima di darla.
+Ad es.
+quando parli di splittare, spiega che quando le regioni sono interessanti noi le splittiamo cosi' da esplorarle meglio.
+Al contrario quando le mergiamo.
+Mettere una sezione del tipo "Required operations at a glance" per giustificare tutte le definizioni prima di buttarle}.
 
@@
 		\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}
+		\figLC{contiguous_regions}{Contiguous and non contiguous
+		regions.}
+	\end{figure}
 
-\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
-regions}
-\end{figure}
+\begin{definition}[Merging intervals]
+Let $\left[a_{i}\dots b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$ be two contiguous $p_i$-intervals. The merge operation applied to them produces a new $p_i$-interval of the following form:
+	\begin{align}
+		\mu	 \left( \begin{array}{l}
+				\left[a_{j}..y_{j}\right] \\
+				\left[x_{j}..b_{j}\right]
+		     \end{array} \right)
+		=\begin{cases}
+			\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
+			\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
+		\end{cases}
+	\end{align}
+
+\end{definition}
 
@@
 \label{pers02.def:Merging-regions}
-Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
-ones. Because of the definition of contiguous intervals, it is possible
-that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
-intervals and obtain a new interval, as the following
-\[
-\left[t_{j},z_{j}\right]=\begin{cases}
-\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
-\end{cases}
-\]
-
-The region ``$R_{1}$ merged with $R_{2}$'' is defined as
-\[
-R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
-\]
-
-Such an $R$ will be indicated with the following notation:
-\[
-R=R_{1}+R_{2}
-\]
+Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$ be two contiguous regions and let $p_j$ be the contiguity parameter. 
+The merge operation $\mu$ applied to $R_1$ and $R_2$ produces a new region of the following form:
+	\begin{align}
+		\mu(R_1,R_2)=\prod_{i<j}\left[a_{i}..b_{i}\right]
+		\times
+		\mu	 \left( \begin{array}{l}
+				\left[a_{j}..y_{j}\right] \\
+				\left[x_{j}..b_{j}\right]
+		     \end{array} \right)
+		\times
+		\prod_{i>j}\left[a_{i}..b_{i}\right]
+	\end{align}
 \end{definition}
 
-\begin{remark}
-$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
-However, using $R_{1}+R_{2}$ notation, we enforce the argument that
+Note that $\mu(R_{1},R_{2})$ is mathematically equivalent to $R_{1}\cup R_{2}$. However, we use the notation above to enforce the requirement that
 $R_{1}$ and $R_{2}$ must be to contiguous regions.
-\end{remark}
 
-\begin{definition}[Separation]Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
-be two points of $O_{1}\times\dots\times O_{m}$. The separation between
-$\mathbf{o}$ and $\mathbf{q}$ is 
+In \secR{sketch} we observed that, in order to estimate how much interesting is a region, it is crucial to understand the novelty that it introduces, i.e.
+how distant the Pareto-optimal configurations discovered in that region are from the Pareto-optimal configuration previously discovered.
+The concept of distance is expressed by the operator defined in the next definition.
+We prefer to call it \emph{separation} rather than \emph{distance}, because usually distance denote a commutative operator while our definition of separation is non commutative.
+
+\begin{definition}[Separation]
+Let $\mathbf{c}',\mathbf{c}''\in S$ be two configurations, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e.
+$\mathbf{o}'=E \left(\mathbf{c}', b\right)$, $\mathbf{o}''=E \left(\mathbf{c}'', b\right)$, where $E$ is the evaluation function.
+The separation between
+$\mathbf{c}'$ and $\mathbf{c}''$ is 
 	\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
+	s\left(\mathbf{c}'\rightarrow\mathbf{c}''\right)=\sum_{i=1}^{m}\left|\frac{o'_{i}-o''_{i}}{o'_{i}}\right|
 	\]
-Notice that the separation is not a commutative operator.
+where $o'_i$ and $o''_i$ are the $i$-th components of $\mathbf{o}'$ and $\mathbf{o}''$, respectively.
 \end{definition}
 
-\begin{remark}
-The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
-much we must vary $\mathbf{o}$ to transform it in $\mathbf{q}$.
-The separation is a ``normalized'' measure that is independent of
-the nature and the unit of measurement of the objectives.
-\end{remark}
-
-\begin{definition}[Separation (alternative)] Another definition of separation could be:
-\[
-s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
-\]
-
-\end{definition}
+The separation between $\mathbf{c}'$ and $\mathbf{c}''$ measures how
+much we must vary the image of the former to obtain the image of the latter.
+Note that the separation is a \emph{normalized} measure, thanks to $o'_i$ at the denominator.
+This is important since usually objectives are heterogeneous, e.g.
+delay and power consumption, having different unity of measurement and different scale.
+If we did not use a normalized measure, in presence of objectives whose absolute values are small and other objectives with big values, the notion of distance would have been biased toward the latter.

### 2014-07-24 algorithm.tex
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

@@
 \label{sec:algorithm}
+\comment{Mettiamo PS algorithm come titolo della sezione almeno rinforziamo nella memoria il suo nome?}
+In this section we present PS, the algorithm that we propose to perform the Design Space Exploration (DSE).
+As any other DSE algorithm, its input is the parameterized system $S$ and a benchmark application $b$, while the output is an approximation of the Pareto-optimal set $\mathcal{P}\left(S,b\right)$.
+\comment{E' corretto?}
+PS is iterative and we will describe, separately, the initialization phase, the operations performed inside each iteration and the condition that triggers the termination.
 
-The algorithm we present is iterative. Each iteration is called \emph{era}.
+By a slightly abuse of notation, considering a subset $I$ of the configuration space, we will denote with $\mathcal{P}(I,b)$ the non-dominated feasible configurations in $I$, i.e.
+	\begin{align}
+		\mathcal{P}(I,b)=
+		\left\{ \mathbf{c} \in I \cap \mathcal{C}^*(S) | \nexists \ \mathbf{c}' \in I \cap \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \right\}
+	\end{align}
+Since in each run of the algorithm we will consider only one benchmark application $b\in\mathcal{B}$, we will omit it, replacing, for example, $\mathcal{P}(I,b)$ with  $\mathcal{P}(I)$.
 
-Each era $era_{i}$ is characterized by 
+Each iteration is called \emph{era}. The $i$-th era is characterized by: 
 	\begin{itemize}
-\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
-$P_{1}\times\dots\times P_{n}$ is divided
-\item its Pareto set $\mathscr{P}_{i}$
-\item a set $test_{i}$ of at most $K$ configurations to evaluate
+	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
+	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
+	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
+	\item a set $test_{i}$ of at most $K$ configurations evaluated in the era. \comment{Nella era i o nella successiva?}
 	\end{itemize}
-$K$ is a parameter that must be set before the algorithm runs.
+$K$ is a parameter that must be set before the algorithm runs. \comment{Spiegare un po' l'impatto di K.} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
+	\begin{align}\begin{array}{l}
+		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
+		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
+	\end{array}\end{align}
 
-\subsection{Start Condition}
-$\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
-i.e. era $0$ has only one region that is the whole parameter space.
+\comment{Prima di sbattere tutta la sfilza di steps, dovremmo dare un'idea preliminare di cosa si andra' a fare.}
+
+\subsection{Initialization}
+We fix $\mathcal{R}_0$, $\mathscr{P}_0$ and $test_0$ for the era $0$ as follows. Era $0$ has only one region that is the whole parameter space,
+i.e. $\mathcal{R}_{0}=\left\{ V_{1}\times\dots\times V_{n}\right\} $.
 A random set $test_{0}$ of $K$ configurations is evaluated. The
 Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
-calculated (see def \ref{pers02.def:Pareto-set} for the definition
-of the operator $\mathscr{P}_{i}$ over a set)
+calculated.
 
-\subsection{Iteration Rules}
+\subsection{Iteration steps}
 
@@
 \begin{enumerate}
-\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
-$test_{R,i}$ of configurations is randomly chosen in%
-\footnote{Therefore the chosen configurations can only be configurations of
-$R$ not yet evaluated in past eras.%
-} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
-in $test_{R,i}$ is set to%
-\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
-are to be chosen, but if not yet evaluated configurations in $R$
-are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
-are chosen%
-} 
+\item \label{pers02.enu:K}
+In each era $i$, a set $test_i$ of $K$ configurations will be evaluated. We call them \emph{test configurations} and selecting them is exactly the goal of this step.
+We select only \emph{new} configurations, i.e. the ones that have not been evaluated in past eras. In other words, $test_i$ must not contain $\bigcup_{j=0}^{i-1}test_{j}$.
+Since all regions $R$ in the configuration space partition $\mathcal{R}_{i}$ must be properly explored, we have to distribute the test configurations among all these regions.
+For this reason, $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations are randomly extracted from the new configurations of each region $R\in\mathcal{R}_{i}$.
+We denote the set of the selected configurations with $test_{R,i}$ and, obviously, $\bigcup_{R\in\mathcal{R}_{i}} test_{R,i} = test_i$.
+ In case the new configurations in $R$ are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them are selected.
+In this case $test_{R,i}=R\setminus\bigcup_{j=0}^{i-1}test_{j}$, where  $\bigcup_{j=0}^{i-1}test_{j}$ is the set of the configurations already in the past.\footnote{Note that if such regions exist, the total number of evaluations in era $i$ will be less than $K$}
+\item All configurations on $test_{i}$ are simulated.
+\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as the set of non-dominated configurations among the ones evaluated so far, i.e.
 	\[
-\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
+	\mathscr{P}_{i} \triangleq
+	\mathscr{P}\left(\bigcup_{j\leq i}test_j\right)=
+	\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
 	\]
-The set 
+where the last equality can easily be proved.
+
+\item \label{pers02.enu:novelty_score_of_a_configuration}
+The test configurations that are dominated, i.e.
+do not belong to $\mathscr{P}_i$, are neglected, while an \emph{innovation score} is given to the other ones, computed on the base of their separation from the non-dominated configurations of the past eras.
+Recalling that $s$ is the separation (see \defR{separation}), the innovation score of a non-dominated test configuration $\mathbf{c}^*$ is defined as
 	\[
-test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
+	is\left(\mathbf{c}^*\right)=\min\left\{ \left.s\left(\mathbf{c}\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\} 
 	\]
- is defined. 
-\item All configurations on $test_{i}$ are simulated.
-\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
+In other words, a configuration $\mathbf{c}^*$ is characterized by as much innovation
+as more separated it is from the configurations of the previous era.
+
+\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
+as the sum of the innovation scores of its non-dominated test configurations:
 	\[
-\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
+	is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} 
 	\]
 
-\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
-of%
-\footnote{The innovation score is not given to those points in $test_{i}$ that
-are not in the Pareto set%
-} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
-}defined as:
-\[
-is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
-\]
- (a configuration $\mathbf{p}$ is characterized by as much innovation
-as more separated it is from the configurations of the previous era)\@.
-\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
-as:
-\[
-is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
-\]
-
-\item The total innovation score for the entire era is:
+\item The total innovation and average score for the entire era is calculated:
 	\[
@@
 
-\item The average innovation score for the entire era is also calculated
-as:
-\[
-is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
-\]
-where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
-era $i$ .
-\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
-will be discussed later):
+\item The configuration space partition $\mathcal{R}_{i}$ is divided in three subsets, that we will comment later \comment{e invece sarebbe bene commentarli ora, anche}:
 
@@
 	 where $\alpha$ is a constant defined by the designer (for example
-$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
-(as stated in def \ref{pers02.def:Splitting-a-region})
+	$\alpha=1.2$). 
 	\item low innovation regions 
@@
 	\]
-They are not changed.
 	\item no innovation regions 
@@
 
-\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
-with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
-couples is indicated as $\mathcal{C}$. The couples of regions are
-merged:
-\[
-\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
-\]
- (see def \ref{pers02.def:Merging-regions})
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
-as:
+\item The goal of this step is preparing the regions that will compose the configuration space partition of the next era, i.e. $\mathscr{R}_{i+1}$. The following operations are performed:
+	\begin{enumerate}
+		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split obtaining $\psi(R)$, as stated in def \defR{splitting-a-region}.
+We denote with $\psi\left(\mathscr{R}_{i,h}\right)$ the set of regions obtained as explained.
+		\item Low innovation regions are left unchanged.
+		\item No innovation regions are merged, two by two.
+To do so, couples of no innovation contiguous regions $(R_1,R_2)$ are selected.
+We denote the set of these couples as $\mathscr{M}_i$.
+This set is constructed such that couples are independent, i.e.
+there cannot be two of them sharing a region.
+In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq$.
+We merge each couple of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
+We stress that the regions that belong to each selected couple must be contiguous, otherwise it is impossible to merge them.
+We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e.
+$\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$
+	\end{enumerate}
+
+\item The set of regions $\mathcal{R}_{i+1}$ for the following era is computed as:
 	\[
@@
 	\[
-=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
+	=\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
 	\]
 	\[
-\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
+	\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
 	\]
-\[
-\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
-\]
+\end{enumerate}
 
-\end{enumerate}
+\comment{commentare questa formula}
+
+\comment{SONO ARRIVATO A LEGGERE QUA}
 
@@
 \end{figure}
+
+\comment{Ci vorrebbe una rappresentazione schematica dell'algoritmo usando l'ambiente latex Algorithm o non mi ricordo come si chiama}
 

### 2014-07-24 concepts.tex
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

@@
 
-\comment{Theoretical suona troppo pomposo? Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio e aggiutare i nomi degli assi}
-In this section we provide the concepts and the formal definitions that we will use later to express our algorithm.
-\comment{Ha un nome l'algoritmo?} First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on.
+\comment{Theoretical suona troppo pomposo?
+Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come si vede in \figR{3}.
+Aggiustare i nomi degli assi che in alcune figure sono sbagliati.
+O forse basta esportarli col nuovo libreoffice che fa meglio}
+In this section we provide the concepts and the formal definitions that we will use later to express PS, the algorithm we propose.
+ First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on.
 Then, we sketch the fundamental idea behind our algorithm.
@@
 \subsection{Pareto-set and Pareto-front}
-\label{sec:pareto}
+\secL{pareto}
 
@@
 set:
-\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ | \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
+\[ \mathcal{P}(S,b) = \left\{ \mathbf{c} \in \mathcal{C}^*(S) \ | \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \right\} \]
 \end{definition}
@@
 \begin{definition}[Splitting an interval]
-\label{pers02.def:Splitting-a-region}
+\defL{splitting-a-region}
 Given a $p_i$ interval $\left[a_{i}..b_{i}\right]$ with more than one element, i.e.
@@
 \begin{definition}[Merging regions]
-\label{pers02.def:Merging-regions}
+\defL{merging-regions}
 Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$ be two contiguous regions and let $p_j$ be the contiguity parameter. 
@@
 \begin{definition}[Separation]
-Let $\mathbf{c}',\mathbf{c}''\in S$ be two configurations, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e.
+\defL{separation}
+Let $\mathbf{c}',\mathbf{c}''\in \mathcal{C}^*(S)$ be two feasible \comment{e' giusto che ho messo feasible?
+Se considerassimo anche le unfeasible sarebbe impossibile calcolarne le immagini nell'objective space?} configurations of the system $S$, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e.
 $\mathbf{o}'=E \left(\mathbf{c}', b\right)$, $\mathbf{o}''=E \left(\mathbf{c}'', b\right)$, where $E$ is the evaluation function.

### 2014-07-24 introduction.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

@@
 \section{Introduction and Motivation}
+\comment{Si capisce che noi provide an algorithm?}
+
+\comment{Mettere our contribution?}
+
+\comment{Usare triangleq quando definiamo noi le cose, per distinguerlo dall'= di calcolo}
 
@@
 that introduces the concept of Parameter Space Representation of
-Pareto Set (PS). The main idea is focusing on the ``innovation''
+Pareto Set (PS).\comment{Provo a fare il reviewer stronzo.
+Allora, quando parliamo di parameter space, non si capisce bene di cosa parliamo.
+Alla fin fine penso (ma gia' se nemmeno io che ci ho messo mano ne sono sicuro, figuriamoci il reviewer) stiamo parlando del configuration space, che definiamo precisamente nella \secR{pareto}.
+In altre parole parameter space == configuration space.
+Quindi, visto che il Pareto set e' contenuto nel configuration space, il Pateto-set e' gia', lui stesso, una Parameter Space Representation of Pareto-set.
+E' come dire ``io sono la rappresentazione di me stesso'', che filosoficamente e' affascinante ma matematicamente non lo e' altrettanto!} The main idea is focusing on the ``innovation''
 introduced in the Pareto sets and then accordingly distributing the

### 2014-07-24 paper.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

@@
 
+\usepackage{subfigure}
 \usepackage{cite}
@@
 %------------------------------------------------------------------------------
+\newcommand{\figR}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\figLC}[2]{
+        \caption{#2}
+        \label{fig:#1}
+        %\vspace{-10pt}
+}
+\newcommand{\secL}[1]{\label{sec:#1}}
+\newcommand{\secR}[1]{Sec.~\ref{sec:#1}}
+
+\newcommand{\defL}[1]{\label{def:#1}}
+\newcommand{\defR}[1]{Def.~\ref{def:#1}}
 
@@
 develop an analytical model of the system. In this work we present PS,
-a multiobjective exploration strategy that introduces the notion of
+a multiobjective exploration \comment{metterei algorithm anziche' strategy, che mi sembra troppo vago e non fa capire bene} strategy that introduces the notion of
 Parameters Space Representation. After a detailed formal description

### 2014-07-25 algorithm.tex
Fixes

@@
-\section{The algorithm}
+\section{The PS algorithm}
 \label{sec:algorithm}
-\comment{Mettiamo PS algorithm come titolo della sezione almeno rinforziamo nella memoria il suo nome?}
 In this section we present PS, the algorithm that we propose to perform the Design Space Exploration (DSE).
 As any other DSE algorithm, its input is the parameterized system $S$ and a benchmark application $b$, while the output is an approximation of the Pareto-optimal set $\mathcal{P}\left(S,b\right)$.
-\comment{E' corretto?}
 PS is iterative and we will describe, separately, the initialization phase, the operations performed inside each iteration and the condition that triggers the termination.
@@
 	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
-	\item a set $test_{i}$ of at most $K$ configurations evaluated in the era. \comment{Nella era i o nella successiva?}
+	\item a set $test_{i}$ of at most $K$ configurations evaluated
+	in the era. \comment{Nella era i o nella successiva? DP: non mi ricordo!}
 	\end{itemize}
-$K$ is a parameter that must be set before the algorithm runs. \comment{Spiegare un po' l'impatto di K.} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
+$K$ is a parameter that must be set before the algorithm runs.
+\comment{Spiegare un po' l'impatto di K. DP: se c'e' tempo...} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
 	\begin{align}\begin{array}{l}
@@
 
-\comment{Prima di sbattere tutta la sfilza di steps, dovremmo dare un'idea preliminare di cosa si andra' a fare.}
+\comment{Prima di sbattere tutta la sfilza di steps, dovremmo dare
+un'idea preliminare di cosa si andra' a fare. DP: se c'e' tempo bis}
 

### 2014-07-25 concepts.tex
Fixes

@@
 \section{Underlying concepts and theoretical formulation}
-\comment{Attenzione: siamo capaci di avere a che fare con unfeasible configurations?}
+\label{sec:statement_of_the_problem}
 
-\comment{Theoretical suona troppo pomposo?
-Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come si vede in \figR{3}.
-Aggiustare i nomi degli assi che in alcune figure sono sbagliati.
-O forse basta esportarli col nuovo libreoffice che fa meglio}
-In this section we provide the concepts and the formal definitions that we will use later to express PS, the algorithm we propose.
- First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on.
-Then, we sketch the fundamental idea behind our algorithm.
-Finally, we provide a formal definition of the regions, of their properties and of the operations that will be performed on them by the algorithm.
+\comment{Theoretical suona troppo pomposo? DP: boh... AA: Esportare di
+nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
+si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
+sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
+meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
+cose} 
+In this section we provide the concepts and the formal
+definitions that we will use later to express PS, the algorithm we
+propose.  First, we give the definitions of Pareto set and Pareto
+front that lie on the basis of Design Space Exploration is based on.
+Then, we sketch the fundamental idea behind our algorithm. Finally, we
+provide a formal definition of the regions, of their properties and of
+the operations that will be performed on them by the algorithm.
 
-\subsection{Pareto-set and Pareto-front}
+\subsection{Pareto set and Pareto front}
 \secL{pareto}
@@
 that is, the set of configurations $\mathbf{c} \in
-\mathcal{C}^*(S)$ not dominated by any other \comment{feasible}
- configuration.
+\mathcal{C}^*(S)$ not dominated by any other configuration.
 The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} is their image, i.e. the set:
@@
 
-\comment{Mi sembra solo un cambio di notazione. }
-On the contrary, we call ``parameter space representation'' of the
-Pareto set the representation in which each configuration $\mathbf{p}$
-is simply represented as a point of $P_{1}\times\dots\times P_{n}$
-space. We will investigate the relation between the ``objective space
-representation'' and the ``parameter space representation''. We
-are particularly interested in the relation between the evolution
-of the objective space representation of the Pareto set and the evolution
-of its parameter space representation.
+\comment{Mi sembra solo un cambio di notazione. DP: c'era un On the
+contrary troppo aggressivio, ho cercato di alleggerire la cosa, ma dai
+un'occhiata }
+
+For each point of the Pareto front we can imagine the corresponding
+configuration as a point of $P_{1}\times\dots\times P_{n}$
+space. We will also refer to these points as ``parameter space representation'' of the
+Pareto front. Figure~\ref{fig:psos} shows the relation between the objective space
+(containing the Pareto front) and its parameter space representation.
+In particular in this work we are interested in the relation between
+the evolution of the points in the two spaces, e.g. how some
+properties of the Pareto front points can reflect some features of the
+corresponding points in the parameter space.
 
 \begin{figure}[h]
+\label{fig:psos}
 \includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
 \caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'').
-\comment{Questa figura sembra molto ``didattica''.
-La relazione tra Pareto front e Pareto set magari deve essere illustarta a studenti ma in un paper va bene?
-Io la apprezzerei se la trovassi, ma di solito si fa cosi'?}}
+and Pareto front (``objective space representation'').}
 \end{figure}
@@
 \defL{separation}
-Let $\mathbf{c}',\mathbf{c}''\in \mathcal{C}^*(S)$ be two feasible \comment{e' giusto che ho messo feasible?
-Se considerassimo anche le unfeasible sarebbe impossibile calcolarne le immagini nell'objective space?} configurations of the system $S$, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e.
+Let $\mathbf{c}',\mathbf{c}''\in \mathcal{C}^*(S)$ be two configurations of the system $S$, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e.
 $\mathbf{o}'=E \left(\mathbf{c}', b\right)$, $\mathbf{o}''=E \left(\mathbf{c}'', b\right)$, where $E$ is the evaluation function.

### 2014-07-25 experiments.tex
Fixes

@@
 
-The results presented in the next section compare PS against one
-widely adopted Multi-objective Genetic
-Algorithm~\cite{knowles_techrep06}. At best of our knowledge, genetic
+The results presented in the next section compare PS one widely
+adopted Multi-objective Genetic Algorithm
+(MOGA)~\cite{knowles_techrep06}. At best of our knowledge, genetic
 approaches in general still represent the best compromise between
@@
 Finally, it should be pointed out that in this introductory work we
-will explicitly use the SPEA~\cite{zitzler_eurogen01} variant of MOGA,
-remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for
-a detailed analysis on how it differs and what could be expected from
+will explicitly use the \emph{SPEA}~\cite{zitzler_eurogen01} variant of MOGA,
+remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for a
+detailed analysis on how it differs and what could be expected from
 similar multi-objective strategies.
@@
 similar algorithm parameters have been adopted. In particular a
-population size of 30 has been chosen for GA, corresponding to the
+population size of 30 has been chosen for the genetic approach (GA), corresponding to the
 same value for the $K$ of PS. The number of generations (or era)
@@
 comparison between the variation range for different benchmarks
-between a FCP and a VCP exploration for both power dissipation and
+between a PS and a GA exploration for both power dissipation and
 execution time is shown in Fig.~\ref{fig:dispersion}(a) and (b)
@@
   \begin{tabular}{c}
-    \includegraphics[width=0.4\textwidth]{pictures/variation_power.eps} \\
+    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
     (a) \\
-    \includegraphics[width=0.4\textwidth]{pictures/variation_etime.eps} \\
+    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} \\
     (b) \\
-    \includegraphics[width=0.4\textwidth]{pictures/dispersion.eps} \\
+    \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
     (c) 
@@
 Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
-dispersion errors for different benchmarks for PS and MOGA
-exploration. As it can be observed, MOGA still shows a tendency in
+dispersion errors for different benchmarks for PS and GA
+exploration. As it can be observed, GA still shows a tendency in
 discovering more uniformly dispersed points (i.e. higher values). These results,

### 2014-07-25 introduction.tex
Fixes

--- 2014-07-23 introduction.tex
@@
 \section{Introduction and Motivation}
+\comment{Si capisce che noi provide an algorithm? DP: penso di si',
+che intendi precisamente ?}
+\comment{Mettere our contribution? DP: dove ? casomai fai tu}
 
@@
 The final result of a design space exploration is a subset of the
-configurations called Pareto Set (\cite{pareto}) (See also Definition
-\ref{pers02.def:Pareto-set}). It represents the trade-offs between
-objectives, so that for each configuration of the Pareto Set there is no
-other configuration performing better for all the objectives
-considered. Once these few promising configurations have been obtained, a
-subsequent step of the design flow can eventually afford a more
-accurate low level simulation.
+configurations called \emph{Pareto set} (\cite{pareto}) (See also Definition
+\ref{pers02.def:Pareto-set}). The corresponding values of the
+objectives for each configuration of the Pareto Set is called
+\emph{Pareto front}: it represents the trade-offs between objectives, i.e.  for each
+point of the Pareto front there is no other configuration performing
+better for all the objectives considered. Once these few promising
+configurations have been obtained, a subsequent step of the design
+flow can eventually afford a more accurate low level simulation.
 
@@
 that introduces the concept of Parameter Space Representation of
-Pareto Set (PS). The main idea is focusing on the ``innovation''
-introduced in the Pareto sets and then accordingly distributing the
+Pareto front (PS).\comment{Provo a fare il reviewer stronzo. Allora,
+quando parliamo di parameter space, non si capisce bene di cosa
+parliamo. Alla fin fine penso (ma gia' se nemmeno io che ci ho messo
+mano ne sono sicuro, figuriamoci il reviewer) stiamo parlando del
+configuration space, che definiamo precisamente nella \secR{pareto}.
+In altre parole parameter space == configuration space. Quindi, visto
+che il Pareto set e' contenuto nel configuration space, il Pateto set
+e' gia', lui stesso, una Parameter Space Representation of Pareto set.
+E' come dire ``io sono la rappresentazione di me stesso'', che
+filosoficamente e' affascinante ma matematicamente non lo e'
+altrettanto! DP: risolto ?} 
+The main idea is focusing on the ``innovation''
+introduced in the Pareto front and then accordingly distributing the
 exploration effort in regions created in the multidimensional space of
@@
 in exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
-the already evaluated configurations. We claim that the
-approach presented in this paper has most of the benefits of the genetic
+the already evaluated configurations. In this work we will compare 
+the proposed approach against a well known Multi-Objective Genetic
+Algoritm~\cite{knowles_techrep06}.
+We claim that the approach presented in this paper has most of the benefits of the genetic
 approaches, although the rationale is completely different.
@@
 Section~\ref{sec:statement_of_the_problem} we formally introduce the
-main concepts and the definitions required to apply the proposed strategy. Next in
-Section~\ref{sec:algorithm} we present the PS algorithm in detail.
-Finally in Section~\ref{sec:ee} we show a case study involving the
-exploration of the hardware/software parameters of a Very Long
- Instruction Word (VLIW) architecture, performing a qualitative
- and quantitative comparison of
-PS agains the state-of-art of multiobjective genetic based approaches.
+main concepts and the definitions required to apply the proposed
+strategy. Next in Section~\ref{sec:algorithm} we present the PS
+algorithm in detail.  Finally in Section~\ref{sec:ee} we show a case
+study involving the exploration of the hardware/software parameters of
+a Very Long Instruction Word (VLIW) architecture, performing a
+qualitative and quantitative comparison of PS against the state-of-art
+of multiobjective genetic based approaches.

### 2014-07-25 paper.tex
Fixes

@@
 develop an analytical model of the system. In this work we present PS,
-a multiobjective exploration \comment{metterei algorithm anziche' strategy, che mi sembra troppo vago e non fa capire bene} strategy that introduces the notion of
+a multiobjective exploration algorithm that introduces the notion of
 Parameters Space Representation. After a detailed formal description
@@
 introduces the concept of Parameter Space representation of Pareto
-Set. A case study of a VLIW architecture involving strong
+Front. A case study of a VLIW architecture involving strong
 hardware/software dependencies has been carried out to evaluate

### 2014-07-25 experiments.tex
Added ACM style tables

@@
 along with a brief description.
+% IEEE table style
+%\begin{table}
+%	\centering
+%	\caption{Benchmarks}
+%	\label{tab:bench}
+%	\begin{tabular}{ll}
+%	\hline
+%	\multicolumn{1}{c}{Benchmark} & \multicolumn{1}{c}{Application} \\
+%	\hline
+%	Alloca\_test & Memory array allocation test \\
+%	Bmm & Matrices multiplication and elements sum \\
+%	Fir\_int & Finite impulse response \\
+%	Mm & Floating point matrices multiplication \\
+%	Sha256 & Cryptocurrency header Hashing \\
+%	Wave & Wavefront computation \\
+%	\hline
+%	\end{tabular}
+%\end{table}
+
+% ACM table style
 \begin{table}
-	\centering
-	\caption{Benchmarks}
-	\label{tab:bench}
+	\tbl{Benchmarks\label{tab:bench}}{
 	\begin{tabular}{ll}
@@
 	\hline
-	\end{tabular}
+	\end{tabular}}
 \end{table}
-
 \subsection{Evaluation Metrics}
@@
 
-\begin{table*}
-  \centering
+% IEEE table style
+%\begin{table}
+%  \centering
+%  \begin{tabular}{ccc}
+%    \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps} & 
+%    \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps} \\
+%    \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
+%  \end{tabular}
+%  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
+%  \label{fig:pareto_fronts_100}
+%\end{table}
+%
+%\begin{table}
+%  \centering
+%  \begin{tabular}{ccc}
+%    \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps} & 
+%    \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps} \\
+%    \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps} &
+%    \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 
+%  \end{tabular}
+%  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
+%  \label{fig:pareto_fronts_500}
+%\end{table}
+
+\begin{table}
+  \tbl{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.\label{fig:pareto_fronts_100}}{
   \begin{tabular}{ccc}
@@
     \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
-  \end{tabular}
-  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
-  \label{fig:pareto_fronts_100}
-\end{table*}
+  \end{tabular}}
 
-\begin{table*}
-  \centering
+\end{table}
+
+\begin{table}
+  \tbl{Pareto fronts found by PS and GA for a fixed budget of 500
+  configurations.\label{fig:pareto_fronts_500}}{
   \begin{tabular}{ccc}
@@
     \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 
-  \end{tabular}
-  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
-  \label{fig:pareto_fronts_500}
-\end{table*}
-
+  \end{tabular}}
+\end{table}
 Low budget Pareto sets are shown in
@@
 MOGA exploration for power dissipation and execution time, respectively.
+%\begin{table}
+%  \centering
+%  \begin{tabular}{c}
+%    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
+%    (a) \\
+%    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} \\
+%    (b) \\
+%    \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
+%    (c) 
+%  \end{tabular}
+%  \caption{(a)(b) Variation range for different benchmarks between PS and GA
+%  and average dispersion absolute dispersion (c)}
+%  \label{fig:dispersion}
+%\end{table}
+
 \begin{table}
-  \centering
+  \tbl{(a)(b) Variation range for different benchmarks between PS and GA
+  and average dispersion absolute dispersion (c)
+  \label{fig:dispersion}}{
   \begin{tabular}{c}
@@
     (c) 
-  \end{tabular}
-  \caption{(a)(b) Variation range for different benchmarks between PS and GA
-  and average dispersion absolute dispersion (c)}
-  \label{fig:dispersion}
+  \end{tabular}}
 \end{table}
-
 The average normalised absolute dispersion error measures

### 2014-07-27 algorithm.tex
AA: aggiustato fino a initialization phase

@@
-\section{The PS algorithm}
-\label{sec:algorithm}
+\section{PS algorithm}
+\secL{algorithm}
 In this section we present PS, the algorithm that we propose to perform the Design Space Exploration (DSE).
@@
 PS is iterative and we will describe, separately, the initialization phase, the operations performed inside each iteration and the condition that triggers the termination.
+
+At a glance, at each iterations simulations are performed.
+Regions are classified based on the innovation introduced by their configurations in the Pareto-front so far calculated.
+The most interesting regions are split, so that each subregion will receive evaluation effort in the next iteration.
+On the contrary, uninteresting regions are merged.
 
@@
 	\item a set $test_{i}$ of at most $K$ configurations evaluated
-	in the era. \comment{Nella era i o nella successiva? DP: non mi ricordo!}
+	in the era.
 	\end{itemize}
@@
 
-\comment{Prima di sbattere tutta la sfilza di steps, dovremmo dare
-un'idea preliminare di cosa si andra' a fare. DP: se c'e' tempo bis}
+We now describe formally PS.
 
@@
 with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/small_and_big}
-
-\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
-are evaluated in a small region and in a bigger region. In can be
-seen that smaller region is more crowded.}
-
-\end{figure}
-
 \end{remark}

### 2014-07-27 concepts.tex
AA: aggiustato fino a initialization phase

@@
 \section{Underlying concepts and theoretical formulation}
-\label{sec:statement_of_the_problem}
+\secL{statement_of_the_problem}
 
-\comment{Theoretical suona troppo pomposo? DP: boh... AA: Esportare di
-nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
-si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
-sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
-meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
-cose} 
 In this section we provide the concepts and the formal
@@
 propose.  First, we give the definitions of Pareto set and Pareto
-front that lie on the basis of Design Space Exploration is based on.
+front that lie on the basis of Design Space Exploration.
 Then, we sketch the fundamental idea behind our algorithm. Finally, we
@@
 is feasible. We call this subset {\em
-feasible configuration space} $S$ and indicate it as
+feasible configuration space} of $S$ and indicate it as
 $\mathcal{C}^*(S)$].
@@
 cost, performance, etc.). An {\em evaluation function}
-$E:\mathcal{C}^*(S)\times \mathcal{B} \longrightarrow \Re^m$ is a
-function that associates each feasible configuration of $S$ with
-an $m$-tuple of values corresponding to the objectives to be
-optimized when any application belonging to the set of benchmarks
+$E:\mathcal{C}^*(S)\times \mathcal{B} \longrightarrow \Re^m$ associates each feasible configuration of $S$ to
+an $m$-tuple of values corresponding to the objectives when any application belonging to the set of benchmarks
 $\mathcal{B}$ is executed.
@@
 
-\begin{definition}[Pareto Set]
-\label{pers02.def:Pareto-set}
-The {\em Pareto-optimal set} of $S$ for the application $b$ is the
+\begin{definition}[Pareto set and Pareto front]
+\defL{pareto-set}
+The {\em Pareto-optimal set} of $S$ (or, shortly, Pareto-set) for the application $b$ is the
 set:
@@
 \mathcal{C}^*(S)$ not dominated by any other configuration.
-The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} is their image, i.e. the set:
+The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} (or, shortly, Pareto-front) is their image, i.e. the set:
 \[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} | \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
@@
 The aim of a Design Space Exploration (DSE) strategy is to give a
-good approximation of the Pareto-optimal front for a system $S$ and an
+good approximation of the Pareto-optimal set for a system $S$ and an
 application $b$, simulating as few configurations as possible.
@@
 
-\comment{Mi sembra solo un cambio di notazione. DP: c'era un On the
-contrary troppo aggressivio, ho cercato di alleggerire la cosa, ma dai
-un'occhiata }
+As we will show later, at each iteration, PS calculates an approssimation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on.
+The image of $\mathscr{P}_i$ is an approssimation of the Pareto-front.
+The simulation effort is distributed more on the regions that provide configurations in $\mathscr{P}_i$ which introduce more \emph{innovation}, i.e.
+whose image in the objective space is more distant, thus ``more different'', from the previous Pareto-front approssimation point.
 
-For each point of the Pareto front we can imagine the corresponding
-configuration as a point of $P_{1}\times\dots\times P_{n}$
-space. We will also refer to these points as ``parameter space representation'' of the
-Pareto front. Figure~\ref{fig:psos} shows the relation between the objective space
-(containing the Pareto front) and its parameter space representation.
-In particular in this work we are interested in the relation between
-the evolution of the points in the two spaces, e.g. how some
-properties of the Pareto front points can reflect some features of the
-corresponding points in the parameter space.
+% A PROPOSITO DI QUESTO DUBBIO:
+%\comment{AA: Mi sembra solo un cambio di notazione. DP: c'era un On the contrary troppo aggressivio, ho cercato di alleggerire la cosa, ma dai un'occhiata }
+% HO CANCELLATO TUTTA QUESTA PARTE.
+% For each point of the Pareto front we can imagine the corresponding configuration as a point of $P_{1}\times\dots\times P_{n}$ space.
+We will also refer to these points as ``parameter space representation'' of the Pareto front.
+Figure~\ref{fig:psos} shows the relation between the objective space (containing the Pareto front) and its parameter space representation.
+In particular in this work we are interested in the relation between the evolution of the points in the two spaces, e.g.
+how some properties of the Pareto front points can reflect some features of the corresponding points in the parameter space.
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:psos}
 \includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
-\caption{Relation between Pareto set (its ``parameter space representation'')
-and Pareto front (``objective space representation'').}
+\caption{Relation between Pareto-set and Pareto front.}
 \end{figure}
@@
  (where $s_{1}$ and $s_{2}$ are some threshold values) is \emph{uninteresting}. This clearly shows that there are cases when, if a parameter lies in
-a certain range, there are ranges of the other that are not worth exploring. Intuitively, the Cartesian product of these ranges is an ``uninteresting
- region''.
+a certain range, there are ranges of the other one that are not worth being explored. Intuitively, the cartesian product of these ranges is an \emph{uninteresting region}.
 
-The problem is that, in complex scenarios, not all relations of this
-kind are known in advance. Some dependency may exist but may be hidden
-to the designer. Or they may be ``local'', i.e. two
-parameters may be related by a dependency but only if their values
-lie on some ranges (so we cannot treat them as they were related by
-a ``complete'' dependency). 
+The problem is that, in complex scenarios, not all the relations of this
+kind are known in advance. Some dependency may be hidden
+to the designer.
 Therefore, as stated in section \ref{sec:Related-work},
@@
 \emph{innovation} that it adds. If, during a design space exploration,
-a Pareto front is temporarily calculated, adding a new Pareto front
+a Pareto front approximation is temporarily calculated, adding a new Pareto front
 point near to the previous ones is not a considerable innovation,
@@
 since it let the experimenter discover potential performance that have not yet considered before.
+At each iteration, PS ``zooms in'' the most interesting regions while ``zooming out'' from the rest of configuration space.
+In order to implement this behavior algorithmically, at each iteration PS assigns the same number $N$ of simulations to each region.
+If a region $R$ is interesting, it is split in $k$ subregions before the next iteration starts.
+Therefore, in the next iteration, $N$ simulations are assigned to each subregion.
+As a result, we are populating the original region $R$ with $k\cdot N$ simulations.
+On the contrary, uninteresting regions are merged, so that each one will receive less effort in the next iteration.
+In other words, ares of the configuration space that are more promising are split in small subregions, while the other ones are blended in big regions.
+As illustrated in \figR{small_and_big}, assigning $N$ simulations to each region makes small ones well populated while bigger ones sparsely explored.
+
+	\begin{figure}[t]
+	\includegraphics[width=0.5\columnwidth]{img/small_and_big}
+	\figLC{small_and_big}{In this example 5 configurations
+	are evaluated in a small region and in a bigger region. In can be
+	seen that smaller region is more crowded.}
+	\end{figure}
 
@@
 
-\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in V_{i},a_{i}<b_{i}$.
+Since regions will be defined as cartesian products of parameter intervals, we need the following definition.
+\begin{definition}[Parameter interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in V_{i},a_{i}<b_{i}$.
 A $p_{i}$- interval is
@@
 \end{definition}
-
-We consider only parameters $p_{i}$ with ordering, i.e. such
-that $\forall a,b\in V_{i}$ it is possible
-to say $a<b$ or $a=b$ or $a>b$.
-
-%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
-%PARAMETRI SENZA ORDINAMENTO{]}
 
@@
 
+We consider only parameters $p_{i}$ with ordering, i.e. such
+that $\forall a,b\in V_{i}$ it is possible
+to say $a<b$ or $a=b$ or $a>b$. 
+The following definition of interval contiguity will be the base of the concept of region contiguity, used to define merging and splitting operations.
 \begin{definition}[Contiguous intervals]
@@
 
-We now provide some rules to split and merge regions. They will be
-useful when explaining our proposed exploration algorithm.
+As already explain, we will split interesting regions and merge uninteresting ones.
+The region splitting and merging operations are defined starting from the corresponding operations defined on intervals.
 \begin{definition}[Splitting an interval]
@@
 
+The merging operation will be defined only on region pairs that satisfy the conditions provided in the following definition.
 \begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
@@
 Examples of contiguous and non contiguous regions are given in \figR{contiguous_regions}.
-\comment{Spiegare le figure e inserire a dx una figura con le contiguous regions mergiate.
-Le definizioni buttate cosi' rendono difficile la lettura a chi non sa ancora dove vogliamo andare a parare.
-Giustifica ogni definizione prima di darla.
-Ad es.
-quando parli di splittare, spiega che quando le regioni sono interessanti noi le splittiamo cosi' da esplorarle meglio.
-Al contrario quando le mergiamo.
-Mettere una sezione del tipo "Required operations at a glance" per giustificare tutte le definizioni prima di buttarle}.
+The two regions at the top are contiguous because their union can be expressed as the cartesian product of parameter intervals, thus they can be merged to obtain a new bigger region.
+The same applies also to the regions on the right.
+On the contrary, the two regions on the left (or of the two regions at the bottom) cannot be merged.
 
@@
 		\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}
-		\figLC{contiguous_regions}{Contiguous and non contiguous
-		regions.}
+		\figLC{contiguous_regions}{Contiguous and non contiguous regions. \comment{Inserire a dx una figura con le contiguous regions mergiate.}	}
 	\end{figure}
 
+We now describe formally the merging operations.
 \begin{definition}[Merging intervals]

### 2014-07-27 introduction.tex
AA: aggiustato fino a initialization phase

--- 2014-07-23 introduction.tex
@@
 system configurations and objectives. In such cases a high level
-system simulation is often the only way to have a picture of how system
+system simulation is the only way to have a picture of how system
 parameters impact on the objectives.  A key problem is that the size
 of the design space to be simulated grows with the product of
-cardinalities of each parameter, easily resulting in an intractable number
-of simulations. In these cases a ``Design Space
-Exploration'' strategy is required, i.e. a methodology to evaluate
-only a small subset of all possible configurations while maintaining a
-good level of efficiency and accuracy~\cite{surviving_soc}.
+cardinalities of each parameter, resulting in an intractable number
+of simulations. In these cases a Design Space
+Exploration (DSE) strategy is required, i.e. an algorithm that selects
+only a tractable subset of all possible configurations to simulate while providing, at the end, configurations that are close to the optimum and that are worth evaluating, in a following step of the design process, in a more thorough way.
 
-The final result of a design space exploration is a subset of the
-configurations called Pareto Set (\cite{pareto}) (See also Definition
-\ref{pers02.def:Pareto-set}). It represents the trade-offs between
-objectives, so that for each configuration of the Pareto Set there is no
-other configuration performing better for all the objectives
-considered. Once these few promising configurations have been obtained, a
-subsequent step of the design flow can eventually afford a more
-accurate low level simulation.
+%The final result of a design space exploration is a subset of the configurations called \emph{Pareto set} (\cite{pareto}, see also \defR{pareto-set}).
+The corresponding values of the objectives for each configuration of the Pareto Set is called \emph{Pareto front}: it represents the trade-offs between objectives, i.e.
+for each point of the Pareto front there is no other configuration performing better for all the objectives considered.
+Once these few promising configurations have been obtained, a subsequent step of the design flow can eventually afford a more accurate low level simulation.
 
-In this work we present a multiobjective design exploration strategy
+In this work we present a multiobjective design exploration algorithm
+that introduces the concept of interesting and uninteresting regions of the configuration space.
+\comment{AA: prima era ``algorithm
 that introduces the concept of Parameter Space Representation of
-Pareto Set (PS). The main idea is focusing on the ``innovation''
-introduced in the Pareto sets and then accordingly distributing the
-exploration effort in regions created in the multidimensional space of
-system parameters. The aim of the PS approach is to propose a new
+Pareto front''.
+Se io fossi un reviewer, direi: guardi, questo io non credo, anche pecche' non siamo noi che introduciamo il concetto di parameter space representation del pareto set.
+Il concetto esiste gia' dal 1896 e si chiama ``Pareto-set''!
+Ho cambiato il claim dicendo che introduciamo interesting/uninteresting regions, che mi sembra piu' rispondente alla verita'.
+Cosi' ti va bene?}
+The algorithm is iterative.
+The main idea can be simplified as follows.
+At each iteration, the configuration space is divided in regions.
+A score is given to each region based on the \emph{innovation} provided by its configurations in the Pareto front w.r.t.
+the previous iterations.
+The regions with high score are considered the most \emph{interesting} and more simulations are distributed there rather than in the rest of the configuration space.
+Since the fundamental operations consist in the formation of regions in the Parameter Space (aka configuration space), we call our algorithm PS.
+
+\comment{AA: Le seguenti referenze a cose di psicologia cognitiva potrebbero essere interpretate come una figata o una cagata. Tu come le interpreti?}
+Our algorithm mimics the attention shift in human beings.
+Authors in \cite{attention} models human attention as a single resource with a limited budget that must be distributed among tasks, preferring the task which the focus is on.
+ Authors in \cite{spatial_attention} describes the visual attention as a spotlight that focuses, each time, in a particular region of the visual space in order to process it more deeply.
+Similarly, PS focuses its ``spotlight'' only to the interesting regions and explore them more thoroughly distributing the simulation budget on them.
+% Ispirzione: http://en.wikipedia.org/wiki/Attentional_shift
+
+With PS, we propose a new
 perspective on the configuration space, where parameter
@@
 
-\section{Related work and Contribution}
-\label{sec:Related-work}
+The paper is organized as follows. First, \secR{Related-work} places our work in the context of related effort.
+Then we give a theoretical formulation of the algorithm.
+In particular, in \secR{statement_of_the_problem} we provide formal definitions of the concepts and the operations that will be used to describe PS algorithm.
+In \secR{algorithm} we give the theoretical description of PS.
+Finally in Section~\ref{sec:ee} we show a case
+study involving the exploration of the hardware/software parameters of
+a Very Long Instruction Word (VLIW) architecture, performing a
+qualitative and quantitative comparison of PS against the state-of-art
+of multiobjective genetic based approaches.
+
+\section{Related work}
+\secL{Related-work}
 Many different design space exploration algorithms have been proposed
@@
 in exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
-the already evaluated configurations. We claim that the
-approach presented in this paper has most of the benefits of the genetic
+the already evaluated configurations. In this work we will compare 
+the proposed approach against a well known Multi-Objective Genetic
+Algoritm~\cite{knowles_techrep06}.
+We claim that the approach presented in this paper has most of the benefits of the genetic
 approaches, although the rationale is completely different.
-
-The paper is organized as follows: in
-Section~\ref{sec:statement_of_the_problem} we formally introduce the
-main concepts and the definitions required to apply the proposed strategy. Next in
-Section~\ref{sec:algorithm} we present the PS algorithm in detail.
-Finally in Section~\ref{sec:ee} we show a case study involving the
-exploration of the hardware/software parameters of a Very Long
- Instruction Word (VLIW) architecture, performing a qualitative
- and quantitative comparison of
-PS agains the state-of-art of multiobjective genetic based approaches.

### 2014-07-27 paper.tex
AA: aggiustato fino a initialization phase

@@
 
-\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
+\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
 %\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
@@
 \begin{abstract}
-Embedded Systems Design often requires conflicting objectives to be
-optimized with an appropriate choice of hardware/software parameters .
-Interdependencies among these parameters can make this task even more
-difficult, since an a-priori knowledge of them would  be required to
-develop an analytical model of the system. In this work we present PS,
-a multiobjective exploration algorithm that introduces the notion of
-Parameters Space Representation. After a detailed formal description
-of the algorithm and its concepts, we show a hardware/software
+Embedded Systems Design requires conflicting objectives to be
+optimized with an appropriate choice of hardware/software parameters.
+A simulation campaign guides the design in finding the best trade-offs, but, due to the big number of possible configurations, it is unfeasible to simulate all of them.
+For these reason Design Space Exploration (DSE) algorithms aim at finding near-optimal system configurations, only simulating a subset of them.
+
+In this work we present PS, a new multiobjective exploration algorithm.
+The basic idea is to recognize \emph{interesting}, i.e.
+regions of the configuration space that are proving to provide better configurations w.r.t.
+other ones.
+PS evaluates more configurations in interesting regions while exploring less thoroughly the rest of the configuration space.
+After a detailed formal description
+of the algorithm and the underlying concepts, we show a hardware/software
 exploration case study. Qualitative and quantitative comparisons of PS
@@
 
+\comment{AA: Esportare di
+nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
+si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
+sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
+meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
+cose}
+
 \end{document}

### 2014-07-27 algorithm.tex
AA: aggiustata tutta la prima parte

@@
 \item The total innovation and average score for the entire era is calculated:
-	\[
-	is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
-	\]
+	\begin{align} \begin{array}{l}
+	is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right) \\
+	is_{av,i}=is_{TOT,i} / |\mathcal{R}_i|
+	\end{array} \end{align}
 
-\item The configuration space partition $\mathcal{R}_{i}$ is divided in three subsets, that we will comment later \comment{e invece sarebbe bene commentarli ora, anche}:
+\item The configuration space partition $\mathcal{R}_{i}$ is divided in three subsets, that we will comment later:
 
 	\begin{enumerate}
-	\item high innovation regions 
+	\item \emph{high innovation regions}, whose innovation score exceeds the average score of the previous era by a factor of $\alpha$, i.e.
 	\[
@@
 	$\alpha=1.2$). 
-	\item low innovation regions 
+	\item \emph{low innovation regions}, whose score is positive but modest, i.e.
 	\[
@@
 	\]
-	\item no innovation regions 
+	\item \emph{no innovation regions}, whose innovation is null, i.e. 
 	\[
@@
 		\item No innovation regions are merged, two by two.
-To do so, couples of no innovation contiguous regions $(R_1,R_2)$ are selected.
-We denote the set of these couples as $\mathscr{M}_i$.
-This set is constructed such that couples are independent, i.e.
+To do so, pairs of no innovation contiguous regions $(R_1,R_2)$ are selected.
+We denote the set of these pairs as $\mathscr{M}_i$.
+This set is constructed such that pairs are independent, i.e.
 there cannot be two of them sharing a region.
 In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq$.
-We merge each couple of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
-We stress that the regions that belong to each selected couple must be contiguous, otherwise it is impossible to merge them.
+We merge each pair of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
+We stress that the regions that belong to each selected pair must be contiguous, otherwise it is impossible to merge them.
 We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e.
@@
 
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is computed as:
+\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the subregions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$.
+Formally:
 	\[
@@
 
-\comment{commentare questa formula}
-
-\comment{SONO ARRIVATO A LEGGERE QUA}
-
 \subsection{Termination Condition}
@@
 \]
- where $\beta$ and $\gamma$ are selected by the experimenter (see
-remark \ref{rem:termination}).
-\begin{remark}
-\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
-the iteration rules says that the smaller is a region, the more ``crowded''
-it is. It means that configurations in smaller regions are evaluated
-with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
-\end{remark}
-
-\begin{remark}
-The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
-a configuration whose objectives are more ``separated'' by the previous
-Pareto front, has to be taken in greater account than others. A configuration
-that is very near, in the objective space, to the previous Pareto
-front doesn't add a true innovation. Therefore, the innovation score
-of a configuration is a measure of how much interest we have in considering
-it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{img/novelty_score}
-
-\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
-configuration}
-
-\end{figure}
-
-\comment{Ci vorrebbe una rappresentazione schematica dell'algoritmo usando l'ambiente latex Algorithm o non mi ricordo come si chiama}
-
-\end{remark}
-
-\begin{remark}
-The innovation score of a region is a measure of how much different
-are the points that it adds to Pareto Front compared to the previous
-Pareto front. ``High innovation regions'' are the ones in which
-more configurations are worth evaluating, because they add many points
-on not yet well explored Pareto front areas. Therefore, these regions
-are split in the next era (see remark \ref{pers02.rem:smaller_regions})
-and more ``crowded'' by simulations. ``No innovation regions''
-are the ones that have proved to add few points on Pareto fronts,
-probably very near to previous Pareto front points and a Pareto front
-point near to previous points is not so much interesting. Therefore
-it's not worth evaluating many of their configurations and it is useful
-to merge these regions, in order to less densely evaluate them.
-
-%ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
-%DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
-
-\end{remark}
-
-\begin{remark}
-\label{rem:termination}The algorithm terminates when in the last
+ where $\beta$ and $\gamma$ are selected by the experimenter. 
+The algorithm terminates when in the last
 $\beta$ iterations not a great ``amount of innovation'' has been
 discovered. Therefore it is very probably that carrying on iterating
-will not considerably change the Pareto front already formed. It's
-not recommended to chose $\beta=1$, because it is possible that the
-Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
-are not very different but next Pareto fronts could be. In other words,
-it's unsafe to terminate as soon as the Pareto front doesn't change
-enough between two consecutive eras, thus a strategy taking into
+will not considerably change the Pareto-front approximation already formed.
+
+It is not recommended to chose $\beta=1$, because it is possible that the
+$k-1$-th and $k$-th Pareto front approximations are not very different but next ones could be. In other words,
+it is unsafe to terminate as soon as the Pareto front does not considerably change
+between two consecutive eras, thus a strategy taking into
 account the history of the Pareto fronts has been adopted in the
 proposed approach.
-\end{remark}
 %!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
@@
 
-\begin{remark}
-Merging and splitting the regions are very dynamic processes. A portion
-of the parameter space can be populated by a large number of small
+Observe that merging and splitting operation are dynamic processes. A portion
+of the parameter space may be populated by a large number of small
 regions in some eras, but can be covered by a small number of large
-regions in next eras. This can be explained saying that, after a number
-of eras of intense exploration of a portion of parameter space, this
-exploration has turned to be enough thorough and so it was time for
+regions in next eras. This is a desirable property of PS, since, after a number
+of eras of intense exploration of a portion of configuration space, this
+exploration has turned to be enough thorough and so it may be time for
 other portions to be minutely scanned.

### 2014-07-27 algorithm.tex
AA: prima parte finalizzata, manca solo di una lettura complessiva

@@
 $K$ is a parameter that must be set before the algorithm runs.
-\comment{Spiegare un po' l'impatto di K. DP: se c'e' tempo...} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
+Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
 	\begin{align}\begin{array}{l}
@@
 there cannot be two of them sharing a region.
-In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq$.
-We merge each pair of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
+In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq j$.
+We merge each pair of these regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
 We stress that the regions that belong to each selected pair must be contiguous, otherwise it is impossible to merge them.
@@
 Formally:
-	\[
-	\mathcal{R}_{i+1}=
-	\]
-	\[
-	=\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
-	\]
-	\[
-	\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
-	\]
+	\begin{align} 
+	\mathcal{R}_{i+1} \triangleq
+	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
+	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
+	\end{align}
 \end{enumerate}
@@
 other portions to be minutely scanned.
-\end{remark}
+
+A pseudocode representation of PS algorithm is in Alg.\ref{alg:algo}
+
+\begin{algorithm}[t]
+	\small
+	\caption{PS Algorithm}
+	\label{alg:algo}
+	  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+	  \Input{S}
+	  \Output{ $\tilde{\mathscr{P}}$ // Approximation of Pareto-set}
+%
+	  \nl //Initialization \\
+	  \nl $\mathscr{R}_0\Leftarrow
+				\left\{ V_{1}\times\dots\times V_{n}\right\} $; \\
+	  \nl $\mathscr{P}_0\Leftarrow $ extract\_non\_dominated($test_0$);\\
+	  \nl \\
+	  \nl $i\Leftarrow 0$;\\
+	  \nl \While{ !termination\_condition } {
+			// Iteration steps\\
+			\nl $test_i=\emptyset$;\\
+	  		\nl \ForEach {$R \in \mathscr{R}_i$}{
+				\nl $\mathscr{N}_{R,i} \Leftarrow$ configurations in $R$ not evaluated so far;\\
+				\nl $|\mathscr{N}_{R,i}|\leq K/|\mathscr{R}_i|$? \\
+						$\mbox{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}test_{R,i}\Leftarrow \mathscr{N}_{R,i}$:\\
+						\mbox{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}$test_{R,i}\Leftarrow K/|\mathscr{R}_i|$ randomly selected configurations from $\mathscr{N}_{R,i}$;\\
+			\nl $test_i\Leftarrow test_i \cup test_{R,i}$
+
+			}
+
+			\nl simulate ($test_i$);\\
+			\nl $\mathscr{P}_i \Leftarrow 
+				\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)$;\\
+			\nl \ForEach{$\mathbf{c}^*\in\mathscr{P}_i$} {
+				\nl $is\left(\mathbf{c}^*\right) \Leftarrow \min\left\{ \left.s\left(\mathbf{c}\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\}$;\\
+				}
+			\nl \ForEach{$R\in\mathscr{R}_i$} {
+				\nl $is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} $;
+			}
+
+			\nl $is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)$ \\
+			\nl $is_{av,i}=is_{TOT,i} / |\mathcal{R}_i|$\\
+			\nl \\ //Region classification\\
+			\nl $\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\}$; \\
+			\nl $\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} $; \\
+			\nl $\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} $;
+
+			\nl \\ // Splitting and merging operations\\
+			\nl $\psi(\mathscr{R}_{i,h}) \Leftarrow \lbrace 
+					\psi(R) | R\in \mathscr{R}_{i,h}	
+				\rbrace$; \\
+			\nl construct $\mathscr{M}_i$; // the set of pair of contiguous no innovation regions \\
+			\nl $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$;\\
+			\nl\\ // Prepare the configuration space partition for the next iteration \\
+			\nl $\mathcal{R}_{i+1} \triangleq
+	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
+	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)$;\\
+		}
+	\nl $\tilde{\mathscr{P}} \Leftarrow \mathscr{P}_i$
+\end{algorithm}
+%

### 2014-07-27 paper.tex
AA: prima parte finalizzata, manca solo di una lettura complessiva

@@
 \usepackage{listings}
+\usepackage[ruled]{algorithm2e}
 
@@
 
-\comment{AA: Esportare di
-nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
-si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
-sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
-meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
-cose}
-
 \end{document}

### 2014-07-28 paper.tex
Some fixes

@@
 optimized with an appropriate choice of hardware/software parameters.
-A simulation campaign guides the design in finding the best trade-offs, but, due to the big number of possible configurations, it is unfeasible to simulate all of them.
-For these reason Design Space Exploration (DSE) algorithms aim at finding near-optimal system configurations, only simulating a subset of them.
+A simulation campaign can guide the design in finding the best
+trade-offs, but due to the big number of possible configurations it
+is often unfeasible to simulate all of them. For these reasons Design Space
+Exploration (DSE) algorithms aim at finding near-optimal system
+configurations only simulating a subset of them.
 
-In this work we present PS, a new multiobjective exploration algorithm.
-The basic idea is to recognize \emph{interesting}, i.e.
-regions of the configuration space that are proving to provide better configurations w.r.t.
-other ones.
-PS evaluates more configurations in interesting regions while exploring less thoroughly the rest of the configuration space.
-After a detailed formal description
-of the algorithm and the underlying concepts, we show a hardware/software
-exploration case study. Qualitative and quantitative comparisons of PS
+In this work we present PS, a new multiobjective exploration
+algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
+regions of the configuration space that are proving to provide better
+configurations with regard to other ones. PS evaluates more configurations in
+interesting regions while exploring less thoroughly the rest of the
+configuration space. After a detailed formal description of the
+algorithm and the underlying concepts, we show a 
+case study involving the hardware/software exploration of a VLIW
+architcture. Qualitative and quantitative comparisons of PS
 against a well-know multiobjective genetic approach demonstrate that,

### 2014-07-28 introduction.tex
readded pareto descr

@@
 objectives (energy consumption, performance, area) to be fulfilled.
+The growing demand and reduced time-to-market of these systems are
+introducing even more challenges that designers have to
+face~\cite{wsts}.
 Several factors are involved in this goal and real cases show how
@@
 cardinalities of each parameter, resulting in an intractable number
-of simulations. In these cases a Design Space
+of simulations.
+
+In these cases a Design Space
 Exploration (DSE) strategy is required, i.e. an algorithm that selects
-only a tractable subset of all possible configurations to simulate while providing, at the end, configurations that are close to the optimum and that are worth evaluating, in a following step of the design process, in a more thorough way.
+only a tractable subset of all possible configurations.
+The final result of a design space exploration is a subset of the
+configurations called \emph{Pareto set} (\cite{pareto}, see also
+\defR{pareto-set}). The corresponding values of the objectives for
+each configuration of the Pareto Set is called \emph{Pareto front}:
+it represents the trade-offs between objectives, i.e.  for each point
+of the Pareto front there is no other configuration performing better
+for all the objectives considered. Of course this is only a first
+high-level system simulation, thus these few promising
+configurations will need to be further evaluated in a next step of the design
+flow using a more accurate low level simulation (e.g. register
+transfer level).
 
-%The final result of a design space exploration is a subset of the configurations called \emph{Pareto set} (\cite{pareto}, see also \defR{pareto-set}).
-The corresponding values of the objectives for each configuration of the Pareto Set is called \emph{Pareto front}: it represents the trade-offs between objectives, i.e.
-for each point of the Pareto front there is no other configuration performing better for all the objectives considered.
-Once these few promising configurations have been obtained, a subsequent step of the design flow can eventually afford a more accurate low level simulation.
+\comment{DP: ho reintrodotto la descrizione di cos'e' un pareto set e
+front che ci serve dopo quando descriviamo PS, inoltre ho sostituito
+la tua frase era un po' contorta. In breve, il fatto che il pareto set
+del DSE sia un'approssimazioen di quello divino irraggiungibile e' una
+cosa che e' inutile dire qui, fa solo confondere col concetto di
+approssimazione che e' invece dovuto al fatto che usiamo modelli di
+alto livello}
+%while providing, at the end, configurations that are close to the
+%optimum and that are worth evaluating, in a following step of the
+%design process, in a more thorough way.
 
-In this work we present a multiobjective design exploration algorithm
-that introduces the concept of interesting and uninteresting regions of the configuration space.
-\comment{AA: prima era ``algorithm
-that introduces the concept of Parameter Space Representation of
-Pareto front''.
-Se io fossi un reviewer, direi: guardi, questo io non credo, anche pecche' non siamo noi che introduciamo il concetto di parameter space representation del pareto set.
-Il concetto esiste gia' dal 1896 e si chiama ``Pareto-set''!
-Ho cambiato il claim dicendo che introduciamo interesting/uninteresting regions, che mi sembra piu' rispondente alla verita'.
-Cosi' ti va bene?}
-The algorithm is iterative.
-The main idea can be simplified as follows.
-At each iteration, the configuration space is divided in regions.
-A score is given to each region based on the \emph{innovation} provided by its configurations in the Pareto front w.r.t.
-the previous iterations.
-The regions with high score are considered the most \emph{interesting} and more simulations are distributed there rather than in the rest of the configuration space.
-Since the fundamental operations consist in the formation of regions in the Parameter Space (aka configuration space), we call our algorithm PS.
+\comment{DP: poi dobbiamo trovare un nome piu' interessante rispetto a
+interesting regions, ci pensiamo questa estate}
 
-\comment{AA: Le seguenti referenze a cose di psicologia cognitiva potrebbero essere interpretate come una figata o una cagata. Tu come le interpreti?}
-Our algorithm mimics the attention shift in human beings.
-Authors in \cite{attention} models human attention as a single resource with a limited budget that must be distributed among tasks, preferring the task which the focus is on.
- Authors in \cite{spatial_attention} describes the visual attention as a spotlight that focuses, each time, in a particular region of the visual space in order to process it more deeply.
-Similarly, PS focuses its ``spotlight'' only to the interesting regions and explore them more thoroughly distributing the simulation budget on them.
+In this work we present PS, a multiobjective design exploration
+algorithm that introduces the concept of \emph{interesting} and
+\emph{uninteresting regions} of the configuration space.  The main
+idea can be simplified as follows: at each iteration of the algorithm,
+the configuration space is divided in regions. A score is given to
+each region based on the \emph{innovation} provided by its
+configurations in the Pareto front. The regions with high score are
+considered the most \emph{interesting} and more simulations are
+distributed there rather than in the rest of the configuration space.
+Several geometrical trasformations (splitting, merging etc...) are
+involved in the Parameter Space (aka configuration space), hence
+the name PS for the algorithm.
+
+From a more abstract but interesting perspective, the proposed
+algorithm mimics the attention shift in human beings. For example,
+authors in \cite{attention} models human attention as a single
+resource with a limited budget that must be distributed among tasks,
+preferring the task which the focus is on.  Authors in
+\cite{spatial_attention} describes the visual attention as a spotlight
+that focuses, each time, in a particular region of the visual space in
+order to process it more deeply. Similarly, PS focuses its
+``spotlight'' only to the interesting regions and explore them more
+thoroughly distributing the simulation budget on them.
 % Ispirzione: http://en.wikipedia.org/wiki/Attentional_shift
-
-With PS, we propose a new
-perspective on the configuration space, where parameter
-interdependencies play the fundamental role of making some regions
-more capable of generating hardly predictable solutions: catching this
-sort of ``chaoticity'' in the parameter space is the main idea behind
-the strategy that is being introduced in this work.
+In other words, with PS we propose a new perspective on the configuration space,
+where parameter interdependencies play the fundamental role of making
+some regions more capable of generating hardly predictable solutions:
+catching this sort of ``chaoticity'' in the parameter space is the
+main idea behind the strategy that is being introduced in this work.
 

### 2014-07-28 concepts.tex
AA: prima parte finalizzata, manca solo di una lettura complessiva
Some final touches, added more results comment

@@
 \label{fig:psos}
+\center
 \includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
@@
 
-In the design process, there are often a lot of ``local decisions''
-in which the designer can take advantage of well-known results or
-heuristics. For example, if we consider a VLIW architecture in a configuration with very few registers, it is well-known that increasing the number of ALUs does not bring tangible better performances
-but only cause an increase in area occupation. An intelligent exploration
-algorithm would not waste time evaluating configurations with many
-ALUs and few registers. If $p_{1}$ is the parameter ``number of
-registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
-can say that the region:
+In the design process, there are often a lot of ``local decisions'' in
+which the designer can take advantage of well-known results or
+heuristics. For example, if we consider a highly parallel
+computer architecture in a configuration with very few registers, it is
+well-known that increasing the number of ALUs does not bring tangible
+better performances but only cause an increase in area occupation. An
+intelligent exploration algorithm would not waste time evaluating
+configurations with many ALUs and few registers. If $p_{1}$ is the
+parameter ``number of registers'' and $p_{2}$ is the parameter
+``number of ALUs'', we can say that the region:
 \[
@@
 	\begin{figure}[t]
+	\center
 	\includegraphics[width=0.5\columnwidth]{img/small_and_big}
@@
 
-	\begin{figure}[h]
-		\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}
-		\figLC{contiguous_regions}{Contiguous and non contiguous regions. \comment{Inserire a dx una figura con le contiguous regions mergiate.}	}
+	\begin{figure}[t]
+		\center
+		\includegraphics[width=0.8\columnwidth]{img/contiguous_regions}
+		\figLC{contiguous_regions}{Contiguous and non contiguous regions.}
 	\end{figure}

### 2014-07-28 experiments.tex
Some final touches, added more results comment

@@
 \begin{itemize}
-\item{Multi-Objective trade-offs}: VLIW architectures let designers
+\item \emph{Multi-Objective trade-offs}: VLIW architectures let designers
 easily trade between power, energy and performances, resulting
 in extended Pareto sets which are an ideal ground for our testing
-purposes focused on parameter-space space representation
-\item{Compiler awareness}: Instruction Level Parallelism (ILP)
-is statically obtained by the compiler which
-performs code transformations being aware of the underlying hardware
-configuration.  This tight hardware/software dependence, makes the
+purposes focused on parameter-space representation
+\item \emph{Compiler awareness}: code scheduling for the execution of
+applications is statically obtained by the compiler which
+performs code transformations ``being aware'' of the underlying hardware
+configuration.  This tight hardware/software dependence makes the
 VLIW scenario perfectly suitable for investigating hardly predictable
-hardware/software interactions.
+parameter interactions.
 \end{itemize}
@@
 \begin{itemize}
-\item{tcc\_region}: Specifies the scope of action of the compiler and the type
+\item \emph{tcc\_region}: Specifies the scope of action of the compiler and the type
 of code transformation involved (basic block, super block and hyper
 block) 
-\item {max\_unroll\_allowed}: The number of unroll iterations allowed
-\item{regroup\_only}: Avoids inlining 
-\item{do\_classic\_opti}: A set of classical optimization, not VLIW related,
+\item \emph {max\_unroll\_allowed}: The number of unroll iterations allowed
+\item \emph{regroup\_only}: Avoids inlining 
+\item \emph{do\_classic\_opti}: A set of classical optimization, not VLIW related,
 such as common expression removal 
-\item{do\_prepass\_scalar\_scheduling}: Performs a schedule before
+\item \emph{do\_prepass\_scalar\_scheduling}: Performs a schedule before
 forming regions 
-\item{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
+\item \emph{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
 do\_modulo\_scheduling  Modular scheduling 
-\item{memvr\_profiled}: Performs a memory-dependencies profiling 
+\item \emph{memvr\_profiled}: Performs a memory-dependencies profiling 
 \end{itemize}
@@
 genetic approach while even discovering very different Pareto fronts.
-Continuing with a more extended simulation budget as depicted in
+Considering the extended simulation budget as depicted in
 Figure~\ref{fig:pareto_fronts_500}, we can qualitatively observe that
@@
 range that is, on average, wider than that provided by a
-MOGA exploration for power dissipation and execution time, respectively.
+GA exploration for power dissipation and execution time, respectively.
 %\begin{table}
@@
 exploration. As it can be observed, GA still shows a tendency in
-discovering more uniformly dispersed points (i.e. higher values). These results,
+discovering more uniformly dispersed points (i.e. higher values in the
+chart). These results,
 together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
 (b) confirm the the availability of density vs extension trade-offs
-when comparing PS and multi-objective genetic approaches.
+when comparing PS and GA approaches. Again, it
+should be pointed out how a definitive claim about the superiority of
+the PS behaviour is stricly dependent on the design 
+requirements and constraints, e.g. whether we need wide or dense
+results. Nevetheless, the proposed algorithm introduces a new
+perspective on thinking the allocation of a simulations budget, paving the way for
+the development of further strategies for addressing the problem of
+multi-objective hardware/software desing space exploration.

### 2014-07-28 introduction.tex
Some final touches, added more results comment

@@
 of the Pareto front there is no other configuration performing better
-for all the objectives considered. Of course this is only a first
+for all the objectives considered (see Figure~\ref{fig:psos}). Of course this is only a first
 high-level system simulation, thus these few promising
@@
 ``automated approaches for computing interdependencies'' is declared
-in the same paper.  These drawbacks are not present in our algorithm,
+in the same paper.  These drawbacks are not present in PS,
 since, although it leverages dependencies as in

### 2014-07-28 experiments.tex
added comment

@@
 
+\comment{DP:il discorso si concludeva troppo di botto, ho aggiunto una
+specie di finale che devi immaginare tipo il finale di rocky ''se io posso cambiare, e tu puoi
+cambiare, tutto il mondo puo' cambiare, adriaaaanaa! ''}
 Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute

### 2014-07-31 algorithm.tex
Some final touches, added more results comment
AA: ho letto i numerical results

@@
 
-At a glance, at each iterations simulations are performed.
+At a glance, at each iteration simulations are performed.
 Regions are classified based on the innovation introduced by their configurations in the Pareto-front so far calculated.
-The most interesting regions are split, so that each subregion will receive evaluation effort in the next iteration.
+The most interesting regions are split, so that each sub-region will receive evaluation effort in the next iteration.
 On the contrary, uninteresting regions are merged.
@@
 
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the subregions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$.
+\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the sub-regions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$.
 Formally:
@@
 
-A pseudocode representation of PS algorithm is in Alg.\ref{alg:algo}
+A pseudo-code representation of PS algorithm is in Alg.\ref{alg:algo}
 

### 2014-07-31 concepts.tex
AA: ho letto i numerical results

@@
 
-As we will show later, at each iteration, PS calculates an approssimation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on.
-The image of $\mathscr{P}_i$ is an approssimation of the Pareto-front.
+As we will show later, at each iteration, PS calculates an approximation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on.
+The image of $\mathscr{P}_i$ is an approximation of the Pareto-front.
 The simulation effort is distributed more on the regions that provide configurations in $\mathscr{P}_i$ which introduce more \emph{innovation}, i.e.
-whose image in the objective space is more distant, thus ``more different'', from the previous Pareto-front approssimation point.
+whose image in the objective space is more distant, thus ``more different'', from the previous Pareto-front approximation point.
 
@@
 In order to implement this behavior algorithmically, at each iteration PS assigns the same number $N$ of simulations to each region.
-If a region $R$ is interesting, it is split in $k$ subregions before the next iteration starts.
-Therefore, in the next iteration, $N$ simulations are assigned to each subregion.
+If a region $R$ is interesting, it is split in $k$ sub-regions before the next iteration starts.
+Therefore, in the next iteration, $N$ simulations are assigned to each sub-region.
 As a result, we are populating the original region $R$ with $k\cdot N$ simulations.
 On the contrary, uninteresting regions are merged, so that each one will receive less effort in the next iteration.
-In other words, ares of the configuration space that are more promising are split in small subregions, while the other ones are blended in big regions.
+In other words, ares of the configuration space that are more promising are split in small sub-regions, while the other ones are blended in big regions.
 As illustrated in \figR{small_and_big}, assigning $N$ simulations to each region makes small ones well populated while bigger ones sparsely explored.
@@
 \label{pers02.def:Splitting-a-region}
-Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it in a set of subregions obtained splitting each $p_i$-interval and combining the resulting subintervals with the cartesian product, as in \figR{split}~(b).
+Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it in a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the cartesian product, as in \figR{split}~(b).
 Formally:

### 2014-07-31 experiments.tex
AA: ho letto i numerical results

--- 2014-07-28 experiments.tex
@@
 In order to evaluate the behavior of the proposed approach
-we will be using a parameterized Very Long Instruction
-Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The same philosophy
+we use \comment{AA:da ``we will be using'' a ``we use''} a parameterized Very Long Instruction
+Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The \comment{AA:Ho eliminato ``same'' che non avevo capito a cosa si riferisse} philosophy
 behind a VLIW system makes this a natural choice for several reasons:
 \begin{itemize}
-\item \emph{Multi-Objective trade-offs}: VLIW architectures let designers
-easily trade between power, energy and performances, resulting
+\item \emph{Multi-Objective trade-offs}: VLIW architectures require designers
+to trade between power \comment{AA:Prima era ``let designers easily trade'', ma mi suonava strano}, energy and performances, resulting
 in extended Pareto sets which are an ideal ground for our testing
@@
 of the register files and the number of functional
-units for each type. In particular, five different types of register
+units of each type\comment{AA:Da ``for each type'' a ``of each type''}. In particular, five different types of register
 files are supported:
@@
 \item \emph{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
-do\_modulo\_scheduling  Modular scheduling 
+do\_modulo\_scheduling \comment{AA:Non ho capito; E' un nuovo item questo?} Modular scheduling 
 \item \emph{memvr\_profiled}: Performs a memory-dependencies profiling 
@@
 
-The results presented in the next section compare PS one widely
+The results presented in the next section compare PS with one widely
 adopted Multi-objective Genetic Algorithm
-(MOGA)~\cite{knowles_techrep06}. At best of our knowledge, genetic
+(MOGA)~\cite{knowles_techrep06}. To the best of our knowledge \comment{AA:da ``At best ...'' a ``To the best'': lo leggo quasi sempre cosi}, genetic
 approaches in general still represent the best compromise between
 efficiency (i.e. time required for exploration) and accuracy of the
-reported Paret Sets.  Note that for the reasons described above,
+reported Pareto Sets.  Note that, for the reasons described above,
 mono-objective approaches have been explicitly excluded from this
-analysis. Same decision has been taken for other approaches (e.g.
+analysis.  We also exclude other approaches (e.g.
 dependency based~\cite{givargis_tvlsi02}) that make use of some
@@
 regions without any external judgement or help based on heuristics.
+\comment{AA: Nella frase precedente sono passato da da ``Same decision has been taken for'' a ``We also exclude'' perche a un lettore disattento potrebbe sembrare che volevamo dire che anche givargis and co.
+avessero adottato la nostra decision di escludere genetic approaches}
 Finally, it should be pointed out that in this introductory work we
@@
 remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for a
-detailed analysis on how it differs and what could be expected from
+detailed analysis on how it differs \comment{AA: from what?} and what could be expected from
 similar multi-objective strategies.
@@
 Set of Figures~\ref{fig:pareto_fronts_100}
-and~\ref{fig:pareto_fronts_500} show the resulting pareto fronts for two
+and~\ref{fig:pareto_fronts_500} show the resulting Pareto fronts for two
 different scenarios of 100 and 500 simulations budget. When possible,
@@
 configuration being investigated the two sets are often overlapping,
-being also strongly depended upon the application being considered.
-These results are obtained in about 5 eras, and the main aim was
-demonstrating that with a so limited budget PS still can compete with
-genetic approach while even discovering very different Pareto fronts.
+being also strongly dependent upon the application being considered.
+These results are obtained in about 5 eras and demonstrate that with a so limited budget PS\comment{AA: ho tolto ``still'' perche' non ne ho capito il senso} can compete with
+genetic approach while even discovering very different Pareto fronts. \comment{AA: nella frase precedente cambiato da ``, and the main aim was demonstrating'' a "and demonstrate"}
 Considering the extended simulation budget as depicted in
@@
 objective, the variation range represents the ratio between the
-maximum and the minimum value observed for that objective. A
+maximum and the minimum value observed for that objective.
+A comparison between the variation ranges of both power dissipation and execution time, obtained by PS and GA for different benchmarks is shown in Fig.~\ref{fig:dispersion}(a) and (b) respectively.
+\comment{La frase precedente e' un rifrasamento (esiste sto termine in italiano?) di ``A
 comparison between the variation range for different benchmarks
@@
 execution time is shown in Fig.~\ref{fig:dispersion}(a) and (b)
-respectively. As it can be observed, the PS exploration provides solutions which fall on a
-range that is, on average, wider than that provided by a
+respectively.''}
+ As it can be observed, the PS exploration provides solutions which fall on a
+range that is, on average, wider than the one provided by a
 GA exploration for power dissipation and execution time, respectively.
@@
 %  \end{tabular}
-%  \caption{(a)(b) Variation range for different benchmarks between PS and GA
+%  \caption{(a)(b) Variation range obtained by PS and GA for different benchmarks
 %  and average dispersion absolute dispersion (c)}
@@
 \begin{table}
-  \tbl{(a)(b) Variation range for different benchmarks between PS and GA
-  and average dispersion absolute dispersion (c)
+  \tbl{(a)(b) Variation range obtained by PS and GA for different benchmarks
+  and average dispersion absolute dispersion (c). \comment{AA: manca il titolo nella figura (c)}
   \label{fig:dispersion}}{
@@
 dispersion errors for different benchmarks for PS and GA
-exploration. As it can be observed, GA still shows a tendency in
+exploration. As it can be observed, GA \comment{AA: ho tolto ``still'' perche' non ne ho capito il senso} shows a tendency in
 discovering more uniformly dispersed points (i.e. higher values in the
@@
 together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
-(b) confirm the the availability of density vs extension trade-offs
+(b) confirm the \comment{AA: cambiato da ``availability '' a ``existence''} of density vs extension trade-offs
 when comparing PS and GA approaches. Again, it
-should be pointed out how a definitive claim about the superiority of
-the PS behaviour is stricly dependent on the design 
+is worth pointing out how a definitive claim about the superiority of
+the PS behaviour is strictly dependent on the design 
 requirements and constraints, e.g. whether we need wide or dense
-results. Nevetheless, the proposed algorithm introduces a new
-perspective on thinking the allocation of a simulations budget, paving the way for
+results. Nevertheless, the proposed algorithm introduces a new
+perspective on \comment{AA: ho rimosso `` thinking'' perche' altrimenti avrei preferito ``a new way of thinking''} the allocation of a simulations budget, paving the way for
 the development of further strategies for addressing the problem of
-multi-objective hardware/software desing space exploration.
+multi-objective hardware/software design space exploration.

### 2014-07-31 introduction.tex
AA: ho letto i numerical results

@@
 
-\comment{DP: ho reintrodotto la descrizione di cos'e' un pareto set e
-front che ci serve dopo quando descriviamo PS, inoltre ho sostituito
-la tua frase era un po' contorta. In breve, il fatto che il pareto set
-del DSE sia un'approssimazioen di quello divino irraggiungibile e' una
-cosa che e' inutile dire qui, fa solo confondere col concetto di
-approssimazione che e' invece dovuto al fatto che usiamo modelli di
-alto livello}
 %while providing, at the end, configurations that are close to the
@@
 %design process, in a more thorough way.
-
-\comment{DP: poi dobbiamo trovare un nome piu' interessante rispetto a
-interesting regions, ci pensiamo questa estate}
 
@@
 distributed there rather than in the rest of the configuration space.
-Several geometrical trasformations (splitting, merging etc...) are
+Several geometrical transformations (splitting, merging etc...) are
 involved in the Parameter Space (aka configuration space), hence
@@
 among certain ranges of parameters and may not hold when considering
-the entires ranges. This cannot be modelled in Dependency Analysis.
+the entire ranges. This cannot be modeled in Dependency Analysis.
 
@@
 the proposed approach against a well known Multi-Objective Genetic
-Algoritm~\cite{knowles_techrep06}.
+Algorithm~\cite{knowles_techrep06}.
 We claim that the approach presented in this paper has most of the benefits of the genetic

### 2014-07-31 paper.tex
AA: ho letto i numerical results

@@
 case study involving the hardware/software exploration of a VLIW
-architcture. Qualitative and quantitative comparisons of PS
+architecture. Qualitative and quantitative comparisons of PS
 against a well-know multiobjective genetic approach demonstrate that,
@@
 \section{Conclusions}
-In this work we presented a multiobjective strategy which 
+In this work we presented PS, a multiobjective strategy which 
 introduces the concept of Parameter Space representation of Pareto
 Front. A case study of a VLIW architecture involving strong
-hardware/software dependencies has been carried out to evaluate
+hardware/software dependencies has been analyzed \comment{AA: da ``carried out'' a ``analyzed'', carry out a case study (effettuare un caso studio) mi suonava strano } carried out to evaluate
 effectiveness with different amount of simulations budget.
@@
 distribution of Pareto points which trades solutions granularity with
-improved pareto extension.
+improved Pareto extension.
 

### 2014-08-01 experiments.tex
Final fixes, removed accepted commennts

@@
 In order to evaluate the behavior of the proposed approach
-we use \comment{AA:da ``we will be using'' a ``we use''} a parameterized Very Long Instruction
-Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The \comment{AA:Ho eliminato ``same'' che non avevo capito a cosa si riferisse} philosophy
+we use a parameterized Very Long Instruction
+Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The philosophy
 behind a VLIW system makes this a natural choice for several reasons:
 \begin{itemize}
-\item \emph{Multi-Objective trade-offs}: VLIW architectures require designers
-to trade between power \comment{AA:Prima era ``let designers easily trade'', ma mi suonava strano}, energy and performances, resulting
+\item \emph{Multi-Objective trade-offs}: VLIW architectures allow designers
+to trade between power, energy and performances objectives, resulting
 in extended Pareto sets which are an ideal ground for our testing
@@
 of the register files and the number of functional
-units of each type\comment{AA:Da ``for each type'' a ``of each type''}. In particular, five different types of register
+units of each type. In particular, five different types of register
 files are supported:
@@
 \item \emph{do\_classic\_opti}: A set of classical optimization, not VLIW related,
-such as common expression removal 
+such as common expression removal and loop unrolling
 \item \emph{do\_prepass\_scalar\_scheduling}: Performs a schedule before
@@
 \item \emph{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
-do\_modulo\_scheduling \comment{AA:Non ho capito; E' un nuovo item questo?} Modular scheduling 
+\item \emph{do\_modulo\_scheduling}: Modular scheduling of loop code
 \item \emph{memvr\_profiled}: Performs a memory-dependencies profiling 
@@
 adopted Multi-objective Genetic Algorithm
-(MOGA)~\cite{knowles_techrep06}. To the best of our knowledge \comment{AA:da ``At best ...'' a ``To the best'': lo leggo quasi sempre cosi}, genetic
+(MOGA)~\cite{knowles_techrep06}. At the best of our knowledge, genetic
 approaches in general still represent the best compromise between
@@
 mono-objective approaches have been explicitly excluded from this
-analysis.  We also exclude other approaches (e.g.
-dependency based~\cite{givargis_tvlsi02}) that make use of some
-a-priori knowledge about the role and meaning of each parameter, since
-our aim is evaluate the capacity of focusing on interesting parameter
-regions without any external judgement or help based on heuristics.
-\comment{AA: Nella frase precedente sono passato da da ``Same decision has been taken for'' a ``We also exclude'' perche a un lettore disattento potrebbe sembrare che volevamo dire che anche givargis and co.
-avessero adottato la nostra decision di escludere genetic approaches}
-Finally, it should be pointed out that in this introductory work we
-will explicitly use the \emph{SPEA}~\cite{zitzler_eurogen01} variant of MOGA,
-remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for a
-detailed analysis on how it differs \comment{AA: from what?} and what could be expected from
-similar multi-objective strategies.
+analysis.  We also exclude other approaches (e.g.  dependency
+based~\cite{givargis_tvlsi02}) that make use of some a-priori
+knowledge about the role and meaning of each parameter, since our aim
+is evaluate the capacity of focusing on interesting parameter regions
+without any external judgement or help based on heuristics.  Finally,
+it should be pointed out that in this introductory work we will
+explicitly use the \emph{SPEA}~\cite{zitzler_eurogen01} variant of
+MOGA, remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03}
+for a detailed analysis on how it differs from other genetic approaches
+and what could be expected from similar multi-objective strategies.
 
@@
 being also strongly dependent upon the application being considered.
-These results are obtained in about 5 eras and demonstrate that with a so limited budget PS\comment{AA: ho tolto ``still'' perche' non ne ho capito il senso} can compete with
-genetic approach while even discovering very different Pareto fronts. \comment{AA: nella frase precedente cambiato da ``, and the main aim was demonstrating'' a "and demonstrate"}
+These results are obtained in about 5 eras and demonstrate that with a so limited budget PS can compete with
+genetic approach while even discovering very different Pareto fronts. 
 Considering the extended simulation budget as depicted in
@@
 maximum and the minimum value observed for that objective.
-A comparison between the variation ranges of both power dissipation and execution time, obtained by PS and GA for different benchmarks is shown in Fig.~\ref{fig:dispersion}(a) and (b) respectively.
-\comment{La frase precedente e' un rifrasamento (esiste sto termine in italiano?) di ``A
-comparison between the variation range for different benchmarks
-between a PS and a GA exploration for both power dissipation and
-execution time is shown in Fig.~\ref{fig:dispersion}(a) and (b)
-respectively.''}
- As it can be observed, the PS exploration provides solutions which fall on a
-range that is, on average, wider than the one provided by a
-GA exploration for power dissipation and execution time, respectively.
+A comparison between the variation ranges of both power dissipation
+and execution time, obtained by PS and GA for different benchmarks is
+shown in Fig.~\ref{fig:dispersion}(a) and (b) respectively.  As it can
+be observed, the PS exploration provides solutions which fall on a
+range that is, on average, wider than the one provided by a GA
+exploration for power dissipation and execution time, respectively.
 %\begin{table}
@@
 dispersion errors for different benchmarks for PS and GA
-exploration. As it can be observed, GA \comment{AA: ho tolto ``still'' perche' non ne ho capito il senso} shows a tendency in
+exploration. As it can be observed, GA shows a tendency in
 discovering more uniformly dispersed points (i.e. higher values in the
@@
 together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
-(b) confirm the \comment{AA: cambiato da ``availability '' a ``existence''} of density vs extension trade-offs
+(b) confirm the of density vs extension trade-offs
 when comparing PS and GA approaches. Again, it
@@
 results. Nevertheless, the proposed algorithm introduces a new
-perspective on \comment{AA: ho rimosso `` thinking'' perche' altrimenti avrei preferito ``a new way of thinking''} the allocation of a simulations budget, paving the way for
+perspective on the allocation of a simulations budget, paving the way for
 the development of further strategies for addressing the problem of

### 2014-08-01 paper.tex
Final fixes, removed accepted commennts

@@
 Front. A case study of a VLIW architecture involving strong
-hardware/software dependencies has been analyzed \comment{AA: da ``carried out'' a ``analyzed'', carry out a case study (effettuare un caso studio) mi suonava strano } carried out to evaluate
+hardware/software dependencies has been analyzed to evaluate
 effectiveness with different amount of simulations budget.

### 2014-08-01 paper.tex
last fixes for acm submission

@@
 
-\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
-%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
+%\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
+\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
 
@@
 
+% Metadata Information
+%\acmVolume{9}
+%\acmNumber{4}
+%\acmArticle{39}
+%\acmYear{2010}
+%\acmMonth{3}
+
 \begin{document}
@@
 ANDREA ARALDO
-\affil{University of Catania}
+\affil{Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
+Paris, France;}
 DAVIDE PATTI
@@
 \begin{abstract}
+%Embedded Systems Design requires conflicting objectives to be
+%optimized with an appropriate choice of hardware/software parameters.
+%In this work we present PS, a new multiobjective exploration algorithm
+%exploiting the parameter space representation of the pareto front.
+%After a detailed formal description of the algorithm and the
+%underlying concepts, we show a case study involving the
+%hardware/software exploration of a VLIW architecture. Qualitative and
+%quantitative comparisons of the PS approach against a well-known
+%multiobjective genetic technique demonstrate that, while not
+%outperforming it in terms of pareto dominance, the proposed approach
+%can trade the uniformity and granularity qualities of the solutions
+%found for obtaining larger Pareto sets, thus representing a further
+%choice for designer when objective constrains allow it.
+
 Embedded Systems Design requires conflicting objectives to be
@@
 architecture. Qualitative and quantitative comparisons of PS
-against a well-know multiobjective genetic approach demonstrate that,
-while not outperforming it in terms of dominance, the proposed
+against a well-known multiobjective genetic approach demonstrate that,
+while not outperforming it in terms of pareto dominance, the proposed
 approach can trade the uniformity and granularity qualities of the
@@
 Author's addresses: V. Catania, DIEEI University of Catania;
-A. Araldo, DIEEI University of Catania;
+A. Araldo, Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
+Paris, France;
 D. Patti, DIEEI University of Catania.

### 2014-10-12 algorithm.tex
AA: implementati i suggerimenti sull'espressione inglese del reviewer II

@@
 
-By a slightly abuse of notation, considering a subset $I$ of the configuration space, we will denote with $\mathcal{P}(I,b)$ the non-dominated feasible configurations in $I$, i.e.
+By a slightly abuse of notation, considering a subset $I$ of the configuration space, we will use  $\mathcal{P}(I,b)$ to denote the non-dominated feasible configurations in $I$, i.e.
 	\begin{align}
@@
 For this reason, $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations are randomly extracted from the new configurations of each region $R\in\mathcal{R}_{i}$.
-We denote the set of the selected configurations with $test_{R,i}$ and, obviously, $\bigcup_{R\in\mathcal{R}_{i}} test_{R,i} = test_i$.
+We use $test_{R,i}$ to denote the set of the selected configurations and, obviously, $\bigcup_{R\in\mathcal{R}_{i}} test_{R,i} = test_i$.
  In case the new configurations in $R$ are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them are selected.
@@
 	\begin{enumerate}
-		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split obtaining $\psi(R)$, as stated in def \defR{splitting-a-region}.
-We denote with $\psi\left(\mathscr{R}_{i,h}\right)$ the set of regions obtained as explained.
+		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split to obtain $\psi(R)$, as stated in \defR{splitting-a-region}.
+We use $\psi\left(\mathscr{R}_{i,h}\right)$ to denote the set of regions obtained as explained.
 		\item Low innovation regions are left unchanged.
@@
 To do so, pairs of no innovation contiguous regions $(R_1,R_2)$ are selected.
-We denote the set of these pairs as $\mathscr{M}_i$.
+We use $\mathscr{M}_i$ to represent the set of these pairs.
 This set is constructed such that pairs are independent, i.e.
@@
 We stress that the regions that belong to each selected pair must be contiguous, otherwise it is impossible to merge them.
-We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e.
+We use $\mu(\mathscr{M}_i)$ to denote the set of the merged regions, i.e.
 $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$

### 2014-10-12 concepts.tex
AA: implementati i suggerimenti sull'espressione inglese del reviewer II

@@
 We will also refer to these points as ``parameter space representation'' of the Pareto front.
-Figure~\ref{fig:psos} shows the relation between the objective space (containing the Pareto front) and its parameter space representation.
+\figR{psos} shows the relation between the objective space (containing the Pareto front) and its parameter space representation.
 In particular in this work we are interested in the relation between the evolution of the points in the two spaces, e.g.
@@
 \begin{figure}[t]
-\label{fig:psos}
+\figLC{psos}{Relation between Pareto-set and Pareto front.}
 \center
 \includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
-\caption{Relation between Pareto-set and Pareto front.}
 \end{figure}
@@
 to the designer.
-Therefore, as stated in section \ref{sec:Related-work},
+Therefore, as stated in \secR{Related-work},
 setting up an exploration trying to take into account as much dependencies
@@
 
-%TODO: sync name of values with formulation
 \subsection{Formal definitions}
@@
 \label{pers02.def:Contiguous-intervals}
-Two intervals are contiguous iff they do not overlap and merging them results in a new interval.More formally, let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
+Two intervals are contiguous iff they do not overlap and merging them results in a new interval. More formally, let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
 be two $p_{i}$-intervals. They are said to be contiguous (see \figR{interval_and_region}(a) ) iff
@@
 
-As already explain, we will split interesting regions and merge uninteresting ones.
+As already explained, we will split interesting regions and merge uninteresting ones.
 The region splitting and merging operations are defined starting from the corresponding operations defined on intervals.
@@
 
-We define the split operator $\psi$ as the one that, applied to the intervals, gives the result of the split operation, i.e., in the case above, $\psi \left[a_{i}..b_{i}\right]=\lbrace \left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right] \rbrace$.
+We define the split operator $\psi$ as the one that, when applied to the intervals, gives the result of the split operation, i.e., in the case above, $\psi \left[a_{i}..b_{i}\right]=\lbrace \left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right] \rbrace$.
 If $\left|\left[a_{i}..b_{i}\right]\right|=1$, the interval
@@
 \label{pers02.def:Splitting-a-region}
-Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it in a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the cartesian product, as in \figR{split}~(b).
+Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it into a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the cartesian product, as shown in \figR{split}~(b).
 Formally:
@@
 	\begin{figure}[t]
+	    \figLC{split}{Split operations.}
 		\begin{center}
@@
 				\includegraphics[width=0.60\textwidth]{img/splitting_regions} }
-		    \figLC{split}{Split operations.}
 		\end{center}
@@
 The two regions at the top are contiguous because their union can be expressed as the cartesian product of parameter intervals, thus they can be merged to obtain a new bigger region.
-The same applies also to the regions on the right.
+The same also applies to the regions on the right.
 On the contrary, the two regions on the left (or of the two regions at the bottom) cannot be merged.
@@
 
-We now describe formally the merging operations.
+We now formally describe the merging operations.
 \begin{definition}[Merging intervals]
@@
 
-In \secR{sketch} we observed that, in order to estimate how much interesting is a region, it is crucial to understand the novelty that it introduces, i.e.
+In \secR{sketch} we observed that, in order to estimate how interesting a region is, it is crucial to understand the novelty it introduces, i.e.
 how distant the Pareto-optimal configurations discovered in that region are from the Pareto-optimal configuration previously discovered.
 The concept of distance is expressed by the operator defined in the next definition.
-We prefer to call it \emph{separation} rather than \emph{distance}, because usually distance denote a commutative operator while our definition of separation is non commutative.
+We prefer to call it \emph{separation} rather than \emph{distance}, because usually distance denotes a commutative operator while our definition of separation is non commutative.
 
@@
 Note that the separation is a \emph{normalized} measure, thanks to $o'_i$ at the denominator.
-This is important since usually objectives are heterogeneous, e.g.
-delay and power consumption, having different unity of measurement and different scale.
+This is important since objectives are usually heterogeneous, e.g.
+delay and power consumption have different unities of measurement and different scale.
 If we did not use a normalized measure, in presence of objectives whose absolute values are small and other objectives with big values, the notion of distance would have been biased toward the latter.

### 2014-10-12 experiments.tex
AA: implementati i suggerimenti sull'espressione inglese del reviewer II

@@
 \section{A Case Study: VLIW Hardware/Software Design Space}
-\label{sec:ee}
+\secL{ee}
 \subsection{Motivation}
@@
 adopted Multi-objective Genetic Algorithm
-(MOGA)~\cite{knowles_techrep06}. At the best of our knowledge, genetic
+(MOGA)~\cite{knowles_techrep06}. To the best of our knowledge, genetic
 approaches in general still represent the best compromise between
@@
 
-Set of Figures~\ref{fig:pareto_fronts_100}
-and~\ref{fig:pareto_fronts_500} show the resulting Pareto fronts for two
+\figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the resulting Pareto fronts for two
 different scenarios of 100 and 500 simulations budget. When possible,
@@
 
-\begin{table}
-  \tbl{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.\label{fig:pareto_fronts_100}}{
-  \begin{tabular}{ccc}
-    \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps} &
-    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps} & 
-    \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps} \\
-    \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps} &
-    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps} &
+\begin{figure}
+  \figLC{pareto_fronts_100}{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.
+\comment{AA: nelle due figure centrali la linea di GA e' continua, mentre in tutte le altre figure e' tratteggiata.
+Il revisore ci chiede di uniformare.
+Non so come riottenere le figure.
+Potresti pensarci tu?}}
+  \begin{center}
+    \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps}
     \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
-  \end{tabular}}
+  \end{center}
+\end{figure}
 
-\end{table}
-
-\begin{table}
-  \tbl{Pareto fronts found by PS and GA for a fixed budget of 500
-  configurations.\label{fig:pareto_fronts_500}}{
-  \begin{tabular}{ccc}
-    \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps} &
-    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps} & 
-    \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps} \\
-    \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps} &
-    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps} &
+\begin{figure}
+  \figLC{pareto_fronts_500}{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.\comment{AA: nelle due figure centrali la linea di GA e' continua, mentre in tutte le altre figure e' tratteggiata.
+Il revisore ci chiede di uniformare.
+Non so come riottenere le figure.
+Potresti pensarci tu?}}
+  \begin{center}
+    \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps}
     \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 
-  \end{tabular}}
-\end{table}
-Low budget Pareto sets are shown in
-Figure~\ref{fig:pareto_fronts_100}. With a so small number of
+  \end{center}
+\end{figure}
+Low budget Pareto sets are shown in \figR{pareto_fronts_100}. With a so small number of
 configuration being investigated the two sets are often overlapping,
@@
 Considering the extended simulation budget as depicted in
-Figure~\ref{fig:pareto_fronts_500}, we can qualitatively observe that
+\figR{pareto_fronts_500}, we can qualitatively observe that
 even if PS does not strictly outperforms genetic in terms of dominance, it shows in
@@
 various design factors such as desired results granularity, prefixed objective
-range constraints, estimated error of the models used etc~\ldots.
+range constraints, estimated error of the models used etc.
 
@@
 and execution time, obtained by PS and GA for different benchmarks is
-shown in Fig.~\ref{fig:dispersion}(a) and (b) respectively.  As it can
+shown in \figR{dispersion}(a) and (b) respectively.  As it can
 be observed, the PS exploration provides solutions which fall on a
@@
 
-\begin{table}
-  \tbl{(a)(b) Variation range obtained by PS and GA for different benchmarks
-  and average dispersion absolute dispersion (c). \comment{AA: manca il titolo nella figura (c)}
-  \label{fig:dispersion}}{
-  \begin{tabular}{c}
-    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
-    (a) \\
-    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} \\
-    (b) \\
-    \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
-    (c) 
-  \end{tabular}}
-\end{table}
+\begin{figure}
+  \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for different benchmarks and average dispersion absolute dispersion (c). \comment{AA: manca il titolo nella figura (c)} }
+  \begin{center}
+    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} }
+    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} }
+    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} }
+  \end{center}
+\end{figure}
+
 The average normalised absolute dispersion error measures
@@
 
-Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
+\figR{dispersion}(c) shows the average normalised absolute
 dispersion errors for different benchmarks for PS and GA
@@
 chart). These results,
-together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
+together with the variation ranges of \figR{dispersion}(a) and
 (b) confirm the of density vs extension trade-offs

### 2014-10-12 introduction.tex
AA: implementati i suggerimenti sull'espressione inglese del reviewer II

@@
 of the Pareto front there is no other configuration performing better
-for all the objectives considered (see Figure~\ref{fig:psos}). Of course this is only a first
+for all the objectives considered (see \figR{psos}). Of course this is only a first
 high-level system simulation, thus these few promising
@@
 distributed there rather than in the rest of the configuration space.
-Several geometrical transformations (splitting, merging etc...) are
+Several geometrical transformations (splitting, merging etc.) are
 involved in the Parameter Space (aka configuration space), hence
@@
 In \secR{algorithm} we give the theoretical description of PS.
-Finally in Section~\ref{sec:ee} we show a case
+Finally in \secR{ee} we show a case
 study involving the exploration of the hardware/software parameters of
@@
 were perfectly isolated, i.e., if there were no dependencies among
-them. But real scenarios seldom if ever
-expose monotonicity property thus resulting in inaccuracies, as stated in the same paper).
+them. But real scenarios rarely expose monotonicity property thus resulting in inaccuracies, as stated in the same paper).
 

### 2014-10-12 paper.tex
AA: implementati i suggerimenti sull'espressione inglese del reviewer II

@@
 
-%\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
-\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
+\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
+%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear
 
@@
 
-\section{Conclusions}
+\secL{Conclusions}
 In this work we presented PS, a multiobjective strategy which 

### 2014-10-12 experiments.tex
AA: fornendo motivazioni alle metriche scelte

@@
 \end{table}
-\subsection{Evaluation Metrics}
+\subsection{Terms of comparison}
 
@@
 %------------------------------------------------------------------------------
+
+\subsection{Evaluation metrics}
+In order to evaluate the Paretos from a quantitative point-of-view we
+will consider two metrics, namely, the \emph{variation range} and the
+\emph{average normalised absolute dispersion error}.
+
+For a given objective, the \emph{variation range} represents the ratio between the maximum and the minimum value observed for that objective.
+\comment{AA: Per rappresentare l'extent del Pereto front, forse sarebbe meglio evitare di usare il variation range, per come l'hai definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5 ``Metrics of performance'', che mi pare rappresenti la stessa cosa, concettualmente.
+Questo ci permette di essere meno attaccabili (del tipo ``non te la prendere con noi, prenditela con Zitzler se non capisci l'utilita' della metrica'').}
+It quantifies the extent of the of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
+Indeed, authors in \cite{zitzler_ec00} carefully observe that an exploration algorithm should preferably provide pareto fronts whose objective function range is large.
+Such Pareto fronts permit to investigate in a broader way the potentials of the designed device.
+This is important, in general, and turns out to be essential when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
+
+The average \emph{normalised absolute dispersion error} measures
+the average absolute difference between the distribution of points in
+the objective space and an ideal distribution in which the points are
+uniformly distributed over the objective space. 
+The motivation behind this metric is, again, given by \cite{zitzler_ec00}, in which authors remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.
+In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front.
+\comment{AA: commentare perche' e' importante questa metrica. Cercare la parola chiave ``deception'' o qualcosa del genere}.
+Formally, let $O$ be
+the image, in the objective space, of the configurations visited by
+the design space exploration. The generic element of $O$ (\ie, a
+solution) is a pair $(p,t)$ where $p$ and $t$ are the average power
+and execution time, respectively. The two-dimensional objective space
+is then partitioned by a $M_x \times M_y$ mesh. For each tile $T_i,
+\ i=1, 2, \ldots, M_xM_y$ of the mesh, let $N_i$ be the number
+of points in $O$ which fall in $T_i$. The average absolute error, $E_i$, for
+$T_i$ is the absolute value of the difference between $N_i$ and the
+ideal number of solutions, $\overline{N}$, which should fall in $T_i$
+in case of uniform distribution. Such $\overline{N}$ can be simply
+computed as the ratio between the cardinality of $O$ and the number of
+tiles. Thus,
+\[ E_i = |N_i - \overline{N}|, \]
+where $\overline{N} = |O| / (M_x M_y)$. The average
+normalised absolute dispersion error ($ANADE$) is the average of $E_i$
+normalised to the maximum absolute error $E_{max}$:
+\[ ANADE = \frac{\sum_{i=1}^{M_xM_y} E_i/(M_xM_y)}{E_{max}}, \]
+where $E_{max}$ can be computed as the average absolute error in the worst
+case in which all the solutions fall in a single tile:
+\[ E_{max} = \frac{(M_x M_y - 1) \overline{N} + |\overline{N} -
+    |O|| }{M_x M_y}. \]
 
@@
 
-In order to evaluate the Paretos from a quantitative point-of-view we
-will consider two metrics, namely, the \emph{variation range} and the
-\emph{average normalised absolute dispersion error}. For a given
-objective, the variation range represents the ratio between the
-maximum and the minimum value observed for that objective.
 A comparison between the variation ranges of both power dissipation
@@
 
-The average normalised absolute dispersion error measures
-the average absolute difference between the distribution of points in
-the objective space and an ideal distribution in which the points are
-uniformly distributed over the objective space. Formally, let $O$ be
-the image, in the objective space, of the configurations visited by
-the design space exploration. The generic element of $O$ (\ie, a
-solution) is a pair $(p,t)$ where $p$ and $t$ are the average power
-and execution time, respectively. The two-dimensional objective space
-is then partitioned by a $M_x \times M_y$ mesh. For each tile $T_i,
-\ i=1, 2, \ldots, M_xM_y$ of the mesh, let $N_i$ be the number
-of points in $O$ which fall in $T_i$. The average absolute error, $E_i$, for
-$T_i$ is the absolute value of the difference between $N_i$ and the
-ideal number of solutions, $\overline{N}$, which should fall in $T_i$
-in case of uniform distribution. Such $\overline{N}$ can be simply
-computed as the ratio between the cardinality of $O$ and the number of
-tiles. Thus,
-\[ E_i = |N_i - \overline{N}|, \]
-where $\overline{N} = |O| / (M_x M_y)$. The average
-normalised absolute dispersion error ($ANADE$) is the average of $E_i$
-normalised to the maximum absolute error $E_{max}$:
-\[ ANADE = \frac{\sum_{i=1}^{M_xM_y} E_i/(M_xM_y)}{E_{max}}, \]
-where $E_{max}$ can be computed as the average absolute error in the worst
-case in which all the solutions fall in a single tile:
-\[ E_{max} = \frac{(M_x M_y - 1) \overline{N} + |\overline{N} -
-    |O|| }{M_x M_y}. \]
-
 \figR{dispersion}(c) shows the average normalised absolute

### 2014-10-12 introduction.tex
AA: fornendo motivazioni alle metriche scelte

@@
 each region based on the \emph{innovation} provided by its
-configurations in the Pareto front. The regions with high score are
-considered the most \emph{interesting} and more simulations are
-distributed there rather than in the rest of the configuration space.
+configurations in the Pareto front, i.e.
+how different these configurations are, in terms of objectives, with respect to the ones already found previously.
+The regions with high score are considered the most \emph{interesting} and more simulations are distributed there rather than in the rest of the configuration space.
 Several geometrical transformations (splitting, merging etc.) are
@@
 
+\cite{dellnitz2005covering} proposes three different methods for the numerical approximation of the Pareto set.
+The first two require the knowledge of the gradient of the objective functions, which is usually not available in embedded system design, since the closed form expression of the objective functions is not known a priori.
+The third one, called ``Sampling algorithm'', does not need this requirement and is the closest to ours, although the mechanism is different.
+At every iteration a set of regions of configuration space is constructed with the aim to cover the Pareto set.
+The size of these regions becomes smaller at each iteration so that the covering becomes tighter.
+A random set of test points are evaluated in each new region; only the regions containing non-dominated points will be considered in the next iteration.
+Our approach is different.
+First, in the Sampling algorithm only the selected regions are examined, even though there is no guarantee that all the Pareto points are included in them.
+As a consequence, the Sampling algorithm may erroneously and prematurely neglect some regions that may possibly contain a non-negligible number of Pareto points.
+Our algorithm avoids this, since even though a region has not provided non-dominated points, it is not neglected, rather it is simply populated with fewer test points, thus giving the chance to find non-dominated points in them.
+From this behavior also comes another important difference.
+The Sampling algorithm of \cite{dellnitz2005covering} keeps reinforcing the analysis of the regions selected in the previous iterations.
+In other words, it keeps zooming into the regions that have been considered ``interesting'', i.e.
+rich of non-dominated points, in the previous iterations.
+The philosophy behind our algorithm is different.
+A region, which has been considered interesting at a certain iterations, may be not in the future, since it has been thoroughly analyzed.
+On the other hand, a region, initially uninteresting, may turn out to be interesting in the future, once all the other regions have been already exploited.
+Therefore, from an iteration to the next, our algorithm zoom in on regions that are currently interesting and zoom out from the uninteresting ones,  spanning in a broader and more dynamical way the configuration space.
+In addition, in the Sampling region only the number of non-dominated points is accounted to see how interesting a region is.
+On the contrary, we also consider the \emph{innovation}, as already anticipated in the introduction.
+
 Many studies, as \cite{coello_easmop} and others, focus on genetic approaches to solve multiobjective
@@
 and require no a-priori knowledge to the designer.  The strong
-point of genetic approaches can be summarized saying that they consist
-in exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
+point of genetic approaches can be summarized as follows: they consist
+in an exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
 the already evaluated configurations. In this work we will compare 

### 2014-10-13 algorithm.tex
AA: fornendo motivazioni alle metriche scelte
AA: altre modifiche

@@
 	$\alpha=1.2$). 	
+		\comment{AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia.
+Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente.
+Non e' motivata da nessuna parte.
+Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso.
+E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale.
+Che ne dici di cambiare l'espressione in
+			\[
+			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
+			\]
+		}
 	\item \emph{low innovation regions}, whose score is positive but modest, i.e.
@@
 %
+
+\subsection{Algorithm parameters}
+The parameters that completely determine the algorithm are $K$ and $\alpha$.
+$K$ corresponds to the population size of the genetic approach.
+Authors of \cite{zitzler_ec00} found that increasing $k$ not necessarily has a considerable impact on the performance of the algorithm.
+This holds also in our algorithm.
+In addition, while in the genetic approach $K$ must be sufficiently large in order to guarantee diversity of the Pareto set configurations, in our algorithm the diversity is not impacted by $K$ since, by construction, it is guaranteed by the way the configuration space is partitioned, independently from number of configurations evaluated at each iteration.
+\comment{This is confirmed by the experimental results in \secR{parameter_impact}.
+}
+
+Parameter $\alpha$ determines when a region is considered of high innovation.
+High values of $\alpha$ mean that a region will hardly be elected as high-innovation, yielding less splitting operations.
+This slows down zooming in on portions of configuration space and make the distribution of the simulated configuration more uniform, as there are fewer small regions with a high test configuration concentration.
+The opposite happens when small values of $\alpha$ are used.
+\comment{This is confirmed by results of \secR{parameter_impact}.
+}

### 2014-10-13 appendix.tex
AA: altre modifiche

@@
+\section{appendix}
 Metto qua tutte le cose che non si possono lasciare nel testo ma che e' un peccato buttare nel dimenticatoio
@@
 	\]
+\end{definition}
 
-\end{definition}
+\subsection{Virtual merging}
+PROBLEMA: Secondo il punto debole del nostro algoritmo, che fa si che noi ci facciamo sempre fregare da GA e' il merging.
+Il merging puo' essere effettuato solo tra regioni contigue.
+Non so come siano andati i run, ma ad intuito, trovare delle no-innovation-regions che sono pure contigue e' proprio una botta di fortuna.
+Secondo me la maggior parte delle no-innovation-regions sono non contigue e quindi non si mergiano, continuando a restistere imperterritamente col procedere dei run.
+Risultato: le no-innovation-regions continuano a fregarsi, ad ogni iterazione, piu' run di quanti dovrebbero.
+
+SOLUZIONE: Forse per migliorare l'algoritmo si dovrebbe abbandonare il concetto di merging, visto che mi sa che per ora e' sulla carta, ma durante i run avviene poche volte.
+In alternativa, si potrebbe usare un fattore di qualita', che simuli l'avvenimento dei merge.
+Ad ogni regione $R$ si associa un fattore di qualita' $q_R$, di default 0.
+Quando la regione e' classificata come no-innovation, $q_R$ si decrementa.
+A ciascuna iterazione, anziche' assegnare ad ogni regione K/N simulazioni, dove N è il numero di regioni, ogni regione $R*$ dovrebbe avere il seguente numero di simulazioni
+	\begin{align}
+    \frac{2^{q_R*} K} { \sum_R  2^{q_R} }
+	\end{align}
+
+\subsection{Importance given to the innovation score}
+AND: una prova che si potrebbe fare e' modificare leggerment l'innovation score di una regione.
+Forse questa metrica da troppo peso all'innovation delle configurazioni.
+Se una regione e' ricca di pareto points, ma essi sono tutti simili (nel senso che le loro immagini nello spazio degli obiettivi sono tutte vicine), dopo un po' di iterazioni l'analisi di quella regione non portera' sufficiente innovazione e la regione sara' abbandonata.
+Il che e' un peccato, perche' magari quei punti che in questo modo ci stiamo perdendo permetterebbero di fregare, o eguagliare, genetic algo.
+Questo spiega anche perche' le nostre soluzioni spaziano di piu' lo spazio degli obiettivi e vanno piu' verso gli estremi.
+Se volessimo rinunciare a spaziare per forza tutto il range degli obiettivi, volendo essere piu' simili e competitivi con genetic algorithm, potremmo modificare il calcolo dell'innovation score (step (4) della sezione 4.2), nel seguente modo:
+	\begin{align}
+	    is(c^*) = 1 + B\cdot \min[ s(c \rightarrow c^*) | c \in \mathscr{P}_{i-1} ]
+	\end{align}
+In questo modo, il fattore B permette di pesare quanta importanza dare all'innovativita' del nuovo pareto point.
+Ad es, per B=0, tutti i nuovi pareto points sono buoni uguali, a prescindere dalla loro innovativita'.
+Per B=0.2, un nuovo pareto point gia' e' una cosa bella, se poi ha innovativita', meglio ancora, sarebbe la ciliegina sulla torta, ecc ....
+Si potrebbero fare nuovi run con questo calcolo di innovation score, io li farei per B=1 e B=0.5, per vedere se le cose migliorano.

### 2014-10-13 experiments.tex
AA: altre modifiche

@@
 \end{table}
+
 \subsection{Terms of comparison}
@@
 %------------------------------------------------------------------------------
+\subsection{Evaluation campaign}
+In order to obtain the results presented in this section, we implemented our exploration strategy in Epic Explorer~\cite{ascia2003epic}, an open source framework for the design space explora=tion of embedded systems.
+\comment{AA: continuare descrivendo un po' il workflow.
+The reader can refer to~\cite{ascia2003epic} for more details about the estimation models of the power dissipation and execution time.
+Scrivere che it is possible to run benchmarks }.
+
+%------------------------------------------------------------------------------
 
@@
 \emph{average normalised absolute dispersion error}.
+Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
+Indeed, authors in \cite{zitzler_ec00} carefully observe that an exploration algorithm should preferably provide pareto fronts whose objective function range is large.
+Such Pareto fronts permit to investigate in a broader way the potentials of the designed device.
+This is important, in general, and turns out to be essential when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
 
@@
 \comment{AA: Per rappresentare l'extent del Pereto front, forse sarebbe meglio evitare di usare il variation range, per come l'hai definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5 ``Metrics of performance'', che mi pare rappresenti la stessa cosa, concettualmente.
-Questo ci permette di essere meno attaccabili (del tipo ``non te la prendere con noi, prenditela con Zitzler se non capisci l'utilita' della metrica'').}
-It quantifies the extent of the of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
-Indeed, authors in \cite{zitzler_ec00} carefully observe that an exploration algorithm should preferably provide pareto fronts whose objective function range is large.
-Such Pareto fronts permit to investigate in a broader way the potentials of the designed device.
-This is important, in general, and turns out to be essential when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
+Questo ci permette di essere meno attaccabili (del tipo ``non te la prendere con noi, prenditela con Zitzler (che e' citato 3064 volte!) se non capisci l'utilita' della metrica'').}
 
@@
 uniformly distributed over the objective space. 
-The motivation behind this metric is, again, given by \cite{zitzler_ec00}, in which authors remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.
-In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front.
-\comment{AA: commentare perche' e' importante questa metrica. Cercare la parola chiave ``deception'' o qualcosa del genere}.
 Formally, let $O$ be
@@
 
+\comment{AA: Un'altra interessante metrica potrebbe essere questa: Auhtors of \cite{zitzler_ec00} remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.
+In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front, since we have not been captured by only one possible subset of Pareto configurations but we are able to span all over the configuration space and find configurations whose parameter values differ considerably.
+Mi aspetto che PS performi bene sotto questo punto di vista.
+Ovviamente, non so se e' il caso di considerarla ora.
+Se non e' il caso, puoi spostare questo testo nel file ``appendix.tex'' come possibile spunto futuro.
+Per quantificare questa cosa, si potrebbe usare come metrica la normalised absolute dispersion error pero' non nello spazio degli obiettivi, ma nello spazio delle configurazioni.}.
+
+\subsection{Impact of the algorithm parameters}
+\secL{parameter_impact}
+\comment{IMPACT OF $K$.
+Si potrebbero presentare un plot in cui il numero totale di simulazioni e' fissato e vengono eseguiti diversi run dell'algoritmo con diversi valori di K.
+Per ogni run, il pareto set e' rappresentato nel plot, sottoforma di una curva diversa.
+Mi aspetterei che tutte le curve siano molto simili.
+Per ciascun run, il valore di variation range e average absolute dispersion error sono riportati.
+Mi aspetto valori simili, il che confermerebbe che la diversity nel nostro algoritmo non dipende da $K$.
+Ne vale la pena rifare questi run?
+Ci vuole troppo tempo?}
+
+\comment{Si potrebbe mettere un plot con nelle ascisse l'era e nelle ordinate il numero di split avvenuti in quell'era.
+Si potrebbero disegnare diverse curve, una per ogni valore di alpha, per far vedere che il numero di split e' piu' alto q.
+Recommended values are close to 1, as results in \secR{ee} confirm.
+Using different values, if sufficiently close to 1, does not have a considerable impact on the resulting Pareto front approximation.
+Ne vale la pena rifare questi run?
+Ci vuole troppo tempo?}
+
 \subsection{Results}
@@
 \figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the resulting Pareto fronts for two
-different scenarios of 100 and 500 simulations budget. When possible,
+different scenarios of 100 and 500 simulations budget. \comment{AA: per curiosita': quando facevi piu' run, PS andava ancora peggio rispetto a GA?} When possible,
 similar algorithm parameters have been adopted. In particular a
 population size of 30 has been chosen for the genetic approach (GA), corresponding to the
-same value for the $K$ of PS. The number of generations (or era)
+same value for the $K$ of PS. \comment{AA: che valore di $alpha$ hai usato?} The number of generations (or era)
 has been chosen so that the only the given amount of simulations is

### 2014-10-18 appendix.tex
AA: niente di che

@@
 \end{definition}
+
+\subsection{Other metrics}
+Un'altra interessante metrica potrebbe essere questa: Auhtors of \cite{zitzler_ec00} remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.
+In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front, since we have not been captured by only one possible subset of Pareto configurations but we are able to span all over the configuration space and find configurations whose parameter values differ considerably.
+Mi aspetto che PS performi bene sotto questo punto di vista.
+Ovviamente, non so se e' il caso di considerarla ora.
+Se non e' il caso, puoi spostare questo testo nel file ``appendix.tex'' come possibile spunto futuro.
+Per quantificare questa cosa, si potrebbe usare come metrica la normalised absolute dispersion error pero' non nello spazio degli obiettivi, ma nello spazio delle configurazioni.
 

### 2014-10-18 experiments.tex
AA: niente di che

@@
 
-\comment{AA: Un'altra interessante metrica potrebbe essere questa: Auhtors of \cite{zitzler_ec00} remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.
-In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front, since we have not been captured by only one possible subset of Pareto configurations but we are able to span all over the configuration space and find configurations whose parameter values differ considerably.
-Mi aspetto che PS performi bene sotto questo punto di vista.
-Ovviamente, non so se e' il caso di considerarla ora.
-Se non e' il caso, puoi spostare questo testo nel file ``appendix.tex'' come possibile spunto futuro.
-Per quantificare questa cosa, si potrebbe usare come metrica la normalised absolute dispersion error pero' non nello spazio degli obiettivi, ma nello spazio delle configurazioni.}.
-
 \subsection{Impact of the algorithm parameters}

### 2014-10-21 algorithm.tex
AA: exploration vs exploitation; parallelism

@@
 
-Observe that merging and splitting operation are dynamic processes. A portion
+\subsection{Exploration vs exploitation in PS}
+Our algorithm is able to inherently balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
+While a detailed survey on the exploration vs exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
+Following the terminology in \cite{weise2012evolutionary}, if the exploration is not sufficiently wide, we sat that the algorithm suffers from \emph{premature convergence}, i.e.
+it starts to analyze only a narrow portion of the configuration space, that may lead to ignore potential Pareto configurations that are outside this portion.
+When premature convergence happens, there is insufficient \emph{diversity}~\cite{weise2012evolutionary}, i.e.
+all the provided solutions are similar.
+On the other hand, \emph{exploitation} is the capability to recognize and densely analyze the parts of configuration space that have many Pareto configurations.
+
+As in genetic algorithms exploration and exploration are guaranteed by mutation, crossover and selection, in our algorithm these guarantees are provided for the following reasons:
+	\begin{itemize}
+		\item Merging and splitting operation are dynamic processes. A portion
 of the parameter space may be populated by a large number of small
-regions in some eras, but can be covered by a small number of large
-regions in next eras. This is a desirable property of PS, since, after a number
-of eras of intense exploration of a portion of configuration space, this
-exploration has turned to be enough thorough and so it may be time for
-other portions to be minutely scanned.
+regions in some eras.
+However, after having been sufficiently explored, the innovation score of these regions may decrease and therefore that portion may be covered by a small number of large regions in next eras.
+This is a desirable property of PS, since, after a number of eras of intense exploration of a portion of configuration space, this exploration may turn to be enough thorough and so it may be time for other portions to be minutely scanned.
+Otherwise stated, PS dynamics can be summarized as follows: while eras alternate, PS zooms out from the configurations subspaces already sufficiently scanned in the past, whereas it zooms in subspaces which provide novelty (guaranteeing exploitation), meaning that they have not been properly analyzed yet (this helps exploration).
+		\item No portion of parameter space is neglected since, at each era, all the regions, even the least interesting ones, have the chance to be explored with new evaluated points (providing exploration), even though some regions are less densely explored than others.
+	\end{itemize}
 
-A pseudo-code representation of PS algorithm is in Alg.\ref{alg:algo}
+To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are while not being trapped in only a narrow subset of configuration space.
+
+A pseudo-code representation of PS algorithm is in Alg.\ref{alg:algo}.
 

### 2014-10-21 appendix.tex
AA: exploration vs exploitation; parallelism

@@
 \end{definition}
+
+\subsection{Parallelism}
+While a detailed analysis of the parallel capabilities of the algorithm is not in the scope of this paper, we point out that our algorithm shows parallel capabilities.
+Following the approach used in the ``Master-Slaves parallel genetic algorithms''~\cite{Cantu-Paz98asurvey,Borkar14parallel}, at each era a master processing node assigns to each slave processing node a set of regions.
+Each processing node independently performs the analysis of the assigned regions and calculates the innovation score.
+At the end of each era, the master collects the results from the slaves, decide performs the splitting/merging operations and the next era starts.
+Another possible approach is closer to the ``Island scheme'' for GA parallelization~\cite{Borkar14parallel}.
+The configuration space is initially divided in $n$ macro-regions, each one assigned to a different processing node.
+Then, each processing node performs PS algorithm on the assigned macro-regions, autonomously performing all the steps of the algorithm, including merging and splitting.
+Note that, while the Island scheme for GA parallelization requires a migration operator, that is not easy to properly tune, we do not have special requirements.
+On the other hand, one of the macro-regions may begin to provide very low innovation at a certain era.
+In this case, dedicating to it the same number $K$ of test function as the other macro-regions is inefficient.
+To solve this problems, periodically, the number $k$ of test functions assigned to each macro-region should be renegotiated, in favor of the macro-regions providing most innovation.
 

### 2014-10-21 experiments.tex
AA: exploration vs exploitation; parallelism

@@
 Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
-Indeed, authors in \cite{zitzler_ec00} carefully observe that an exploration algorithm should preferably provide pareto fronts whose objective function range is large.
+Indeed, authors in \cite{zitzler_ec00,weise2012evolutionary} carefully observe that an exploration algorithm should preferably provide Pareto fronts whose objective function range is large.
+Following the terminology of~\cite{weise2012evolutionary}, a \emph{uniform convergence} should be guaranteed.
 Such Pareto fronts permit to investigate in a broader way the potentials of the designed device.
-This is important, in general, and turns out to be essential when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
+This is important, in general, since if only a narrow portion of the Pareto front is provided due to non-uniform convergence, the decision maker may neglect some important options~\cite{weise2012evolutionary}.
+Having a narrow Pareto front becomes essential, in particular, when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
 

### 2014-10-21 algorithm.tex
AA: ultimati i TODO AND sul testo

@@
 	$\alpha=1.2$). 	
-		\comment{AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia.
-Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente.
-Non e' motivata da nessuna parte.
-Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso.
-E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale.
-Che ne dici di cambiare l'espressione in
-			\[
-			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
-			\]
-		}
 	\item \emph{low innovation regions}, whose score is positive but modest, i.e.

### 2014-10-21 appendix.tex
AA: ultimati i TODO AND sul testo

@@
 To solve this problems, periodically, the number $k$ of test functions assigned to each macro-region should be renegotiated, in favor of the macro-regions providing most innovation.
+
+\subsection{Region classification}
+Refer to step 7 of the algorithm.
+AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia.
+Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente.
+Non e' motivata da nessuna parte.
+Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso.
+E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale.
+Che ne dici di cambiare l'espressione in
+			\[
+			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
+			\]
+?
 

### 2014-10-21 concepts.tex
AA: ultimati i TODO AND sul testo

@@
 the operations that will be performed on them by the algorithm.
+
+In this section and the following one, we will deliberately keep our formulation as general as possible, even if the focus of this paper is the embedded system design space exploration.
+The goal is to make the generality of PS emerge.
+We argue that it is a strong point for PS, as for genetic algorithms, since (i) it permits to apply it to a wide range of different problems and (ii) it can be effectually used when the embedded system design is particularly challenging and no much a-priori knowledge is available to the designer.
+As already pointed in \secL{related_work}, the generality of genetic algorithms has made them widely deployed with respect to the other approaches.
+Thanks to the generality of PS, we will not need to modify or adapt it in order to apply it to the case of embedded system design, as we will show in \secL{ee}.
+On the one hand, this legitimate our choice of keeping formulation general.
+On the other hand, more importantly, this confirms the capability of PS to automatically adapt to the problem under investigation, without any explicit intervention or knowledge of the designer, required, on the contrary, by~\cite{givargis_tvlsi02,santosh_hptr00,dellnitz2005covering} .
 

### 2014-10-23 algorithm.tex
added notes on bounds

@@
 
+\comment{TODO AND: c'e' un problema col mathcal, dai un'occhiata qui sotto}
 Each iteration is called \emph{era}. The $i$-th era is characterized by: 
@@
 
-\subsection{Algorithm parameters}
-The parameters that completely determine the algorithm are $K$ and $\alpha$.
-$K$ corresponds to the population size of the genetic approach.
-Authors of \cite{zitzler_ec00} found that increasing $k$ not necessarily has a considerable impact on the performance of the algorithm.
-This holds also in our algorithm.
-In addition, while in the genetic approach $K$ must be sufficiently large in order to guarantee diversity of the Pareto set configurations, in our algorithm the diversity is not impacted by $K$ since, by construction, it is guaranteed by the way the configuration space is partitioned, independently from number of configurations evaluated at each iteration.
-\comment{This is confirmed by the experimental results in \secR{parameter_impact}.
-}
+\subsection{Algorithm Parameters and Scalability} The parameters that
+completely determine the algorithm are the configurations budget each
+era $K$ and the threshold factor $\alpha$. From a functional point of
+view, $K$ is somewhat similar to the population size of a genetic
+approach, determining which configuration should be evaluated in the
+in the subsequent step of the algorithm. However, as seen in the
+previous subsection, the way this $K$ configurations are distributed
+across the parameters space is completely different.
+Authors of \cite{zitzler_ec00} found that
+increasing $k$ not necessarily has a considerable impact on the
+performance of the algorithm, and this holds also in our algorithm.
+But while in the genetic approach $K$ must be sufficiently large
+in order to guarantee diversity of the Pareto set configurations, in
+our algorithm the diversity is not impacted by $K$ since, by
+construction, it is guaranteed by the way the configuration space is
+partitioned, independently from number of configurations evaluated at
+each iteration.
 
-Parameter $\alpha$ determines when a region is considered of high innovation.
-High values of $\alpha$ mean that a region will hardly be elected as high-innovation, yielding less splitting operations.
-This slows down zooming in on portions of configuration space and make the distribution of the simulated configuration more uniform, as there are fewer small regions with a high test configuration concentration.
-The opposite happens when small values of $\alpha$ are used.
-\comment{This is confirmed by results of \secR{parameter_impact}.
-}
+On the other side, parameter $\alpha$ determines when a region is considered of high
+innovation. High values of $\alpha$ mean that a region will hardly be
+elected as high-innovation, yielding less splitting operations. This
+slows down zooming in on portions of configuration space and make the
+distribution of the simulated configuration more uniform, as there are
+fewer small regions with a high test configuration concentration. The
+opposite happens when small values of $\alpha$ are used. In this
+introductory work we are not explicitly focused on a deep
+investigation on how these parameters can be fine tuned, nevertheless
+we conducted some preliminary tests to confirm the relative stability
+of $PS$ with different choices and to select some ``reasonable'' average
+values to perform the design space exploration (see Figure 
+\comment{TODO This is confirmed by results of \secR{parameter_impact}
+}).
+
+\comment{TODO: Usare notazioni coerenti con le precedenti}
+As regards the performance of the proposed approach we can estimate that the
+performance of $PS$ is strictly related to the total number of
+different configurations evaluated during the exploration. We can
+safely make such assumption, because the process of evalutating a new
+configuration is the time-dominating one among all the operations
+performed. As we will show the
+next Section, this is especially true in the hardware/software
+design space exploration scenario we are addressing, since benchmark compiling and execution times
+are orders of magnitude bigger than the splitting/merging operations and
+innovation scores computations.  Ideally, the $i$-th era would provide a new set
+$test_i$ of $K$ configurations to be tested. However, we cannot know
+a priori how many of
+these will actually be new configurations, i.e. requiring a process of
+evaluation. Thus, number of total new simulations $N_{tot}$ 
+can be estimated to be bounded as follows:
+\[
+K \le N_{tot} \le K \times E_{tot}
+\]
+where $E_{tot}$ is the nuber of eras executed and assuming that at
+least $K$ evaluation should be performed in order to obtain the first
+pareto $\mathscr{P}_0$.

### 2014-10-23 experiments.tex
AA: ultimati i TODO AND sul testo
added platform description

@@
 \secL{ee}
+Since our main focus is the embedded system design, we apply PS to a
+related case study.  In this section, we briefly describe the
+parameterized platform used as testbed for the experiments, the
+general evaluation flow along with the high-level estimation models
+and applications used as benchmarks.
+
 \subsection{Motivation}
@@
 
+%------------------------------------------------------------------------------
+\subsection{Evaluation Flow}
+
+To evaluate and compare the performance indexes of different
+architectures for a specific application, one needs to simulate the
+architecture running the code of the application. To make
+architectural exploration possible both the compiler and the simulator
+have to be retargetable. Trimaran~\cite{trimaran_hp} provides these
+tools and thus represents the pillar around which we have constructed
+\ee~\cite{palpatti_estimedia03}. \ee{} is a framework that not only
+allows us to evaluate any instance of a platform in terms of area,
+performance and power, but also implements various techniques for
+exploration of the design space.
+
+We will now show a functional scheme highlighting the main blocks of
+the \ee{} framework and the interface with the Trimaran tools. The
+input for the whole evaluation flow is the source of the application
+involved in the optimization and the configuration of the architecture
+being evaluated.  With reference to Figure~\ref{fig:evaluation_flow}
+this input is represented by the blocks \emph{App.c} and
+\emph{Config}.
+\begin{figure}
+        \centering
+        \includegraphics[width=0.65\textwidth]{pictures/evaluation_flow.eps}
+        \caption{Block diagram of the framework.}
+        \label{fig:evaluation_flow}
+\end{figure}
+
+The application (App.c) is first compiled by the Trimaran's compiler
+front-end (IMPACT). At the end of the compilation flow,
+Trimaran supplies a simulation library (Emulib) which makes it
+possible to execute the VLIW code produced by Elcor, generating a file
+(Stats) containing the execution statistics (e.g., instruction mix,
+execution cycles, utilization of functional units, etc.). A cache
+simulator, along with a bus simulator, is used to gather information
+about the behavior of the memory hierarchy in terms of miss rate and
+data/address traffic on the interconnection buses.
+
+Together with the configuration of the system, the statistics produced
+by simulation contain all the information needed to apply the area,
+performance and power consumption estimation model implemented in the
+\emph{Estimator} component of \ee{}. The results obtained by these
+models are the input for the \emph{Explorer} component. This component
+executes an optimization algorithm, the aim of which is to modify the
+parameters of the configuration so as to minimize the three cost
+functions (area, execution time and energy/power consumption).
+
+\subsection{Estimation Models}
+Several models have been implemented in the \ee{} platform in order to
+estimate the power/energy/performance indexes of each simulated system
+configuration.
+
+The average power consumed by the processor was estimated using an
+adaptation of the Cai-Lim model~\cite{cai_micro99} to the VLIW
+processor. As regards the cache subsystem, a transition-based model
+was used, according to the equations described
+in~\cite{kamble_islped97}.  The main memory energy is based on the
+model in~\cite{shiue_dac99} and assumes a per main memory access
+energy of $4.95 \times 10^{-9} J$ based on the data for the Cypress
+CY7C1326-133 memory chip.  The contribution towards power consumption
+made by the interconnection system was calculated by counting the
+number of transitions on the bus lines and applying the formula
+$P_{bus} = 1/2 V_{dd}^2 \alpha f C_l$ where $V_{dd}$ is the supply
+voltage, $\alpha$ is the switching activity, $f$ is the clock
+frequency and $C_l$ is the capacity of a bus line. For the on-chip
+buses we also considered the coupling capacitances between bus lines,
+using the model in~\cite{lekatsas_dac01}. For a detailed description
+of the models used and their adaption to the case of a VLIW based
+system see~\cite{palpatti_estimedia03}.
+
 \subsection{Terms of comparison}
@@
 and what could be expected from similar multi-objective strategies.
-
-%------------------------------------------------------------------------------
-\subsection{Evaluation campaign}
-In order to obtain the results presented in this section, we implemented our exploration strategy in Epic Explorer~\cite{ascia2003epic}, an open source framework for the design space explora=tion of embedded systems.
-\comment{AA: continuare descrivendo un po' il workflow.
-The reader can refer to~\cite{ascia2003epic} for more details about the estimation models of the power dissipation and execution time.
-Scrivere che it is possible to run benchmarks }.
 

### 2014-10-24 algorithm.tex
Added selfreferences and discussions

@@
 opposite happens when small values of $\alpha$ are used. In this
-introductory work we are not explicitly focused on a deep
-investigation on how these parameters can be fine tuned, nevertheless
+introductory work we are not explicitly focused on investigating how
+these parameters could be fine tuned, nevertheless
 we conducted some preliminary tests to confirm the relative stability
 of $PS$ with different choices and to select some ``reasonable'' average
-values to perform the design space exploration (see Figure 
+values to perform the design space exploration (see for example Figure
+TODO in Section \ref{sec:ee})
 \comment{TODO This is confirmed by results of \secR{parameter_impact}

### 2014-10-24 introduction.tex
AA: exploration vs exploitation; parallelism
Added selfreferences and discussions

@@
 
-Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to decompose
-the system under evaluation into components that interact minimally
-with each other. Pareto sets for each component are found and, provided
-that ``monotonicity'' exists, the complete Pareto set is computed
-merging the component Pareto sets. Roughly speaking (see section 4
-of the same paper for more details), monotonicity property guarantees
-that the best system can be obtained as a composition of the best
-components. This approach would perfectly work if all the components
-were perfectly isolated, i.e., if there were no dependencies among
-them. But real scenarios rarely expose monotonicity property thus resulting in inaccuracies, as stated in the same paper).
+A preliminary estimation of hardware/software dependencies in order to
+reduce the design space is addressed in~\cite{Catania2008}, where
+authors propose to deal with the software parameters separately,
+statistically testing their average effect on objectives before the
+actual exploration is performed. Also in~\cite{merging} authors
+analyze the impact of including compilation parameters into the design
+space space exploration. The results of both works confirm the
+important role that hardware/software dependencies can play in a
+multi-objective exploration and thus justify the choice of explicitly
+including the two class of parameters in the design space without
+making any distinction between them from the algorithm's perspective.
 
-Other approaches, as \cite{fornaciari_codes01,palesi_iwsoc02}, are based the concept of \emph{sensitivity analysis}, i.e. measuring of how much the objective varies when varying each parameter.
-Parameters are ordered based on their sensitivity.
-The first parameter (the most sensitive one) is varied, while keeping the other parameters fixed to arbitrary values, and its best value is found.
-The limited accuracy shown by these approaches can be explained by the limited and rigid exploration of the parameter
-space: after fixing the best first parameter value, there are no more chances to consider different values. It is worth noticing that this approach can not capture
-``local sensitivity'', i.e. the objectives may be more sensitive to some
-ranges of a parameter and less sensitive to other ranges of the same
-parameter. Moreover it can not capture ``combined sensitivity'', i.e. the objectives may be
-more sensitive to a range of a parameter $p_{1}$, only when other
-parameters are within certain ranges, and less sensitive to the same
-range of $p_{1}$ when the other parameters are in different ranges. Otherwise, our algorithm can both capture local and combined sensitivity.
+Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to
+decompose the system under evaluation into components that interact
+minimally with each other. Pareto sets for each component are found
+and, provided that ``monotonicity'' exists, the complete Pareto set is
+computed merging the component Pareto sets. Roughly speaking (see
+section 4 of the same paper for more details), monotonicity property
+guarantees that the best system can be obtained as a composition of
+the best components. This approach would perfectly work if all the
+components were perfectly isolated, i.e., if there were no
+dependencies among them. But real scenarios rarely expose monotonicity
+property thus resulting in inaccuracies, as stated in the same paper).
 
-\cite{dellnitz2005covering} proposes three different methods for the numerical approximation of the Pareto set.
-The first two require the knowledge of the gradient of the objective functions, which is usually not available in embedded system design, since the closed form expression of the objective functions is not known a priori.
-The third one, called ``Sampling algorithm'', does not need this requirement and is the closest to ours, although the mechanism is different.
-At every iteration a set of regions of configuration space is constructed with the aim to cover the Pareto set.
-The size of these regions becomes smaller at each iteration so that the covering becomes tighter.
-A random set of test points are evaluated in each new region; only the regions containing non-dominated points will be considered in the next iteration.
-Our approach is different.
-First, in the Sampling algorithm only the selected regions are examined, even though there is no guarantee that all the Pareto points are included in them.
-As a consequence, the Sampling algorithm may erroneously and prematurely neglect some regions that may possibly contain a non-negligible number of Pareto points.
-Our algorithm avoids this, since even though a region has not provided non-dominated points, it is not neglected, rather it is simply populated with fewer test points, thus giving the chance to find non-dominated points in them.
-From this behavior also comes another important difference.
-The Sampling algorithm of \cite{dellnitz2005covering} keeps reinforcing the analysis of the regions selected in the previous iterations.
-In other words, it keeps zooming into the regions that have been considered ``interesting'', i.e.
-rich of non-dominated points, in the previous iterations.
-The philosophy behind our algorithm is different.
-A region, which has been considered interesting at a certain iterations, may be not in the future, since it has been thoroughly analyzed.
-On the other hand, a region, initially uninteresting, may turn out to be interesting in the future, once all the other regions have been already exploited.
-Therefore, from an iteration to the next, our algorithm zoom in on regions that are currently interesting and zoom out from the uninteresting ones,  spanning in a broader and more dynamical way the configuration space.
-In addition, in the Sampling region only the number of non-dominated points is accounted to see how interesting a region is.
-On the contrary, we also consider the \emph{innovation}, as already anticipated in the introduction.
+Other approaches, as \cite{fornaciari_codes01,palesi_iwsoc02}, are
+based the concept of \emph{sensitivity analysis}, i.e. measuring of
+how much the objective varies when varying each parameter.  Parameters
+are ordered based on their sensitivity. The first parameter (the most
+sensitive one) is varied, while keeping the other parameters fixed to
+arbitrary values, and its best value is found. The limited accuracy
+shown by these approaches can be explained by the limited and rigid
+exploration of the parameter space: after fixing the best first
+parameter value, there are no more chances to consider different
+values. It is worth noticing that this approach can not capture
+``local sensitivity'', i.e. the objectives may be more sensitive to
+some ranges of a parameter and less sensitive to other ranges of the
+same parameter. Moreover it can not capture ``combined sensitivity'',
+i.e. the objectives may be more sensitive to a range of a parameter
+$p_{1}$, only when other parameters are within certain ranges, and
+less sensitive to the same range of $p_{1}$ when the other parameters
+are in different ranges. Otherwise, our algorithm can both capture
+local and combined sensitivity.
 
-Many studies, as \cite{coello_easmop} and others, focus on genetic approaches to solve multiobjective
-optimization problems. Genetic approaches
-have many advantages: they provide good accuracy, they are customizable and very general
-and require no a-priori knowledge to the designer.  The strong
-point of genetic approaches can be summarized as follows: they consist
-in an exploration that is sufficiently broad (the mutation avoids being rigidly restricted to limited parts of parameter space), and, at the same time, not too scattered as it is guided by the performances of
-the already evaluated configurations. In this work we will compare 
-the proposed approach against a well known Multi-Objective Genetic
-Algorithm~\cite{knowles_techrep06}.
-We claim that the approach presented in this paper has most of the benefits of the genetic
+Authors of \cite{dellnitz2005covering,dellnitz2009computation} propose
+three different methods for the numerical approximation of the Pareto
+set. The first two require the knowledge of the gradient of the
+objective functions, which is usually not available in embedded system
+design, since the closed form expression of the objective functions is
+not known a priori. The third one, called ``Sampling algorithm'', does
+not need this requirement and is the closest to ours, although the
+mechanism is different. At every iteration a set of regions of
+configuration space is constructed with the aim to cover the Pareto
+set. The size of these regions becomes smaller at each iteration so
+that the covering becomes tighter. A random set of test points are
+evaluated in each new region; only the regions containing
+non-dominated points will be considered in the next iteration. Our
+approach is different. First, in the Sampling algorithm only the
+selected regions are examined, even though there is no guarantee that
+all the Pareto points are included in them. As a consequence, the
+Sampling algorithm may erroneously and prematurely neglect some
+regions that may possibly contain a non-negligible number of Pareto
+points. Our algorithm avoids this, since even though a region has not
+provided non-dominated points, it is not neglected, rather it is
+simply populated with fewer test points, thus giving the chance to
+find non-dominated points in them. From this behavior also comes
+another important difference. The Sampling algorithm of
+\cite{dellnitz2005covering} keeps reinforcing the analysis of the
+regions selected in the previous iterations. In other words, it keeps
+zooming into the regions that have been considered ``interesting'',
+i.e. rich of non-dominated points, in the previous iterations. The
+philosophy behind our algorithm is different. A region, which has been
+considered interesting at a certain iterations, may be not in the
+future, since it has been thoroughly analyzed. On the other hand, a
+region, initially uninteresting, may turn out to be interesting in the
+future, once all the other regions have been already exploited.
+Therefore, from an iteration to the next, our algorithm zoom in on
+regions that are currently interesting and zoom out from the
+uninteresting ones,  spanning in a broader and more dynamical way the
+configuration space. In addition, in the Sampling region only the
+number of non-dominated points is accounted to see how interesting a
+region is. On the contrary, we also consider the \emph{innovation}, as
+already anticipated in the introduction.
+
+Many studies, as \cite{coello_easmop} and others, focus on genetic
+approaches to solve multiobjective optimization problems. Genetic
+approaches have many advantages: they provide good accuracy, they are
+customizable and very general and require no a-priori knowledge to the
+designer. The strong point of genetic approaches can be summarized as
+follows: they consist in an exploration that is sufficiently broad
+(the mutation avoids being rigidly restricted to limited parts of
+parameter space), and, at the same time, not too scattered as it is
+guided by the performances of the already evaluated configurations.
+Different variants of these algorithms have been proposed in
+literature, including mixed approaches as in~\cite{Ascia2011382},
+where authors specifically focuse on increasing the performance of a
+evolutionaly exploration strategy, proposing a fuzzy based technique
+to avoing the actual simulation of a certain number of configurations.
+In particular, in this work we compare the proposed approach against a
+well known Multi-Objective Genetic Algorithm~\cite{knowles_techrep06}
+which is at best of our knowledge one of the most appropriate for the
+particular scenario we adopted as testbed.  We claim that the approach
+presented in this paper has most of the benefits of the genetic
 approaches, although the rationale is completely different.

### 2014-10-24 concepts.tex
added dependency definition

@@
 \[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} | \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]
+
+Another fundamental concept, which adds further complexity to the
+problem of multiobjective design space exploration, is the following
+
+\begin{definition}[Parameter dependencies]
+\defL{dependency}
+A parameter $x$ is said to be dependent on another parameter $y$ if
+the optimal value of $y$, i.e. the $x_{opt}$ which optimizes the
+objectives is dependent upon the current value of $y$. 
+\end{definition}
+Note that when this happens, we cannot make any safe assumption on the
+``meaning'' of $a$ in order to intuitively choose an appropriate
+value.
 

### 2014-10-24 experiments.tex
added dependency definition

@@
 \secL{ee}
-Since our main focus is the embedded system design, we apply PS to a
-related case study.  In this section, we briefly describe the
-parameterized platform used as testbed for the experiments, the
-general evaluation flow along with the high-level estimation models
-and applications used as benchmarks.
-
-\subsection{Motivation}
 In order to evaluate the behavior of the proposed approach
@@
 
-\subsection{Parameter Space}
-In general, system parameters can be classified in three main categories:
-\emph{processor}, \emph{memory sub-system} and \emph{compiler}. 
-The first is directly related to the VLIW core and includes the size
+In this section, we will also briefly describe the parameterized platform used
+as testbed for the experiments, the general evaluation flow along with
+the high-level estimation models and applications used as benchmarks.
+
+\subsection{Design Space: Hardware and Software Parameters}
+Conceptually, system parameters can be classified in three main categories:
+\emph{processor}, \emph{memory sub-system} and \emph{compiler}. The
+first two categories are directly related to the physical
+implementation of the system, so parameters of those
+classes are usually referred ``hardware parameters''. On the other
+side, all the parameters affecting the behaviour of the compiler
+are referred as ``software parameters'', being directly involved in
+the process of generating the application executables running on the
+underlying hardware.
+
+Processor hardware parameters are directly related to the VLIW core and includes the size
 of the register files and the number of functional
@@
 load/store operations) and \emph{branch units} (associated with branch
-operations). With respect to the memory sub-system, the parameters
+operations). With respect to the memory sub-system hardware, the parameters
 include \emph{size}, \emph{associativity} and
@@
 
-Next, a set of the most impacting code compilation parameters has been
-selected and included in the configuration space:
+On the software side, a set of the most impacting code
+compilation parameters has been selected and included in the
+configuration space, in particular:
 \begin{itemize}

### 2014-10-24 introduction.tex
added dependency definition

@@
 
-In these cases a Design Space
-Exploration (DSE) strategy is required, i.e. an algorithm that selects
-only a tractable subset of all possible configurations.
-The final result of a design space exploration is a subset of the
-configurations called \emph{Pareto set} (\cite{pareto}, see also
-\defR{pareto-set}). The corresponding values of the objectives for
-each configuration of the Pareto Set is called \emph{Pareto front}:
-it represents the trade-offs between objectives, i.e.  for each point
-of the Pareto front there is no other configuration performing better
-for all the objectives considered (see \figR{psos}). Of course this is only a first
-high-level system simulation, thus these few promising
-configurations will need to be further evaluated in a next step of the design
-flow using a more accurate low level simulation (e.g. register
-transfer level).
+In these cases a Design Space Exploration (DSE) strategy is required,
+i.e. an algorithm that selects only a tractable subset of all possible
+configurations.  The final result of a design space exploration is a
+subset of the configurations called \emph{Pareto set} (\cite{pareto},
+see also \defR{pareto-set}). The corresponding values of the
+objectives for each configuration of the Pareto Set is called
+\emph{Pareto front}: it represents the trade-offs between objectives,
+i.e.  for each point of the Pareto front there is no other
+configuration performing better for all the objectives considered (see
+\figR{psos}). Of course this is only a first high-level system
+simulation, thus these few promising configurations will need to be
+further evaluated in a next step of the design flow using a more
+accurate low level simulation (e.g. register transfer level).
 
@@
 Many different design space exploration algorithms have been proposed
-in literature.  The motivations of an exploration
-algorithm are rather heuristic, have some form of arbitrariness and,
+in literature.  What makes the exploration of embedded systems so
+complex is not only the huge size of the parameter spaces involved,
+but also the tight interaction between parameters in relation to their
+effect on the objective to be optimised, which take the form of
+\emph{parameter dependencies} (see~\defR{dependency}). The 
+motivations of an exploration algorithm and how it deals with such
+complexity are often rather heuristic, have some form of arbitrariness and,
 to a large extend, intuition lies behind them.
@@
 making any distinction between them from the algorithm's perspective.
+In fact, one of the purposes of the proposed PS algorithm is avoiding
+the need of any a priori knowledge about those dependencies, letting
+the algorithm itself discover regions where interaction between
+parameters generates new pareto-optimal points (see the PS scoring
+system described in the next sections).
 
@@
 evolutionaly exploration strategy, proposing a fuzzy based technique
-to avoing the actual simulation of a certain number of configurations.
+to avoid the actual simulation of a certain number of configurations.
 In particular, in this work we compare the proposed approach against a

### 2014-10-24 algorithm.tex
AA: Section on the parallelizability added

@@
 \subsection{Iteration steps}
+\secL{steps}
 
@@
 
-\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
+\item \label{enu:region_innovation_score} Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
 as the sum of the innovation scores of its non-dominated test configurations:
@@
 pareto $\mathscr{P}_0$.
+
+\subsection{On the parallelizability of PS}
+While the detailed analysis and the evaluation of a parallel implementation of our algorithm is not in the scope of this paper, we provide in this section some arguments to show that PS is parallelizable.
+
+Following the approach used in the ``Master-Slaves parallel genetic algorithms''~\cite{Cantu-Paz98asurvey,Borkar14parallel}, we can distinguish a master and different slave processing nodes.
+At each era the master assigns a set of regions to each slave, which, in turn, independently performs the analysis and calculates the innovation score of the assigned regions.
+At the end of each era, the master collects the results from the slaves, performs the splitting/merging operations and the next era starts.
+
+Another possible approach is closer to the ``Island scheme'' for GA parallelization~\cite{Borkar14parallel}.
+The configuration space is initially divided in $n$ macro-regions, each one assigned to a different processing node, which autonomously performs all the PS steps, including merging and splitting, considering the assigned macro-region as the entire parameter space.
+Note that, while the Island scheme for GA parallelization requires a migration operator, that is not easy to properly tune, we do not have special requirements.
+On the other hand, one of the macro-regions may begin to provide very low innovation at a certain era.
+In this case, dedicating to it the same number $K$ of test function as the other macro-regions is inefficient.
+To solve this problem, the number of test functions assigned to each macro-region should be perdiodically renegotiated, in favor of the macro-regions providing most innovation.
+
+Opposite to the ``Island  scheme'', a novel parallelization technique permitted by PS can consist of different instances of PS, each one running on the whole configuration space but having its own configuration space partition that separately evolves.
+Each PS instance independently performs the zoom-out and zoom-in in on configuration space, splitting and merging its own regions.
+All PS instances share the indication of the configurations already tested, so that a configuration already tested by some PS instance, will not be tested again by some other PS instance.
+In addition, PS instances share the set of non-dominated configuration.
+Therefore, when a PS instance evaluates the innovation score of its regions (steps \ref{pers02.enu:novelty_score_of_a_configuration} and \ref{enu:region_innovation_score} of \secR{steps}), it considers the solutions found by the other PS instances.
+In this way, the configuration space is spanned in parallel by multiple PS instances, but, altough autonomous, they are not isolated; on the contrary, they continuously exchange information and influence each other, thanks to sharing the already simulated configurations and the non-dominated one.
+Otherwise stated, all the PS instances (independently but jointly) contribute at the formation of the Pareto-set.
+
+We defer the evaluation of these different proposals to our future research, the aim of this section being just to show that our algorithm has the potentiality of being parallelized, thus leaving room for performance improvement.

### 2014-10-24 appendix.tex
AA: Section on the parallelizability added

--- 2014-10-18 appendix.tex
@@
 \end{definition}
+
+\subsection{Region classification}
+Refer to step 7 of the algorithm.
+AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia.
+Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente.
+Non e' motivata da nessuna parte.
+Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso.
+E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale.
+Che ne dici di cambiare l'espressione in
+			\[
+			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
+			\]
+?
 
@@
 Si potrebbero fare nuovi run con questo calcolo di innovation score, io li farei per B=1 e B=0.5, per vedere se le cose migliorano.
+
+\subsection{Other stuff}
+Qualche altro spunto di miglioramento si trova alla fine di \url{https://docs.google.com/document/d/1ts8ZNrVSBWimBlRzRpytBdcbM3LmQJNfl0fndKD6Ojc/edit?usp=sharing}.

### 2014-10-25 algorithm.tex
AA

@@
 
-\subsection{Termination Condition}
-The algorithm terminates at step $k$ if
-\[
-is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
-\]
- where $\beta$ and $\gamma$ are selected by the experimenter. 
-The algorithm terminates when in the last
-$\beta$ iterations not a great ``amount of innovation'' has been
-discovered. Therefore it is very probably that carrying on iterating
-will not considerably change the Pareto-front approximation already formed.
-
-It is not recommended to chose $\beta=1$, because it is possible that the
-$k-1$-th and $k$-th Pareto front approximations are not very different but next ones could be. In other words,
-it is unsafe to terminate as soon as the Pareto front does not considerably change
-between two consecutive eras, thus a strategy taking into
-account the history of the Pareto fronts has been adopted in the
-proposed approach.
-%!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
-%FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
-
-\subsection{Exploration vs exploitation in PS}
-Our algorithm is able to inherently balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
-While a detailed survey on the exploration vs exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
-Following the terminology in \cite{weise2012evolutionary}, if the exploration is not sufficiently wide, we sat that the algorithm suffers from \emph{premature convergence}, i.e.
-it starts to analyze only a narrow portion of the configuration space, that may lead to ignore potential Pareto configurations that are outside this portion.
-When premature convergence happens, there is insufficient \emph{diversity}~\cite{weise2012evolutionary}, i.e.
-all the provided solutions are similar.
-On the other hand, \emph{exploitation} is the capability to recognize and densely analyze the parts of configuration space that have many Pareto configurations.
-
-As in genetic algorithms exploration and exploration are guaranteed by mutation, crossover and selection, in our algorithm these guarantees are provided for the following reasons:
-	\begin{itemize}
-		\item Merging and splitting operation are dynamic processes. A portion
-of the parameter space may be populated by a large number of small
-regions in some eras.
-However, after having been sufficiently explored, the innovation score of these regions may decrease and therefore that portion may be covered by a small number of large regions in next eras.
-This is a desirable property of PS, since, after a number of eras of intense exploration of a portion of configuration space, this exploration may turn to be enough thorough and so it may be time for other portions to be minutely scanned.
-Otherwise stated, PS dynamics can be summarized as follows: while eras alternate, PS zooms out from the configurations subspaces already sufficiently scanned in the past, whereas it zooms in subspaces which provide novelty (guaranteeing exploitation), meaning that they have not been properly analyzed yet (this helps exploration).
-		\item No portion of parameter space is neglected since, at each era, all the regions, even the least interesting ones, have the chance to be explored with new evaluated points (providing exploration), even though some regions are less densely explored than others.
-	\end{itemize}
-
-To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are while not being trapped in only a narrow subset of configuration space.
-
-A pseudo-code representation of PS algorithm is in Alg.\ref{alg:algo}.
-
 \begin{algorithm}[t]
@@
 \end{algorithm}
+
+\subsection{Termination Condition}
+The algorithm terminates at step $k$ if
+\[
+is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
+\]
+ where $\beta$ and $\gamma$ are selected by the experimenter. 
+The algorithm terminates when in the last
+$\beta$ iterations not a great ``amount of innovation'' has been
+discovered. Therefore it is very probably that carrying on iterating
+will not considerably change the Pareto-front approximation already formed.
+
+It is not recommended to chose $\beta=1$, because it is possible that the
+$k-1$-th and $k$-th Pareto front approximations are not very different but next ones could be. In other words,
+it is unsafe to terminate as soon as the Pareto front does not considerably change
+between two consecutive eras, thus a strategy taking into
+account the history of the Pareto fronts has been adopted in the
+proposed approach.
+
+A pseudo-code representation of PS algorithm is in Alg.\ref{alg:algo}.
+%!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
+%FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')
+
+\subsection{Exploration vs exploitation in PS}
+Our algorithm is able to inherently balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
+While a detailed survey on the exploration vs exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
+Following the terminology of \cite{weise2012evolutionary}, if the exploration is not sufficiently wide, the algorithm suffers from \emph{premature convergence}, i.e.
+it starts to analyze only a narrow portion of the configuration space, thus ignoring potential Pareto configurations that are outside this portion.
+When premature convergence happens, there is insufficient \emph{diversity}~\cite{weise2012evolutionary}, i.e.
+all the provided solutions are similar.
+On the other hand, \emph{exploitation} is the capability to recognize and densely analyze the parts of configuration space that have many Pareto configurations.
+
+While in genetic algorithms exploration and exploration are guaranteed by mutation, crossover and selection, in our algorithm these guarantees are provided for the following reasons:
+	\begin{itemize}
+		\item Merging and splitting operation are dynamic processes. A portion
+of the parameter space may be populated by a large number of small
+regions in some eras, and thus a large number of test configurations.
+However, after having been sufficiently explored, the innovation score of these regions may decrease, they may be merged and therefore that portion of configuration space may be covered by a small number of large regions in next eras.
+This is a desirable property of PS, since, after a number of eras of intense exploration of a configuration space part, this exploration may turn to be enough thorough and so it may be time for other parts to be minutely scanned.
+PS dynamics can be summarized as follows: while eras alternate, PS zooms out from the configurations subspaces already sufficiently scanned in the past, whereas it zooms in on subspaces which provide novelty (guaranteeing exploitation), meaning that they have not been properly analyzed yet (this helps exploration).
+		\item No portion of parameter space is neglected since, at each era, all the regions, even the least interesting ones, have the chance to be explored with new evaluated points (providing exploration), even though some regions are less densely explored than others.
+	\end{itemize}
+
+To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.
+
 %
@@
 The configuration space is initially divided in $n$ macro-regions, each one assigned to a different processing node, which autonomously performs all the PS steps, including merging and splitting, considering the assigned macro-region as the entire parameter space.
-Note that, while the Island scheme for GA parallelization requires a migration operator, that is not easy to properly tune, we do not have special requirements.
+Note that, while the Island scheme for GA parallelization requires a migra0tion operator, that is not easy to properly tune, we do not have special requirements.
 On the other hand, one of the macro-regions may begin to provide very low innovation at a certain era.

### 2014-10-25 experiments.tex
AA

@@
 Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
-Indeed, authors in \cite{zitzler_ec00,weise2012evolutionary} carefully observe that an exploration algorithm should preferably provide Pareto fronts whose objective function range is large.
-Following the terminology of~\cite{weise2012evolutionary}, a \emph{uniform convergence} should be guaranteed.
-Such Pareto fronts permit to investigate in a broader way the potentials of the designed device.
+Indeed, authors in \cite{zitzler_ec00,weise2012evolutionary} observe that an exploration algorithm should preferably provide Pareto fronts whose objective function range is large.
+In other words, following the terminology of~\cite{weise2012evolutionary}, a \emph{uniform convergence} should be guaranteed.
+Pareto fronts with large objective function ranges permit to investigate in a broader way the potentials of the designed device.
 This is important, in general, since if only a narrow portion of the Pareto front is provided due to non-uniform convergence, the decision maker may neglect some important options~\cite{weise2012evolutionary}.

### 2014-10-25 algorithm.tex
AA

@@
 
-\comment{TODO AND: c'e' un problema col mathcal, dai un'occhiata qui sotto}
 Each iteration is called \emph{era}. The $i$-th era is characterized by: 
@@
 	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
-	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
+	$\mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
 	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
@@
 
-We now describe formally PS.
+We now formally describe PS.
 

### 2014-10-25 experiments.tex
AA

@@
 \secL{ee}
-In order to evaluate the behavior of the proposed approach
-we use a parameterized Very Long Instruction
+Although PS has been formally described as a general exploration algorithm, the goal of this work is giving a method applicable to the embedded system design.
+For this reason, we evaluate PS in this context.
+To this aim, we use a parameterized Very Long Instruction
 Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The philosophy
@@
 This is important, in general, since if only a narrow portion of the Pareto front is provided due to non-uniform convergence, the decision maker may neglect some important options~\cite{weise2012evolutionary}.
-Having a narrow Pareto front becomes essential, in particular, when designing a device that may be required to work in different operational conditions, for example with stringent execution time constraints and less strict power dissipation ones or, on the contrary, with low power requirements and tolerance to high execution time.
+Having a wide Pareto front becomes essential, in particular, when designing a device that may be required to satisfy different constraints.
+For example, the decision maker may want to design two different multi-purpose processors.
+The first design may adapt to situations in which the processor is used for real time elaboration (thus requiring low execution time) and is attached to the powerline (thus not having stringent power dissipation constraints).
+The second design, on the contrary, may fit situations in which the energy is provided by a battery (stringent power constraints) but only background computations are performed (long execution time is tolerable).
+These two processors may be successfully designed maintaining the same architecture, using different values for the design parameters.
+A wide Pareto front helps in achieving this goal.
 

### 2014-10-27 concepts.tex
fixed notes on dependency

--- 2014-10-21 concepts.tex
@@
 
+Another fundamental concept, which adds further complexity to the
+problem of multiobjective design space exploration, is the following
+
+\begin{definition}[Parameter dependencies]
+\defL{dependency}
+Given a system $S$, application $b \in \mathcal{B}$ and two parameters
+$p_x$ and $p_y$, $p_x$ is said to
+be dependent on another parameter $p_y$ if the optimal value of $p_x$,
+that is the $v_{x} \in V_x$ which optimizes the objectives of the
+evaluation function $E$, is dependent upon the current value of $p_y$. 
+\end{definition}
+
+When a dependency is present any safe assumption about the ``meaning'' of
+$p_x$ in order to intuitively choose an appropriate value that
+optimizes objective could be misleading.  It should be also pointed
+out that it's often very difficult to identify dependencies using
+analytical techniques and often designers have to use different
+strategies to deal with such complexity, as seen
+in~\secR{Related-work}.
+
 The aim of a Design Space Exploration (DSE) strategy is to give a
@@
 application $b$, simulating as few configurations as possible.
-
-%----------------------------------------------------------------
-
 As we will show later, at each iteration, PS calculates an approximation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on.

### 2014-10-27 experiments.tex
Draft of Comparison Setup subsection

@@
 %------------------------------------------------------------------------------
-\subsection{Evaluation Flow}
+\subsection{Configuration Evaluation Flow}
 
@@
 architectural exploration possible both the compiler and the simulator
-have to be retargetable. Trimaran~\cite{trimaran_hp} provides these
-tools and thus represents the pillar around which we have constructed
-\ee~\cite{palpatti_estimedia03}. \ee{} is a framework that not only
-allows us to evaluate any instance of a platform in terms of area,
-performance and power, but also implements various techniques for
-exploration of the design space.
+have to be retargetable. The open source project Trimaran~\cite{trimaran_hp} provides these
+tools and together with estimation framework \ee~\cite{palpatti_estimedia03} has been
+adopted as a tested and flexible platform for carrying out the
+experiments described in the previous subsection.
 
@@
 
-\subsection{Terms of comparison}
+\subsection{Comparison Setup}
 
 The results presented in the next section compare PS with one widely
-adopted Multi-objective Genetic Algorithm
-(MOGA)~\cite{knowles_techrep06}. To the best of our knowledge, genetic
-approaches in general still represent the best compromise between
-efficiency (i.e. time required for exploration) and accuracy of the
-reported Pareto Sets.  Note that, for the reasons described above,
-mono-objective approaches have been explicitly excluded from this
-analysis.  We also exclude other approaches (e.g.  dependency
-based~\cite{givargis_tvlsi02}) that make use of some a-priori
-knowledge about the role and meaning of each parameter, since our aim
-is evaluate the capacity of focusing on interesting parameter regions
-without any external judgement or help based on heuristics.  Finally,
-it should be pointed out that in this introductory work we will
-explicitly use the \emph{SPEA}~\cite{zitzler_eurogen01} variant of
-MOGA, remanding to works like~\cite{zitzler_ec00}~\cite{zitzler_tec03}
-for a detailed analysis on how it differs from other genetic approaches
-and what could be expected from similar multi-objective strategies.
+adopted Multi-objective Genetic Algorithm~\cite{knowles_techrep06}. To
+the best of our knowledge, genetic approaches in general still
+represent the best compromise between efficiency (i.e. time required
+for exploration) and accuracy of the reported Pareto Sets.  Note that,
+for the reasons described above, mono-objective approaches have been
+explicitly excluded from this analysis.  We also exclude other
+approaches (e.g.  dependency based~\cite{givargis_tvlsi02}) that make
+use of some a-priori knowledge about the role and meaning of each
+parameter, since our aim is evaluate the capacity of focusing on
+interesting parameter regions without any external judgement or help
+based on heuristics.  In particular in this work when referring to
+genetic approach (or GA) we will denote the widely spread 
+\emph{SPEA}~\cite{zitzler_eurogen01} variant of the Multi-objective
+Genetic Algorithm, remanding to
+works like~\cite{zitzler_ec00}~\cite{zitzler_tec03} for a detailed
+analysis on how it could differ from other genetic approaches and what
+could be expected from similar multi-objetive strategies.
+
+\comment{TODO controllare inglese}
+Even if an analogy between the concepts of ``era'' and ``generation'' 
+can be considered, a fixed amount of total different simulations has been
+considered for each of the tests. The purpose is to make the
+comparison fair from a algorithm performance perspective, since a
+fixed budget of simulations is directly related to the amount of time
+required to execute the exploration; on the other side, simply
+referring to number of generations/era could be misleading when a
+significative number of configuration remain unaltered in the current
+population (e.g. because of a local optimum).
+
+The set of default algorithm tuning parameters used for both the
+genetic and PS approaches to perform the simulations are shown in
+Table~\ref{tab:defaults}. Given the similarity, both in terms of
+meaning and functionality, of the parameter $K$ with the population size
+of the genetic approach, they both have been set to the same values. As discussed
+when introducing the main PS algorithm concepts, an accurate
+investigation of algorithm tuning is beyond the scope of this
+introductory work. Nevertheless, a set of preliminary tests with
+different values of $K$ have been conducted. As shown in
+Figure~\ref{fig:kimpact}, which refer to the alloca\_test application
+and a fixed amount of 500 configurations, initially increasing values
+of $K$ seem to improve both pareto (left picture) and objective
+distribution (right picture), but after some threshold the $K$ does
+not seem to provide any benefit, even returning to slightly worse
+results for the last value considered (100). Similar results have been
+reported on average for the different benchmarks considered, which are
+not included for space reasons. A complete resource with the whole 
+results and data obtained in the tests performed can be found
+at~\cite{ps_results}.
+
+\begin{table}
+	\tbl{Benchmarks\label{tab:defaults}}{
+	\begin{tabular}{ll}
+	\hline
+	\multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Default Value} \\
+	\hline
+	GA population size & 30 \\
+	GA crossover probability & 0.8 \\
+	GA mutation probability  & 0.1 \\
+	$K$ era budget & 30 \\
+	alpha threshold & 1 \\
+	Total simulations budgets & 100-500 \\
+	\hline
+	\end{tabular}}
+\end{table}
+
+\begin{figure}
+  \figLC{kimpact}{Impact of increased K values on Pareto fronts and distribution for the alloca\_test application.}
+  \begin{center}
+    \includegraphics[width=0.45\textwidth]{pictures/alloca_K.eps} 
+    \includegraphics[width=0.45\textwidth]{pictures/alloca_K_ALL.eps} 
+  \end{center}
+\end{figure}
 
@@
 \begin{figure}
-  \figLC{pareto_fronts_100}{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.
-\comment{AA: nelle due figure centrali la linea di GA e' continua, mentre in tutte le altre figure e' tratteggiata.
-Il revisore ci chiede di uniformare.
-Non so come riottenere le figure.
-Potresti pensarci tu?}}
+  \figLC{pareto_fronts_100}{Pareto fronts found by PS and GA for a
+  fixed budget of 100 configurations. \comment{AA: nelle due figure
+  centrali la linea di GA e' continua, mentre in tutte le altre figure
+  e' tratteggiata. Il revisore ci chiede di uniformare. Non so come
+  riottenere le figure. Potresti pensarci tu?}}
   \begin{center}
@@
 \begin{figure}
-  \figLC{pareto_fronts_500}{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.\comment{AA: nelle due figure centrali la linea di GA e' continua, mentre in tutte le altre figure e' tratteggiata.
-Il revisore ci chiede di uniformare.
-Non so come riottenere le figure.
-Potresti pensarci tu?}}
+  \figLC{pareto_fronts_500}{Pareto fronts found by PS and GA for a
+  fixed budget of 500 configurations.\comment{AA: nelle due figure
+  centrali la linea di GA e' continua, mentre in tutte le altre figure
+  e' tratteggiata. Il revisore ci chiede di uniformare. Non so come
+  riottenere le figure. Potresti pensarci tu?}}
   \begin{center}
@@
 \end{figure}
+
 Low budget Pareto sets are shown in \figR{pareto_fronts_100}. With a so small number of

### 2014-10-27 experiments.tex
discussion on sweet spot

@@
 not seem to provide any benefit, even returning to slightly worse
-results for the last value considered (100). Similar results have been
-reported on average for the different benchmarks considered, which are
-not included for space reasons. A complete resource with the whole 
+results for the last value considered (100). Similar trends have been
+found for other benchmarks in the set considered (which are
+not included for space reasons), showing a value of $K$ around 30 as
+reasonable sweet spot for the objectives. A complete resource with the whole 
 results and data obtained in the tests performed can be found

### 2014-10-28 algorithm.tex
Fixed references

@@
 approach, determining which configuration should be evaluated in the
-in the subsequent step of the algorithm. However, as seen in the
+subsequent step of the algorithm. However, as seen in the
 previous subsection, the way this $K$ configurations are distributed
@@
 Authors of \cite{zitzler_ec00} found that
-increasing $k$ not necessarily has a considerable impact on the
-performance of the algorithm, and this holds also in our algorithm.
+increasing $K$ not necessarily has a considerable impact on the
+performance of the algorithm, and this holds also in our algorithm (see for example
+Figure~\ref{fig:kimpact} in Subsection~\ref{sec:comparison}).
 But while in the genetic approach $K$ must be sufficiently large
@@
 of $PS$ with different choices and to select some ``reasonable'' average
-values to perform the design space exploration (see for example Figure
-TODO in Section \ref{sec:ee})
-\comment{TODO This is confirmed by results of \secR{parameter_impact}
-}).
+values to perform the design space exploration, as it will discussed
+in~\secR{ee}.
 

### 2014-10-28 experiments.tex
Fixed references

@@
 \subsection{Comparison Setup}
+\secL{comparison}
 
@@
 fixed budget of simulations is directly related to the amount of time
-required to execute the exploration; on the other side, simply
-referring to number of generations/era could be misleading when a
+required to execute the exploration; on the other side, just simply
+referring to a given number of generations/era could be misleading when a
 significative number of configuration remain unaltered in the current
@@
 distribution (right picture), but after some threshold the $K$ does
-not seem to provide any benefit, even returning to slightly worse
+not seem to provide any benefit, returning to slightly worse
 results for the last value considered (100). Similar trends have been

### 2014-10-28 experiments.tex
Fixed pics legends

@@
 performance and power consumption estimation model implemented in the
-\emph{Estimator} component of \ee{}. The results obtained by these
+\emph{Estimator} component. These are high-level abstraction models
+that allow to quickly get an estimation while still providing a
+discrete level of accuracy (for a detailed description of the models
+see also~\cite{palpatti_estimedia03}).
+
+Finally, the results obtained by these
 models are the input for the \emph{Explorer} component. This component
@@
 
-\subsection{Estimation Models}
-Several models have been implemented in the \ee{} platform in order to
-estimate the power/energy/performance indexes of each simulated system
-configuration.
-
-The average power consumed by the processor was estimated using an
-adaptation of the Cai-Lim model~\cite{cai_micro99} to the VLIW
-processor. As regards the cache subsystem, a transition-based model
-was used, according to the equations described
-in~\cite{kamble_islped97}.  The main memory energy is based on the
-model in~\cite{shiue_dac99} and assumes a per main memory access
-energy of $4.95 \times 10^{-9} J$ based on the data for the Cypress
-CY7C1326-133 memory chip.  The contribution towards power consumption
-made by the interconnection system was calculated by counting the
-number of transitions on the bus lines and applying the formula
-$P_{bus} = 1/2 V_{dd}^2 \alpha f C_l$ where $V_{dd}$ is the supply
-voltage, $\alpha$ is the switching activity, $f$ is the clock
-frequency and $C_l$ is the capacity of a bus line. For the on-chip
-buses we also considered the coupling capacitances between bus lines,
-using the model in~\cite{lekatsas_dac01}. For a detailed description
-of the models used and their adaption to the case of a VLIW based
-system see~\cite{palpatti_estimedia03}.
+%\subsection{Estimation Models}
+%
+%The average power consumed by the processor was estimated using an
+%adaptation of the Cai-Lim model~\cite{cai_micro99} to the VLIW
+%processor. As regards the cache subsystem, a transition-based model
+%was used, according to the equations described
+%in~\cite{kamble_islped97}.  The main memory energy is based on the
+%model in~\cite{shiue_dac99} and assumes a per main memory access
+%energy of $4.95 \times 10^{-9} J$ based on the data for the Cypress
+%CY7C1326-133 memory chip.  The contribution towards power consumption
+%made by the interconnection system was calculated by counting the
+%number of transitions on the bus lines and applying the formula
+%$P_{bus} = 1/2 V_{dd}^2 \alpha f C_l$ where $V_{dd}$ is the supply
+%voltage, $\alpha$ is the switching activity, $f$ is the clock
+%frequency and $C_l$ is the capacity of a bus line. For the on-chip
+%buses we also considered the coupling capacitances between bus lines,
+%using the model in~\cite{lekatsas_dac01}.
 
@@
 
-\subsection{Impact of the algorithm parameters}
-\secL{parameter_impact}
-\comment{IMPACT OF $K$.
+%\subsection{Impact of the algorithm parameters}
+%\secL{parameter_impact}
+%\comment{IMPACT OF $K$.
 Si potrebbero presentare un plot in cui il numero totale di simulazioni e' fissato e vengono eseguiti diversi run dell'algoritmo con diversi valori di K.
@@
 Ci vuole troppo tempo?}
-
-\comment{Si potrebbe mettere un plot con nelle ascisse l'era e nelle ordinate il numero di split avvenuti in quell'era.
+%
+%\comment{Si potrebbe mettere un plot con nelle ascisse l'era e nelle ordinate il numero di split avvenuti in quell'era.
 Si potrebbero disegnare diverse curve, una per ogni valore di alpha, per far vedere che il numero di split e' piu' alto q.
@@
   \figLC{pareto_fronts_100}{Pareto fronts found by PS and GA for a
-  fixed budget of 100 configurations. \comment{AA: nelle due figure
-  centrali la linea di GA e' continua, mentre in tutte le altre figure
-  e' tratteggiata. Il revisore ci chiede di uniformare. Non so come
-  riottenere le figure. Potresti pensarci tu?}}
+  fixed budget of 100 configurations.}
   \begin{center}
     \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps}
-    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_100_bis.eps}
     \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps}
     \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps}
-    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/sha_100_bis.eps}
     \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
@@
   \figLC{pareto_fronts_500}{Pareto fronts found by PS and GA for a
-  fixed budget of 500 configurations.\comment{AA: nelle due figure
-  centrali la linea di GA e' continua, mentre in tutte le altre figure
-  e' tratteggiata. Il revisore ci chiede di uniformare. Non so come
-  riottenere le figure. Potresti pensarci tu?}}
+  fixed budget of 500 configurations.}
   \begin{center}
     \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps}
-    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/bmm_500_bis.eps}
     \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps}
     \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps}
-    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/sha_500_bis.eps}
     \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 

### 2014-10-28 experiments.tex
added gratis partitioning discussion draft

@@
 
-\figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the resulting Pareto fronts for two
-different scenarios of 100 and 500 simulations budget. \comment{AA: per curiosita': quando facevi piu' run, PS andava ancora peggio rispetto a GA?} When possible,
-similar algorithm parameters have been adopted. In particular a
-population size of 30 has been chosen for the genetic approach (GA), corresponding to the
-same value for the $K$ of PS. \comment{AA: che valore di $alpha$ hai usato?} The number of generations (or era)
-has been chosen so that the only the given amount of simulations is
-actually performed. Thus, when accounting these simulations only unique simulations
-has been considered, removing repetitions and unfeasible
-configurations.
+\figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the
+resulting Pareto fronts for two different scenarios of 100 and 500
+simulations budget. The set of algorithm parameters involved and their
+values are the one previously shown in Table~\ref{tab:defaults}. It
+should be pointed out again that the number of generations (or era)
+has been chosen so that only the given amount of simulations is
+actually performed. Thus, when accounting these simulations only
+unique simulations has been considered, removing repetitions and
+unfeasible configurations.
 
@@
 
-Low budget Pareto sets are shown in \figR{pareto_fronts_100}. With a so small number of
-configuration being investigated the two sets are often overlapping,
-being also strongly dependent upon the application being considered.
-These results are obtained in about 5 eras and demonstrate that with a so limited budget PS can compete with
+Low budget Pareto sets are shown in \figR{pareto_fronts_100}. Note
+that with a so small number of configuration being investigated the
+two sets are often overlapping, being also strongly dependent upon the
+application being considered.  These results are obtained in about 5
+eras and demonstrate that with a so limited budget PS can compete with
 genetic approach while even discovering very different Pareto fronts.
 Considering the extended simulation budget as depicted in
-\figR{pareto_fronts_500}, we can qualitatively observe that
-even if PS does not strictly outperforms genetic in terms of dominance, it shows in
-some cases largely Pareto in terms of extension. We can intuitively
+\figR{pareto_fronts_500}, we can qualitatively observe that even if PS
+does not strictly outperforms genetic in terms of dominance, it shows
+in some cases largely Pareto in terms of extension. We can intuitively
 relate this to the ``novelty-based'' score system, so that instead of
@@
 ``better'' or ``worse'' as compared to the genetic one, it depends on
-various design factors such as desired results granularity, prefixed objective
-range constraints, estimated error of the models used etc.
+various design factors such as desired results granularity, prefixed
+objective range constraints, estimated error of the models used etc.
 
@@
 discovering more uniformly dispersed points (i.e. higher values in the
-chart). These results,
-together with the variation ranges of \figR{dispersion}(a) and
+chart). These results, together with the variation ranges of \figR{dispersion}(a) and
 (b) confirm the of density vs extension trade-offs
@@
 requirements and constraints, e.g. whether we need wide or dense
-results. Nevertheless, the proposed algorithm introduces a new
-perspective on the allocation of a simulations budget, paving the way for
-the development of further strategies for addressing the problem of
-multi-objective hardware/software design space exploration.
+results.
+
+\comments{Da lasciare, da spostare ? da mostrare in modo semplice ?
+non so}
+Another interesting feature of PS is that the final output of its
+execution is not only the set of pareto optimal configurations, but also a set
+of more or less innovation regions of the parameter space, obtained as
+a result of the merge/splitting operators described
+in~\secR{algorithm}.
+
+%Nevertheless, the proposed algorithm introduces a new
+%perspective on the allocation of a simulations budget, paving the way for
+%the development of further strategies for addressing the problem of
+%multi-objective hardware/software design space exploration.

### 2014-10-29 introduction.tex
related works fixes

@@
 
-\section{Related work}
+\section{Related work and Our Contribution}
 \secL{Related-work}
@@
 not known a priori. The third one, called ``Sampling algorithm'', does
-not need this requirement and is the closest to ours, although the
+not need this requirement and is the closest to the PS approach
+presented in this work, although the
 mechanism is different. At every iteration a set of regions of
@@
 evaluated in each new region; only the regions containing
-non-dominated points will be considered in the next iteration. Our
-approach is different. First, in the Sampling algorithm only the
+non-dominated points will be considered in the next iteration.
+However, an important feature differentiates it from PS. The Sampling algorithm only the
 selected regions are examined, even though there is no guarantee that
@@
 regions that may possibly contain a non-negligible number of Pareto
-points. Our algorithm avoids this, since even though a region has not
+points. The PS algorithm avoids this, since even though a region has not
 provided non-dominated points, it is not neglected, rather it is
@@
 
-Many studies, as \cite{coello_easmop} and others, focus on genetic
-approaches to solve multiobjective optimization problems. Genetic
-approaches have many advantages: they provide good accuracy, they are
-customizable and very general and require no a-priori knowledge to the
-designer. The strong point of genetic approaches can be summarized as
-follows: they consist in an exploration that is sufficiently broad
+The most well documented and widespread class of algorithms adopted in the
+design space exploration of embedded systems is probably the one of Evolutionary
+Multiobjective Optimization Algorithms~\cite{coello_easmop}. For this
+reason this is the class of algorithms that we will use for the
+experiments discussed in~\secR{ee}.
+Evolutionary approaches have many advantages: they provide good accuracy, they are
+problem-independent and do not require any a-priori knowledge of the
+system. The strong point of these approaches is that they consist in an exploration that is sufficiently broad
 (the mutation avoids being rigidly restricted to limited parts of
@@
 to avoid the actual simulation of a certain number of configurations.
-In particular, in this work we compare the proposed approach against a
-well known Multi-Objective Genetic Algorithm~\cite{knowles_techrep06}
-which is at best of our knowledge one of the most appropriate for the
-particular scenario we adopted as testbed.  We claim that the approach
-presented in this paper has most of the benefits of the genetic
-approaches, although the rationale is completely different.
+In particular, in this work we will compare the proposed approach against a
+well known SPEA2 multi-objective genetic algorithm~\cite{knowles_techrep06}
+which is, at best of our knowledge, one of the most appropriate and
+tested for the particular scenario we are assuming.  We
+claim that the approach presented in this paper has most of the
+benefits of the evolutionary approaches, although the rationale is
+completely different.

### 2014-10-29 concepts.tex
fixed deps descr

@@
 
-\begin{definition}[Parameter dependencies]
+\begin{definition}[Parameter dependency]
 \defL{dependency}
@@
 
-When a dependency is present any safe assumption about the ``meaning'' of
-$p_x$ in order to intuitively choose an appropriate value that
-optimizes objective could be misleading.  It should be also pointed
+When a dependency is present between parameters, it could be
+misleading to use assumption about the ``meaning'' of
+parameters in order to intuitively choose an appropriate value that
+optimizes objectives.  It should be also pointed
 out that it's often very difficult to identify dependencies using
@@
 strategies to deal with such complexity, as seen
-in~\secR{Related-work}.
+in~\secR{Related-work}. In this work we will often refer to
+hardware/sofware dependencies, denoting dependencies occourring
+between parameters belonging to the hardware and software categories,
+as defined in~\secR{designspace}.
 

### 2014-10-29 algorithm.tex
Added table on design space

@@
 
-\subsection{Exploration vs exploitation in PS}
-Our algorithm is able to inherently balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
+\subsection{Exploration vs Exploitation in PS}
+The proposed algorithm has been designed in order to be inherently able to balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
 While a detailed survey on the exploration vs exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
@@
 
+\comment{CHECK AND: Per caso era where invece di when ? o manca qualcosa ?}
 To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.
@@
 
-\comment{TODO: Usare notazioni coerenti con le precedenti}
 As regards the performance of the proposed approach we can estimate that the
@@
 \subsection{On the parallelizability of PS}
-While the detailed analysis and the evaluation of a parallel implementation of our algorithm is not in the scope of this paper, we provide in this section some arguments to show that PS is parallelizable.
+While the detailed analysis and the evaluation of a parallel
+implementation of the proposed algorithm is not in the scope of this paper, we
+provide in this subsection some arguments to show different strategies
+that could be applied to make PS execution parallelizable.
 
-Following the approach used in the ``Master-Slaves parallel genetic algorithms''~\cite{Cantu-Paz98asurvey,Borkar14parallel}, we can distinguish a master and different slave processing nodes.
-At each era the master assigns a set of regions to each slave, which, in turn, independently performs the analysis and calculates the innovation score of the assigned regions.
-At the end of each era, the master collects the results from the slaves, performs the splitting/merging operations and the next era starts.
+Following the approach used in the ``Master-Slaves parallel genetic
+algorithms''~\cite{Cantu-Paz98asurvey,Borkar14parallel}, we can
+distinguish a master and different slave processing nodes. At each era
+the master assigns a set of regions to each slave, which, in turn,
+independently performs the analysis and calculates the innovation
+score of the assigned regions. At the end of each era, the master
+collects the results from the slaves, performs the splitting/merging
+operations and the next era starts.
 
-Another possible approach is closer to the ``Island scheme'' for GA parallelization~\cite{Borkar14parallel}.
-The configuration space is initially divided in $n$ macro-regions, each one assigned to a different processing node, which autonomously performs all the PS steps, including merging and splitting, considering the assigned macro-region as the entire parameter space.
-Note that, while the Island scheme for GA parallelization requires a migra0tion operator, that is not easy to properly tune, we do not have special requirements.
-On the other hand, one of the macro-regions may begin to provide very low innovation at a certain era.
-In this case, dedicating to it the same number $K$ of test function as the other macro-regions is inefficient.
-To solve this problem, the number of test functions assigned to each macro-region should be perdiodically renegotiated, in favor of the macro-regions providing most innovation.
+Another possible approach is closer to the ``Island scheme'' for GA
+parallelization~\cite{Borkar14parallel}. The configuration space is
+initially divided in $n$ macro-regions, each one assigned to a
+different processing node, which autonomously performs all the PS
+steps, including merging and splitting, considering the assigned
+macro-region as the entire parameter space. Note that, while the
+Island scheme for GA parallelization requires a migration operator,
+that is not easy to properly tune, we do not have special
+requirements. On the other hand, one of the macro-regions may begin to
+provide very low innovation at a certain era. In this case, dedicating
+to it the same number $K$ of test function as the other macro-regions
+is inefficient. To solve this problem, the number of test functions
+assigned to each macro-region should be perdiodically renegotiated, in
+favor of the macro-regions providing most innovation.
 
-Opposite to the ``Island  scheme'', a novel parallelization technique permitted by PS can consist of different instances of PS, each one running on the whole configuration space but having its own configuration space partition that separately evolves.
-Each PS instance independently performs the zoom-out and zoom-in in on configuration space, splitting and merging its own regions.
-All PS instances share the indication of the configurations already tested, so that a configuration already tested by some PS instance, will not be tested again by some other PS instance.
-In addition, PS instances share the set of non-dominated configuration.
-Therefore, when a PS instance evaluates the innovation score of its regions (steps \ref{pers02.enu:novelty_score_of_a_configuration} and \ref{enu:region_innovation_score} of \secR{steps}), it considers the solutions found by the other PS instances.
-In this way, the configuration space is spanned in parallel by multiple PS instances, but, altough autonomous, they are not isolated; on the contrary, they continuously exchange information and influence each other, thanks to sharing the already simulated configurations and the non-dominated one.
-Otherwise stated, all the PS instances (independently but jointly) contribute at the formation of the Pareto-set.
+Opposite to the ``Island  scheme'', a novel parallelization technique
+permitted by PS can consist of different instances of PS, each one
+running on the whole configuration space but having its own
+configuration space partition that separately evolves. Each PS
+instance independently performs the zoom-out and zoom-in in on
+configuration space, splitting and merging its own regions. All PS
+instances share the indication of the configurations already tested,
+so that a configuration already tested by some PS instance, will not
+be tested again by some other PS instance. In addition, PS instances
+share the set of non-dominated configuration. Therefore, when a PS
+instance evaluates the innovation score of its regions (steps
+\ref{pers02.enu:novelty_score_of_a_configuration} and
+\ref{enu:region_innovation_score} of \secR{steps}), it considers the
+solutions found by the other PS instances. In this way, the
+configuration space is spanned in parallel by multiple PS instances,
+but, altough autonomous, they are not isolated; on the contrary, they
+continuously exchange information and influence each other, thanks to
+sharing the already simulated configurations and the non-dominated
+one. Otherwise stated, all the PS instances (independently but
+jointly) contribute at the formation of the Pareto-set.
 
-We defer the evaluation of these different proposals to our future research, the aim of this section being just to show that our algorithm has the potentiality of being parallelized, thus leaving room for performance improvement.
+We defer the evaluation of these different proposals to our future
+research, the aim of this section being just to show that our
+algorithm has the potentiality of being parallelized, thus leaving
+room for performance improvement.

### 2014-10-29 experiments.tex
related works fixes
fixed deps descr
Added table on design space

@@
 \secL{ee}
-Although PS has been formally described as a general exploration algorithm, the goal of this work is giving a method applicable to the embedded system design.
-For this reason, we evaluate PS in this context.
-To this aim, we use a parameterized Very Long Instruction
+Although PS has been formally introduced and described as a general
+multi-objective optimization algorithm, in this work we will
+explicitly refer to the more restricted (but still very large)
+embedded system design scenario,  since its properties
+are the one that suggested to the authors the concepts of pareto-based
+innovation and region scoring system.
+
+In particular, we will use a parameterized Very Long Instruction
 Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The philosophy
@@
 purposes focused on parameter-space representation
-\item \emph{Compiler awareness}: code scheduling for the execution of
+\item \emph{Software Compiler awareness}: code scheduling for the execution of
 applications is statically obtained by the compiler which
@@
 \subsection{Design Space: Hardware and Software Parameters}
+\secL{designspace}
 Conceptually, system parameters can be classified in three main categories:
@@
 implementation of the system, so parameters of those
-classes are usually referred ``hardware parameters''. On the other
+classes are usually referred as ``hardware parameters''. On the other
 side, all the parameters affecting the behaviour of the compiler
 are referred as ``software parameters'', being directly involved in
-the process of generating the application executables running on the
+the process of generating the application executable running on the
 underlying hardware.
 
-Processor hardware parameters are directly related to the VLIW core and includes the size
-of the register files and the number of functional
-units of each type. In particular, five different types of register
-files are supported:
-GPR (32-bit registers for integers), FPR (64-bit registers for
-floating point values) PR (1-bit registers used to store the Boolean
-values of predicated instructions), BTR (64-bit registers containing
-information about possible future branches) and CR (32-bit control
-registers containing information about the internal state of the
-processor). The functional units involved are: \emph{Integer units},
-\emph{floating point units}, \emph{memory units} (associated with
-load/store operations) and \emph{branch units} (associated with branch
-operations). With respect to the memory sub-system hardware, the parameters
-include \emph{size}, \emph{associativity} and
-\emph{block size} for each of the three caches: First-level data cache
-(L1D), first-level instruction cache (L1I) and second-level unified
-cache (L2U).
-
-On the software side, a set of the most impacting code
-compilation parameters has been selected and included in the
-configuration space, in particular:
-\begin{itemize}
-\item \emph{tcc\_region}: Specifies the scope of action of the compiler and the type
-of code transformation involved (basic block, super block and hyper
-block) 
-\item \emph {max\_unroll\_allowed}: The number of unroll iterations allowed
-\item \emph{regroup\_only}: Avoids inlining 
-\item \emph{do\_classic\_opti}: A set of classical optimization, not VLIW related,
-such as common expression removal and loop unrolling
-\item \emph{do\_prepass\_scalar\_scheduling}: Performs a schedule before
-forming regions 
-\item \emph{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
-\item \emph{do\_modulo\_scheduling}: Modular scheduling of loop code
-\item \emph{memvr\_profiled}: Performs a memory-dependencies profiling 
-\end{itemize}
+Processor hardware parameters are directly related to the VLIW core
+and includes the size of the register files and the number of
+functional units of each type. On the software side, a set of the most
+impacting code compilation parameters has been selected.
+Table~\ref{tab:param} show the complete set of parameters included in
+the design space and their possible values. The total size of design
+space, which grows with the product of parameter cardinalities is
+about $1.33 \times 10^{14}$.
 
@@
 
+\begin{table}
+	\tbl{Design Space\label{tab:param}}{
+	\begin{tabular}{lll}
+	\hline
+	\multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Values} & \multicolumn{1}{c}{Type}\\
+	\hline
+	General Purpose Registers & 16, 32, 64, 128 & HW \\
+	Floating Point Registers & 16, 32, 64, 128 & HW \\
+	Predicate Instructions registers & 32, 64, 128 & HW \\
+	Branch Target Registers & 16, 32, 64 & HW \\
+	Control Registers & 32, 64, 128 & HW \\
+	\hline
+	Integer Functional Units & 1, 2, 3, 4, 5, 6 & HW \\
+	Floating Point Units & 1, 2, 3, 4, 5, 6 & HW\\
+	Memory Units & 1, 2, 3, 4  & HW \\
+	Branch Units & 1, 2, 3, 4  & HW \\
+	\hline
+	L1 Data Cache Size (KB) & 1, 2, 4, 8, 16, 32, 64, 128 & HW \\
+	L1 Data Cache Blocksize & 32, 68, 128 & HW \\
+	L1 Data Cache Associativity (KB) & 1, 2, 4 & HW \\
+	L1 Instruction Cache Size (KB) & 1, 2, 4, 8, 16, 32, 64, 128 & HW \\
+	L1 Instruction Cache Blocksize & 32, 68, 128 & HW \\
+	L1 Instruction Cache Associativity (KB) & 1, 2, 4 & HW \\
+	L2 Unified Cache Size (KB) & 32, 64, 128, 256, 512  & HW\\
+	L2 Unified Cache Blocksize & 32, 68, 128 & HW \\
+	L2 Unified Cache Associativity (KB) & 2, 4, 8 & HW \\
+	\hline
+        tcc\_region: Scope of action of the compiler & basic block, super block, hyper block & SW \\
+        max\_unroll\_allowed: unroll iterations allowed & none, medium, high & SW \\
+        regroup\_only: Avoids inlining & yes, no & SW \\
+        do\_classic\_opti: Classical optimizations & yes, no & SW \\
+        do\_prepass\_scalar\_scheduling: Performs a prepass schedule & yes, no & SW \\
+        do\_postpass\_scalar\_scheduling: Performs a schedule after & yes, no & SW \\
+	do\_modulo\_scheduling: Modular scheduling of loop code & yes, no & SW \\
+        memvr\_profiled: Memory-dependencies profiling & yes, no & SW \\
+	\hline
+	\end{tabular}}
+\end{table}
+
 % ACM table style
@@
 \end{table}
-
 %------------------------------------------------------------------------------
@@
 
-\comment{TODO controllare inglese}
 Even if an analogy between the concepts of ``era'' and ``generation'' 
@@
 introductory work. Nevertheless, a set of preliminary tests with
-different values of $K$ have been conducted. As shown in
-Figure~\ref{fig:kimpact}, which refer to the alloca\_test application
-and a fixed amount of 500 configurations, initially increasing values
-of $K$ seem to improve both pareto (left picture) and objective
-distribution (right picture), but after some threshold the $K$ does
-not seem to provide any benefit, returning to slightly worse
-results for the last value considered (100). Similar trends have been
-found for other benchmarks in the set considered (which are
-not included for space reasons), showing a value of $K$ around 30 as
-reasonable sweet spot for the objectives. A complete resource with the whole 
+different values of $K$ have been conducted, similar the one shown in
+Figure~\ref{fig:kimpact} which refer to the alloca\_test application
+and a fixed amount of 500 configurations. We found that initially increasing values
+of $K$ seem to improve both pareto (as in the picture on the left) and objective
+distribution (right picture), but after some threshold value the $K$ does
+not seem to provide any benefit, even returning to slightly worse
+results for the last value of $K$ considered (100). Similar trends have been
+found for the other benchmarks (not included for space reasons),
+showing on average a value of $K$ around 30 as
+reasonable sweet spot for the objectives. A complete online resource with the whole 
 results and data obtained in the tests performed can be found
@@
 \subsection{Evaluation metrics}
+Qualitative evaluation of paretos is probably the simplest way for
+having a quick glance on algorithm behviour and results. However, in
+tests involving a comparison between different exploration strategies
+that approach could not help in capturing the whole picture, e.g. missing
+some important properties related to the distribution of the solutions
+found.
 In order to evaluate the Paretos from a quantitative point-of-view we
@@
 
-\comments{Da lasciare, da spostare ? da mostrare in modo semplice ?
-non so}
+\comment{Da lasciare, da spostare ? da mostrare in modo semplice ?  non so}
 Another interesting feature of PS is that the final output of its

### 2014-10-30 algorithm.tex
Final english fixes

@@
 \subsection{Algorithm Parameters and Scalability} The parameters that
-completely determine the algorithm are the configurations budget each
+completely determine the algorithm are the configurations budget for each
 era $K$ and the threshold factor $\alpha$. From a functional point of
@@
 construction, it is guaranteed by the way the configuration space is
-partitioned, independently from number of configurations evaluated at
+partitioned, independently from the number of configurations evaluated at
 each iteration.
@@
 
-As regards the performance of the proposed approach we can estimate that the
+With regard to the performance of the proposed approach we can estimate that the
 performance of $PS$ is strictly related to the total number of
 different configurations evaluated during the exploration. We can
-safely make such assumption, because the process of evalutating a new
+safely make such assumption, because the process of evaluating a new
 configuration is the time-dominating one among all the operations
-performed. As we will show the
+performed. As we will show in the
 next Section, this is especially true in the hardware/software
-design space exploration scenario we are addressing, since benchmark compiling and execution times
+design space exploration scenario we are addressing, since benchmark
+compilation and execution times
 are orders of magnitude bigger than the splitting/merging operations and
@@
 \]
-where $E_{tot}$ is the nuber of eras executed and assuming that at
+where $E_{tot}$ is the number of eras executed and assuming that at
 least $K$ evaluation should be performed in order to obtain the first
@@
 is inefficient. To solve this problem, the number of test functions
-assigned to each macro-region should be perdiodically renegotiated, in
+assigned to each macro-region should be periodically renegotiated, in
 favor of the macro-regions providing most innovation.
@@
 configuration space is spanned in parallel by multiple PS instances,
-but, altough autonomous, they are not isolated; on the contrary, they
+but, although autonomous, they are not isolated; on the contrary, they
 continuously exchange information and influence each other, thanks to

### 2014-10-30 concepts.tex
Final english fixes

@@
 Another fundamental concept, which adds further complexity to the
-problem of multiobjective design space exploration, is the following
+problem of multi-objective design space exploration, is the following
 
@@
 \defL{dependency}
-Given a system $S$, application $b \in \mathcal{B}$ and two parameters
+Given a system $S$, an application $b \in \mathcal{B}$ and two parameters
 $p_x$ and $p_y$, $p_x$ is said to
@@
 in~\secR{Related-work}. In this work we will often refer to
-hardware/sofware dependencies, denoting dependencies occourring
+hardware/software dependencies, denoting dependencies occurring
 between parameters belonging to the hardware and software categories,

### 2014-10-30 experiments.tex
Final english fixes

@@
 embedded system design scenario,  since its properties
-are the one that suggested to the authors the concepts of pareto-based
+are the one that suggested to the authors the concepts of Pareto-based
 innovation and region scoring system.
@@
 classes are usually referred as ``hardware parameters''. On the other
-side, all the parameters affecting the behaviour of the compiler
+side, all the parameters affecting the behavior of the compiler
 are referred as ``software parameters'', being directly involved in
@@
 parameter, since our aim is evaluate the capacity of focusing on
-interesting parameter regions without any external judgement or help
+interesting parameter regions without any external judgment or help
 based on heuristics.  In particular in this work when referring to
@@
 analysis on how it could differ from other genetic approaches and what
-could be expected from similar multi-objetive strategies.
+could be expected from similar multi-objective strategies.
 
-Even if an analogy between the concepts of ``era'' and ``generation'' 
-can be considered, a fixed amount of total different simulations has been
-considered for each of the tests. The purpose is to make the
-comparison fair from a algorithm performance perspective, since a
-fixed budget of simulations is directly related to the amount of time
-required to execute the exploration; on the other side, just simply
-referring to a given number of generations/era could be misleading when a
-significative number of configuration remain unaltered in the current
-population (e.g. because of a local optimum).
+Although an analogy between the concepts of ``era'' and ``generation''
+can be considered, comparisons have been carried out using as
+reference a fixed amount of total unique simulations, instead of a given
+number of eras/generations . The purpose is to make the comparison
+fair and accurate from the algorithm performance perspective, since a fixed budget of
+different simulations is more directly related to the actual amount of time
+required to execute the exploration; on the other side, simply
+referring to a given number of generations/eras could be inaccurate
+when a significative number of configuration remain unaltered in the
+current population (e.g. because of a local optimum).
 
@@
 introductory work. Nevertheless, a set of preliminary tests with
-different values of $K$ have been conducted, similar the one shown in
+different values of $K$ have been conducted, similar to the one shown in
 Figure~\ref{fig:kimpact} which refer to the alloca\_test application
 and a fixed amount of 500 configurations. We found that initially increasing values
-of $K$ seem to improve both pareto (as in the picture on the left) and objective
-distribution (right picture), but after some threshold value the $K$ does
+of $K$ seem to improve both Pareto (as in the picture on the left) and objective
+distribution (on the right), but after some threshold value the $K$ does
 not seem to provide any benefit, even returning to slightly worse
@@
 showing on average a value of $K$ around 30 as
-reasonable sweet spot for the objectives. A complete online resource with the whole 
-results and data obtained in the tests performed can be found
+reasonable sweet spot for the objectives. A complete resource with the
+whole set of results and data obtained in the tests performed can be found online
 at~\cite{ps_results}.
@@
 \begin{table}
-	\tbl{Benchmarks\label{tab:defaults}}{
+	\tbl{Algorithm Parameters\label{tab:defaults}}{
 	\begin{tabular}{ll}
@@
 \subsection{Evaluation metrics}
-Qualitative evaluation of paretos is probably the simplest way for
-having a quick glance on algorithm behviour and results. However, in
+\secL{metrics}
+A qualitative evaluation of Paretos is probably the simplest way for
+having a quick glance on algorithm behavior and results. However, in
 tests involving a comparison between different exploration strategies
-that approach could not help in capturing the whole picture, e.g. missing
+this approach could not help in capturing the whole picture, missing
 some important properties related to the distribution of the solutions
@@
 will consider two metrics, namely, the \emph{variation range} and the
-\emph{average normalised absolute dispersion error}.
+\emph{average normalized absolute dispersion error}.
 Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
@@
 
-For a given objective, the \emph{variation range} represents the ratio between the maximum and the minimum value observed for that objective.
-\comment{AA: Per rappresentare l'extent del Pereto front, forse sarebbe meglio evitare di usare il variation range, per come l'hai definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5 ``Metrics of performance'', che mi pare rappresenti la stessa cosa, concettualmente.
-Questo ci permette di essere meno attaccabili (del tipo ``non te la prendere con noi, prenditela con Zitzler (che e' citato 3064 volte!) se non capisci l'utilita' della metrica'').}
+For a given objective, the \emph{variation range} represents the ratio
+between the maximum and the minimum value observed for that objective.
 
-The average \emph{normalised absolute dispersion error} measures
+\comment{AA: Per rappresentare l'extent del Pereto front, forse
+sarebbe meglio evitare di usare il variation range, per come l'hai
+definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5
+``Metrics of performance'', che mi pare rappresenti la stessa cosa,
+concettualmente. Questo ci permette di essere meno attaccabili (del
+tipo ``non te la prendere con noi, prenditela con Zitzler (che e'
+citato 3064 volte!) se non capisci l'utilita' della metrica'').}
+
+Another metric is the average \emph{normalized absolute dispersion
+error}: it measures
 the average absolute difference between the distribution of points in
@@
 where $\overline{N} = |O| / (M_x M_y)$. The average
-normalised absolute dispersion error ($ANADE$) is the average of $E_i$
-normalised to the maximum absolute error $E_{max}$:
+normalized absolute dispersion error ($ANADE$) is the average of $E_i$
+normalized to the maximum absolute error $E_{max}$:
 \[ ANADE = \frac{\sum_{i=1}^{M_xM_y} E_i/(M_xM_y)}{E_{max}}, \]
@@
 
+In this Section we first analyze the results of GA and PS approaches from a
+qualitative perspective, showing how Pareto curves compare when
+plotted on the bidimensional space of power and performance
+objectives. Next, we perform a quantitative
+analysis of the results in order to more accurately figure out in which
+features/properties the two approaches can differentiate.
+
 \figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the
-resulting Pareto fronts for two different scenarios of 100 and 500
-simulations budget. The set of algorithm parameters involved and their
+resulting Pareto fronts for two scenarios of 100 and 500
+simulations budget respectively. The set of algorithm parameters involved and their
 values are the one previously shown in Table~\ref{tab:defaults}. It
-should be pointed out again that the number of generations (or era)
-has been chosen so that only the given amount of simulations is
+should be pointed out again that the number of generations (or eras)
+has been chosen so that only the given amount of different simulations is
 actually performed. Thus, when accounting these simulations only
-unique simulations has been considered, removing repetitions and
+unique simulations have been considered, removing repetitions and
 unfeasible configurations.
@@
 enlarge the range itself, resulting in less dense but more extended
-Paretos. Of course we cannot classify this different behaviour as
-``better'' or ``worse'' as compared to the genetic one, it depends on
-various design factors such as desired results granularity, prefixed
-objective range constraints, estimated error of the models used etc.
+Paretos. Of course we cannot classify this different behavior as
+being strictly better or worse when compared to the genetic one: other
+design factors should be evaluated on a case-by-case basis, e.g. the
+desired granularity of the results, objective range constraints or
+estimated error of the models used.
 
-A comparison between the variation ranges of both power dissipation
-and execution time, obtained by PS and GA for different benchmarks is
-shown in \figR{dispersion}(a) and (b) respectively.  As it can
-be observed, the PS exploration provides solutions which fall on a
-range that is, on average, wider than the one provided by a GA
-exploration for power dissipation and execution time, respectively.
+To better evaluate results from a different perspective, we will
+adopted the two quantitative metrics of variation range and average absolute
+dispersion error, which have been described and motivated
+in~\secR{metrics}. In particular, a comparison between the variation
+ranges of both power dissipation and execution time, obtained by PS
+and GA for different benchmarks is shown in \figR{dispersion}(a) and
+(b) respectively.  As it can be observed, the PS exploration provides
+solutions which fall on a range that is, on average, wider than the
+one provided by a GA exploration for power dissipation and execution
+time, respectively.
 %\begin{table}
@@
 \begin{figure}
-  \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for different benchmarks and average dispersion absolute dispersion (c). \comment{AA: manca il titolo nella figura (c)} }
+  \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for
+  different benchmarks and average dispersion absolute dispersion (c).
+  \comment{AA: manca il titolo nella figura (c)} }
   \begin{center}
@@
 
-\figR{dispersion}(c) shows the average normalised absolute
-dispersion errors for different benchmarks for PS and GA
-exploration. As it can be observed, GA shows a tendency in
-discovering more uniformly dispersed points (i.e. higher values in the
-chart). These results, together with the variation ranges of \figR{dispersion}(a) and
-(b) confirm the of density vs extension trade-offs
-when comparing PS and GA approaches. Again, it
-is worth pointing out how a definitive claim about the superiority of
-the PS behaviour is strictly dependent on the design 
-requirements and constraints, e.g. whether we need wide or dense
-results.
+\figR{dispersion}(c) shows the average normalized absolute dispersion
+errors for different benchmarks for PS and GA exploration.  As it can
+be observed, GA shows a tendency in discovering more uniformly
+dispersed points (i.e. higher values in the chart). These results,
+together with the variation ranges of \figR{dispersion}(a) and (b)
+confirm the of density vs extension trade-offs when comparing PS and
+GA approaches. Again, it is worth pointing out how a definitive claim
+about which algorithm shows better results, being that strictly
+dependent on the design requirements and constraints, e.g.  whether we
+need wide or dense results.
+\comment{Da lasciare, da spostare ? da mostrare in modo semplice ?  non so}
 
-\comment{Da lasciare, da spostare ? da mostrare in modo semplice ?  non so}
-Another interesting feature of PS is that the final output of its
-execution is not only the set of pareto optimal configurations, but also a set
-of more or less innovation regions of the parameter space, obtained as
-a result of the merge/splitting operators described
-in~\secR{algorithm}.
+Finally, it should be pointed out that the final output of PS
+execution is not only the Pareto-optimal set of configurations, but also
+a partitioning of the parameter space in more or less innovative
+regions, obtained as a result of the merge/splitting operators
+described in~\secR{algorithm}. Exploiting the information carried out
+by this partitioning could be an interesting added-value of PS to be
+investigated in future developments of the proposed strategy.
 

### 2014-10-30 introduction.tex
Final english fixes

@@
 
-In this work we present PS, a multiobjective design exploration
+In this work we present PS, a multi-objective design exploration
 algorithm that introduces the concept of \emph{interesting} and
@@
 qualitative and quantitative comparison of PS against the state-of-art
-of multiobjective genetic based approaches.
+of multi-objective genetic based approaches.
 
@@
 Many different design space exploration algorithms have been proposed
-in literature.  What makes the exploration of embedded systems so
-complex is not only the huge size of the parameter spaces involved,
+in literature.  What makes so complex the exploration of embedded
+systems is not only the huge size of parameter spaces involved,
 but also the tight interaction between parameters in relation to their
-effect on the objective to be optimised, which take the form of
+effect on the objective to be optimized, which take the form of
 \emph{parameter dependencies} (see~\defR{dependency}). The 
@@
 analyze the impact of including compilation parameters into the design
-space space exploration. The results of both works confirm the
-important role that hardware/software dependencies can play in a
+space exploration. The results of both works confirm the
+important role that hardware/software dependencies play in a
 multi-objective exploration and thus justify the choice of explicitly
@@
 making any distinction between them from the algorithm's perspective.
-In fact, one of the purposes of the proposed PS algorithm is avoiding
+In fact, one of the purposes of the proposed PS algorithm is to avoid
 the need of any a priori knowledge about those dependencies, letting
-the algorithm itself discover regions where interaction between
-parameters generates new pareto-optimal points (see the PS scoring
+the algorithm itself to discover regions where interaction among
+parameters generates new Pareto-optimal points (see the PS scoring
 system described in the next sections).
@@
 The most well documented and widespread class of algorithms adopted in the
-design space exploration of embedded systems is probably the one of Evolutionary
-Multiobjective Optimization Algorithms~\cite{coello_easmop}. For this
-reason this is the class of algorithms that we will use for the
+design space exploration of embedded systems is probably the Evolutionary
+Multi-objective Optimization Algorithms~\cite{coello_easmop}. For this
+reason, this is the class of algorithms that we will use for the
 experiments discussed in~\secR{ee}.
@@
 literature, including mixed approaches as in~\cite{Ascia2011382},
-where authors specifically focuse on increasing the performance of a
-evolutionaly exploration strategy, proposing a fuzzy based technique
+where authors specifically focus on increasing the performance of an
+evolutionary exploration strategy, proposing a fuzzy-based technique
 to avoid the actual simulation of a certain number of configurations.

### 2014-10-30 paper.tex
AA: altre modifiche
AA: ultimati i TODO AND sul testo
added platform description
AA
Final english fixes

@@
 \usepackage[ruled]{algorithm2e}
+
+\newcommand{\ee}{{\sf EPIC-Explorer}}
 
@@
 %optimized with an appropriate choice of hardware/software parameters.
-%In this work we present PS, a new multiobjective exploration algorithm
+%In this work we present PS, a new multi-objective exploration algorithm
 %exploiting the parameter space representation of the pareto front.
@@
 %quantitative comparisons of the PS approach against a well-known
-%multiobjective genetic technique demonstrate that, while not
+%multi-objective genetic technique demonstrate that, while not
 %outperforming it in terms of pareto dominance, the proposed approach
@@
 
-In this work we present PS, a new multiobjective exploration
-algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
+In this work we present PS, a new multi-objective optimization algorithm and evaluate it in the context of the exploration the embedded system design space.
+The basic idea is to recognize \emph{interesting} regions, i.e.
 regions of the configuration space that are proving to provide better
@@
 architecture. Qualitative and quantitative comparisons of PS
-against a well-known multiobjective genetic approach demonstrate that,
+against a well-known multi-objective genetic approach demonstrate that,
 while not outperforming it in terms of pareto dominance, the proposed
@@
 
+\section{Conclusions}
 \secL{Conclusions}
-In this work we presented PS, a multiobjective strategy which 
+In this work we presented PS, a multi-objective strategy which 
 introduces the concept of Parameter Space representation of Pareto
@@
 effectiveness with different amount of simulations budget.
-A qualitative/quantitative comparison against a widespread multiobjective genetic
+A qualitative/quantitative comparison against a widespread multi-objective genetic
 approach showed how the proposed strategy can result in a different
@@
 
+\input{appendix.tex}
+
 \end{document}

### 2014-10-31 algorithm.tex
AA: during the answer revision

@@
 
-With regard to the performance of the proposed approach we can estimate that the
-performance of $PS$ is strictly related to the total number of
+With regard to the performance of the proposed approach, we observe that the
+performance of $PS$ is related to the total number of
 different configurations evaluated during the exploration. We can
@@
 are orders of magnitude bigger than the splitting/merging operations and
-innovation scores computations.  Ideally, the $i$-th era would provide a new set
+innovation scores computations.  The $i$-th era would provide a new set
 $test_i$ of $K$ configurations to be tested. However, we cannot know
@@
 these will actually be new configurations, i.e. requiring a process of
-evaluation. Thus, number of total new simulations $N_{tot}$ 
-can be estimated to be bounded as follows:
+evaluation. Thus, the number of total new simulations $N_{tot}$ 
+is bounded as follows:
 \[

### 2014-10-31 appendix.tex
AA: during the answer revision

@@
 \subsection{Other metrics}
+Per rappresentare l'extent del Pereto front, forse
+sarebbe meglio evitare di usare il variation range, per come l'hai
+definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5
+``Metrics of performance'', che mi pare rappresenti la stessa cosa,
+concettualmente. Questo ci permette di essere meno attaccabili (del
+tipo ``non te la prendere con noi, prenditela con Zitzler (che e'
+citato 3064 volte!) se non capisci l'utilita' della metrica'').
+
 Un'altra interessante metrica potrebbe essere questa: Auhtors of \cite{zitzler_ec00} remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space.

### 2014-10-31 experiments.tex
AA: during the answer revision

@@
 referring to a given number of generations/eras could be inaccurate
-when a significative number of configuration remain unaltered in the
-current population (e.g. because of a local optimum).
+when a considerable number of configurations remain unaltered in the
+current population (e.g. because of a local optimum)\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.
 
@@
 of the genetic approach, they both have been set to the same values. As discussed
-when introducing the main PS algorithm concepts, an accurate
-investigation of algorithm tuning is beyond the scope of this
-introductory work. Nevertheless, a set of preliminary tests with
-different values of $K$ have been conducted, similar to the one shown in
-Figure~\ref{fig:kimpact} which refer to the alloca\_test application
-and a fixed amount of 500 configurations. We found that initially increasing values
-of $K$ seem to improve both Pareto (as in the picture on the left) and objective
+when introducing the main PS algorithm concepts, a sensitivity analysis on the algorithm parameters is beyond the scope of this work. Nevertheless, we conducted several tests with
+different values of $K$, similar to the ones shown in
+Figure~\ref{fig:kimpact} which refers to the alloca\_test application
+and a total budget of 500 configurations. We found that initially increasing values
+of $K$ seems to improve both Pareto (as in the picture on the left) and objective
 distribution (on the right), but after some threshold value the $K$ does
@@
 	\tbl{Algorithm Parameters\label{tab:defaults}}{
-	\begin{tabular}{ll}
+	\begin{tabular}{cll}
 	\hline
-	\multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Default Value} \\
+	\multicolumn{1}{c}{Algorithm} & \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Default Value} \\
 	\hline
-	GA population size & 30 \\
-	GA crossover probability & 0.8 \\
-	GA mutation probability  & 0.1 \\
-	$K$ era budget & 30 \\
-	alpha threshold & 1 \\
-	Total simulations budgets & 100-500 \\
+	GA & population size & 30 \\
+	GA & crossover probability & 0.8 \\
+	GA & mutation probability  & 0.1 \\
+	PS & era budget ($K$) & 30 \\
+	PS & innovation threshold ($\alpha$ ) & 1 \\
+	both PS and GA & Total simulations budget & 100-500 \\
 	\hline
@@
 \begin{figure}
-  \figLC{kimpact}{Impact of increased K values on Pareto fronts and distribution for the alloca\_test application.}
+  \figLC{kimpact}{Impact of increased K values on Pareto fronts and distribution for the alloca\_test application.
+\comment{AA: non capisco cosa sia la figura a destra.
+Inoltre, io vedo sulle ascisse e le ordinate di entrambi i grafici, le stesse grandezze (Time vs Power), quindi mi aspetto di trovare esattamente lo stesso plot sia a destra che a sinistra}}
   \begin{center}
@@
 between the maximum and the minimum value observed for that objective.
-
-\comment{AA: Per rappresentare l'extent del Pereto front, forse
-sarebbe meglio evitare di usare il variation range, per come l'hai
-definito tu, e usare la funzione M3 di \cite{zitzler_ec00}, Sec.5
-``Metrics of performance'', che mi pare rappresenti la stessa cosa,
-concettualmente. Questo ci permette di essere meno attaccabili (del
-tipo ``non te la prendere con noi, prenditela con Zitzler (che e'
-citato 3064 volte!) se non capisci l'utilita' della metrica'').}
 
@@
 confirm the of density vs extension trade-offs when comparing PS and
-GA approaches. Again, it is worth pointing out how a definitive claim
-about which algorithm shows better results, being that strictly
-dependent on the design requirements and constraints, e.g.  whether we
-need wide or dense results.
-\comment{Da lasciare, da spostare ? da mostrare in modo semplice ?  non so}
+GA approaches.
+We highlight that PS shows a stronger \emph{uniform convergence} (discussed in \secL{metrics}), i.e.
+it provides a more extended Pareto front, avoiding the designer to neglect some important options, and offering a wider view of the potentiality of the designed device.
 

### 2014-10-31 introduction.tex
AA: during the answer revision

@@
 non-dominated points will be considered in the next iteration.
-However, an important feature differentiates it from PS. The Sampling algorithm only the
+However, an important feature differentiates it from PS. In the Sampling algorithm only the
 selected regions are examined, even though there is no guarantee that
-all the Pareto points are included in them. As a consequence, the
+they contain all the Pareto points. As a consequence, the
 Sampling algorithm may erroneously and prematurely neglect some
@@
 points. The PS algorithm avoids this, since even though a region has not
-provided non-dominated points, it is not neglected, rather it is
-simply populated with fewer test points, thus giving the chance to
-find non-dominated points in them. From this behavior also comes
+provided non-dominated points, it is not neglected, but it is
+populated with fewer test points, allowing to
+find its other non-dominated points. From this behavior also comes
 another important difference. The Sampling algorithm of
@@
 regions selected in the previous iterations. In other words, it keeps
-zooming into the regions that have been considered ``interesting'',
+zooming in into the regions that have been considered ``interesting'',
 i.e. rich of non-dominated points, in the previous iterations. The

### 2014-10-31 algorithm.tex
AA: during the answer revision

@@
 
-\comment{CHECK AND: Per caso era where invece di when ? o manca qualcosa ?}
-To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.
+To summarize, thanks to the above characteristics, PS is able to recognize the regions where the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.
 

### 2014-10-31 introduction.tex
AA: piccole correzioni

@@
 face~\cite{wsts}.
-Several factors are involved in this goal and real cases show how
+Real cases show how
 often no analytical results are known to predict the relation between
@@
 configurations.  The final result of a design space exploration is a
-subset of the configurations called \emph{Pareto set} (\cite{pareto},
-see also \defR{pareto-set}). The corresponding values of the
-objectives for each configuration of the Pareto Set is called
-\emph{Pareto front}: it represents the trade-offs between objectives,
+subset of configurations called \emph{Pareto set} (\cite{pareto},
+see also \defR{pareto-set}). The set of the corresponding tuples of objective values is called \emph{Pareto front}: it represents the trade-off between objectives,
 i.e.  for each point of the Pareto front there is no other
 configuration performing better for all the objectives considered (see
-\figR{psos}). Of course this is only a first high-level system
-simulation, thus these few promising configurations will need to be
-further evaluated in a next step of the design flow using a more
-accurate low level simulation (e.g. register transfer level).
-
+\figR{psos}).
 %while providing, at the end, configurations that are close to the
@@
 configurations in the Pareto front, i.e.
-how different these configurations are, in terms of objectives, with respect to the ones already found previously.
-The regions with high score are considered the most \emph{interesting} and more simulations are distributed there rather than in the rest of the configuration space.
+how different these configurations are, in terms of objective values, with respect to the ones previously found.
+The regions with high score are considered the most \emph{interesting} and more simulations are distributed there, rather than in the rest of the configuration space.
 Several geometrical transformations (splitting, merging etc.) are

### 2014-10-31 paper.tex
AA: piccole correzioni

@@
 
-Embedded Systems Design requires conflicting objectives to be
+The Embedded Systems Design requires conflicting objectives to be
 optimized with an appropriate choice of hardware/software parameters.
 A simulation campaign can guide the design in finding the best
-trade-offs, but due to the big number of possible configurations it
-is often unfeasible to simulate all of them. For these reasons Design Space
+trade-offs, but, due to the big number of possible configurations, it
+is often unfeasible to simulate them all. For these reasons, Design Space
 Exploration (DSE) algorithms aim at finding near-optimal system
-configurations only simulating a subset of them.
+configurations, by simulating only a subset of them.
 
-In this work we present PS, a new multi-objective optimization algorithm and evaluate it in the context of the exploration the embedded system design space.
-The basic idea is to recognize \emph{interesting} regions, i.e.
+In this work we present PS, a new multi-objective optimization algorithm and evaluate it in the context of the embedded system design. The basic idea is to recognize \emph{interesting} regions, i.e.
 regions of the configuration space that are proving to provide better
-configurations with regard to other ones. PS evaluates more configurations in
-interesting regions while exploring less thoroughly the rest of the
+configurations with respect to other ones. PS evaluates more configurations in the
+interesting regions, while less thoroughly exploring the rest of the
 configuration space. After a detailed formal description of the
@@
 against a well-known multi-objective genetic approach demonstrate that,
-while not outperforming it in terms of pareto dominance, the proposed
-approach can trade the uniformity and granularity qualities of the
-solutions found for obtaining larger Pareto sets, thus representing a
-further choice for designer when objective constrains allow it.
+while not outperforming it in terms of Pareto dominance, the proposed
+approach can balance the uniformity and granularity qualities of the
+solutions found, obtaining more extended Pareto-fronts that provide a wider view of the potentiality of the designed device. Therefore, PS represents a
+further valid choice for the designer, when objective constrains allow it.
 \end{abstract}

### 2014-10-31 experiments.tex
Halloween camera-ready

@@
 the design space and their possible values. The total size of design
-space, which grows with the product of parameter cardinalities is
+space, which grows with the product of parameter cardinalities, is
 about $1.33 \times 10^{14}$.
@@
 different simulations is more directly related to the actual amount of time
-required to execute the exploration; on the other side, simply
-referring to a given number of generations/eras could be inaccurate
-when a considerable number of configurations remain unaltered in the
-current population (e.g. because of a local optimum)\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.
+required to execute the exploration.
+%; on the other side, simply
+%referring to a given number of generations/eras could be inaccurate
+%when a considerable number of configurations remain unaltered in the
+%current population (e.g. because of a local optimum)
+\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.
+\comment{DAV: se non lo capisci vuol dire che o e' scritto male o e'
+inutile, per adesso lo tolgo.}
 

### 2015-01-20 algorithm.tex
AA: errori segnalati da reviewer 2 corretti. Rilettura ancora da fare

@@
 	\[
-	is\left(\mathbf{c}^*\right)=\min\left\{ \left.s\left(\mathbf{c}\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\} 
+	is\left(\mathbf{c}^*\right)=\min\left\{ \left.s\left(\mathbf{c}^*\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\} 
 	\]
@@
 	\begin{enumerate}
-		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split to obtain $\psi(R)$, as stated in \defR{splitting-a-region}.
+		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split to obtain $\psi(R)$, as stated in \defR{splitting-regions}.
 We use $\psi\left(\mathscr{R}_{i,h}\right)$ to denote the set of regions obtained as explained.
@@
 elected as high-innovation, yielding less splitting operations. This
-slows down zooming in on portions of configuration space and make the
+slows down zooming in on portions of configuration space and makes the
 distribution of the simulated configuration more uniform, as there are
@@
 of $PS$ with different choices and to select some ``reasonable'' average
-values to perform the design space exploration, as it will discussed
+values to perform the design space exploration, as we will discuss
 in~\secR{ee}.
@@
 configuration space partition that separately evolves. Each PS
-instance independently performs the zoom-out and zoom-in in on
+instance independently performs the zoom-out and zoom-in on
 configuration space, splitting and merging its own regions. All PS

### 2015-01-20 concepts.tex
AA: errori segnalati da reviewer 2 corretti. Rilettura ancora da fare

@@
 We argue that it is a strong point for PS, as for genetic algorithms, since (i) it permits to apply it to a wide range of different problems and (ii) it can be effectually used when the embedded system design is particularly challenging and no much a-priori knowledge is available to the designer.
-As already pointed in \secL{related_work}, the generality of genetic algorithms has made them widely deployed with respect to the other approaches.
-Thanks to the generality of PS, we will not need to modify or adapt it in order to apply it to the case of embedded system design, as we will show in \secL{ee}.
+As already pointed in \secR{Related-work}, the generality of genetic algorithms has made them widely deployed with respect to the other approaches.
+Thanks to the generality of PS, we will not need to modify or adapt it in order to apply it to the case of embedded system design, as we will show in \secR{ee}.
 On the one hand, this legitimate our choice of keeping formulation general.
@@
 feasible configuration space} of $S$ and indicate it as
-$\mathcal{C}^*(S)$].
+$\mathcal{C}^*(S)$.
 
@@
 
-When a dependency is present between parameters, it could be
-misleading to use assumption about the ``meaning'' of
+When a dependency between parameters is present, it could be
+misleading to use assumptions about the ``meaning'' of
 parameters in order to intuitively choose an appropriate value that
-optimizes objectives.  It should be also pointed
+optimizes the objectives.  It should be also pointed
 out that it's often very difficult to identify dependencies using
@@
 \[
-R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
+R=\left\{ \left.\left(v_{1},v_{2}\right)\in V_{1}\times V_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
 \]
@@
 On the contrary, uninteresting regions are merged, so that each one will receive less effort in the next iteration.
-In other words, ares of the configuration space that are more promising are split in small sub-regions, while the other ones are blended in big regions.
+In other words, areas of the configuration space that are more promising are split in small sub-regions, while the other ones are blended in big regions.
 As illustrated in \figR{small_and_big}, assigning $N$ simulations to each region makes small ones well populated while bigger ones sparsely explored.
@@
 	\[
-	\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
+	\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap V_{i}
 	\]
@@
 \begin{definition}[Splitting an interval]
-\defL{splitting-a-region}
+\defL{splitting-intervals}
 Given a $p_i$ interval $\left[a_{i}..b_{i}\right]$ with more than one element, i.e.
@@
 \begin{definition}[Splitting a region]
-\label{pers02.def:Splitting-a-region}
+\defL{splitting-regions}
 Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it into a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the cartesian product, as shown in \figR{split}~(b).
@@
 		\mu	 \left( \begin{array}{l}
-				\left[a_{j}..y_{j}\right] \\
-				\left[x_{j}..b_{j}\right]
+				\left[a_{i}..y_{i}\right] \\
+				\left[x_{i}..b_{i}\right]
 		     \end{array} \right)
 		=\begin{cases}
-			\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
-			\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
+			\left[a_{i}..y_{i}\right] & \mbox{ if }b_{i}<x_{i}\\
+			\left[x_{i}..b_{i}\right] & \mbox{ if }y_{i}<a_{i}
 		\end{cases}

### 2015-01-20 introduction.tex
AA: errori segnalati da reviewer 2 corretti. Rilettura ancora da fare

@@
 multi-objective exploration and thus justify the choice of explicitly
-including the two class of parameters in the design space without
+including the two classes of parameters in the design space without
 making any distinction between them from the algorithm's perspective.
@@
 dependencies among them. But real scenarios rarely expose monotonicity
-property thus resulting in inaccuracies, as stated in the same paper).
+property thus resulting in inaccuracies, as stated in the same paper.
 
 Other approaches, as \cite{fornaciari_codes01,palesi_iwsoc02}, are
-based the concept of \emph{sensitivity analysis}, i.e. measuring of
+based on the concept of \emph{sensitivity analysis}, i.e. measuring of
 how much the objective varies when varying each parameter.  Parameters

### 2015-01-24 algorithm.tex
AA: dato un colpo di aspell. Manca rilettura finale. Da rivedere la caption della figura 10

@@
 In this section we present PS, the algorithm that we propose to perform the Design Space Exploration (DSE).
-As any other DSE algorithm, its input is the parameterized system $S$ and a benchmark application $b$, while the output is an approximation of the Pareto-optimal set $\mathcal{P}\left(S,b\right)$.
+As any other DSE algorithm, its input is the parametrized system $S$ and a benchmark application $b$, while the output is an approximation of the Pareto-optimal set $\mathcal{P}\left(S,b\right)$.
 PS is iterative and we will describe, separately, the initialization phase, the operations performed inside each iteration and the condition that triggers the termination.
@@
 least $K$ evaluation should be performed in order to obtain the first
-pareto $\mathscr{P}_0$.
+Pareto $\mathscr{P}_0$.
 

### 2015-01-24 concepts.tex
AA: dato un colpo di aspell. Manca rilettura finale. Da rivedere la caption della figura 10

@@
 
-Let $S$ be a parameterized system with $n$ parameters. The generic
+Let $S$ be a parametrized system with $n$ parameters. The generic
 parameter $p_i, \ i \in \{1,2,\ldots,n\}$ can take any value in
@@
  (where $s_{1}$ and $s_{2}$ are some threshold values) is \emph{uninteresting}. This clearly shows that there are cases when, if a parameter lies in
-a certain range, there are ranges of the other one that are not worth being explored. Intuitively, the cartesian product of these ranges is an \emph{uninteresting region}.
+a certain range, there are ranges of the other one that are not worth being explored. Intuitively, the Cartesian product of these ranges is an \emph{uninteresting region}.
 
@@
 
-Since regions will be defined as cartesian products of parameter intervals, we need the following definition.
+Since regions will be defined as Cartesian products of parameter intervals, we need the following definition.
 \begin{definition}[Parameter interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in V_{i},a_{i}<b_{i}$.
@@
 \label{pers02.def:Contiguous-intervals}
-Two intervals are contiguous iff they do not overlap and merging them results in a new interval. More formally, let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
-be two $p_{i}$-intervals. They are said to be contiguous (see \figR{interval_and_region}(a) ) iff
+Two intervals are contiguous if and only if they do not overlap and merging them results in a new interval. More formally, let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
+be two $p_{i}$-intervals. They are said to be contiguous (see \figR{interval_and_region}(a) ) if and only if
 \begin{align}\begin{array}{l}
@@
 \begin{definition}[Region] 
-A region is a cartesian product of parameter intervals, as illustrated in \figR{interval_and_region} (b).
+A region is a Cartesian product of parameter intervals, as illustrated in \figR{interval_and_region} (b).
 More formally, if $p_1,\dots,p_n$ are the parameters of the system, and $\left[ a_{i}..b_{i} \right]$ is a $p_i$-interval, a region is a set of the following form:
@@
 is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
-iff 
+if and only if 
 $\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|$.
@@
 \defL{splitting-regions}
-Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it into a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the cartesian product, as shown in \figR{split}~(b).
+Consider a region $R=\prod\left[a_{i}..b_{i}\right]$.The split operator $\psi$ divides it into a set of sub-regions obtained splitting each $p_i$-interval and combining the resulting sub-intervals with the Cartesian product, as shown in \figR{split}~(b).
 Formally:
@@
 \begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
-be two regions. They are said to be contiguous iff they do not overlap and, merging them, a new region can be obtained. Formally, $R_1$ and $R_2$ are contiguous iff there exists a $j$ such that:
+be two regions.
+They are said to be contiguous if and only if they do not overlap and, merging them, a new region can be obtained.
+Formally, $R_1$ and $R_2$ are contiguous if and only if there exists a $j$ such that:
 	\begin{align}\begin{array}{l}
@@
 Examples of contiguous and non contiguous regions are given in \figR{contiguous_regions}.
-The two regions at the top are contiguous because their union can be expressed as the cartesian product of parameter intervals, thus they can be merged to obtain a new bigger region.
+The two regions at the top are contiguous because their union can be expressed as the Cartesian product of parameter intervals, thus they can be merged to obtain a new bigger region.
 The same also applies to the regions on the right.

### 2015-01-24 experiments.tex
AA: errori segnalati da reviewer 2 corretti. Rilettura ancora da fare
AA: dato un colpo di aspell. Manca rilettura finale. Da rivedere la caption della figura 10

@@
 
-In particular, we will use a parameterized Very Long Instruction
+In particular, we will use a parametrized Very Long Instruction
 Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The philosophy
@@
 
-In this section, we will also briefly describe the parameterized platform used
+In this section, we will also briefly describe the parametrized platform used
 as testbed for the experiments, the general evaluation flow along with
@@
 %current population (e.g. because of a local optimum)
-\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.
-\comment{DAV: se non lo capisci vuol dire che o e' scritto male o e'
-inutile, per adesso lo tolgo.}
 
@@
 \begin{figure}
-  \figLC{kimpact}{Impact of increased K values on Pareto fronts and distribution for the alloca\_test application.
-\comment{AA: non capisco cosa sia la figura a destra.
-Inoltre, io vedo sulle ascisse e le ordinate di entrambi i grafici, le stesse grandezze (Time vs Power), quindi mi aspetto di trovare esattamente lo stesso plot sia a destra che a sinistra}}
+  \figLC{kimpact}{Impact of increased K values on Pareto fronts and distribution for the alloca\_test application. }
   \begin{center}
@@
   \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for
-  different benchmarks and average dispersion absolute dispersion (c).
-  \comment{AA: manca il titolo nella figura (c)} }
+  different benchmarks and average dispersion absolute dispersion (c). }
   \begin{center}
@@
 GA approaches.
-We highlight that PS shows a stronger \emph{uniform convergence} (discussed in \secL{metrics}), i.e.
+We highlight that PS shows a stronger \emph{uniform convergence} (discussed in \secR{metrics}), i.e.
 it provides a more extended Pareto front, avoiding the designer to neglect some important options, and offering a wider view of the potentiality of the designed device.

### 2015-01-25 introduction.tex
AA

@@
 objectives (energy consumption, performance, area) to be fulfilled.
-The growing demand and reduced time-to-market of these systems are
-introducing even more challenges that designers have to
-face~\cite{wsts}.
-Real cases show how
-often no analytical results are known to predict the relation between
+In addition, it has to cope with an increasing demand and a reduced time-to-market~\cite{wsts}.
+In many real cases, no analytical results are known to predict the relation between
 system configurations and objectives. In such cases a high level
@@
 i.e.  for each point of the Pareto front there is no other
-configuration performing better for all the objectives considered (see
+configuration performing better for all the objectives (see
 \figR{psos}).
@@
 how different these configurations are, in terms of objective values, with respect to the ones previously found.
-The regions with high score are considered the most \emph{interesting} and more simulations are distributed there, rather than in the rest of the configuration space.
+The regions with high score are considered the most \emph{interesting} and, at the next iteration, more configurations are simulated there, rather than in the rest of the configuration space.
 Several geometrical transformations (splitting, merging etc.) are
@@
 preferring the task which the focus is on.  Authors in
-\cite{spatial_attention} describes the visual attention as a spotlight
-that focuses, each time, in a particular region of the visual space in
-order to process it more deeply. Similarly, PS focuses its
-``spotlight'' only to the interesting regions and explore them more
-thoroughly distributing the simulation budget on them.
+\cite{spatial_attention} describe the visual attention as a spotlight
+that focuses, each time, on a particular region of the visual space in
+order to deeply process it. Similarly, PS focuses its
+``spotlight'' only on the interesting regions and thoroughly explore them distributing the simulation budget on them.
 % Ispirzione: http://en.wikipedia.org/wiki/Attentional_shift
@@
 a Very Long Instruction Word (VLIW) architecture, performing a
-qualitative and quantitative comparison of PS against the state-of-art
+qualitative and quantitative comparison of PS against the state-of-the-art
 of multi-objective genetic based approaches.
@@
 Many different design space exploration algorithms have been proposed
-in literature.  What makes so complex the exploration of embedded
-systems is not only the huge size of parameter spaces involved,
-but also the tight interaction between parameters in relation to their
-effect on the objective to be optimized, which take the form of
-\emph{parameter dependencies} (see~\defR{dependency}). The 
-motivations of an exploration algorithm and how it deals with such
-complexity are often rather heuristic, have some form of arbitrariness and,
-to a large extend, intuition lies behind them.
+in literature.
+Exploring the design space of embedded systems is a difficult not only because of the huge size of the parameter space, but also due to the tight \emph{dependencies} (see~\defR{dependency}) between parameters, which impact the objectives.
+Due to this complexity, exploration algorithms are usually heuristic and, to a large extent, rely on simple intuitions rather then formal arguments.
 
-Some exploration strategies assume some kind of knowledge about the
-system parameters, their meaning and their impact on design
+Some exploration strategies assume some knowledge about the
+system parameters, their semantics and their impact on design
 objectives.  The \emph{Dependency analysis}, proposed in
 \cite{givargis_tvlsi02}, is meant to take advantage of the parameter
-dependencies. Starting from them, he can construct a ``dependency graph''
-and recognize clusters, i.e. subsets of strongly dependency-connected
-parameters. Each cluster is exhaustively evaluated and its ``local''
+dependencies. A ``dependency graph'' is constructed and clusters -- i.e. subsets of strongly dependency-connected parameters -- are recognized. Each cluster is exhaustively evaluated and its ``local''
 Pareto set is found. Then, all local Pareto sets are merged. In this
@@
 an exhaustive evaluation of all the possible configurations. Some
-problems arise: i) In real scenarios, it may be difficult to recognize
-really independent clusters of parameters, because there may be
-interdependencies among a large number of parameters. This may lead to
+problems arise: i) In real scenarios, parameter interdependencies may be so deep that it may be difficult to recognize independent clusters. This may lead to
 the need of an evaluation of almost all the possible configurations.
@@
 since, although it leverages dependencies as in
-\cite{givargis_tvlsi02}, it is able to detect them automatically, with
-no a-priori knowledge required. Moreover, our algorithm is able to
+\cite{givargis_tvlsi02}, it is able to detect them automatically, requiring no a-priori knowledge. Moreover, our algorithm is able to
 capture also ``local dependencies", i.e. dependencies that emerge only
@@
 A preliminary estimation of hardware/software dependencies in order to
-reduce the design space is addressed in~\cite{Catania2008}, where
+reduce the exploration of the design space is addressed in~\cite{Catania2008}, where
 authors propose to deal with the software parameters separately,
@@
 the need of any a priori knowledge about those dependencies, letting
-the algorithm itself to discover regions where interaction among
+the algorithm itself discover regions where interaction among
 parameters generates new Pareto-optimal points (see the PS scoring
@@
 Abraham, Rau and Schreiber proposed in \cite{santosh_hptr00} to
-decompose the system under evaluation into components that interact
-minimally with each other. Pareto sets for each component are found
+decompose the system under evaluation into components that minimally interact with each other. Pareto sets for each component are found
 and, provided that ``monotonicity'' exists, the complete Pareto set is
@@
 dependencies among them. But real scenarios rarely expose monotonicity
-property thus resulting in inaccuracies, as stated in the same paper.
+property, and thus inaccuracies may occur, as stated in the same paper.
 
 Other approaches, as \cite{fornaciari_codes01,palesi_iwsoc02}, are
-based on the concept of \emph{sensitivity analysis}, i.e. measuring of
+based on the concept of \emph{sensitivity analysis}, i.e. measuring
 how much the objective varies when varying each parameter.  Parameters
@@
 sensitive one) is varied, while keeping the other parameters fixed to
-arbitrary values, and its best value is found. The limited accuracy
+arbitrary values, and its best value is found. The same procedure is repeated for the second parameter and so on. The limited accuracy
 shown by these approaches can be explained by the limited and rigid
@@
 some ranges of a parameter and less sensitive to other ranges of the
-same parameter. Moreover it can not capture ``combined sensitivity'',
+same parameter. Moreover, it can not capture ``combined sensitivity'',
 i.e. the objectives may be more sensitive to a range of a parameter
@@
 less sensitive to the same range of $p_{1}$ when the other parameters
-are in different ranges. Otherwise, our algorithm can both capture
-local and combined sensitivity.
+are in different ranges. On the contrary, our algorithm can capture
+both local and combined sensitivity.
 
@@
 non-dominated points will be considered in the next iteration.
-However, an important feature differentiates it from PS. In the Sampling algorithm only the
+An important feature differentiates it from PS. In the Sampling algorithm only the
 selected regions are examined, even though there is no guarantee that
@@
 regions selected in the previous iterations. In other words, it keeps
-zooming in into the regions that have been considered ``interesting'',
+zooming in on the regions that have been considered ``interesting'',
 i.e. rich of non-dominated points, in the previous iterations. The
 philosophy behind our algorithm is different. A region, which has been
-considered interesting at a certain iterations, may be not in the
+considered interesting at certain iterations, may not be in the
 future, since it has been thoroughly analyzed. On the other hand, a
@@
 future, once all the other regions have been already exploited.
-Therefore, from an iteration to the next, our algorithm zoom in on
-regions that are currently interesting and zoom out from the
+Therefore, from an iteration to the next, our algorithm zooms in on
+regions that are currently interesting and zooms out from the
 uninteresting ones,  spanning in a broader and more dynamical way the
-configuration space. In addition, in the Sampling region only the
+configuration space. In addition, in the Sampling algorithm only the
 number of non-dominated points is accounted to see how interesting a
@@
 The most well documented and widespread class of algorithms adopted in the
-design space exploration of embedded systems is probably the Evolutionary
+design space exploration of embedded systems is represented by the Evolutionary
 Multi-objective Optimization Algorithms~\cite{coello_easmop}. For this
-reason, this is the class of algorithms that we will use for the
-experiments discussed in~\secR{ee}.
+reason, this is the class of algorithms that we will compare to ours in the experiments of~\secR{ee}.
 Evolutionary approaches have many advantages: they provide good accuracy, they are
@@
 (the mutation avoids being rigidly restricted to limited parts of
-parameter space), and, at the same time, not too scattered as it is
+parameter space), and, at the same time, not too scattered, as it is
 guided by the performances of the already evaluated configurations.
@@
 well known SPEA2 multi-objective genetic algorithm~\cite{knowles_techrep06}
-which is, at best of our knowledge, one of the most appropriate and
+which is, to the best of our knowledge, one of the most appropriate and
 tested for the particular scenario we are assuming.  We

### 2015-01-25 paper.tex
Halloween camera-ready
AA

@@
 ANDREA ARALDO
-\affil{Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
-Paris, France;}
+\affil{Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France}
 DAVIDE PATTI
@@
 In this work we present PS, a new multi-objective optimization algorithm and evaluate it in the context of the embedded system design. The basic idea is to recognize \emph{interesting} regions, i.e.
-regions of the configuration space that are proving to provide better
+regions of the configuration space that provide better
 configurations with respect to other ones. PS evaluates more configurations in the
@@
 Author's addresses: V. Catania, DIEEI University of Catania;
-A. Araldo, Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
-Paris, France;
+A. Araldo, Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France;
 D. Patti, DIEEI University of Catania.
@@
 
-\input{appendix.tex}
+%\input{appendix.tex}
 

### 2015-01-25 algorithm.tex
AA: half reading

@@
 Regions are classified based on the innovation introduced by their configurations in the Pareto-front so far calculated.
-The most interesting regions are split, so that each sub-region will receive evaluation effort in the next iteration.
+The most interesting regions are split, so that each sub-region will receive more evaluation effort in the next iteration.
 On the contrary, uninteresting regions are merged.
@@
 In each era $i$, a set $test_i$ of $K$ configurations will be evaluated. We call them \emph{test configurations} and selecting them is exactly the goal of this step.
-We select only \emph{new} configurations, i.e. the ones that have not been evaluated in past eras. In other words, $test_i$ must not contain $\bigcup_{j=0}^{i-1}test_{j}$.
+We select only \emph{new} configurations, i.e. the ones that have not been evaluated in past eras. In other words, $test_i$ must not overlap with $\bigcup_{j=0}^{i-1}test_{j}$.
 Since all regions $R$ in the configuration space partition $\mathcal{R}_{i}$ must be properly explored, we have to distribute the test configurations among all these regions.
@@
  In case the new configurations in $R$ are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them are selected.
-In this case $test_{R,i}=R\setminus\bigcup_{j=0}^{i-1}test_{j}$, where  $\bigcup_{j=0}^{i-1}test_{j}$ is the set of the configurations already in the past.\footnote{Note that if such regions exist, the total number of evaluations in era $i$ will be less than $K$}
+In this case $test_{R,i}=R\setminus\bigcup_{j=0}^{i-1}test_{j}$, where  $\bigcup_{j=0}^{i-1}test_{j}$ is the set of the configurations already evaluated in the past.\footnote{Note that if such regions exist, the total number of evaluations in era $i$ will be less than $K$}
 \item All configurations on $test_{i}$ are simulated.
@@
 	\[
-	is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} 
+	is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap test_{R,i} \right\} 
 	\]
@@
 
-\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the sub-regions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)$.
+\item The set of regions $\mathcal{R}_{i+1}$ for the following era is composed of the sub-regions resulting from splitting operations ($\psi\left(\mathscr{R}_{i,h}\right)$), the low innovation regions unchanged $\mathcal{R}_{i,l}$, the result of the merging operations ($\mu(\mathscr{M}_i))$ and the no innovation regions that was not possible to merge $\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathscr{M}_i }\left\{ R_{1},R_{2}\right\} \right)$.
 Formally:
@@
 	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
-	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
+	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathscr{M}_i }\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
 	\end{align}
@@
 			\nl \ForEach{$R\in\mathscr{R}_i$} {
-				\nl $is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} $;
+				\nl $is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap test_{R,i} \right\} $;
 			}
@@
  where $\beta$ and $\gamma$ are selected by the experimenter. 
-The algorithm terminates when in the last
-$\beta$ iterations not a great ``amount of innovation'' has been
-discovered. Therefore it is very probably that carrying on iterating
+In other words, the algorithm terminates if, in the last
+$\beta$ iterations, the ``amount of innovation'' has been
+small. Therefore, it is very probably that carrying on iterating
 will not considerably change the Pareto-front approximation already formed.
@@
 it is unsafe to terminate as soon as the Pareto front does not considerably change
-between two consecutive eras, thus a strategy taking into
-account the history of the Pareto fronts has been adopted in the
-proposed approach.
+between two consecutive eras. For this reason, we take into
+account the history of the Pareto fronts.
 
@@
 
-\subsection{Exploration vs Exploitation in PS}
+\subsection{Exploration vs. Exploitation in PS}
 The proposed algorithm has been designed in order to be inherently able to balance exploration and exploitation, which are ``two cornerstones of problem solving by search''~\cite{eiben1998evolutionary}.
-While a detailed survey on the exploration vs exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
+While a detailed survey on the exploration vs.
+exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
 Following the terminology of \cite{weise2012evolutionary}, if the exploration is not sufficiently wide, the algorithm suffers from \emph{premature convergence}, i.e.

### 2015-01-25 experiments.tex
AA: half reading

@@
 together with the variation ranges of \figR{dispersion}(a) and (b)
-confirm the of density vs extension trade-offs when comparing PS and
+confirm the of density vs. extension trade-offs when comparing PS and
 GA approaches.

### 2015-01-26 algorithm.tex
AA: rilettura fatta e colpo di aspell

@@
 	\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
-	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)$;\\
+	\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathscr{M}_i }\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)$;\\
 		}
@@
 While a detailed survey on the exploration vs.
-exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset and being trapped in local optima.
+exploitation trade-off can be found in~\cite{vcrepinvsek2013exploration}, here we limitedly recall that \emph{exploration} is the capability of an algorithm to consider different parts of the configuration space, not being confined only to a limited subset, and thus not being trapped in local optima.
 Following the terminology of \cite{weise2012evolutionary}, if the exploration is not sufficiently wide, the algorithm suffers from \emph{premature convergence}, i.e.
@@
 
-While in genetic algorithms exploration and exploration are guaranteed by mutation, crossover and selection, in our algorithm these guarantees are provided for the following reasons:
+While in genetic algorithms exploration and exploitation are guaranteed by mutation, crossover and selection, in our algorithm these guarantees are provided for the following reasons:
 	\begin{itemize}
-		\item Merging and splitting operation are dynamic processes. A portion
+		\item Merging and splitting operations are dynamic processes. A portion
 of the parameter space may be populated by a large number of small
@@
 However, after having been sufficiently explored, the innovation score of these regions may decrease, they may be merged and therefore that portion of configuration space may be covered by a small number of large regions in next eras.
-This is a desirable property of PS, since, after a number of eras of intense exploration of a configuration space part, this exploration may turn to be enough thorough and so it may be time for other parts to be minutely scanned.
+This is a desirable property of PS, since, after a number of eras of intense exploration of a configuration space part, this exploration may turn out to be enough thorough and so it may be time for other parts to be minutely scanned.
 PS dynamics can be summarized as follows: while eras alternate, PS zooms out from the configurations subspaces already sufficiently scanned in the past, whereas it zooms in on subspaces which provide novelty (guaranteeing exploitation), meaning that they have not been properly analyzed yet (this helps exploration).
@@
 
-\subsection{Algorithm Parameters and Scalability} The parameters that
-completely determine the algorithm are the configurations budget for each
+\subsection{Algorithm Parameters and Scalability} The parameters that determine the algorithm are the configurations budget for each
 era $K$ and the threshold factor $\alpha$. From a functional point of
 view, $K$ is somewhat similar to the population size of a genetic
-approach, determining which configuration should be evaluated in the
+approach, determining how many configurations should be evaluated in the
 subsequent step of the algorithm. However, as seen in the
@@
 performance of the algorithm, and this holds also in our algorithm (see for example
-Figure~\ref{fig:kimpact} in Subsection~\ref{sec:comparison}).
-But while in the genetic approach $K$ must be sufficiently large
-in order to guarantee diversity of the Pareto set configurations, in
+Figure~\ref{fig:kimpact} and Subsection~\ref{sec:comparison}).
+Nonetheless, while in the genetic approach $K$ must be sufficiently large
+in order to guarantee the diversity of the Pareto set configurations, in
 our algorithm the diversity is not impacted by $K$ since, by
 construction, it is guaranteed by the way the configuration space is
-partitioned, independently from the number of configurations evaluated at
+partitioned, independently of the number of configurations evaluated at
 each iteration.
@@
 innovation. High values of $\alpha$ mean that a region will hardly be
-elected as high-innovation, yielding less splitting operations. This
+elected as high-innovation, producing less splitting operations. This
 slows down zooming in on portions of configuration space and makes the
-distribution of the simulated configuration more uniform, as there are
+distribution of the simulated configurations more uniform, since there are
 fewer small regions with a high test configuration concentration. The
@@
 
-With regard to the performance of the proposed approach, we observe that the
-performance of $PS$ is related to the total number of
+With regard to the performance of the proposed approach, we observe it is related to the total number of
 different configurations evaluated during the exploration. We can
@@
 different processing node, which autonomously performs all the PS
-steps, including merging and splitting, considering the assigned
+steps. When merging and splitting, each processing node consider the assigned
 macro-region as the entire parameter space. Note that, while the
@@
 provide very low innovation at a certain era. In this case, dedicating
-to it the same number $K$ of test function as the other macro-regions
+to it the same number $K$ of test functions as to the other macro-regions
 is inefficient. To solve this problem, the number of test functions
@@
 be tested again by some other PS instance. In addition, PS instances
-share the set of non-dominated configuration. Therefore, when a PS
+share the set of non-dominated configurations. Therefore, when a PS
 instance evaluates the innovation score of its regions (steps
 \ref{pers02.enu:novelty_score_of_a_configuration} and
-\ref{enu:region_innovation_score} of \secR{steps}), it considers the
+\ref{enu:region_innovation_score} of \secR{steps}), it considers also the
 solutions found by the other PS instances. In this way, the
 configuration space is spanned in parallel by multiple PS instances,
-but, although autonomous, they are not isolated; on the contrary, they
+that, although autonomous, are not isolated; on the contrary, they
 continuously exchange information and influence each other, thanks to
-sharing the already simulated configurations and the non-dominated
-one. Otherwise stated, all the PS instances (independently but
-jointly) contribute at the formation of the Pareto-set.
+the sharing of the the set of already simulated configurations and the set of non-dominated
+ones. Otherwise stated, all the PS instances (independently but
+jointly) contribute to the formation of the Pareto-set.
 

### 2015-01-26 experiments.tex
AA: rilettura fatta e colpo di aspell

@@
 embedded system design scenario,  since its properties
-are the one that suggested to the authors the concepts of Pareto-based
+are the ones that suggested to the authors the concepts of Pareto-based
 innovation and region scoring system.
 
-In particular, we will use a parametrized Very Long Instruction
+In particular, we use a parametrized Very Long Instruction
 Word (VLIW) architecture~\cite{kathail_tr00} as testbed. The philosophy
@@
 \item \emph{Multi-Objective trade-offs}: VLIW architectures allow designers
-to trade between power, energy and performances objectives, resulting
+to balance power, energy and performances objectives, resulting
 in extended Pareto sets which are an ideal ground for our testing
@@
 first two categories are directly related to the physical
-implementation of the system, so parameters of those
+implementation of the system, and thus parameters of those
 classes are usually referred as ``hardware parameters''. On the other
@@
 Processor hardware parameters are directly related to the VLIW core
-and includes the size of the register files and the number of
+and include the size of the register files and the number of
 functional units of each type. On the software side, a set of the most
 impacting code compilation parameters has been selected.
-Table~\ref{tab:param} show the complete set of parameters included in
-the design space and their possible values. The total size of design
+Table~\ref{tab:param} shows the complete set of parameters included in
+the design space and their possible values. The total size of the design
 space, which grows with the product of parameter cardinalities, is
@@
 
-As regards the class of benchmark being considered, a set applications representative of some common
+As regards the class of benchmark being considered, a set of applications representative of some common
 frequently running code kernels has been selected. Table~\ref{tab:bench} shows the set of applications
@@
 have to be retargetable. The open source project Trimaran~\cite{trimaran_hp} provides these
-tools and together with estimation framework \ee~\cite{palpatti_estimedia03} has been
+tools and, together with the estimation framework \ee~\cite{palpatti_estimedia03}, has been
 adopted as a tested and flexible platform for carrying out the
-experiments described in the previous subsection.
+experiments.
 
@@
 the \ee{} framework and the interface with the Trimaran tools. The
-input for the whole evaluation flow is the source of the application
-involved in the optimization and the configuration of the architecture
+input for the whole evaluation flow is the source file of an application
+benchmark and the configuration of the architecture
 being evaluated.  With reference to Figure~\ref{fig:evaluation_flow}
@@
 approaches (e.g.  dependency based~\cite{givargis_tvlsi02}) that make
-use of some a-priori knowledge about the role and meaning of each
+use of some a-priori knowledge about the role and the semantics of each
 parameter, since our aim is evaluate the capacity of focusing on
 interesting parameter regions without any external judgment or help
-based on heuristics.  In particular in this work when referring to
-genetic approach (or GA) we will denote the widely spread 
-\emph{SPEA}~\cite{zitzler_eurogen01} variant of the Multi-objective
+based on heuristics.  In this work, when referring to
+genetic approach (or GA), we consider the widely spread 
+\emph{SPEA2}~\cite{zitzler_eurogen01} variant of the Multi-objective
 Genetic Algorithm, remanding to
@@
 The set of default algorithm tuning parameters used for both the
-genetic and PS approaches to perform the simulations are shown in
+genetic and PS approaches is shown in
 Table~\ref{tab:defaults}. Given the similarity, both in terms of
-meaning and functionality, of the parameter $K$ with the population size
+meaning and functionality, between the parameter $K$ and the population size
 of the genetic approach, they both have been set to the same values. As discussed
@@
 different values of $K$, similar to the ones shown in
-Figure~\ref{fig:kimpact} which refers to the alloca\_test application
+Figure~\ref{fig:kimpact}, which refers to the alloca\_test application
 and a total budget of 500 configurations. We found that initially increasing values
-of $K$ seems to improve both Pareto (as in the picture on the left) and objective
-distribution (on the right), but after some threshold value the $K$ does
+of $K$ seems to improve both Pareto front (as in the picture on the left) and objective
+distribution (on the right), but, after some threshold value, $K$ does
 not seem to provide any benefit, even returning to slightly worse
-results for the last value of $K$ considered (100). Similar trends have been
+results for the last values of $K$ considered (100). Similar trends have been
 found for the other benchmarks (not included for space reasons),
@@
 \secL{metrics}
-A qualitative evaluation of Paretos is probably the simplest way for
-having a quick glance on algorithm behavior and results. However, in
-tests involving a comparison between different exploration strategies
+A qualitative evaluation of Paretos is probably the simplest way to
+have a quick glance on algorithm behavior and results. However, in
+tests involving a comparison between different exploration strategies,
 this approach could not help in capturing the whole picture, missing
@@
 \emph{average normalized absolute dispersion error}.
-Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating the quality of a Pareto front.
-Indeed, authors in \cite{zitzler_ec00,weise2012evolutionary} observe that an exploration algorithm should preferably provide Pareto fronts whose objective function range is large.
+Both of them permit to quantify the extent of the Pareto front that is an important factor to consider when evaluating its quality.
+Indeed, authors of \cite{zitzler_ec00,weise2012evolutionary} observe that an exploration algorithm should preferably provide Pareto fronts whose objective function range is large.
 In other words, following the terminology of~\cite{weise2012evolutionary}, a \emph{uniform convergence} should be guaranteed.
@@
 The second design, on the contrary, may fit situations in which the energy is provided by a battery (stringent power constraints) but only background computations are performed (long execution time is tolerable).
-These two processors may be successfully designed maintaining the same architecture, using different values for the design parameters.
+These two processors may be successfully designed maintaining the same architecture and simply using different values for the design parameters.
 A wide Pareto front helps in achieving this goal.
@@
 analysis of the results in order to more accurately figure out in which
-features/properties the two approaches can differentiate.
+features/properties the two approaches differentiate.
 
@@
 resulting Pareto fronts for two scenarios of 100 and 500
-simulations budget respectively. The set of algorithm parameters involved and their
-values are the one previously shown in Table~\ref{tab:defaults}. It
+simulation budget, respectively. The set of algorithm parameters involved and their
+values are the ones previously shown in Table~\ref{tab:defaults}. It
 should be pointed out again that the number of generations (or eras)
@@
 Low budget Pareto sets are shown in \figR{pareto_fronts_100}. Note
-that with a so small number of configuration being investigated the
+that with such a small number of configurations being investigated, the
 two sets are often overlapping, being also strongly dependent upon the
 application being considered.  These results are obtained in about 5
-eras and demonstrate that with a so limited budget PS can compete with
+eras and demonstrate that, with such a limited budget, PS can compete with
 genetic approach while even discovering very different Pareto fronts.
@@
 \figR{pareto_fronts_500}, we can qualitatively observe that even if PS
-does not strictly outperforms genetic in terms of dominance, it shows
-in some cases largely Pareto in terms of extension. We can intuitively
+does not strictly outperforms GA in terms of dominance, it shows
+in some cases larger Pareto in terms of extension. We can intuitively
 relate this to the ``novelty-based'' score system, so that instead of
-focusing on getting better points inside a given range it tries to
+focusing on getting better points inside a given range PS tries to
 enlarge the range itself, resulting in less dense but more extended
@@
 desired granularity of the results, objective range constraints or
-estimated error of the models used.
+estimated error of the adopted models.
 
-To better evaluate results from a different perspective, we will
-adopted the two quantitative metrics of variation range and average absolute
-dispersion error, which have been described and motivated
+To better evaluate results from a different perspective, we
+adopt the \emph{variation range} and the \emph{average absolute
+dispersion error}, the two quantitative metrics described and motivated
 in~\secR{metrics}. In particular, a comparison between the variation
 ranges of both power dissipation and execution time, obtained by PS
-and GA for different benchmarks is shown in \figR{dispersion}(a) and
-(b) respectively.  As it can be observed, the PS exploration provides
+and GA for different benchmarks, is shown in \figR{dispersion}(a) and~(b), respectively.  As it can be observed, the PS exploration provides
 solutions which fall on a range that is, on average, wider than the
@@
 dispersed points (i.e. higher values in the chart). These results,
-together with the variation ranges of \figR{dispersion}(a) and (b)
-confirm the of density vs. extension trade-offs when comparing PS and
+together with the variation ranges of \figR{dispersion}(a) and~(b)
+confirm the density vs. extension trade-offs when comparing PS and
 GA approaches.
 We highlight that PS shows a stronger \emph{uniform convergence} (discussed in \secR{metrics}), i.e.
-it provides a more extended Pareto front, avoiding the designer to neglect some important options, and offering a wider view of the potentiality of the designed device.
+it provides a more extended Pareto front, avoiding the designer to neglect some important options, and offering a wider view of the potentials of the designed device.
 

### 2015-01-26 introduction.tex
AA: rilettura fatta e colpo di aspell

@@
 in literature.
-Exploring the design space of embedded systems is a difficult not only because of the huge size of the parameter space, but also due to the tight \emph{dependencies} (see~\defR{dependency}) between parameters, which impact the objectives.
+Exploring the design space of embedded systems is difficult not only because of the huge size of the parameter space, but also due to the tight \emph{dependencies} between parameters, which impact the objectives.
 Due to this complexity, exploration algorithms are usually heuristic and, to a large extent, rely on simple intuitions rather then formal arguments.

### 2015-01-26 paper.tex
AA: rilettura fatta e colpo di aspell

@@
 ANDREA ARALDO
-\affil{Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France}
+\affil{Universit\'e Paris-Sud and T\'el\'ecom ParisTech}
 DAVIDE PATTI
@@
 Author's addresses: V. Catania, DIEEI University of Catania;
-A. Araldo, Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France;
+A. Araldo, Universit\'e Paris-Sud and T\'el\'ecom ParisTech;
 D. Patti, DIEEI University of Catania.
@@
 hardware/software dependencies has been analyzed to evaluate
-effectiveness with different amount of simulations budget.
+the PS effectiveness with different amounts of simulations budget.
 A qualitative/quantitative comparison against a widespread multi-objective genetic
-approach showed how the proposed strategy can result in a different
-distribution of Pareto points which trades solutions granularity with
+approach showed that the proposed strategy can result in a different
+distribution of Pareto points which balances solutions granularity and
 improved Pareto extension.

### 2015-04-22 experiments.tex
fixed caption
corretti i due typo notificati

@@
 multi-objective optimization algorithm, in this work we will
-explicitly refer to the more restricted (but still very large)
 embedded system design scenario,  since its properties
@@
 does not strictly outperforms GA in terms of dominance, it shows
-in some cases larger Pareto in terms of extension. We can intuitively
+in some cases Pareto fronts whose extension is larger. We can intuitively
 relate this to the ``novelty-based'' score system, so that instead of
@@
 enlarge the range itself, resulting in less dense but more extended
-Paretos. Of course we cannot classify this different behavior as
+Pareto fronts. Of course we cannot classify this different behavior as
 being strictly better or worse when compared to the genetic one: other
@@
   \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for
-  different benchmarks and average dispersion absolute dispersion (c). }
+  different benchmarks and average absolute dispersion errors (c). }
   \begin{center}

### 2015-04-27 experiments.tex
ACM camera ready

@@
 have to be retargetable. The open source project Trimaran~\cite{trimaran_hp} provides these
-tools and, together with the estimation framework \ee~\cite{palpatti_estimedia03}, has been
+tools and, together with the estimation framework
+\ee~\cite{Ascia2005940}, has been
 adopted as a tested and flexible platform for carrying out the
@@
 discrete level of accuracy (for a detailed description of the models
-see also~\cite{palpatti_estimedia03}).
+see also~\cite{Ascia2005940}).
 
